### 2015-11-04 Paper/paper.tex
added paper files

%\documentclass[useAMS, usenatbib,usegraphicx,letter]{mn2e}
%\documentclass[11pt]{article}
\documentclass[reprint,aps,prd,superscriptaddress,showkeys,showpacs]{revtex4-1}
\usepackage{epsfig,amsmath,natbib}

\usepackage{aas_macros}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{dsfont}
\usepackage{hyperref}
\usepackage{color}
\usepackage{pbox}
\usepackage{booktabs}

\hypersetup{
	colorlinks=false,
	citecolor=green
}
% \usepackage{graphicx}
% \usepackage{epstopdf}
% \usepackage{natbib}

%%%%%%%%%%%%%%%%%
%Custom commands%
%%%%%%%%%%%%%%%%%

\newcommand{\bb}[1]{\mathbf{#1}}
\newcommand{\bbh}[1]{\mathbf{\hat{#1}}}
\newcommand{\h}[1]{\hat{#1}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\title{Simulating cosmic variance in Weak Lensing: effects on parameter inferences}

\author{Andrea Petri}
\email{apetri@phys.columbia.edu}
\affiliation{Department of Physics, Columbia University, New York, NY 10027, USA}
\affiliation{Physics Department, Brookhaven National Laboratory, Upton, NY 11973, USA}

\author{Zolt\'an Haiman}
\affiliation{Department of Astronomy, Columbia University, New York, NY 10027, USA}

\author{Morgan May}
\affiliation{Physics Department, Brookhaven National Laboratory, Upton, NY 11973, USA}

\date{\today}

\label{firstpage}

\begin{abstract}
Constraining cosmology using Weak Gravitational Lensing consists in comparing measured features with simulated ones. An accurate estimate of the feature covariance matrix is essential to obtain accurate parameter confidence intervals. When this covariance matrix $\bb{C}$ is measured from simulations, an important question to ask is how big the simulation set should be for an accurate estimation of $\bb{C}$. We construct different mock ensembles with $N_r$ realizations of the same shear field, based on $N_s<N_r$ independent $N$--body simulations. Using the shear--shear power spectrum as a summary statistic, we find that the scaling of the forecasted error bar for $w$ shows the expected behavior with $N_r$ (see \citep{DodelsonSchneider13}). The same quantity shows a mild dependence on $N_s$ and on the effective dimensionality of the feature space.     
\end{abstract}

\keywords{Weak Gravitational Lensing --- Simulations --- Methods: numerical,statistical}
\pacs{98.80.-k, 95.36.+x, 95.30.Sf, 98.62.Sb}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%% INTRO %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}
%
Weak Gravitational lensing is a promising cosmological probe for constraining the Dark Energy equation of state $w$, and has been considered by a range of past (CFHTLens), current (DES) and future (LSST) experiments. In an era where cosmology is becoming data driven, accurate numerical simulations of shear fields are becoming important for a number of reasons including the study of baryonic effects, non--Gaussian statistics, systematics... Building cosmological predictions from simulations naturally introduces fluctuations in the forecasts, mainly due to cosmic variance. These fluctuations have been shown to have non negligible effects on estimates of features covariance matrices and hence on parameter constraints (see \citep{DodelsonSchneider13}). This work studies this issue further, focusing on the number of independent $N$--body simulations that is necessary to run for obtaining accurate estimates of parameter constraints, with particular focus on $w$. This paper is organized as follows: in the first paragraph we briefly describe the shear simulation methods we used, as well as the formalism we adopted to compute cosmological parameter constraints. We then outline our main findings and discuss the results, as well as future prospects for continuing this study.

%%%%%%%%%%%%%%%%%%% METHODS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Methods}

\subsection{Shear field simulations}
\label{shearsim}
%
In this paragraph we describe how we constructed our shear field ensembles. Background galaxies at redshift $z_s$ are lensed by large scale structure between $z=0$ and $z_s$. The shape distortions due to the cosmic shear $\pmb{\gamma}$ can be computed in terms of the dark matter gravitational potential $\Phi(\bb{x},z)$. Because the evolution of $\Phi$ in redshift is non--linear, its evolution needs to be computed with numerical simulations. We make use of the public code Gadget2 \citep{Gadget2}, with which we run a sequence of dark--matter--only $N$--body simulations that track the evolution of the density fluctuations in the large scale structure of the universe. We assume a standard $\Lambda$CDM framework with $(\Omega_m,\Omega_\Lambda,h,w,\sigma_8,ns)=(0.26,0.74,0.72,-1,0.8,0.96)$ and we fix the comoving size of the simulation box to $240\mathrm{Mpc}/h$. We fill the box with $512^3$ particles, which correspond to a mass resolution of $10^{10}M_\odot$. We assume a uniform galaxy distribution at a constant redshift $z_s=2$ (at which the simulation box has an angular size of $\theta_{box}=3.5\mathrm{deg}$) and we disctretize the mass distribution between $z_s$ and the observer at $z=0$ with a sequence of 60 two dimensional lenses of thickness $80\mathrm{Mpc}/h$. The surface density on each lens is computed by projecting the three dimensional density measured from Gadget2 snapshots. We then apply the multi--lens--plane algorithm (see \citep{RayTracingHartlap,RayTracingJain} for example) to trace the deflections of $2048^2$ light rays arranged on a square grid of total size $\theta_{box}$, from $z=0$ to $z_s$. The light deflection calculations have been performed with our implementation of multi--lens--plane algorithm, which is part of the LensTools computing package \citep{LensTools} (released under the MIT license). Different realizations $r$ of the same shear field $\pmb{\gamma}_r(\pmb{\theta})$ can be generated with different choices of the lenses that lay between the observer and $z_s$. The randomization procedure we adopt is the following:

\begin{itemize}
\item Pick a lens redshift $z_l$, and select the snapshot at $z_l$ from the $i$--th $N$--body simulation at disposal, where $i$ is a random number in $[1,N_s]$
\item Choose randomly a direction in $(\bb{n}_x,\bb{n}_y,\bb{n}_z)$: the lens plane will be pependicular to this direction
\item Choose the cutting point of the plane in the snapshot: because the lenses are $80\mathrm{Mpc}/h=240/3\mathrm{Mpc}/h$ thick, we have 3 different possibilities for choosing the random cut point
\item Perform a periodical random shift of the lens plane along its two directions
\item Repeat this procedure for each lens redshift $z_l$  
\end{itemize}  
%
This randomization procedure allows us to produce an arbitrary number $N_r$ of mock shear realizations $\pmb{\gamma}_r(\pmb{\theta})$, which however will not be all independent if $N_s$ is not large enough. Using a set of 200 independent $N$--body simulations, we construct different ensembles with different choices of $N_s\in[1,200]$, each made of 1000 mock shear realizations. From each of these mocks we reconstruct the convergence $\kappa_r(\pmb{\theta})$ and measure its angular power spectrum $P^{\kappa\kappa}_r(l)$ defined as
\begin{equation}
\langle\tilde{\kappa}_r(\bb{l})\tilde{\kappa}_r(\bb{l}')\rangle = (2\pi)^2\delta_D(\bb{l}+\bb{l}')P^{\kappa\kappa}_r(l)
\end{equation}
%
The fact that the ensemble of $N_r$ mocks is not completely independent if $N_s$ is not large enough can have an effect on the covariance estimator of $P^{\kappa\kappa}$.

\subsection{Parameter inference}
%
Let $\bbh{d}$ be the measured feature of dimension $N_b$, $\bb{d}(\bb{p})$ be the simulated feature at a point $\bb{p}$ in parameter space and $\bb{C}$ be the $N_b\times N_b$ feature covariance matrix. For the purpose of this work $\bb{p}$ is the triplet $(\Omega_m,w,\sigma_8)$ and $\bb{d}$ is the convergence power spectrum $P^{\kappa\kappa}$, which is measured at $N_b=15$ log--spaced bands between $l\in[100,6000]$. While $d_M(\bb{p})$ can usually be predicted reasonably accurately by already existing emulators (see \citep{coyote2,Nicaea} for example), the matter is more complicated for covariance matrices. Measuring $\bb{C}$ from simulations involves generating a series of mock realizations $\bbh{d}_r$ with $r=1...N_r$ and estimating the sample covariance $\bbh{C}$

\begin{equation}
\bb{\bar{d}} = \frac{1}{N_r}\sum_{r=1}^{N_r} \bbh{d}_r
\end{equation}

\begin{equation}
\label{covest}
\bbh{C} = \frac{1}{N_r-1}\sum_{r=1}^{N_r} (\bbh{d}_r - \bar{\bb{d}}) (\bbh{d}_r - \bar{\bb{d}})^T
\end{equation}
%
Assuming a normal feature likelihood, together with a flat prior on the parameter space, the parameter posterior distribution $\mathcal{L}(\bb{p}\vert\bbh{d})$ can be obtained using Bayes theorem
\begin{equation}
\label{posteriorbayes}
\mathcal{L}(\bb{p}\vert\bbh{d}) = \mathcal{N}_\mathcal{L}\exp{\left[-\frac{1}{2}(\bbh{d}-\bb{d}(\bb{p}))^T\bb{C}^{-1}(\bbh{d}-\bb{d}(\bb{p}))\right]}
\end{equation}
%
For the sake of simplicity, we approximate the posterior as a Gaussian around its maximum. This is easily done approximating the simulated feature at first order around a point $\bb{p}_0$ (that ideally is the maximum of (\ref{posteriorbayes}))
\begin{equation}
\bb{d}(\bb{p}) \approx \bb{d}_0 + \bb{d}_0^\prime(\bb{p}-\bb{p}_0) 
\end{equation}
%
From which we can build the estimators for the parameters expectation value $\bbh{p}$ and covariance $\h{\Sigma}_\bb{p}$, given the observation $\bbh{d}$, as follows:
%
\begin{equation}
\label{estimatormean}
\bbh{p} = \bb{p}_0 + \bbh{T}(\bbh{d}-\bb{d}_0)
\end{equation}

\begin{equation}
\label{estimatorcovariance}
\h{\Sigma}_\bb{p} = \bbh{T}(\bbh{d}-\bb{d}_0)(\bbh{d}-\bb{d}_0)^T\bbh{T}^T
\end{equation}

\begin{equation}
\bbh{T} = (\bb{d}_0'^T\bbh{C}^{-1}\bb{d}_0')^{-1}\bb{d}_0'^T\bbh{C}^{-1}
\end{equation}
%
Where, for simplicity we assumed $\langle\bbh{d}\rangle=\bb{d}_0$, so that $\langle(\bbh{d}-\bb{d}_0)(\bbh{d}-\bb{d}_0)^T\rangle=\bb{C}$. Since the feature we consider is the shear-shear power spectrum, its derivatives $\bb{d}_0'$ with respect to the cosmological parameters can be evaluated by existing analytical codes. For this purpose we use the analytical code NICAEA (see \citep{Nicaea}). The noise in the covariance estimator (\ref{covest}) propagates all the way to the posterior (\ref{posteriorbayes}), the parameter estimate (\ref{estimatormean}) and its variance (\ref{estimatorcovariance}). \citep{DodelsonSchneider13} found that the variance $\h{\sigma}^2_\bb{p}=\mathrm{diag}(\bbh{\Sigma}_\bb{p})$ of each parameter $p$ that is estimated from (\ref{estimatorcovariance}) increases on average with $1/N_r$
\begin{equation}
\label{dodelsonscaling}
\langle\h{\sigma}_\bb{p}^2\rangle = \sigma_p^2\left(1+\frac{D}{N_r}\right)
\end{equation} 
%
where $\sigma^2_p$ is the true parameter variance and $D$ is what we call \textit{effective dimensionality} of the feature space. \citep{DodelsonSchneider13} found $D=N_b$ when every entry in the covariance matrix is subject to noise. In this work we argue that the feature ensemble from which the covariance estimator $\bbh{C}^{-1}$ is measured depends not only on the number of shear mock realizations $N_r$, but in principle also on the number of independent $N$--body simulations $N_s$, on which the randomization procedure we describe in \S~\ref{shearsim}. We propose a modification to the scaling relation (\ref{dodelsonscaling}) that takes the varying $N_s$ into account.

\begin{equation}
\label{ourscaling}
\langle\h{\sigma}_p^2\rangle = \sigma^2_p(N_s,D)\left(1+\frac{D}{N_r}\right)
\end{equation} 
%
The reason for this can be found in that, if $N_s$ is not big enough, the different shear realizations cannot be all independent, and hence the true variance $\sigma^2_p$ cannot be recovered in the limit $N_r\rightarrow\infty$. In particular there could be some residual error in the expectation value of (\ref{estimatorcovariance}) even if $N_r$ is big. In the next paragraph we outline our main findings.

%%%%%%%%%%%%%%%%%%% RESULTS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Results}

\begin{figure*}
\includegraphics[scale=0.4]{Figures/ps_pdf.eps}
\caption{PDF of the $\kappa$ power spectrum,$\mathcal{L}(P_l^{\kappa\kappa})$, at four selected multipoles $l=115,344,1349,5283$, for different shear ensembles constructed with $N_s=$1 (black), 2 (blue), 5 (green), 50 (red), 100 (purple).}
\label{ps_pdf}
\end{figure*}

\begin{figure}
\includegraphics[scale=0.3]{Figures/ps_variance.eps}
\caption{Variance of the $\kappa$ power spectrum as a function of the multipole $l$, in units of the expected gaussian variance from equation (\ref{gaussianvar}). The variance is measured from different shear ensembles with $N_s=$1 (black), 2 (blue), 5 (green), 10 (red), 50 (purple), 100 (orange). }
\label{ps_var}
\end{figure}

\begin{figure}
\includegraphics[scale=0.3]{Figures/scaling_nr.eps}
\caption{Expectation value of the variance on $w$, $\langle\h{\sigma}^2_w\rangle$, as a function of the number of mock realizations $N_r$ used in the feature covariance estimator (\ref{covest}). Results for different mock ensembles generated with $N_s=$1 (black), 2 (blue), 5 (green), 50 (red), 100 (purple) are shown. The figure shows both the measured trends (solid lines) and their best fits according to equation (\ref{dodelsonscaling}). }
\label{wvar_nr}
\end{figure}

\begin{table}
\begin{center}
\begin{tabular}{r|rr}
\toprule
 $N_s$ &  $D$(diagonal) &  $D$(full) \\ \hline
\midrule
    1 &   2.8 &  12.3 \\
    2 &   2.1 &  14.4 \\
    5 &   2.6 &  16.4 \\
   10 &   3.1 &  14.6 \\
   20 &   2.4 &  15.8 \\
   30 &   2.5 &  15.4 \\
   40 &   2.7 &  15.7 \\
   50 &   2.5 &  13.6 \\
   60 &   2.7 &  13.3 \\
   70 &   2.4 &  15.0 \\
   80 &   2.4 &  15.6 \\
   90 &   2.6 &  14.1 \\
  100 &   2.2 &  14.1 \\
  150 &   2.3 &  13.9 \\
  200 &   2.6 &  18.2 \\
\bottomrule
\end{tabular}
\end{center}
\caption{Effective dimensionality of the power spectrum feature space $D$ computed fitting the measured $w$ variance with the scaling relation (\ref{dodelsonscaling}). We show both cases in which we consider the full covariance matrix and the case in which we artificially zero out all the off diagonal elements.}
\label{dimtable}
\end{table}

\begin{figure}
\includegraphics[scale=0.3]{Figures/scaling_ns.eps}
\caption{Expectation value of the variance on $w$, $\langle\h{\sigma}^2_w\rangle$, varying the mock ensemble used to compute the covariance estimator (\ref{covest}). We factored out the $(1/D/N_r)$ dependence, showing only the dependence of $\sigma_0^2$ on $D$. Different choices of $N_r=$100 (black), 300 (blue), 500 (green), 700 (red), 900 (purple) are shown for comparison.}
\label{wvar_ns}
\end{figure}

In this section we outline the main results of this work. We show the qualitative behavior of the $P^{\kappa\kappa}$ probability distribution function (PDF) in ensembles built with different $N_s$. We also show how the forecasts on the Dark Energy equation of state, $w$, depend on $N_s$ and $N_r$. Figure \ref{ps_pdf} shows the power spectrum PDF at four selected multipoles, while Figure \ref{ps_var} shows the variance in each multipole. This result is compared to the one that we would obtain assuming that the convergence is a Gaussian random field
\begin{equation}
\label{gaussianvar}
\mathrm{Var}(P^{\kappa\kappa}(l)) = \frac{P^{\kappa\kappa,2}(l)}{N(l)}
\end{equation}
%
where $N(l)$ is the number of modes used to estimate the power spectrum at $l$, which depends on the mock size $\theta_{box}$ and on the width of the $N_b$ multipole bands. Figure \ref{wvar_nr} and Table \ref{dimtable} show the scaling of the expectation value of $\h{\sigma}_w^2$ with the number of mocks $N_r$ and compare it with the known result obtained in \citep{DodelsonSchneider13}. Figure \ref{wvar_ns} shows the effect of varying $N_s$ on the $w$ constraint. The expectation values $\h{\sigma}^2_w$ (equations (\ref{estimatorcovariance}),(\ref{ourscaling})) have been computed averaging over 100 independent resamples of the $P^{\kappa\kappa}$ ensembles. For the true feature covariance matrix $\langle(\bbh{d}-\bb{d}_0)(\bbh{d}-\bb{d}_0)^T\rangle=\bb{C}$ we use the estimated covariance from the $N_s=200$ ensemble.

%%%%%%%%%%%%%%%%%% DISCUSSION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Discussion}

%%%%%%%%%%%%%%%%%% CONCLUSION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Conclusion}

%%%%%%%%%%%%%%%%%%%%%%%%%% ACKNOWLEDGMENTS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Acknowledgements}

\bibliography{ref}
\label{lastpage}
\end{document}

### 2015-11-04 Paper/Figures/generate.py

@@ -1,0 +1,167 @@
+#!/usr/bin/env python
+
+import argparse
+
+import numpy as np
+import matplotlib.pyplot as plt
+
+from lenstools.statistics.ensemble import Ensemble
+from lenstools.statistics.database import Database
+
+import variance_scaling
+
+#Options
+parser = argparse.ArgumentParser()
+parser.add_argument("-t","--type",dest="type",default="png",help="format of the figure to save")
+parser.add_argument("fig",nargs="*")
+
+#Power spectrum variance
+def ps_variance(cmd_args,nsim=[1,2,5,10,50,100],colors=["black","blue","green","red","purple","orange"],fontsize=18):
+
+	assert len(colors)>=len(nsim)
+
+	#Multipoles and number of modes
+	ell = np.load("features/ell.npy")
+	num_ell = np.load("features/num_ell.npy")
+
+	#Plot
+	fig,ax = plt.subplots()
+	for nc,ns in enumerate(nsim):
+
+		#Load the relevant ensemble,compute mean and variance
+		ens = Ensemble(np.load("features/Maps{0}/power_spectrum_s0.npy".format(ns))).head(1000)
+		p = ens.mean().values
+		pcov = ens.cov().values.diagonal()
+
+		#Scale the covariance to the number of modes
+		pcov = num_ell*pcov/(p**2)
+
+		#Plot
+		ax.plot(ell,pcov,color=colors[nc],label=r"$N_s={0}$".format(ns))
+
+	#Labels
+	ax.set_xlabel(r"$l$",fontsize=fontsize)
+	ax.set_ylabel(r"$\mathrm{Var}(P^{\kappa\kappa}_l)\times N_l/P^{\kappa\kappa,2}_l$",fontsize=fontsize)
+	ax.legend(loc="upper left")
+
+	#Save
+	fig.savefig("ps_variance."+cmd_args.type)
+
+#Power spectrum pdf
+def ps_pdf(cmd_args,nell=[0,4,9,14],nsim=[1,2,5,50,100],colors=["black","blue","green","red","purple"],fontsize=18):
+
+	assert len(colors)>=len(nsim)
+	assert len(nell)==4
+
+	#Multipoles and number of modes
+	ell = np.load("features/ell.npy")
+
+	#Plot
+	fig,ax = plt.subplots(2,2,figsize=(16,12))
+	for nc,ns in enumerate(nsim):
+
[…]

### 2015-11-05 Paper/paper.tex
finished first draft

@@
 %
-Weak Gravitational lensing is a promising cosmological probe for constraining the Dark Energy equation of state $w$, and has been considered by a range of past (CFHTLens), current (DES) and future (LSST) experiments.
-In an era where cosmology is becoming data driven, accurate numerical simulations of shear fields are becoming important for a number of reasons including the study of baryonic effects, non--Gaussian statistics, systematics...
+Weak Gravitational lensing is a promising cosmological probe for constraining the Dark Energy equation of state $w$, and has been considered by a range of past (CFHTLens \citep{cfht1,cfht2}), current (DES \citep{DES}) and future (LSST \citep{LSST}) experiments.
+In an era where cosmology is becoming data driven, accurate numerical simulations of shear fields are becoming important for a number of reasons including the study of baryonic effects \citep{BaryonXiuyuan}, non--Gaussian statistics \citep{PeaksJan,MinkJan,MinkPetri} and various systematics.
 Building cosmological predictions from simulations naturally introduces fluctuations in the forecasts, mainly due to cosmic variance.
@@
 We make use of the public code Gadget2 \citep{Gadget2}, with which we run a sequence of dark--matter--only $N$--body simulations that track the evolution of the density fluctuations in the large scale structure of the universe.
-We assume a standard $\Lambda$CDM framework with $(\Omega_m,\Omega_\Lambda,h,w,\sigma_8,ns)=(0.26,0.74,0.72,-1,0.8,0.96)$ and we fix the comoving size of the simulation box to $240\mathrm{Mpc}/h$.
+We assume a standard $\Lambda$CDM framework with $(\Omega_m,\Omega_\Lambda,h,w,\sigma_8,n_s)=(0.26,0.74,0.72,-1,0.8,0.96)$ and we fix the comoving size of the simulation box to $240\mathrm{Mpc}/h$.
 We fill the box with $512^3$ particles, which correspond to a mass resolution of $10^{10}M_\odot$.
@@
 For this purpose we use the analytical code NICAEA (see \citep{Nicaea}).
-The noise in the covariance estimator (\ref{covest}) propagates all the way to the posterior (\ref{posteriorbayes}), the parameter estimate (\ref{estimatormean}) and its variance (\ref{estimatorcovariance}).
+The noise in the covariance estimator (\ref{covest}) propagates all the way to the posterior (\ref{posteriorbayes}), the parameter estimate (\ref{estimatormean}) and its variance (\ref{estimatorcovariance}), through the transformation matrix $\bbh{T}$.
 \citep{DodelsonSchneider13} found that the variance $\h{\sigma}^2_\bb{p}=\mathrm{diag}(\bbh{\Sigma}_\bb{p})$ of each parameter $p$ that is estimated from (\ref{estimatorcovariance}) increases on average with $1/N_r$
@@
 
+In this section we discuss our main findings.
+Figure \ref{ps_pdf} shows that, although different choices of $N_s$ do not seem to affect the power spectrum PDF at large scales (top two panels), there are some qualitative differences on small scales (bottom two panels), on which a shear ensemble built with a small $N_s$ might not have the same statistical behavior of ensembles built with large $N_s$.
+Figure \ref{ps_var} shows the variance of convergence power spectrum computed from different ensembles, in units of the Gaussian expectation.
+We find that, even with $N_s=1$, our results are in good agreement with the ones obtained by \citep{Sato12}, which used $N_s=400$.
+This fact by itself is not sufficient to conclude that $N_s$ does not have an effect on parameter inferences, since these depend on the cross band covariances.
+
+In Figure \ref{wvar_nr} we examine how the $w$ constraint depends on the number of mocks used to estimate the covariance, and we find good agreement with \citep{DodelsonSchneider13}.
+We determine the effective dimensionality of the feature space, $D$, with a linear regression using equation (\ref{ourscaling}) and we find that this depends strongly on how the noise is distributed across the covariance matrix estimator $\bbh{C}$.
+In particular we find that when every element in the covariance is subject to noise $D$ is close to the number of bands used $N_b=15$, but when we artificially zero out the off diagonal elements of $\bbh{C}$, the effective dimensionality drops to $D\approx2.5$.
+Finally, Figure \ref{wvar_ns} shows the dependence of the dark energy constraint with $N_s$ and $D$.
+We find that, in the range $N_s\in[1,200]$ the $w$ inferred variance has sub--percent fluctuations for both the diagonal and full $\bbh{C}$ cases, while there is a $\sim$10\% change in $\sigma^2_0(N_s,w)$ when the effective dimensionality $D$ is different.
+Finally, the different lines in Figure \ref{wvar_ns} show that equation (\ref{ourscaling}) is a good model for the variance scaling.
+
 %%%%%%%%%%%%%%%%%% CONCLUSION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \section{Conclusion}
+
+In this work we examine the effect of $N$--body simulations based shear ensembles on forecasted cosmological constraints. Our main results can be summarized as follows:
+
+\begin{itemize}
+\item The variance scaling relation proposed by \citep{DodelsonSchneider13} is a good approximation regardless of $N_s$
+\item The fluctuations in the $w$ forecasted variance due to varying $N_s$ are sub--percent, and this effect is sub--dominant with respect of varying the effective dimensionality of the feature space, which in the end is controlled by how the noise is distributed in the covariance estimator
+\end{itemize}
+%
+Future prospects of this work involve extending this analysis to more general feature spaces, such as the ones that characterize non--Gaussian statistics such as shear peaks and higher moments of $\kappa$ fields.
+In order to scale these considerations to future surveys such as LSST, it is necessary to see if our findinds hold when challenged by larger and higher resolutions $N$--body simulations.
 

### 2015-11-16 code/measure/powerSpectrum.py
adapted to API change

@@ -12,7 +12,6 @@ from lenstools.utils import MPIWhirlPool
 from lenstools.simulations.logs import logdriver
 
 from lenstools import ConvergenceMap
-from lenstools import Ensemble
 
 from lenstools.simulations.raytracing import RayTracer
 from lenstools.pipeline.simulation import SimulationBatch
@@ -179,7 +178,7 @@ def singleRedshift(pool,batch,settings,id,**kwargs):
 	begin = time.time()
 
 	#Allocate space for the power spectrum Ensemble
-	ps_ensemble = Ensemble.fromdata(np.zeros((realizations_per_task,settings.l_edges.shape[0]-1)))
+	ps_ensemble = np.zeros((realizations_per_task,settings.l_edges.shape[0]-1))
 
 	#We need one of these for cycles for each map random realization
 	for rloc,r in enumerate(range(first_map_realization,last_map_realization)):
@@ -280,7 +279,7 @@ def singleRedshift(pool,batch,settings,id,**kwargs):
 				np.save(savename,ell)
 
 			#Add the measured power spectrum to the Ensemble
-			ps_ensemble.data[rloc] = P_ell
+			ps_ensemble[rloc] = P_ell
 
 		else:
 			logdriver.error("You need to enable the 'convergence' option!")
@@ -302,7 +301,7 @@ def singleRedshift(pool,batch,settings,id,**kwargs):
 		savename = os.path.join(map_batch.home_subdir,"{0}.npy".format(settings.ensemble_root))
 
 	logdriver.info("Saving power spectrum Ensemble to {0}".format(savename))
-	ps_ensemble.save(savename)
+	np.save(savename,ps_ensemble)
 
 	if (pool is None) or (pool.is_master()):	
 		now = time.time()

### 2015-11-17 code/analysis/algorithms.py
added peak variance scaling script

@@ -1,0 +1,53 @@
+from lenstools.statistics.ensemble import Series,Ensemble
+from scipy.stats import linregress
+
+###############################
+###Bootstrap fisher ellipses###
+###############################
+
+def bootstrap_fisher(ensemble,fisher,true_covariance,extra_items):
+	
+	pcov = fisher.parameter_covariance(ensemble.cov(),observed_features_covariance=true_covariance)
+	pvar = Series(pcov.values.diagonal(),index=pcov.index)
+	for key in extra_items.keys():
+		pvar[key] = extra_items[key]
+	
+	return pvar.to_frame().T
+
+def bootstrap_fisher_diagonal(ensemble,fisher,true_covariance,extra_items):
+
+	cov = Ensemble(np.diag(ensemble.var().values),index=true_covariance.index,columns=true_covariance.columns)
+	pcov = fisher.parameter_covariance(cov,observed_features_covariance=true_covariance)
+	pvar = Series(pcov.values.diagonal(),index=pcov.index)
+	for key in extra_items.keys():
+		pvar[key] = extra_items[key]
+	
+	return pvar.to_frame().T
+
+##########################################
+###Fit for the effective number of bins###
+##########################################
+
+def fit_nbins(variance_ensemble,parameter="w"):
+
+	vmean = variance_ensemble
+
+	#Compute variance expectation values
+	vmean["1/nreal"] = vmean.eval("1.0/nreal")
+
+	#Linear regression of the variance vs 1/nreal
+	fit_results = dict()
+	fit_results["nb"] = list()
+	fit_results["s0"] = list()
+	fit_results["nsim"] = list()
+
+	groupnsim = vmean.groupby("nsim")
+	for g in groupnsim.groups:
+		fit_results["nsim"].append(int(g))
+		vmean_group = groupnsim.get_group(g)
+		a,b,r_value,p_value,err = linregress(vmean_group["1/nreal"].values,vmean_group[parameter].values)
+		fit_results["nb"].append(a/b)
+		fit_results["s0"].append(b)
+
+	#Return to user
+	return Ensemble.from_dict(fit_results)

### 2015-11-17 code/analysis/variance_scaling.py

@@ -1,110 +1,0 @@
-#!/usr/bin/env python
-from __future__ import division
-
-from lenstools.statistics.database import Database
-from lenstools.statistics.ensemble import Series,Ensemble
-from lenstools.statistics.constraints import Emulator
-
-import numpy as np
-from scipy.stats import linregress
-
-###############################
-###Bootstrap fisher ellipses###
-###############################
-
-def bootstrap_fisher(ensemble,fisher,true_covariance,extra_items):
-	
-	pcov = fisher.parameter_covariance(ensemble.cov(),observed_features_covariance=true_covariance)
-	pvar = Series(pcov.values.diagonal(),index=pcov.index)
-	for key in extra_items.keys():
-		pvar[key] = extra_items[key]
-	
-	return pvar.to_frame().T
-
-def bootstrap_fisher_diagonal(ensemble,fisher,true_covariance,extra_items):
-
-	cov = Ensemble(np.diag(ensemble.var().values),index=true_covariance.index,columns=true_covariance.columns)
-	pcov = fisher.parameter_covariance(cov,observed_features_covariance=true_covariance)
-	pvar = Series(pcov.values.diagonal(),index=pcov.index)
-	for key in extra_items.keys():
-		pvar[key] = extra_items[key]
-	
-	return pvar.to_frame().T
-
-##########################################
-###Fit for the effective number of bins###
-##########################################
-
-def fit_nbins(variance_ensemble,parameter="w"):
-
-	vmean = variance_ensemble
-
-	#Compute variance expectation values
-	vmean["1/nreal"] = vmean.eval("1.0/nreal")
-
-	#Linear regression of the variance vs 1/nreal
-	fit_results = dict()
-	fit_results["nb"] = list()
-	fit_results["s0"] = list()
-	fit_results["nsim"] = list()
-
-	groupnsim = vmean.groupby("nsim")
-	for g in groupnsim.groups:
-		fit_results["nsim"].append(int(g))
-		vmean_group = groupnsim.get_group(g)
-		a,b,r_value,p_value,err = linregress(vmean_group["1/nreal"].values,vmean_group[parameter].values)
-		fit_results["nb"].append(a/b)
-		fit_results["s0"].append(b)
-
-	#Return to user
-	return Ensemble.from_dict(fit_results)
-
-
-###########################
-######Main execution#######
-###########################
-
-def main():
-
-	#Number of simulations to test
[…]

### 2015-11-17 code/analysis/variance_scaling_peaks.py

@@ -1,0 +1,46 @@
+#!/usr/bin/env python
+from __future__ import division
+
+from lenstools.statistics.database import Database
+from lenstools.statistics.ensemble import Series,Ensemble
+from lenstools.statistics.constraints import FisherAnalysis
+
+import numpy as np
+
+import algorithms
+
+###########################
+######Main execution#######
+###########################
+
+def main():
+
+	#Number of simulations to test
+	nsim = [1,2,5,10,20,30,40,50,60,70,80,90,100,150,200]
+	nreal = np.arange(100,1100,100)
+	resample = 100
+
+	#Load the fisher analysis
+	fisher = FisherAnalysis.read("../../data/fisher_peaks.pkl")
+	feature_columns = fisher[fisher.feature_names].columns
+
+	#Load in the feature Ensemble, and bootstrap the covariance using a different number of realizations
+	with Database("../../data/variance_scaling_expected_peaks.sqlite") as db:
+
+		#This is the reference covariance matrix
+		true_covariance_ensemble = Ensemble(np.load("../../Om0.260_Ol0.740_w-1.000_ns0.960_si0.800/512b240/Maps200/peaks_s0.npy"),columns=feature_columns).cov()
+		diagonal_covariance = Ensemble(np.diag(true_covariance.values.diagonal()),index=true_covariance.index,columns=true_covariance.columns)
+
+		for n in nsim:
+		
+			#Load the power spectrum Ensemble from the relevant map set
+			ensemble_nsim = Ensemble(np.load("../../Om0.260_Ol0.740_w-1.000_ns0.960_si0.800/512b240/Maps{0}/peaks_s0.npy".format(n)),columns=feature_columns)
+
+			#Bootstrap ensemble_sim and compute the parameter variance for each resample
+			for nr in nreal:
+				print("[+] Bootstraping peak constraints, nsim={0}, nreal={1} with {2} resamples".format(n,nr,resample))
+				variance_ensemble = ensemble_nsim.bootstrap(algorithms.bootstrap_fisher,bootstrap_size=nr,resample=resample,assemble=lambda l:Ensemble.concat(l,ignore_index=True),fisher=fisher,true_covariance=true_covariance,extra_items={"nsim":n,"nreal":nr})
+				db.insert(Ensemble(variance_ensemble.mean()).T,table_name="variance")
+
+if __name__=="__main__":
+	main()

### 2015-11-17 code/analysis/variance_scaling_power.py

@@ -1,0 +1,63 @@
+#!/usr/bin/env python
+from __future__ import division
+
+from lenstools.statistics.database import Database
+from lenstools.statistics.ensemble import Series,Ensemble
+from lenstools.statistics.constraints import Emulator
+
+import numpy as np
+
+import algorithms
+
+###########################
+######Main execution#######
+###########################
+
+def main():
+
+	#Number of simulations to test
+	nsim = [1,2,5,10,20,30,40,50,60,70,80,90,100,150,200]
+	nreal = np.arange(100,1100,100)
+	resample = 100
+
+	#Load the emulator
+	emulator = Emulator.read("../../data/emulators/emulator_power_fine.pkl")
+	feature_columns = emulator[emulator.feature_names].columns
+
+	#Large and small scales
+	scales = {
+	"large" : filter(lambda s:int(s.strip("l"))<=7,emulator[emulator.feature_names[0]].columns),
+	"small" : filter(lambda s:int(s.strip("l"))>7,emulator[emulator.feature_names[0]].columns), 
+	}
+
+	#Fiducial cosmology
+	fiducial_parameters = Series(np.array([0.26,-1.0,0.8]),index=["Om","w","sigma8"])
+
+	#Load in the feature Ensemble, and bootstrap the covariance using a different number of realizations
+	with Database("../../data/variance_scaling_expected.sqlite") as db:
+	
+		for s in scales:
+
+			#This is the reference covariance matrix
+			true_covariance_ensemble = Ensemble(np.load("../../Om0.260_Ol0.740_w-1.000_ns0.960_si0.800/512b240/Maps200/power_spectrum_s0.npy"),columns=emulator[emulator.feature_names[0]].columns)[scales[s]]
+			true_covariance = true_covariance_ensemble.cov()
+			diagonal_covariance = Ensemble(np.diag(true_covariance.values.diagonal()),index=true_covariance.index,columns=true_covariance.columns)
+
+			for n in nsim:
+		
+				#Load the power spectrum Ensemble from the relevant map set
+				ensemble_nsim = Ensemble(np.load("../../Om0.260_Ol0.740_w-1.000_ns0.960_si0.800/512b240/Maps{0}/power_spectrum_s0.npy".format(n)),columns=emulator[emulator.feature_names[0]].columns)[scales[s]]
+				ensemble_nsim.add_name("power_spectrum")
+
+				#Approximate the emulator linearly around the fiducial model
[…]

### 2015-11-17 code/analysis/algorithms.py
first implementation of area scaling method

@@ -1,4 +1,6 @@
 from lenstools.statistics.ensemble import Series,Ensemble
+from lenstools.statistics.contours import ContourPlot
+
 from scipy.stats import linregress
 
 ###############################
@@ -22,6 +24,24 @@ def bootstrap_fisher_diagonal(ensemble,fisher,true_covariance,extra_items):
 	for key in extra_items.keys():
 		pvar[key] = extra_items[key]
 	
+	return pvar.to_frame().T
+
+###############################
+###Bootstrap full likelihood###
+###############################
+
+def bootstrap_area(ensemble,emulator,parameter_grid,test_data,extra_items,pool):
+
+	scores = emulator.score(parameter_grid,test_data,features_covariance=ensemble.cov(),pool=pool)
+	scores["likelihood"] = scores.eval("exp(-0.5*{0})".format(emulator.feature_names[0]))
+	contour = ContourPlot.from_scores(scores,parameters=["Om","sigma8"],feature_names="likelihood")
+	contour.getLikelihoodValues([0.684],precision=0.01)
+	area = contour.confidenceArea()
+
+	parea = Series([area.keys[0],area.values[0]],index=["p_value","area"])
+	for key in extra_items:
+		parea[key] = extra_items[key]
+
 	return pvar.to_frame().T
 
 ##########################################

### 2015-11-17 code/analysis/area_scaling_power.py

@@ -1,0 +1,72 @@
+#!/usr/bin/env python
+from __future__ import division
+
+from lenstools.statistics.database import Database
+from lenstools.statistics.ensemble import Series,Ensemble
+from lenstools.statistics.constraints import Emulator
+
+import numpy as np
+import pandas as pd
+
+import algorithms
+
+###########################
+######Main execution#######
+###########################
+
+def main():
+
+	#Number of simulations to test
+	nsim = [1,2,5,10,20,30,40,50,60,70,80,90,100,150,200]
+	nreal = np.arange(100,1100,100)
+	resample = 100
+
+	#Load the emulator and the test data
+	emulator = Emulator.read("../../data/test/test_emulator.pkl")
+	feature_columns = emulator[emulator.feature_names].columns
+	test_data = pd.read_pickle("../data/test/test_power.pkl")
+
+	#Test data
+	fiducial_parameters = Series(np.array([0.26,-1.0,0.8]),index=["Om","w","sigma8"])
+
+	#Parameters on which to comute the scores
+	parameter_grid = Ensemble.meshgrid({'Om':np.linspace(0.15,0.5,100),'sigma8':np.linspace(0.5,1.0,100)})
+	parameter_grid["w"] = -1.
+
+	#Large and small scales
+	scales = {
+	"all" : emulator[emulator.feature_names[0]].columns, 
+	}
+
+	#Load in the feature Ensemble, and bootstrap the covariance using a different number of realizations
+	with Database("../../data/area_scaling.sqlite") as db:
+	
+		for s in scales:
+
+			#Downsize emulator and test data
+			emulator_scale = emulator.features({"power_spectrum":scales[s]})
+			test_data_scale = test_data[ [("power_spectrum",ell) for ell in scales[s]] ] 
+
+			#Approximate the emulator linearly around the fiducial model
+			fisher = emulator_scale.approximate_linear(fiducial_parameters,derivative_precision=0.01)
+
+			#This is the reference covariance matrix
+			true_covariance_ensemble = Ensemble(np.load("../../Om0.260_Ol0.740_w-1.000_ns0.960_si0.800/512b240/Maps200/power_spectrum_s0.npy"),columns=emulator[emulator.feature_names[0]].columns)[scales[s]]
+			true_covariance = true_covariance_ensemble.cov()
[…]

### 2015-11-17 code/analysis/algorithms.py
debug

@@ -30,19 +30,19 @@ def bootstrap_fisher_diagonal(ensemble,fisher,true_covariance,extra_items):
 ###Bootstrap full likelihood###
 ###############################
 
-def bootstrap_area(ensemble,emulator,parameter_grid,test_data,extra_items,pool):
+def bootstrap_area(ensemble,emulator,parameter_grid,fisher,true_covariance,test_data,extra_items,grid_mpi_pool):
 
-	scores = emulator.score(parameter_grid,test_data,features_covariance=ensemble.cov(),pool=pool)
+	scores = emulator.score(parameter_grid,test_data,features_covariance=ensemble.cov(),pool=grid_mpi_pool)
 	scores["likelihood"] = scores.eval("exp(-0.5*{0})".format(emulator.feature_names[0]))
 	contour = ContourPlot.from_scores(scores,parameters=["Om","sigma8"],feature_names="likelihood")
 	contour.getLikelihoodValues([0.684],precision=0.01)
 	area = contour.confidenceArea()
 
-	parea = Series([area.keys[0],area.values[0]],index=["p_value","area"])
+	parea = Series([area.keys()[0],area.values()[0]],index=["p_value","area"])
 	for key in extra_items:
 		parea[key] = extra_items[key]
 
-	return pvar.to_frame().T
+	return parea.to_frame().T
 
 ##########################################
 ###Fit for the effective number of bins###

### 2015-11-17 code/analysis/area_scaling_power.py

@@ -1,6 +1,10 @@
 #!/usr/bin/env python
 from __future__ import division
 
+import sys
+sys.modules["mpi4py"] = None
+sys.modules["matplotlib"] = None
+
 from lenstools.statistics.database import Database
 from lenstools.statistics.ensemble import Series,Ensemble
 from lenstools.statistics.constraints import Emulator
@@ -17,14 +21,18 @@ import algorithms
 def main():
 
 	#Number of simulations to test
-	nsim = [1,2,5,10,20,30,40,50,60,70,80,90,100,150,200]
-	nreal = np.arange(100,1100,100)
+	#nsim = [1,2,5,10,20,30,40,50,60,70,80,90,100,150,200]
+	#nreal = np.arange(100,1100,100)
+
+	nsim = [2]
+	nreal = [300]
+
 	resample = 100
 
 	#Load the emulator and the test data
 	emulator = Emulator.read("../../data/test/test_emulator.pkl")
 	feature_columns = emulator[emulator.feature_names].columns
-	test_data = pd.read_pickle("../data/test/test_power.pkl")
+	test_data = pd.read_pickle("../../data/test/test_power.pkl")
 
 	#Test data
 	fiducial_parameters = Series(np.array([0.26,-1.0,0.8]),index=["Om","w","sigma8"])
@@ -39,7 +47,7 @@ def main():
 	}
 
 	#Load in the feature Ensemble, and bootstrap the covariance using a different number of realizations
-	with Database("../../data/area_scaling.sqlite") as db:
+	with Database("../../data/area_scaling_power.sqlite") as db:
 	
 		for s in scales:
 
@@ -48,7 +56,7 @@ def main():
 			test_data_scale = test_data[ [("power_spectrum",ell) for ell in scales[s]] ] 
 
 			#Approximate the emulator linearly around the fiducial model
-			fisher = emulator_scale.approximate_linear(fiducial_parameters,derivative_precision=0.01)
+			fisher_scale = emulator_scale.approximate_linear(fiducial_parameters,derivative_precision=0.01)
 
 			#This is the reference covariance matrix
 			true_covariance_ensemble = Ensemble(np.load("../../Om0.260_Ol0.740_w-1.000_ns0.960_si0.800/512b240/Maps200/power_spectrum_s0.npy"),columns=emulator[emulator.feature_names[0]].columns)[scales[s]]
@@ -64,7 +72,7 @@ def main():
[…]

### 2015-11-18 code/analysis/variance_scaling_peaks.py
compute peak constraints with 15 bands

@@ -1,13 +1,28 @@
 #!/usr/bin/env python
 from __future__ import division
 
+import sys
+sys.modules["mpi4py"] = None
+
+from operator import add
+
 from lenstools.statistics.database import Database
 from lenstools.statistics.ensemble import Series,Ensemble
 from lenstools.statistics.constraints import FisherAnalysis
 
 import numpy as np
+from scipy.sparse import csr_matrix
 
 import algorithms
+
+############################################################
+#Compression matrix (49x15) to go from 49 to 15 kappa bands#
+############################################################
+
+i = reduce(add,[(n,n,n) for n in range(15)])
+j = np.arange(45)
+d = np.ones(45) / 3.
+compression = csr_matrix((d,(i,j)),shape=(15,49)).T.toarray()
 
 ###########################
 ######Main execution#######
@@ -21,26 +36,30 @@ def main():
 	resample = 100
 
 	#Load the fisher analysis
-	fisher = FisherAnalysis.read("../../data/fisher_peaks.pkl")
+	fisher = FisherAnalysis.read("../../data/fisher_peaks.pkl").refeaturize(compression,method="dot")
 	feature_columns = fisher[fisher.feature_names].columns
 
 	#Load in the feature Ensemble, and bootstrap the covariance using a different number of realizations
 	with Database("../../data/variance_scaling_expected_peaks.sqlite") as db:
 
+		#Log
+		table_name = "variance_15bands"
+		print("[+] Populating table {0}...".format(table_name))
+
 		#This is the reference covariance matrix
-		true_covariance_ensemble = Ensemble(np.load("../../Om0.260_Ol0.740_w-1.000_ns0.960_si0.800/512b240/Maps200/peaks_s0.npy"),columns=feature_columns).cov()
+		true_covariance = Ensemble(np.load("../../Om0.260_Ol0.740_w-1.000_ns0.960_si0.800/512b240/Maps200/peaks_s0.npy").dot(compression),columns=feature_columns).cov()
 		diagonal_covariance = Ensemble(np.diag(true_covariance.values.diagonal()),index=true_covariance.index,columns=true_covariance.columns)
 
 		for n in nsim:
 		
 			#Load the power spectrum Ensemble from the relevant map set
[…]

### 2015-11-18 code/analysis/variance_scaling_power.py
garbage collect in variance_scaling_power

@@ -1,5 +1,6 @@
 #!/usr/bin/env python
 from __future__ import division
+import gc
 
 from lenstools.statistics.database import Database
 from lenstools.statistics.ensemble import Series,Ensemble
@@ -27,16 +28,24 @@ def main():
 	#Large and small scales
 	scales = {
 	"large" : filter(lambda s:int(s.strip("l"))<=7,emulator[emulator.feature_names[0]].columns),
-	"small" : filter(lambda s:int(s.strip("l"))>7,emulator[emulator.feature_names[0]].columns), 
+	"small" : filter(lambda s:int(s.strip("l"))>7,emulator[emulator.feature_names[0]].columns),
+	"all" :  list(emulator[emulator.feature_names[0]].columns),
 	}
 
 	#Fiducial cosmology
 	fiducial_parameters = Series(np.array([0.26,-1.0,0.8]),index=["Om","w","sigma8"])
 
 	#Load in the feature Ensemble, and bootstrap the covariance using a different number of realizations
-	with Database("../../data/variance_scaling_expected.sqlite") as db:
+	with Database("../../data/variance_scaling_power_expected.sqlite") as db:
 	
 		for s in scales:
+
+			#Log
+			table_name = "variance_" + s
+			print("[+] Populating table {0}...".format(table_name))
+
+			#Approximate the emulator linearly around the fiducial model
+			fisher = emulator.approximate_linear(fiducial_parameters,derivative_precision=0.01).features({"power_spectrum":scales[s]})
 
 			#This is the reference covariance matrix
 			true_covariance_ensemble = Ensemble(np.load("../../Om0.260_Ol0.740_w-1.000_ns0.960_si0.800/512b240/Maps200/power_spectrum_s0.npy"),columns=emulator[emulator.feature_names[0]].columns)[scales[s]]
@@ -49,14 +58,14 @@ def main():
 				ensemble_nsim = Ensemble(np.load("../../Om0.260_Ol0.740_w-1.000_ns0.960_si0.800/512b240/Maps{0}/power_spectrum_s0.npy".format(n)),columns=emulator[emulator.feature_names[0]].columns)[scales[s]]
 				ensemble_nsim.add_name("power_spectrum")
 
-				#Approximate the emulator linearly around the fiducial model
-				fisher = emulator.approximate_linear(fiducial_parameters,derivative_precision=0.01).features({"power_spectrum":scales[s]})
-
[…]

### 2015-11-18 Paper/Figures/generate.py
updated figures

@@ -67,6 +67,13 @@ def ps_pdf(cmd_args,nell=[0,4,9,14],nsim=[1,2,5,50,100],colors=["black","blue","
 		for na,subax in enumerate(ax.reshape(4)):
 			subax.hist(ens[nell[na]].values,histtype="step",bins=50,normed=True,label=r"$N_s={0}$".format(ns),color=colors[nc])
 
+	#Plot the result for the BIG ensemble generated with 1 simulation and 128000 realizations
+	ens = Ensemble(np.load("features/MillionMapsPower/power_spectrum_s0.npy"))
+
+	#Fill each sub plot
+	for na,subax in enumerate(ax.reshape(4)):
+		subax.hist(ens[nell[na]].values,histtype="step",bins=50,normed=True,color=colors[0],linewidth=3)
+
 	#Labels
 	for na,subax in enumerate(ax.reshape(4)):
 		subax.set_xlabel(r"$P^{\kappa\kappa}_l$",fontsize=fontsize)
@@ -86,23 +93,47 @@ def scaling_nr(cmd_args,db_filename="variance_scaling_expected.sqlite",parameter
 	#Plot panel
 	fig,ax = plt.subplots()
 
+	####################################################################################################################################
+
 	#Open the database and look for different nsim
 	with Database("data/"+db_filename) as db:
 		v = db.query("SELECT nsim,nreal,{0} FROM variance WHERE nsim IN ({1})".format(parameter,",".join([str(n) for n in nsim])))
 
-	#Plot the variance scalings
+	#Fit with the Dodelson scaling and overlay the fit
+	vfit = variance_scaling.fit_nbins(v,parameter=parameter)
+	v = Ensemble.merge(v,vfit,on="nsim")
+	v[parameter+"_fit"] = v.eval("s0*nb/nreal")
+	v[parameter+"_subtracted"] = v.eval("{0}-s0".format(parameter))
 	nsim_group = v.groupby("nsim")
+
 	for nc,ns in enumerate(nsim):
-		nsim_group.get_group(ns).plot(x="nreal",y=parameter,color=colors[nc],ax=ax,label=r"$N_s={0}$".format(ns))
+		nsim_group.get_group(ns).plot(x="nreal",y=parameter+"_subtracted",linestyle="-",color=colors[nc],ax=ax,label=r"$N_s={0}$".format(ns))
+		nsim_group.get_group(ns).plot(x="nreal",y=parameter+"_fit",linestyle="--",color=colors[nc],ax=ax,legend=False)
+
[…]

### 2015-11-19 code/analysis/variance_scaling_nb.py
added comparison between peaks and power with same nb

@@ -1,0 +1,125 @@
+#!/usr/bin/env python
+from __future__ import division
+import gc
+
+from lenstools.statistics.database import Database
+from lenstools.statistics.ensemble import Series,Ensemble
+from lenstools.statistics.constraints import FisherAnalysis,Emulator
+
+import numpy as np
+
+import algorithms
+
+###########################
+######Main execution#######
+###########################
+
+#Number of simulations to test
+nsim = [1,2,5,10,20,30,40,50,60,70,80,90,100,150,200]
+nreal = np.arange(100,1100,100)
+resample = 100
+
+def main():
+
+	###########################################
+	####Constraints from the power spectrum####
+	###########################################
+
+	#Load the emulator
+	emulator = Emulator.read("../../data/emulators/emulator_power_fine_nb39.pkl")
+	feature_columns = emulator[emulator.feature_names].columns
+
+	#Large and small scales
+	scales = {
+	"large" : filter(lambda s:int(s.strip("l")) in range(15),emulator[emulator.feature_names[0]].columns),
+	"small" : filter(lambda s:int(s.strip("l")) in range(15,30),emulator[emulator.feature_names[0]].columns),
+	}
+
+	#Fiducial cosmology
+	fiducial_parameters = Series(np.array([0.26,-1.0,0.8]),index=["Om","w","sigma8"])
+
+	#Load in the feature Ensemble, and bootstrap the covariance using a different number of realizations
+	with Database("../../data/variance_scaling_nb_expected.sqlite") as db:
+	
+		for s in scales:
+
+			#Log
+			table_name = "power_" + s
+			print("[+] Populating table {0}...".format(table_name))
+
+			#Approximate the emulator linearly around the fiducial model
+			fisher_scale = emulator.approximate_linear(fiducial_parameters,derivative_precision=0.01).features({emulator.feature_names[0]:scales[s]})
+
+			#This is the reference covariance matrix
+			true_covariance_ensemble = Ensemble(np.load("../../Om0.260_Ol0.740_w-1.000_ns0.960_si0.800/512b240/Maps200/power_spectrum_s0_nb39.npy"),columns=emulator[emulator.feature_names[0]].columns)[scales[s]]
+			true_covariance_ensemble.add_name(emulator.feature_names[0])
+			true_covariance = true_covariance_ensemble.cov()
[…]

### 2015-11-19 Paper/Figures/generate.py
change database for Fig. 3

@@ -1,6 +1,7 @@
 #!/usr/bin/env python
 
-import argparse
+import sys,argparse
+sys.modules["mpi4py"] = None
 
 import numpy as np
 import matplotlib.pyplot as plt
@@ -86,7 +87,7 @@ def ps_pdf(cmd_args,nell=[0,4,9,14],nsim=[1,2,5,50,100],colors=["black","blue","
 	fig.savefig("ps_pdf."+cmd_args.type)
 
 #Scaling of the variance with Nr
-def scaling_nr(cmd_args,db_filename="variance_scaling_expected.sqlite",parameter="w",nsim=[1,2,5,50,100],colors=["black","blue","green","red","purple"],fontsize=18):
+def scaling_nr(cmd_args,db_filename="variance_scaling_power_expected.sqlite",parameter="w",nsim=[1,2,5,50,100],colors=["black","blue","green","red","purple"],fontsize=18):
 
 	assert len(colors)>=len(nsim)
 
@@ -97,7 +98,7 @@ def scaling_nr(cmd_args,db_filename="variance_scaling_expected.sqlite",parameter
 
 	#Open the database and look for different nsim
 	with Database("data/"+db_filename) as db:
-		v = db.query("SELECT nsim,nreal,{0} FROM variance WHERE nsim IN ({1})".format(parameter,",".join([str(n) for n in nsim])))
+		v = db.query("SELECT nsim,nreal,{0} FROM variance_all WHERE nsim IN ({1})".format(parameter,",".join([str(n) for n in nsim])))
 
 	#Fit with the Dodelson scaling and overlay the fit
 	vfit = variance_scaling.fit_nbins(v,parameter=parameter)
@@ -116,7 +117,7 @@ def scaling_nr(cmd_args,db_filename="variance_scaling_expected.sqlite",parameter
 
 	#Open the database and look for different nsim
 	with Database("data/variance_scaling_power_largeNr.sqlite") as db:
-		v = db.query("SELECT nsim,nreal,{0} FROM variance_all WHERE nsim IN ({1})".format(parameter,",".join([str(n) for n in nsim])))
+		v = db.query("SELECT nsim,nreal,{0} FROM variance_all".format(parameter))
 
 	#Fit with the Dodelson scaling and overlay the fit
 	vfit = variance_scaling.fit_nbins(v,parameter=parameter)
@@ -126,8 +127,8 @@ def scaling_nr(cmd_args,db_filename="variance_scaling_expected.sqlite",parameter
[…]

### 2015-11-19 code/analysis/algorithms.py
combine scales and peak thresholds

@@ -48,6 +48,7 @@ def bootstrap_area(ensemble,emulator,parameter_grid,fisher,true_covariance,test_
 ###Fit for the effective number of bins###
 ##########################################
 
+#Fit a single table
 def fit_nbins(variance_ensemble,parameter="w"):
 
 	vmean = variance_ensemble
@@ -71,3 +72,19 @@ def fit_nbins(variance_ensemble,parameter="w"):
 
 	#Return to user
 	return Ensemble.from_dict(fit_results)
+
+#Fit all tables
+def fit_nbins_all(db,parameter="w"):
+
+	nb_all = list()
+
+	#Fit all tables
+	for tbl in db.tables:
+		v = db.read_table(tbl)
+		nb = fit_nbins(v,parameter)
+		nb["feature"] = tbl
+		nb_all.append(nb)
+
+	#Return to user
+	return Ensemble.concat(nb_all,axis=0,ignore_index=True)
+

### 2015-11-19 code/analysis/variance_scaling_nb.py

@@ -33,6 +33,7 @@ def main():
 	scales = {
 	"large" : filter(lambda s:int(s.strip("l")) in range(15),emulator[emulator.feature_names[0]].columns),
 	"small" : filter(lambda s:int(s.strip("l")) in range(15,30),emulator[emulator.feature_names[0]].columns),
+	"large+small" : filter(lambda s:int(s.strip("l")) in range(30),emulator[emulator.feature_names[0]].columns),
 	}
 
 	#Fiducial cosmology
@@ -85,6 +86,8 @@ def main():
 	"low" : filter(lambda s:int(s) in range(15),emulator[emulator.feature_names[0]].columns),
 	"intermediate" : filter(lambda s:int(s) in range(15,30),emulator[emulator.feature_names[0]].columns),
 	"high" : filter(lambda s:int(s) in range(30,45),emulator[emulator.feature_names[0]].columns),
+	"low+intermediate" : filter(lambda s:int(s) in range(30),emulator[emulator.feature_names[0]].columns),
+	"intermediate+high" : filter(lambda s:int(s) in range(15,45),emulator[emulator.feature_names[0]].columns),
 	}
 
 	#Load in the feature Ensemble, and bootstrap the covariance using a different number of realizations

### 2015-11-19 code/analysis/variance_scaling_nb.py
added full range of multipoles/peaks

@@ -34,6 +34,7 @@ def main():
 	"large" : filter(lambda s:int(s.strip("l")) in range(15),emulator[emulator.feature_names[0]].columns),
 	"small" : filter(lambda s:int(s.strip("l")) in range(15,30),emulator[emulator.feature_names[0]].columns),
 	"large+small" : filter(lambda s:int(s.strip("l")) in range(30),emulator[emulator.feature_names[0]].columns),
+	"all" : list(emulator[emulator.feature_names[0]].columns),
 	}
 
 	#Fiducial cosmology
@@ -88,6 +89,7 @@ def main():
 	"high" : filter(lambda s:int(s) in range(30,45),emulator[emulator.feature_names[0]].columns),
 	"low+intermediate" : filter(lambda s:int(s) in range(30),emulator[emulator.feature_names[0]].columns),
 	"intermediate+high" : filter(lambda s:int(s) in range(15,45),emulator[emulator.feature_names[0]].columns),
+	"all" : filter(lambda s:int(s) in range(45),emulator[emulator.feature_names[0]].columns),
 	}
 
 	#Load in the feature Ensemble, and bootstrap the covariance using a different number of realizations

### 2015-11-19 code/analysis/variance_scaling_nb.py
add effective number of bins in database

@@ -70,7 +70,7 @@ def main():
 					gc.collect()
 
 					print("[+] Bootstraping scale={0}, Nb={1}, nsim={2}, nreal={3} with {4} resamples".format(s,ensemble_nsim.shape[1],n,nr,resample))
-					variance_ensemble = ensemble_nsim.bootstrap(algorithms.bootstrap_fisher,bootstrap_size=nr,resample=resample,assemble=lambda l:Ensemble.concat(l,ignore_index=True),fisher=fisher_scale,true_covariance=true_covariance,extra_items={"nsim":n,"nreal":nr})
+					variance_ensemble = ensemble_nsim.bootstrap(algorithms.bootstrap_fisher,bootstrap_size=nr,resample=resample,assemble=lambda l:Ensemble.concat(l,ignore_index=True),fisher=fisher_scale,true_covariance=true_covariance,extra_items={"nsim":n,"nreal":nr,"bins":ensemble_nsim.shape[1]})
 					db.insert(Ensemble(variance_ensemble.mean()).T,table_name=table_name)
 
 
@@ -122,7 +122,7 @@ def main():
 					gc.collect()
 
 					print("[+] Bootstraping scale={0}, Nb={1}, nsim={2}, nreal={3} with {4} resamples".format(s,ensemble_nsim.shape[1],n,nr,resample))
-					variance_ensemble = ensemble_nsim.bootstrap(algorithms.bootstrap_fisher,bootstrap_size=nr,resample=resample,assemble=lambda l:Ensemble.concat(l,ignore_index=True),fisher=fisher_scale,true_covariance=true_covariance,extra_items={"nsim":n,"nreal":nr})
+					variance_ensemble = ensemble_nsim.bootstrap(algorithms.bootstrap_fisher,bootstrap_size=nr,resample=resample,assemble=lambda l:Ensemble.concat(l,ignore_index=True),fisher=fisher_scale,true_covariance=true_covariance,extra_items={"nsim":n,"nreal":nr,"bins":ensemble_nsim.shape[1]})
 					db.insert(Ensemble(variance_ensemble.mean()).T,table_name=table_name)
 
 

### 2015-11-19 code/analysis/variance_scaling_power.py

@@ -36,12 +36,12 @@ def main():
 	fiducial_parameters = Series(np.array([0.26,-1.0,0.8]),index=["Om","w","sigma8"])
 
 	#Load in the feature Ensemble, and bootstrap the covariance using a different number of realizations
-	with Database("../../data/variance_scaling_power_expected.sqlite") as db:
+	with Database("../../data/variance_scaling_nb_expected.sqlite") as db:
 	
 		for s in scales:
 
 			#Log
-			table_name = "variance_" + s
+			table_name = "power_logb_" + s
 			print("[+] Populating table {0}...".format(table_name))
 
 			#Approximate the emulator linearly around the fiducial model
@@ -64,7 +64,7 @@ def main():
 					gc.collect()
 
 					print("[+] Bootstraping scale={0}, Nb={1}, nsim={2}, nreal={3} with {4} resamples".format(s,ensemble_nsim.shape[1],n,nr,resample))
-					variance_ensemble = ensemble_nsim.bootstrap(algorithms.bootstrap_fisher,bootstrap_size=nr,resample=resample,assemble=lambda l:Ensemble.concat(l,ignore_index=True),fisher=fisher,true_covariance=true_covariance,extra_items={"nsim":n,"nreal":nr})
+					variance_ensemble = ensemble_nsim.bootstrap(algorithms.bootstrap_fisher,bootstrap_size=nr,resample=resample,assemble=lambda l:Ensemble.concat(l,ignore_index=True),fisher=fisher,true_covariance=true_covariance,extra_items={"nsim":n,"nreal":nr,"bins":ensemble_nsim.shape[1]})
 					db.insert(Ensemble(variance_ensemble.mean()).T,table_name=table_name)
 
 

### 2015-11-19 Paper/paper.tex
updated figures
added formulas from Taylor

@@
 %
-Let $\bbh{d}$ be the measured feature of dimension $N_b$, $\bb{d}(\bb{p})$ be the simulated feature at a point $\bb{p}$ in parameter space and $\bb{C}$ be the $N_b\times N_b$ feature covariance matrix.
+Let $\bbh{d}$ be the measured feature of dimension $N_b$, $\bb{d}(\bb{p})$ be the simulated feature at a point $\bb{p}$ in parameter space (which has a dimension $N_p$) and $\bb{C}$ be the $N_b\times N_b$ feature covariance matrix.
 For the purpose of this work $\bb{p}$ is the triplet $(\Omega_m,w,\sigma_8)$ and $\bb{d}$ is the convergence power spectrum $P^{\kappa\kappa}$, which is measured at $N_b=15$ log--spaced bands between $l\in[100,6000]$.
@@
 Where, for simplicity we assumed $\langle\bbh{d}\rangle=\bb{d}_0$, so that $\langle(\bbh{d}-\bb{d}_0)(\bbh{d}-\bb{d}_0)^T\rangle=\bb{C}$.
-Since the feature we consider is the shear-shear power spectrum, its derivatives $\bb{d}_0'$ with respect to the cosmological parameters can be evaluated by existing analytical codes.
-For this purpose we use the analytical code NICAEA (see \citep{Nicaea}).
 The noise in the covariance estimator (\ref{covest}) propagates all the way to the posterior (\ref{posteriorbayes}), the parameter estimate (\ref{estimatormean}) and its variance (\ref{estimatorcovariance}), through the transformation matrix $\bbh{T}$.
-\citep{DodelsonSchneider13} found that the variance $\h{\sigma}^2_\bb{p}=\mathrm{diag}(\bbh{\Sigma}_\bb{p})$ of each parameter $p$ that is estimated from (\ref{estimatorcovariance}) increases on average with $1/N_r$
+Following \citep{Taylor12} we can say that, if the feature vector $\bbh{d}$ from which $\bbh{C}$ is estimated is drawn from a multivariate Gaussian distribution, the expectation values of the fluctuations of its inverse $\bbh{\Psi}$ can be computed analytically as:
+
+\begin{equation}
+\langle\delta\h{\Psi}_{ij}\delta\h{\Psi}_{kl}\rangle = A\Psi_{ij}\Psi_{kl} + B(\Psi_{ik}\Psi_{jl} + \Psi_{il}\Psi_{jk})
+\end{equation}
+%
+where $A,B$ are constants that depend on $N_r,N_b$.
+\citep{DodelsonSchneider13} calculated the effect of the $\bbh{\Psi}$ fluctuations on the parameter constraints and found that the parameter variance estimator (\ref{estimatorcovariance}) is biased
+
 \begin{equation}
 \label{dodelsonscaling}
-\langle\h{\sigma}_\bb{p}^2\rangle = \sigma_p^2\left(1+\frac{D}{N_r}\right)
+\langle\bbh{\Sigma}_\bb{p}\rangle = \left[1+B(N_b-N_p)\right]\bb{\Sigma}_\bb{p}
 \end{equation} 
 %
-where $\sigma^2_p$ is the true parameter variance and $D$ is what we call \textit{effective dimensionality} of the feature space.
-\citep{DodelsonSchneider13} found $D=N_b$ when every entry in the covariance matrix is subject to noise.
-In this work we argue that the feature ensemble from which the covariance estimator $\bbh{C}^{-1}$ is measured depends not only on the number of shear mock realizations $N_r$, but in principle also on the number of independent $N$--body simulations $N_s$, on which the randomization procedure we describe in \S~\ref{shearsim}.
-We propose a modification to the scaling relation (\ref{dodelsonscaling}) that takes the varying $N_s$ into account.
-
+With the $\bbh{d}$ Gaussianity assumption, the coefficient $B$ can be calculated exactly as \citep{DodelsonSchneider13,Taylor12}:
+\begin{equation}
+B = \frac{N_r-N_b-2}{(N_r-N_b-1)(N_r-N_b-4)}
+\end{equation}
+%
+In the limit $N_r\gg N_b$ this leads to a degradation of order $(N_b-N_p)/N_r$ for the variance of each estimated parameter $\sigma^2_p$. We test the scaling relation
 \begin{equation}
 \label{ourscaling}
-\langle\h{\sigma}_p^2\rangle = \sigma^2_p(N_s,D)\left(1+\frac{D}{N_r}\right)
+\langle\h{\sigma}_p^2\rangle = \sigma^2_p(N_s)\left(1+\frac{D}{N_r}\right)
 \end{equation}
 %
-The reason for this can be found in that, if $N_s$ is not big enough, the different shear realizations cannot be all independent, and hence the true variance $\sigma^2_p$ cannot be recovered in the limit $N_r\rightarrow\infty$.
+on our simulations.
+We call $D$ the \textit{effective dimensionality} of the feature space which, under Gaussianity assumptions, is equal to $N_b-N_p$.
+The expectation values $\h{\sigma}^2_p$ (equations (\ref{estimatorcovariance}),(\ref{ourscaling})) have been computed averaging over 100 independent resamples of the shear ensembles.
+For the true feature covariance matrix $\langle(\bbh{d}-\bb{d}_0)(\bbh{d}-\bb{d}_0)^T\rangle=\bb{C}$ we use the estimated covariance from the $N_s=200$ ensemble.
+The true parameter variance $\sigma^2_p(N_s)$ in principle depends on the number of independent $N$--body simulations $N_s$, which appears in the randomization procedure we describe in \S~\ref{shearsim}.
+The reason for this can be found in that, if $N_s$ is not big enough, the different shear realizations cannot be all independent, and hence the true variance $\sigma^2_p(N_s\rightarrow\infty)$ cannot be recovered in the limit $N_r\rightarrow\infty$.
 In particular there could be some residual error in the expectation value of (\ref{estimatorcovariance}) even if $N_r$ is big.
@@
 
-\begin{figure*}
-\includegraphics[scale=0.4]{Figures/ps_pdf.eps}
-\caption{PDF of the $\kappa$ power spectrum,$\mathcal{L}(P_l^{\kappa\kappa})$, at four selected multipoles $l=115,344,1349,5283$, for different shear ensembles constructed with $N_s=$1 (black), 2 (blue), 5 (green), 50 (red), 100 (purple).}
-\label{ps_pdf}
-\end{figure*}
-
-\begin{figure}
-\includegraphics[scale=0.3]{Figures/ps_variance.eps}
-\caption{Variance of the $\kappa$ power spectrum as a function of the multipole $l$, in units of the expected gaussian variance from equation (\ref{gaussianvar}).
-The variance is measured from different shear ensembles with $N_s=$1 (black), 2 (blue), 5 (green), 10 (red), 50 (purple), 100 (orange).
-}
-\label{ps_var}
-\end{figure}
-
-\begin{figure}
-\includegraphics[scale=0.3]{Figures/scaling_nr.eps}
-\caption{Expectation value of the variance on $w$, $\langle\h{\sigma}^2_w\rangle$, as a function of the number of mock realizations $N_r$ used in the feature covariance estimator (\ref{covest}).
-Results for different mock ensembles generated with $N_s=$1 (black), 2 (blue), 5 (green), 50 (red), 100 (purple) are shown.
-The figure shows both the measured trends (solid lines) and their best fits according to equation (\ref{dodelsonscaling}).
-}
-\label{wvar_nr}
-\end{figure}
+If the feature we consider is the shear-shear power spectrum, its derivatives $\bb{d}_0'$ with respect to the cosmological parameters can be evaluated by existing analytical codes.
+For this purpose we use the analytical code NICAEA (see \citep{Nicaea}).
 
@@
 
+\begin{figure*}
+\includegraphics[scale=0.4]{Figures/ps_pdf.eps}
+\caption{PDF of the $\kappa$ power spectrum,$\mathcal{L}(P_l^{\kappa\kappa})$, at four selected multipoles $l=115,344,1349,5283$, for different shear ensembles constructed with $N_s=$1 (black), 2 (blue), 5 (green), 50 (red), 100 (purple).}
+\label{ps_pdf}
+\end{figure*}
+
+\begin{figure}
+\includegraphics[scale=0.3]{Figures/ps_variance.eps}
+\caption{Variance of the $\kappa$ power spectrum as a function of the multipole $l$, in units of the expected gaussian variance from equation (\ref{gaussianvar}).
+The variance is measured from different shear ensembles with $N_s=$1 (black), 2 (blue), 5 (green), 10 (red), 50 (purple), 100 (orange).
+}
+\label{ps_var}
+\end{figure}
+
+\begin{figure}
+\includegraphics[scale=0.3]{Figures/scaling_nr.eps}
+\caption{Expectation value of the variance on $w$, $\langle\h{\sigma}^2_w\rangle$, as a function of the number of mock realizations $N_r$ used in the feature covariance estimator (\ref{covest}).
+Results for different mock ensembles generated with $N_s=$1 (black), 2 (blue), 5 (green), 50 (red), 100 (purple) are shown.
+The figure shows both the measured trends (solid lines) and their best fits according to equation (\ref{dodelsonscaling}).
+}
+\label{wvar_nr}
+\end{figure}
+
 \begin{figure}
@@
 \caption{Expectation value of the variance on $w$, $\langle\h{\sigma}^2_w\rangle$, varying the mock ensemble used to compute the covariance estimator (\ref{covest}).
-We factored out the $(1/D/N_r)$ dependence, showing only the dependence of $\sigma_0^2$ on $D$.
+We factored out the $(1+D/N_r)$ dependence, showing only the dependence of $\sigma_0^2$ on $D$.
 Different choices of $N_r=$100 (black), 300 (blue), 500 (green), 700 (red), 900 (purple) are shown for comparison.}
@@
 Figure \ref{wvar_ns} shows the effect of varying $N_s$ on the $w$ constraint.
-The expectation values $\h{\sigma}^2_w$ (equations (\ref{estimatorcovariance}),(\ref{ourscaling})) have been computed averaging over 100 independent resamples of the $P^{\kappa\kappa}$ ensembles.
-For the true feature covariance matrix $\langle(\bbh{d}-\bb{d}_0)(\bbh{d}-\bb{d}_0)^T\rangle=\bb{C}$ we use the estimated covariance from the $N_s=200$ ensemble.
 

### 2015-11-19 code/analysis/algorithms.py
measure true covariance from GrandEnsemble

@@ -49,7 +49,7 @@ def bootstrap_area(ensemble,emulator,parameter_grid,fisher,true_covariance,test_
 ##########################################
 
 #Fit a single table
-def fit_nbins(variance_ensemble,parameter="w"):
+def fit_nbins(variance_ensemble,parameter="w",extra_columns=["bins"]):
 
 	vmean = variance_ensemble
 
@@ -62,6 +62,9 @@ def fit_nbins(variance_ensemble,parameter="w"):
 	fit_results["s0"] = list()
 	fit_results["nsim"] = list()
 
+	for c in extra_columns:
+		fit_results[c] = list()
+
 	groupnsim = vmean.groupby("nsim")
 	for g in groupnsim.groups:
 		fit_results["nsim"].append(int(g))
@@ -70,18 +73,21 @@ def fit_nbins(variance_ensemble,parameter="w"):
 		fit_results["nb"].append(a/b)
 		fit_results["s0"].append(b)
 
+		for c in extra_columns:
+			fit_results[c].append(vmean_group[c].mean())
+
 	#Return to user
 	return Ensemble.from_dict(fit_results)
 
 #Fit all tables
-def fit_nbins_all(db,parameter="w"):
+def fit_nbins_all(db,parameter="w",extra_columns=["bins"]):
 
 	nb_all = list()
 
 	#Fit all tables
 	for tbl in db.tables:
 		v = db.read_table(tbl)
-		nb = fit_nbins(v,parameter)
+		nb = fit_nbins(v,parameter,extra_columns)
 		nb["feature"] = tbl
 		nb_all.append(nb)
 

### 2015-11-19 code/analysis/variance_scaling_nb.py

@@ -53,7 +53,7 @@ def main():
 			fisher_scale = emulator.approximate_linear(fiducial_parameters,derivative_precision=0.01).features({emulator.feature_names[0]:scales[s]})
 
 			#This is the reference covariance matrix
-			true_covariance_ensemble = Ensemble(np.load("../../Om0.260_Ol0.740_w-1.000_ns0.960_si0.800/512b240/Maps200/power_spectrum_s0_nb39.npy"),columns=emulator[emulator.feature_names[0]].columns)[scales[s]]
+			true_covariance_ensemble = Ensemble(np.load("../../Om0.260_Ol0.740_w-1.000_ns0.960_si0.800/512b240/GrandEnsemble/power_spectrum_s0_nb39.npy"),columns=emulator[emulator.feature_names[0]].columns)[scales[s]]
 			true_covariance_ensemble.add_name(emulator.feature_names[0])
 			true_covariance = true_covariance_ensemble.cov()
 			diagonal_covariance = Ensemble(np.diag(true_covariance.values.diagonal()),index=true_covariance.index,columns=true_covariance.columns)
@@ -105,7 +105,7 @@ def main():
 			fisher_scale = emulator.features({emulator.feature_names[0]:scales[s]})
 
 			#This is the reference covariance matrix
-			true_covariance_ensemble = Ensemble(np.load("../../Om0.260_Ol0.740_w-1.000_ns0.960_si0.800/512b240/Maps200/peaks_s0.npy"),columns=emulator[emulator.feature_names[0]].columns)[scales[s]]
+			true_covariance_ensemble = Ensemble(np.load("../../Om0.260_Ol0.740_w-1.000_ns0.960_si0.800/512b240/GrandEnsemble/peaks_s0.npy"),columns=emulator[emulator.feature_names[0]].columns)[scales[s]]
 			true_covariance_ensemble.add_name(emulator.feature_names[0])
 			true_covariance = true_covariance_ensemble.cov()
 			diagonal_covariance = Ensemble(np.diag(true_covariance.values.diagonal()),index=true_covariance.index,columns=true_covariance.columns)

### 2015-11-19 code/analysis/variance_scaling_power.py

@@ -48,7 +48,7 @@ def main():
 			fisher = emulator.approximate_linear(fiducial_parameters,derivative_precision=0.01).features({"power_spectrum":scales[s]})
 
 			#This is the reference covariance matrix
-			true_covariance_ensemble = Ensemble(np.load("../../Om0.260_Ol0.740_w-1.000_ns0.960_si0.800/512b240/Maps200/power_spectrum_s0.npy"),columns=emulator[emulator.feature_names[0]].columns)[scales[s]]
+			true_covariance_ensemble = Ensemble(np.load("../../Om0.260_Ol0.740_w-1.000_ns0.960_si0.800/512b240/GrandEnsemble/power_spectrum_s0.npy"),columns=emulator[emulator.feature_names[0]].columns)[scales[s]]
 			true_covariance = true_covariance_ensemble.cov()
 			diagonal_covariance = Ensemble(np.diag(true_covariance.values.diagonal()),index=true_covariance.index,columns=true_covariance.columns)
 

### 2015-11-19 Paper/paper.tex
added new figure

@@
 \usepackage{booktabs}
+\usepackage[dvipsnames]{xcolor}
 
@@
 We construct different mock ensembles with $N_r$ realizations of the same shear field, based on $N_s<N_r$ independent $N$--body simulations.
-Using the shear--shear power spectrum as a summary statistic, we find that the scaling of the forecasted error bar for $w$ shows the expected behavior with $N_r$ (see \citep{DodelsonSchneider13}).
-The same quantity shows a mild dependence on $N_s$ and on the effective dimensionality of the feature space.
+Using the shear--shear power spectrum as a summary statistic, we find that a single $N$--body simulation can be recycled $O(10^6)$ times to produce an ensemble of $N_r=10^5$ shear realizations that are mutually independent.
+We also find that, for a range of summary statistics that include shear--shear power spectra measured at different scales and converge peak counts, parameter constraints degrade faster than the $O(N_b)$ Gaussian prediction by \citep{DodelsonSchneider13}, where $N_b$ is the length of the feature vector.
 \end{abstract}
@@
 
-If the feature we consider is the shear-shear power spectrum, its derivatives $\bb{d}_0'$ with respect to the cosmological parameters can be evaluated by existing analytical codes.
-For this purpose we use the analytical code NICAEA (see \citep{Nicaea}).
-
-\begin{table}
-\begin{center}
-\begin{tabular}{r|rr}
-\toprule
- $N_s$ &  $D$(diagonal) &  $D$(full) \\ \hline
-\midrule
-    1 &   2.8 &  12.3 \\
-    2 &   2.1 &  14.4 \\
-    5 &   2.6 &  16.4 \\
-   10 &   3.1 &  14.6 \\
-   20 &   2.4 &  15.8 \\
-   30 &   2.5 &  15.4 \\
-   40 &   2.7 &  15.7 \\
-   50 &   2.5 &  13.6 \\
-   60 &   2.7 &  13.3 \\
-   70 &   2.4 &  15.0 \\
-   80 &   2.4 &  15.6 \\
-   90 &   2.6 &  14.1 \\
-  100 &   2.2 &  14.1 \\
-  150 &   2.3 &  13.9 \\
-  200 &   2.6 &  18.2 \\
-\bottomrule
-\end{tabular}
-\end{center}
-\caption{Effective dimensionality of the power spectrum feature space $D$ computed fitting the measured $w$ variance with the scaling relation (\ref{dodelsonscaling}).
-We show both cases in which we consider the full covariance matrix and the case in which we artificially zero out all the off diagonal elements.}
-\label{dimtable}
-\end{table}
-
 \begin{figure*}
@@
 
+\begin{table*}
+\begin{center}
+\begin{tabular}{ccccc}
+\toprule
+\textbf{Feature} &  \textbf{Specifications} & $N_b$ &  \textbf{Symbol} & \textbf{Color} \\ \hline \hline
+\midrule
+Power Spectrum, log binning  & $l \in [100,800] $ & 8 & $\times$ & black  \\ 
+Power Spectrum, log binning  & $l \in [1000,6000] $ & 7 & $\times$ & black  \\ 
+Power Spectrum, log binning  & $l \in [100,6000] $ & 15 & $\times$ & black  \\
+Power Spectrum, linear binning  & $l \in [100,2000] $ & 15 & \textcolor{red}{$+$} & \textcolor{red}{red}  \\ 
+Power Spectrum, linear binning  & $l \in [2500,4500] $ & 15 & \textcolor{red}{$\times$} & \textcolor{red}{red}  \\
+Power Spectrum, linear binning  & $l \in [100,4500] $ & 30 & \textcolor{red}{$\bullet$} & \textcolor{red}{red}  \\ 
+Power Spectrum, linear binning  & $l \in [100,6000] $ & 39 & \textcolor{red}{$\bullet$} & \textcolor{red}{red}  \\ \hline
+Low peaks  & $\kappa_0 \in [-0.06,0.09] $ & 15 & \textcolor{OliveGreen}{$+$} & \textcolor{OliveGreen}{green}  \\ 
+Intermediate peaks  & $\kappa_0 \in [0.1,0.27] $ & 15 & \textcolor{OliveGreen}{$\bigstar$} & \textcolor{OliveGreen}{green}  \\ 
+High peaks  & $\kappa_0 \in [0.28,0.45] $ & 15 & \textcolor{OliveGreen}{$\diamond$} & \textcolor{OliveGreen}{green}  \\
+Low+Intermediate peaks  & $\kappa_0 \in [-0.06,0.27] $ & 30 & \textcolor{OliveGreen}{$\times$} & \textcolor{OliveGreen}{green}  \\
+Intermediate+High peaks  & $\kappa_0 \in [0.1,0.45] $ & 30 & \textcolor{OliveGreen}{$\bullet$} & \textcolor{OliveGreen}{green}  \\
+All peaks  & $\kappa_0 \in [-0.06,0.45] $ & 45 & \textcolor{OliveGreen}{$\blacksquare$} & \textcolor{OliveGreen}{green}  \\ \hline
+\bottomrule
+\end{tabular}
+\end{center}
+\caption{Effective dimensionality of the power spectrum feature space $D$ computed fitting the measured $w$ variance with the scaling relation (\ref{dodelsonscaling}).
+We show both cases in which we consider the full covariance matrix and the case in which we artificially zero out all the off diagonal elements.}
+\label{dimtable}
+\end{table*}
+
+\begin{figure}
+\includegraphics[scale=0.35]{Figures/effective_nb.eps}
+\caption{}
+\label{effectivenb}
+\end{figure}
+
+If the feature we consider is the shear-shear power spectrum, its derivatives $\bb{d}_0'$ with respect to the cosmological parameters can be evaluated by existing analytical codes.
+For this purpose we use the analytical code NICAEA (see \citep{Nicaea}).
 In this section we outline the main results of this work.

### 2015-11-19 Paper/Figures/generate.py

@@ -9,7 +9,7 @@ import matplotlib.pyplot as plt
 from lenstools.statistics.ensemble import Ensemble
 from lenstools.statistics.database import Database
 
-import variance_scaling
+import algorithms
 
 #Options
 parser = argparse.ArgumentParser()
@@ -17,7 +17,7 @@ parser.add_argument("-t","--type",dest="type",default="png",help="format of the 
 parser.add_argument("fig",nargs="*")
 
 #Power spectrum variance
-def ps_variance(cmd_args,nsim=[1,2,5,10,50,100],colors=["black","blue","green","red","purple","orange"],fontsize=18):
+def ps_variance(cmd_args,nsim=[1,2,5,10,50,100],colors=["black","blue","green","red","purple","orange"],fontsize=22):
 
 	assert len(colors)>=len(nsim)
 
@@ -49,7 +49,7 @@ def ps_variance(cmd_args,nsim=[1,2,5,10,50,100],colors=["black","blue","green","
 	fig.savefig("ps_variance."+cmd_args.type)
 
 #Power spectrum pdf
-def ps_pdf(cmd_args,nell=[0,4,9,14],nsim=[1,2,5,50,100],colors=["black","blue","green","red","purple"],fontsize=18):
+def ps_pdf(cmd_args,nell=[0,4,9,14],nsim=[1,2,5,50,100],colors=["black","blue","green","red","purple"],fontsize=22):
 
 	assert len(colors)>=len(nsim)
 	assert len(nell)==4
@@ -87,7 +87,7 @@ def ps_pdf(cmd_args,nell=[0,4,9,14],nsim=[1,2,5,50,100],colors=["black","blue","
 	fig.savefig("ps_pdf."+cmd_args.type)
 
 #Scaling of the variance with Nr
-def scaling_nr(cmd_args,db_filename="variance_scaling_power_expected.sqlite",parameter="w",nsim=[1,2,5,50,100],colors=["black","blue","green","red","purple"],fontsize=18):
+def scaling_nr(cmd_args,db_filename="variance_scaling_nb_expected.sqlite",parameter="w",nsim=[1,2,5,50,100],colors=["black","blue","green","red","purple"],fontsize=22):
 
 	assert len(colors)>=len(nsim)
 
@@ -98,10 +98,10 @@ def scaling_nr(cmd_args,db_filename="variance_scaling_power_expected.sqlite",par
 
 	#Open the database and look for different nsim
 	with Database("data/"+db_filename) as db:
[…]

### 2015-11-20 Paper/paper.tex
slight modifications

@@
 Using a set of 200 independent $N$--body simulations, we construct different ensembles with different choices of $N_s\in[1,200]$, each made of 1000 mock shear realizations.
+We also build an additional ensemble with $N_s=1$ and $10^5$ mocks.
 From each of these mocks we reconstruct the convergence $\kappa_r(\pmb{\theta})$ and measure its angular power spectrum $P^{\kappa\kappa}_r(l)$ defined as
@@
 %
-The fact that the ensemble of $N_r$ mocks is not completely independent if $N_s$ is not large enough can have an effect on the covariance estimator of $P^{\kappa\kappa}$.
+As an additional summary statistic, we consider the counts of local $\kappa$ maxima of a certain height $\kappa_0$, $n_r(\kappa_0)$ (from now on \textit{peak counts}), with varying $\kappa_0$.
+The fact that the ensemble of $N_r$ mocks is not completely independent if $N_s$ is not large enough can have an effect on the covariance estimators of $P^{\kappa\kappa},n(\kappa_0)$.
 
@@
 %
-where $A,B$ are constants that depend on $N_r,N_b$.
+where $A,B$ are constants that depend on $N_r,N_b$ and have the asymptotic behavior $A\propto1/N_r^2,B\propto1/N_r$.
 \citep{DodelsonSchneider13} calculated the effect of the $\bbh{\Psi}$ fluctuations on the parameter constraints and found that the parameter variance estimator (\ref{estimatorcovariance}) is biased
@@
 %
-In the limit $N_r\gg N_b$ this leads to a degradation of order $(N_b-N_p)/N_r$ for the variance of each estimated parameter $\sigma^2_p$. We test the scaling relation
+In the limit $N_r\gg N_b$ this leads to a degradation of order $(N_b-N_p)/N_r$ for the variance of each estimated parameter $\sigma^2_p=\Sigma_{pp}$. We test the scaling relation
 \begin{equation}
@@
 We call $D$ the \textit{effective dimensionality} of the feature space which, under Gaussianity assumptions, is equal to $N_b-N_p$.
-The expectation values $\h{\sigma}^2_p$ (equations (\ref{estimatorcovariance}),(\ref{ourscaling})) have been computed averaging over 100 independent resamples of the shear ensembles.
-For the true feature covariance matrix $\langle(\bbh{d}-\bb{d}_0)(\bbh{d}-\bb{d}_0)^T\rangle=\bb{C}$ we use the estimated covariance from the $N_s=200$ ensemble.
+We compute the expectation values of $\h{\sigma}^2_p$ (equations (\ref{estimatorcovariance}),(\ref{ourscaling})) averaging over 100 random resamplings of our shear ensembles.
+For the true feature covariance matrix $\langle(\bbh{d}-\bb{d}_0)(\bbh{d}-\bb{d}_0)^T\rangle=\bb{C}$ we use the estimated covariance from a grand ensemble built with the union of all the ensembles with different $N_s$.
 The true parameter variance $\sigma^2_p(N_s)$ in principle depends on the number of independent $N$--body simulations $N_s$, which appears in the randomization procedure we describe in \S~\ref{shearsim}.

### 2015-11-20 code/analysis/algorithms.py
introduce bias correction factor in parameter estimates

@@ -49,9 +49,12 @@ def bootstrap_area(ensemble,emulator,parameter_grid,fisher,true_covariance,test_
 ##########################################
 
 #Fit a single table
-def fit_nbins(variance_ensemble,parameter="w",extra_columns=["bins"]):
+def fit_nbins(variance_ensemble,parameter="w",extra_columns=["bins"],correct=False):
 
 	vmean = variance_ensemble
+	if correct:
+		assert "bins" in extra_columns
+		vmean[parameter] = vmean.eval("{0}*(nreal-1)/(nreal-bins-2)".format(parameter))
 
 	#Compute variance expectation values
 	vmean["1/nreal"] = vmean.eval("1.0/nreal")
@@ -80,14 +83,14 @@ def fit_nbins(variance_ensemble,parameter="w",extra_columns=["bins"]):
 	return Ensemble.from_dict(fit_results)
 
 #Fit all tables
-def fit_nbins_all(db,parameter="w",extra_columns=["bins"]):
+def fit_nbins_all(db,parameter="w",extra_columns=["bins"],correct=False):
 
 	nb_all = list()
 
 	#Fit all tables
 	for tbl in db.tables:
 		v = db.read_table(tbl)
-		nb = fit_nbins(v,parameter,extra_columns)
+		nb = fit_nbins(v,parameter,extra_columns,correct)
 		nb["feature"] = tbl
 		nb_all.append(nb)
 

### 2015-11-20 Paper/paper.tex
second draft

@@
 We construct different mock ensembles with $N_r$ realizations of the same shear field, based on $N_s<N_r$ independent $N$--body simulations.
-Using the shear--shear power spectrum as a summary statistic, we find that a single $N$--body simulation can be recycled $O(10^6)$ times to produce an ensemble of $N_r=10^5$ shear realizations that are mutually independent.
-We also find that, for a range of summary statistics that include shear--shear power spectra measured at different scales and converge peak counts, parameter constraints degrade faster than the $O(N_b)$ Gaussian prediction by \citep{DodelsonSchneider13}, where $N_b$ is the length of the feature vector.
+Using the shear--shear power spectrum as a summary statistic, we find that a single $N$--body simulation can be recycled a large number of times to produce an ensemble of $N_r=10^5$ shear realizations that are mutually independent.
+We also find that, for a range of summary statistics that include shear--shear power spectra measured at different scales and convergence peak counts, parameter constraints degrade faster than the $O(N_b)$ Gaussian prediction by \citep{DodelsonSchneider13}, where $N_b$ is the length of the feature vector.
 \end{abstract}
@@
 Because the evolution of $\Phi$ in redshift is non--linear, its evolution needs to be computed with numerical simulations.
-We make use of the public code Gadget2 \citep{Gadget2}, with which we run a sequence of dark--matter--only $N$--body simulations that track the evolution of the density fluctuations in the large scale structure of the universe.
+We make use of the public code \texttt{Gadget2} \citep{Gadget2}, with which we run a sequence of dark--matter--only $N$--body simulations that track the evolution of the density fluctuations in the large scale structure of the universe.
 We assume a standard $\Lambda$CDM framework with $(\Omega_m,\Omega_\Lambda,h,w,\sigma_8,n_s)=(0.26,0.74,0.72,-1,0.8,0.96)$ and we fix the comoving size of the simulation box to $240\mathrm{Mpc}/h$.
 We fill the box with $512^3$ particles, which correspond to a mass resolution of $10^{10}M_\odot$.
-We assume a uniform galaxy distribution at a constant redshift $z_s=2$ (at which the simulation box has an angular size of $\theta_{box}=3.5\mathrm{deg}$) and we disctretize the mass distribution between $z_s$ and the observer at $z=0$ with a sequence of 60 two dimensional lenses of thickness $80\mathrm{Mpc}/h$.
-The surface density on each lens is computed by projecting the three dimensional density measured from Gadget2 snapshots.
+We assume a uniform galaxy distribution at a constant redshift $z_s=2$ (at which the simulation box has an angular size of $\theta_{box}=3.5\mathrm{deg}$) and we disctretize the mass distribution between $z_s$ and the observer at $z=0$ with a sequence of 46 two dimensional lenses of thickness $80\mathrm{Mpc}/h$.
+The surface density on each lens is computed by projecting the three dimensional density measured from \texttt{Gadget2} snapshots.
 We then apply the multi--lens--plane algorithm (see \citep{RayTracingHartlap,RayTracingJain} for example) to trace the deflections of $2048^2$ light rays arranged on a square grid of total size $\theta_{box}$, from $z=0$ to $z_s$.
-The light deflection calculations have been performed with our implementation of multi--lens--plane algorithm, which is part of the LensTools computing package \citep{LensTools} (released under the MIT license).
+The light deflection calculations have been performed with our implementation of multi--lens--plane algorithm, which is part of the \texttt{LensTools} computing package \citep{LensTools} (released under the MIT license).
 Different realizations $r$ of the same shear field $\pmb{\gamma}_r(\pmb{\theta})$ can be generated with different choices of the lenses that lay between the observer and $z_s$.
@@
 %
-From which we can build the estimators for the parameters expectation value $\bbh{p}$ and covariance $\h{\Sigma}_\bb{p}$, given the observation $\bbh{d}$, as follows:
+To measure the feature derivatives $\bb{d}'_0$ with respect to cosmology, we make use of the public code code NICAEA (see \citep{Nicaea}) for the power spectrum, and we use an independent simulation set (that contains mocks at different combinations of $(\Omega_m,w,\sigma_8)$) for the peak counts.
+We can build the estimator for the posterior location parameter $\bbh{p}$, given the observation $\bbh{d}$, as follows:
 %
@@
 \begin{equation}
+\bbh{T} = (\bb{d}_0'^T\bbh{C}^{-1}\bb{d}_0')^{-1}\bb{d}_0'^T\bbh{C}^{-1}
+\end{equation}
+%
+Defining the \textit{precision matrix} $\bbh{\Psi}=\bbh{C}^{-1}$, we can express the estimator of the parameter covariance as
+
+\begin{equation}
 \label{estimatorcovariance}
-\h{\Sigma}_\bb{p} = \bbh{T}(\bbh{d}-\bb{d}_0)(\bbh{d}-\bb{d}_0)^T\bbh{T}^T
+\h{\Sigma}_\bb{p} = \bbh{F}^{-1}\bb{d}_0'^T\bbh{\Psi}\bb{C}\bbh{\Psi}\bb{d}_0'\bbh{F}^{-1}
 \end{equation}
@@
 \begin{equation}
-\bbh{T} = (\bb{d}_0'^T\bbh{C}^{-1}\bb{d}_0')^{-1}\bb{d}_0'^T\bbh{C}^{-1}
+\label{estimatorfisher}
+\bbh{F} = \bb{d}_0'^T\bbh{\Psi}\bb{d}_0'
 \end{equation}
 %
-Where, for simplicity we assumed $\langle\bbh{d}\rangle=\bb{d}_0$, so that $\langle(\bbh{d}-\bb{d}_0)(\bbh{d}-\bb{d}_0)^T\rangle=\bb{C}$.
-The noise in the covariance estimator (\ref{covest}) propagates all the way to the posterior (\ref{posteriorbayes}), the parameter estimate (\ref{estimatormean}) and its variance (\ref{estimatorcovariance}), through the transformation matrix $\bbh{T}$.
-Following \citep{Taylor12} we can say that, if the feature vector $\bbh{d}$ from which $\bbh{C}$ is estimated is drawn from a multivariate Gaussian distribution, the expectation values of the fluctuations of its inverse $\bbh{\Psi}$ can be computed analytically as:
-
+Where we introduced the Fisher matrix estimator $\bbh{F} = \bb{d}_0'^T\bbh{\Psi}\bb{d}_0'$ and, for simplicity, we assumed $\langle\bbh{d}\rangle=\bb{d}_0$, so that $\langle(\bbh{d}-\bb{d}_0)(\bbh{d}-\bb{d}_0)^T\rangle=\bb{C}$.
+The noise in the covariance estimator (\ref{covest}) and its inverse $\bbh{\Psi}$ propagates all the way to the posterior (\ref{posteriorbayes}), the parameter estimate (\ref{estimatormean}) and its variance (\ref{estimatorcovariance}).
+Following \citep{Taylor12} we can say that, if the feature vector $\bbh{d}$ from which $\bbh{C}$ is estimated is drawn from a multivariate Gaussian distribution, the precision matrix estimator $\bbh{\Psi}$ is biased
 \begin{equation}
+\label{psibias}
+\langle\bbh{\Psi}\rangle = \frac{N_r-1}{N_r-N_b-2}\bb{\Psi}
+\end{equation}
+%
+and, once the bias is corrected, the residual fluctuations in $\bbh{\Psi}$ are correlated as follows
+\begin{equation}
+\label{psifluctuations}
 \langle\delta\h{\Psi}_{ij}\delta\h{\Psi}_{kl}\rangle = A\Psi_{ij}\Psi_{kl} + B(\Psi_{ik}\Psi_{jl} + \Psi_{il}\Psi_{jk})
@@
 where $A,B$ are constants that depend on $N_r,N_b$ and have the asymptotic behavior $A\propto1/N_r^2,B\propto1/N_r$.
-\citep{DodelsonSchneider13} calculated the effect of the $\bbh{\Psi}$ fluctuations on the parameter constraints and found that the parameter variance estimator (\ref{estimatorcovariance}) is biased
+We want to estimate the effect of these fluctuations on the parameter constraints $\Sigma_\bb{p}$, following the guidelines of \citep{DodelsonSchneider13}.
+We consider three cases:
+\begin{itemize}
+\item If the true data covariance $\bb{C}$ is known, the estimator (\ref{estimatorcovariance}) is biased, and the dominant contribution of the bias comes from the second order fluctuations in $\bbh{\Psi}$.
+Once the expectation values are taken as in (\ref{psifluctuations}), the bias sums up to
 
@@
 \label{dodelsonscaling}
-\langle\bbh{\Sigma}_\bb{p}\rangle = \left[1+B(N_b-N_p)\right]\bb{\Sigma}_\bb{p}
+\langle\h{\Sigma}_\bb{p}\rangle=\Sigma_\bb{p}(1+B(N_b-N_p))
 \end{equation}
 %
+This is the result obtained by \citep{DodelsonSchneider13}.
+\item If we are not interested in measuring the location parameter $\bbh{p}$, but just the width of the parameter posterior, we can tempted to replace the true covariance $\bb{C}$ with its estimator $\bbh{C}$.
+If we do that, and we do not correct for the bias (\ref{psibias}), the parameter variance will have a contribution from both the second and first order fluctuations in $\bbh{\Psi}$, which now have a non zero expectation value.
+In this case the bias sums up to
+\begin{equation}
+\label{mockscalinguncorrected}
+\langle\h{\Sigma}_\bb{p}\rangle=\Sigma_\bb{p}(1-(1+N_b)/N_r+B(1+N_p))
+\end{equation}
+\item If we repeat the same exercise as above, but we correct for the bias in the precision matrix estimator, we are left with
+
+\begin{equation}
+\label{mockscalingcorrected}
+\langle\h{\Sigma}_\bb{p}\rangle=\Sigma_\bb{p}(1+B(1+N_p))
+\end{equation}
+
+\end{itemize} 
+%
+In the three previous cases we only kept the terms of order $O(1/N_r)$.
+The last two examples have to be considered as academic exercises, as in a real experiment the data has to be used in the end to compute the posterior location parameter and the parameter covariance.
 With the $\bbh{d}$ Gaussianity assumption, the coefficient $B$ can be calculated exactly as \citep{DodelsonSchneider13,Taylor12}:
@@
 %
-In the limit $N_r\gg N_b$ this leads to a degradation of order $(N_b-N_p)/N_r$ for the variance of each estimated parameter $\sigma^2_p=\Sigma_{pp}$. We test the scaling relation
+In the limit $N_r\gg N_b$ this leads to a degradation of order $D/N_r$ for the variance of each estimated parameter $\sigma^2_p=\Sigma_{pp}$. We test the scaling relation
 \begin{equation}
@@
 on our simulations.
-We call $D$ the \textit{effective dimensionality} of the feature space which, under Gaussianity assumptions, is equal to $N_b-N_p$.
+We call $D$ the \textit{effective dimensionality} of the feature space which, under Gaussianity assumptions, is equal to $D=N_b-N_p$ in the case where the true covariance $\bb{C}$ is known, $D=N_p-N_b$ when the true precision matrix is replaced by its biased estimator (computed from the same simulation set) and $D=1+N_p$ when the $\bbh{\Psi}$ is corrected.
+
 We compute the expectation values of $\h{\sigma}^2_p$ (equations (\ref{estimatorcovariance}),(\ref{ourscaling})) averaging over 100 random resamplings of our shear ensembles.
 For the true feature covariance matrix $\langle(\bbh{d}-\bb{d}_0)(\bbh{d}-\bb{d}_0)^T\rangle=\bb{C}$ we use the estimated covariance from a grand ensemble built with the union of all the ensembles with different $N_s$.
+
 The true parameter variance $\sigma^2_p(N_s)$ in principle depends on the number of independent $N$--body simulations $N_s$, which appears in the randomization procedure we describe in \S~\ref{shearsim}.
@@
 \includegraphics[scale=0.4]{Figures/ps_pdf.eps}
-\caption{PDF of the $\kappa$ power spectrum,$\mathcal{L}(P_l^{\kappa\kappa})$, at four selected multipoles $l=115,344,1349,5283$, for different shear ensembles constructed with $N_s=$1 (black), 2 (blue), 5 (green), 50 (red), 100 (purple).}
+\caption{PDF of the $\kappa$ power spectrum,$\mathcal{L}(P_l^{\kappa\kappa})$, at four selected multipoles $l=115,344,1349,5283$, for different shear ensembles constructed with $N_s=$1 (black), 2 (blue), 5 (green), 50 (red), 100 (purple).
+The thick black lines correspond to an ensemble generated with $N_s=1$ and $10^5$ mock realizations.}
 \label{ps_pdf}
@@
 \includegraphics[scale=0.3]{Figures/scaling_nr.eps}
-\caption{Expectation value of the variance on $w$, $\langle\h{\sigma}^2_w\rangle$, as a function of the number of mock realizations $N_r$ used in the feature covariance estimator (\ref{covest}).
+\caption{Bias in the $w$ variance, $\langle\h{\sigma}^2_w\rangle$, as a function of the number of mock realizations $N_r$ used in the feature covariance estimator (\ref{covest}).
 Results for different mock ensembles generated with $N_s=$1 (black), 2 (blue), 5 (green), 50 (red), 100 (purple) are shown.
-The figure shows both the measured trends (solid lines) and their best fits according to equation (\ref{dodelsonscaling}).
+The figure shows both the measured trends (solid lines) and their best fits according to equation (\ref{ourscaling}).
+The thick black line correspond to an ensemble generated with $N_s=1$ and $10^5$ mock realizations.
 }
@@
 \includegraphics[scale=0.3]{Figures/scaling_ns.eps}
-\caption{Expectation value of the variance on $w$, $\langle\h{\sigma}^2_w\rangle$, varying the mock ensemble used to compute the covariance estimator (\ref{covest}).
-We factored out the $(1+D/N_r)$ dependence, showing only the dependence of $\sigma_0^2$ on $D$.
-Different choices of $N_r=$100 (black), 300 (blue), 500 (green), 700 (red), 900 (purple) are shown for comparison.}
+\caption{Variance on $w$ in the limit $N_r\rightarrow\infty$, varying the mock ensemble used to compute the covariance estimator (\ref{covest}).
+We show the dependence of $\sigma_0^2(N_s)$ in units of the mean over $N_s$, for the power spectrum logarithmically binned (black), the power spectrum linearly binned (red) and the peak counts (green).}
 \label{wvar_ns}
@@
 \end{center}
-\caption{Effective dimensionality of the power spectrum feature space $D$ computed fitting the measured $w$ variance with the scaling relation (\ref{dodelsonscaling}).
-We show both cases in which we consider the full covariance matrix and the case in which we artificially zero out all the off diagonal elements.}
-\label{dimtable}
+\caption{Catalog of feature types used in this work, along with the chosen number of bands and the plot legends for Figure \ref{effectivenb}.}
+\label{featuretable}
 \end{table*}
 
-\begin{figure}
-\includegraphics[scale=0.35]{Figures/effective_nb.eps}
-\caption{}
+\begin{figure*}
+\includegraphics[scale=0.3]{Figures/effective_nb.eps}
+\includegraphics[scale=0.3]{Figures/effective_nb_fake_uncorrected.eps}
+\includegraphics[scale=0.3]{Figures/effective_nb_fake_corrected.eps}
+\caption{Effective dimesionality of the feature space, $D$, as a function of the number of bands $N_b$, for the features outlined in Table \ref{featuretable}.
+The dimensionality $D$ is plotted in units of its predicted value from equations (\ref{dodelsonscaling}) in the left panel, equation (\ref{mockscalinguncorrected}) in the center panel and equation (\ref{mockscalingcorrected}) in the right panel.}
 \label{effectivenb}
-\end{figure}
+\end{figure*}
 
-If the feature we consider is the shear-shear power spectrum, its derivatives $\bb{d}_0'$ with respect to the cosmological parameters can be evaluated by existing analytical codes.
-For this purpose we use the analytical code NICAEA (see \citep{Nicaea}).
 In this section we outline the main results of this work.
@@
 %
-where $N(l)$ is the number of modes used to estimate the power spectrum at $l$, which depends on the mock size $\theta_{box}$ and on the width of the $N_b$ multipole bands.
-Figure \ref{wvar_nr} and Table \ref{dimtable} show the scaling of the expectation value of $\h{\sigma}_w^2$ with the number of mocks $N_r$ and compare it with the known result obtained in \citep{DodelsonSchneider13}.
+where $N(l)$ is the number of modes used to estimate the power spectrum at $l$.
+$N_l$ is measured from the Fourier trasformed image grid.
+Figure \ref{wvar_nr} show the scaling of the expectation value of $\h{\sigma}_w^2$ with the number of mocks $N_r$ using the power spectrum and compare it with the known result obtained in \citep{DodelsonSchneider13} and expressed in equation (\ref{ourscaling}).
 Figure \ref{wvar_ns} shows the effect of varying $N_s$ on the $w$ constraint.
+Finally Figure \ref{effectivenb} shows how the effective feature dimensionality $D$ depends on the number of bands $N_b$, for a variety of features and binning choices outlined in Table \ref{featuretable}.
 
@@
 In this section we discuss our main findings.
-Figure \ref{ps_pdf} shows that, although different choices of $N_s$ do not seem to affect the power spectrum PDF at large scales (top two panels), there are some qualitative differences on small scales (bottom two panels), on which a shear ensemble built with a small $N_s$ might not have the same statistical behavior of ensembles built with large $N_s$.
+Figure \ref{ps_pdf} shows that, although different choices of $N_s$ do not seem to affect the power spectrum PDF at large scales (top two panels), there are some qualitative differences on small scales (bottom two panels), on which a shear ensemble built with a small $N_s$ does not have the same statistical behavior of ensembles built with large $N_s$.
+Looking at the black curves, we see that the $N_s=1$ ensembles exibit some stochastic fluctuations in where the PDF peaks.
+We need as small as $N_s=2$ to recover the right location parameter for the power spectrum on small scales.
+
 Figure \ref{ps_var} shows the variance of convergence power spectrum computed from different ensembles, in units of the Gaussian expectation.
@@
 
-In Figure \ref{wvar_nr} we examine how the $w$ constraint depends on the number of mocks used to estimate the covariance, and we find good agreement with \citep{DodelsonSchneider13}.
-We determine the effective dimensionality of the feature space, $D$, with a linear regression using equation (\ref{ourscaling}) and we find that this depends strongly on how the noise is distributed across the covariance matrix estimator $\bbh{C}$.
-In particular we find that when every element in the covariance is subject to noise $D$ is close to the number of bands used $N_b=15$, but when we artificially zero out the off diagonal elements of $\bbh{C}$, the effective dimensionality drops to $D\approx2.5$.
-Finally, Figure \ref{wvar_ns} shows the dependence of the dark energy constraint with $N_s$ and $D$.
-We find that, in the range $N_s\in[1,200]$ the $w$ inferred variance has sub--percent fluctuations for both the diagonal and full $\bbh{C}$ cases, while there is a $\sim$10\% change in $\sigma^2_0(N_s,w)$ when the effective dimensionality $D$ is different.
-Finally, the different lines in Figure \ref{wvar_ns} show that equation (\ref{ourscaling}) is a good model for the variance scaling.
+In Figure \ref{wvar_nr} we examine how the $w$ constraint depends on the number of mocks used to estimate the covariance, and we find good agreement with (\ref{ourscaling}).
+In particular we can see that one $N$--body simulation is enough to construct an ensemble of $O(10^5)$ mutually independent mock power spectra, for which the $w$ constraint scales like $1/N_r$ all the way to $N_r=10^5$.
+
+Figure \ref{wvar_ns} shows the dependence of the dark energy constraint with $N_s$.
+We find that, in the range $N_s\in[1,200]$ the $w$ inferred variance $\sigma_0^2$ fluctuates stochastically and does not show an appreciable trend with $N_s$.
+
+We determine the effective dimensionality of the feature space, $D$, with a linear regression using equation (\ref{ourscaling}), for the set of features outlined in Table \ref{featuretable}.
+The results shown in Figure \ref{effectivenb}, however, show that the feature dimensionality $D$ grows faster than the linear $O(N_b)$ optimistic case predicted by \citep{DodelsonSchneider13}.
+When we estimate the real data covariance $\bb{C}$ from the same simulation set used to measure $\bbh{C}$, the effective dimensionality $D$ shows the expected behavior.
+More in detail, the toy models (\ref{mockscalinguncorrected}) and (\ref{mockscalingcorrected}) tell us that when we do not correct for the bias in the $\bbh{\Psi}$ estimator the effective dimensionality is negative (assuming $N_b>N_p$) and the parameter variance is underestimated when $N_r$ is not large enough.
+This explains what \citep{MinkPetri} observe in their Figures 7,8.
 
@@
 \begin{itemize}
-\item The variance scaling relation proposed by \citep{DodelsonSchneider13} is a good approximation regardless of $N_s$
-\item The fluctuations in the $w$ forecasted variance due to varying $N_s$ are sub--percent, and this effect is sub--dominant with respect of varying the effective dimensionality of the feature space, which in the end is controlled by how the noise is distributed in the covariance estimator
+\item We can recycle a single $N$--body simulation to produce an ensemble of $O(10^5)$ independent maps.
+The mean feature measured from a shear ensemble, though, could be inaccurate if only one $N$--body simulation is used.
+\item The $1/N_r$ scaling for the dark energy constraint has been verified in our simulations, but the effective dimensionality $D$, that regulates the degradation of the error bars, grows faster than the $O(N_b)$ that \citep{DodelsonSchneider13} predicted.
+\item The fluctuations in the $w$ forecasted variance do not exibit an appreciable trend with $N_s$ 
 \end{itemize}

### 2015-11-20 Paper/Figures/generate.py

@@ -152,6 +152,23 @@ def scaling_ns(cmd_args,db_filename="variance_scaling_nb_expected.sqlite",featur
 	#Plot panel
 	fig,ax = plt.subplots()
 
+	#Labels
+	labels = {
+	"power_logb_large" : None,
+	"power_logb_small" : None,
+	"power_logb_all" : "Power spectrum log binning",
+	"power_large" : None,
+	"power_small" : None,
+	"power_large+small" : None,
+	"power_all" : "Power spectrum linear binning",
+	"peaks_low" : None,
+	"peaks_intermediate" : None,
+	"peaks_high" : None,
+	"peaks_low+intermediate" : None,
+	"peaks_intermediate+high" : None,
+	"peaks_all" : "Peak counts",
+	} 
+
 	#Load the database and fit for the effective dimensionality of each feature space
 	with Database("data/"+db_filename) as db:
 		nb_fit = algorithms.fit_nbins_all(db,parameter)
@@ -159,18 +176,19 @@ def scaling_ns(cmd_args,db_filename="variance_scaling_nb_expected.sqlite",featur
 	#Plot the variance coefficient for each feature
 	for nc,f in enumerate(features):
 		nb_fit_feature = nb_fit.query("feature=='{0}'".format(f)).sort_values("nsim")
-		nb_fit_feature["relative"] = nb_fit_feature["s0"] / nb_fit_feature["s0"].iloc[0] 
-		nb_fit_feature.plot(x="nsim",y="relative",ax=ax,color=colors[nc],legend=False)
+		nb_fit_feature["relative"] = nb_fit_feature["s0"] / nb_fit_feature["s0"].mean() 
+		nb_fit_feature.plot(x="nsim",y="relative",ax=ax,color=colors[nc],label=labels[f],legend=False)
 
 	#Labels
 	ax.set_xlabel(r"$N_s$",fontsize=fontsize)
-	ax.set_ylabel(r"$\sigma_0^2(N_s)/\sigma_0^2(1)$",fontsize=fontsize)
+	ax.set_ylabel(r"$\sigma_0^2(N_s)/\sigma_{0,mean}^2$",fontsize=fontsize)
+	ax.legend()
 
 	#Save
 	fig.savefig("scaling_ns."+cmd_args.type)
 
 #Scaling of the effective dimensionality with Nb
-def effective_nb(cmd_args,db_filename="variance_scaling_nb_expected.sqlite",parameter="w",fontsize=22):
[…]

### 2015-11-22 Paper/paper.tex
finalized second draft

@@
 Using the shear--shear power spectrum as a summary statistic, we find that a single $N$--body simulation can be recycled a large number of times to produce an ensemble of $N_r=10^5$ shear realizations that are mutually independent.
-We also find that, for a range of summary statistics that include shear--shear power spectra measured at different scales and convergence peak counts, parameter constraints degrade faster than the $O(N_b)$ Gaussian prediction by \citep{DodelsonSchneider13}, where $N_b$ is the length of the feature vector.
+We also find that, for a range of summary statistics that include shear--shear power spectra measured at different scales and convergence peak counts, parameter constraints degrade faster than the $O(N_b)$ prediction by \citep{DodelsonSchneider13}, where $N_b$ is the length of the feature vector.
 \end{abstract}
@@
 We then apply the multi--lens--plane algorithm (see \citep{RayTracingHartlap,RayTracingJain} for example) to trace the deflections of $2048^2$ light rays arranged on a square grid of total size $\theta_{box}$, from $z=0$ to $z_s$.
-The light deflection calculations have been performed with our implementation of multi--lens--plane algorithm, which is part of the \texttt{LensTools} computing package \citep{LensTools} (released under the MIT license).
+The light deflection calculations have been performed with our implementation of multi--lens--plane algorithm, which is part of the \texttt{LensTools} computing package \citep{LensTools} (released under the \texttt{MIT} license).
 Different realizations $r$ of the same shear field $\pmb{\gamma}_r(\pmb{\theta})$ can be generated with different choices of the lenses that lay between the observer and $z_s$.
@@
 
-\subsection{Parameter inference}
-%
-Let $\bbh{d}$ be the measured feature of dimension $N_b$, $\bb{d}(\bb{p})$ be the simulated feature at a point $\bb{p}$ in parameter space (which has a dimension $N_p$) and $\bb{C}$ be the $N_b\times N_b$ feature covariance matrix.
-For the purpose of this work $\bb{p}$ is the triplet $(\Omega_m,w,\sigma_8)$ and $\bb{d}$ is the convergence power spectrum $P^{\kappa\kappa}$, which is measured at $N_b=15$ log--spaced bands between $l\in[100,6000]$.
-While $d_M(\bb{p})$ can usually be predicted reasonably accurately by already existing emulators (see \citep{coyote2,Nicaea} for example), the matter is more complicated for covariance matrices.
-Measuring $\bb{C}$ from simulations involves generating a series of mock realizations $\bbh{d}_r$ with $r=1...N_r$ and estimating the sample covariance $\bbh{C}$
-
-\begin{equation}
-\bb{\bar{d}} = \frac{1}{N_r}\sum_{r=1}^{N_r} \bbh{d}_r
-\end{equation}
-
-\begin{equation}
-\label{covest}
-\bbh{C} = \frac{1}{N_r-1}\sum_{r=1}^{N_r} (\bbh{d}_r - \bar{\bb{d}}) (\bbh{d}_r - \bar{\bb{d}})^T
-\end{equation}
-%
-Assuming a normal feature likelihood, together with a flat prior on the parameter space, the parameter posterior distribution $\mathcal{L}(\bb{p}\vert\bbh{d})$ can be obtained using Bayes theorem
-\begin{equation}
-\label{posteriorbayes}
-\mathcal{L}(\bb{p}\vert\bbh{d}) = \mathcal{N}_\mathcal{L}\exp{\left[-\frac{1}{2}(\bbh{d}-\bb{d}(\bb{p}))^T\bb{C}^{-1}(\bbh{d}-\bb{d}(\bb{p}))\right]}
-\end{equation}
-%
-For the sake of simplicity, we approximate the posterior as a Gaussian around its maximum.
-This is easily done approximating the simulated feature at first order around a point $\bb{p}_0$ (that ideally is the maximum of (\ref{posteriorbayes}))
-\begin{equation}
-\bb{d}(\bb{p}) \approx \bb{d}_0 + \bb{d}_0^\prime(\bb{p}-\bb{p}_0) 
-\end{equation}
-%
-To measure the feature derivatives $\bb{d}'_0$ with respect to cosmology, we make use of the public code code NICAEA (see \citep{Nicaea}) for the power spectrum, and we use an independent simulation set (that contains mocks at different combinations of $(\Omega_m,w,\sigma_8)$) for the peak counts.
-We can build the estimator for the posterior location parameter $\bbh{p}$, given the observation $\bbh{d}$, as follows:
-%
-\begin{equation}
-\label{estimatormean}
-\bbh{p} = \bb{p}_0 + \bbh{T}(\bbh{d}-\bb{d}_0)
-\end{equation}
-
-\begin{equation}
-\bbh{T} = (\bb{d}_0'^T\bbh{C}^{-1}\bb{d}_0')^{-1}\bb{d}_0'^T\bbh{C}^{-1}
-\end{equation}
-%
-Defining the \textit{precision matrix} $\bbh{\Psi}=\bbh{C}^{-1}$, we can express the estimator of the parameter covariance as
-
-\begin{equation}
-\label{estimatorcovariance}
-\h{\Sigma}_\bb{p} = \bbh{F}^{-1}\bb{d}_0'^T\bbh{\Psi}\bb{C}\bbh{\Psi}\bb{d}_0'\bbh{F}^{-1}
-\end{equation}
-
-\begin{equation}
-\label{estimatorfisher}
-\bbh{F} = \bb{d}_0'^T\bbh{\Psi}\bb{d}_0'
-\end{equation}
-%
-Where we introduced the Fisher matrix estimator $\bbh{F} = \bb{d}_0'^T\bbh{\Psi}\bb{d}_0'$ and, for simplicity, we assumed $\langle\bbh{d}\rangle=\bb{d}_0$, so that $\langle(\bbh{d}-\bb{d}_0)(\bbh{d}-\bb{d}_0)^T\rangle=\bb{C}$.
-The noise in the covariance estimator (\ref{covest}) and its inverse $\bbh{\Psi}$ propagates all the way to the posterior (\ref{posteriorbayes}), the parameter estimate (\ref{estimatormean}) and its variance (\ref{estimatorcovariance}).
-Following \citep{Taylor12} we can say that, if the feature vector $\bbh{d}$ from which $\bbh{C}$ is estimated is drawn from a multivariate Gaussian distribution, the precision matrix estimator $\bbh{\Psi}$ is biased
-\begin{equation}
-\label{psibias}
-\langle\bbh{\Psi}\rangle = \frac{N_r-1}{N_r-N_b-2}\bb{\Psi}
-\end{equation}
-%
-and, once the bias is corrected, the residual fluctuations in $\bbh{\Psi}$ are correlated as follows
-\begin{equation}
-\label{psifluctuations}
-\langle\delta\h{\Psi}_{ij}\delta\h{\Psi}_{kl}\rangle = A\Psi_{ij}\Psi_{kl} + B(\Psi_{ik}\Psi_{jl} + \Psi_{il}\Psi_{jk})
-\end{equation}
-%
-where $A,B$ are constants that depend on $N_r,N_b$ and have the asymptotic behavior $A\propto1/N_r^2,B\propto1/N_r$.
-We want to estimate the effect of these fluctuations on the parameter constraints $\Sigma_\bb{p}$, following the guidelines of \citep{DodelsonSchneider13}.
-We consider three cases:
-\begin{itemize}
-\item If the true data covariance $\bb{C}$ is known, the estimator (\ref{estimatorcovariance}) is biased, and the dominant contribution of the bias comes from the second order fluctuations in $\bbh{\Psi}$.
-Once the expectation values are taken as in (\ref{psifluctuations}), the bias sums up to
-
-\begin{equation}
-\label{dodelsonscaling}
-\langle\h{\Sigma}_\bb{p}\rangle=\Sigma_\bb{p}(1+B(N_b-N_p))
-\end{equation}
-%
-This is the result obtained by \citep{DodelsonSchneider13}.
-\item If we are not interested in measuring the location parameter $\bbh{p}$, but just the width of the parameter posterior, we can tempted to replace the true covariance $\bb{C}$ with its estimator $\bbh{C}$.
-If we do that, and we do not correct for the bias (\ref{psibias}), the parameter variance will have a contribution from both the second and first order fluctuations in $\bbh{\Psi}$, which now have a non zero expectation value.
-In this case the bias sums up to
-\begin{equation}
-\label{mockscalinguncorrected}
-\langle\h{\Sigma}_\bb{p}\rangle=\Sigma_\bb{p}(1-(1+N_b)/N_r+B(1+N_p))
-\end{equation}
-\item If we repeat the same exercise as above, but we correct for the bias in the precision matrix estimator, we are left with
-
-\begin{equation}
-\label{mockscalingcorrected}
-\langle\h{\Sigma}_\bb{p}\rangle=\Sigma_\bb{p}(1+B(1+N_p))
-\end{equation}
-
-\end{itemize} 
-%
-In the three previous cases we only kept the terms of order $O(1/N_r)$.
-The last two examples have to be considered as academic exercises, as in a real experiment the data has to be used in the end to compute the posterior location parameter and the parameter covariance.
-With the $\bbh{d}$ Gaussianity assumption, the coefficient $B$ can be calculated exactly as \citep{DodelsonSchneider13,Taylor12}:
-\begin{equation}
-B = \frac{N_r-N_b-2}{(N_r-N_b-1)(N_r-N_b-4)}
-\end{equation}
-%
-In the limit $N_r\gg N_b$ this leads to a degradation of order $D/N_r$ for the variance of each estimated parameter $\sigma^2_p=\Sigma_{pp}$. We test the scaling relation
-\begin{equation}
-\label{ourscaling}
-\langle\h{\sigma}_p^2\rangle = \sigma^2_p(N_s)\left(1+\frac{D}{N_r}\right)
-\end{equation}
-%
-on our simulations.
-We call $D$ the \textit{effective dimensionality} of the feature space which, under Gaussianity assumptions, is equal to $D=N_b-N_p$ in the case where the true covariance $\bb{C}$ is known, $D=N_p-N_b$ when the true precision matrix is replaced by its biased estimator (computed from the same simulation set) and $D=1+N_p$ when the $\bbh{\Psi}$ is corrected.
-
-We compute the expectation values of $\h{\sigma}^2_p$ (equations (\ref{estimatorcovariance}),(\ref{ourscaling})) averaging over 100 random resamplings of our shear ensembles.
-For the true feature covariance matrix $\langle(\bbh{d}-\bb{d}_0)(\bbh{d}-\bb{d}_0)^T\rangle=\bb{C}$ we use the estimated covariance from a grand ensemble built with the union of all the ensembles with different $N_s$.
-
-The true parameter variance $\sigma^2_p(N_s)$ in principle depends on the number of independent $N$--body simulations $N_s$, which appears in the randomization procedure we describe in \S~\ref{shearsim}.
-The reason for this can be found in that, if $N_s$ is not big enough, the different shear realizations cannot be all independent, and hence the true variance $\sigma^2_p(N_s\rightarrow\infty)$ cannot be recovered in the limit $N_r\rightarrow\infty$.
-In particular there could be some residual error in the expectation value of (\ref{estimatorcovariance}) even if $N_r$ is big.
-In the next paragraph we outline our main findings.
-
-%%%%%%%%%%%%%%%%%%% RESULTS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Results}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \caption{Effective dimesionality of the feature space, $D$, as a function of the number of bands $N_b$, for the features outlined in Table \ref{featuretable}.
-The dimensionality $D$ is plotted in units of its predicted value from equations (\ref{dodelsonscaling}) in the left panel, equation (\ref{mockscalinguncorrected}) in the center panel and equation (\ref{mockscalingcorrected}) in the right panel.}
+The solid black lines show the theory predictions from equations (\ref{dodelsonscaling}) in the left panel, equation (\ref{mockscalinguncorrected}) in the right panel and equation (\ref{mockscalingcorrected}) in the bottom panel.}
 \label{effectivenb}
 \end{figure*}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Parameter inference}
+%
+Let $\bbh{d}$ be the measured feature of dimension $N_b$, $\bb{d}(\bb{p})$ be the simulated feature at a point $\bb{p}$ in parameter space (which has a dimension $N_p$) and $\bb{C}$ be the $N_b\times N_b$ feature covariance matrix.
+For the purpose of this work $\bb{p}$ is the triplet $(\Omega_m,w,\sigma_8)$ and $\bb{d}$ is the convergence power spectrum $P^{\kappa\kappa}$, which is measured at $N_b=15$ log--spaced bands between $l\in[100,6000]$.
+While $d_M(\bb{p})$ can usually be predicted reasonably accurately by already existing emulators (see \citep{coyote2,Nicaea} for example), the matter is more complicated for covariance matrices.
+Measuring $\bb{C}$ from simulations involves generating a series of mock realizations $\bbh{d}_r$ with $r=1...N_r$ and estimating the sample covariance $\bbh{C}$
+
+\begin{equation}
+\bb{\bar{d}} = \frac{1}{N_r}\sum_{r=1}^{N_r} \bbh{d}_r
+\end{equation}
+
+\begin{equation}
+\label{covest}
+\bbh{C} = \frac{1}{N_r-1}\sum_{r=1}^{N_r} (\bbh{d}_r - \bar{\bb{d}}) (\bbh{d}_r - \bar{\bb{d}})^T
+\end{equation}
+%
+Assuming a normal feature likelihood, together with a flat prior on the parameter space, the parameter posterior distribution $\mathcal{L}(\bb{p}\vert\bbh{d})$ can be obtained using Bayes theorem
+\begin{equation}
+\label{posteriorbayes}
+\mathcal{L}(\bb{p}\vert\bbh{d}) = \mathcal{N}_\mathcal{L}\exp{\left[-\frac{1}{2}(\bbh{d}-\bb{d}(\bb{p}))^T\bb{C}^{-1}(\bbh{d}-\bb{d}(\bb{p}))\right]}
+\end{equation}
+%
+For the sake of simplicity, we approximate the posterior as a Gaussian around its maximum.
+This is easily done approximating the simulated feature at first order around a point $\bb{p}_0$ (that ideally is the maximum of (\ref{posteriorbayes}))
+\begin{equation}
+\bb{d}(\bb{p}) \approx \bb{d}_0 + \bb{d}_0^\prime(\bb{p}-\bb{p}_0) 
+\end{equation}
+%
+To measure the feature derivatives $\bb{d}'_0$ with respect to cosmology, we make use of the public code code NICAEA \citep{Nicaea} for the power spectrum, and we use an independent simulation set (that contains mocks at different combinations of $(\Omega_m,w,\sigma_8)$) for the peak counts.
+We can build the estimator for the posterior location parameter $\bbh{p}$, given the observation $\bbh{d}$, as follows:
+%
+\begin{equation}
+\label{estimatormean}
+\bbh{p} = \bb{p}_0 + \bbh{T}(\bbh{d}-\bb{d}_0)
+\end{equation}
+
+\begin{equation}
+\bbh{T} = (\bb{d}_0'^T\bbh{C}^{-1}\bb{d}_0')^{-1}\bb{d}_0'^T\bbh{C}^{-1}
+\end{equation}
+%
+Defining the \textit{precision matrix} $\bbh{\Psi}=\bbh{C}^{-1}$, we can express the estimator of the parameter covariance as
+
+\begin{equation}
+\label{estimatorcovariance}
+\h{\Sigma}_\bb{p} = \bbh{F}^{-1}\bb{d}_0'^T\bbh{\Psi}\bb{C}\bbh{\Psi}\bb{d}_0'\bbh{F}^{-1}
+\end{equation}
+
+\begin{equation}
+\label{estimatorfisher}
+\bbh{F} = \bb{d}_0'^T\bbh{\Psi}\bb{d}_0'
+\end{equation}
+%
+Where we introduced the Fisher matrix estimator $\bbh{F} = \bb{d}_0'^T\bbh{\Psi}\bb{d}_0'$ and, for simplicity, we assumed $\langle\bbh{d}\rangle=\bb{d}_0$, so that $\langle(\bbh{d}-\bb{d}_0)(\bbh{d}-\bb{d}_0)^T\rangle=\bb{C}$.
+The noise in the covariance estimator (\ref{covest}) and its inverse $\bbh{\Psi}$ propagates all the way to the posterior (\ref{posteriorbayes}), the parameter estimate (\ref{estimatormean}) and its variance (\ref{estimatorcovariance}).
+Following \citep{Taylor12} we can say that, if the feature vector $\bbh{d}$ from which $\bbh{C}$ is estimated is drawn from a multivariate Gaussian distribution, the precision matrix estimator $\bbh{\Psi}$ is biased
+\begin{equation}
+\label{psibias}
+\langle\bbh{\Psi}\rangle = \frac{N_r-1}{N_r-N_b-2}\bb{\Psi}
+\end{equation}
+%
+and, once the bias is corrected, the residual fluctuations in $\bbh{\Psi}$ are correlated as follows
+\begin{equation}
+\label{psifluctuations}
+\langle\delta\h{\Psi}_{ij}\delta\h{\Psi}_{kl}\rangle = A\Psi_{ij}\Psi_{kl} + B(\Psi_{ik}\Psi_{jl} + \Psi_{il}\Psi_{jk})
+\end{equation}
+%
+where $A,B$ are constants that depend on $N_r,N_b$ and have the asymptotic behavior $A\propto1/N_r^2,B\propto1/N_r$.
+We want to estimate the effect of these fluctuations on the parameter constraints $\Sigma_\bb{p}$, following the guidelines of \citep{DodelsonSchneider13}.
+We consider three cases:
+\begin{itemize}
+\item If the true data covariance $\bb{C}$ is known, the estimator (\ref{estimatorcovariance}) is biased, and the dominant contribution of the bias comes from the second order fluctuations in $\bbh{\Psi}$.
+Once the expectation values are taken as in (\ref{psifluctuations}), the bias sums up to
+
+\begin{equation}
+\label{dodelsonscaling}
+\langle\h{\Sigma}_\bb{p}\rangle=\Sigma_\bb{p}(1+B(N_b-N_p))
+\end{equation}
+%
+This is the result obtained by \citep{DodelsonSchneider13}.
+
+\item If we are not interested in measuring the location parameter $\bbh{p}$, but just the width of the parameter posterior, we are tempted to estimate errorbars purely from simulations, replacing the true covariance $\bb{C}$ with its estimator $\bbh{C}$, measured from the same simulation set we use to compute $\bbh{\Psi}$.
+If we do that, and we do not correct for the bias (\ref{psibias}), the parameter variance will have a contribution from both the second and first order fluctuations in $\bbh{\Psi}$, which now have a non zero expectation value.
+In this case the bias sums up to
+\begin{equation}
+\label{mockscalinguncorrected}
+\langle\h{\Sigma}_\bb{p}\rangle=\Sigma_\bb{p}(1-(1+N_b)/N_r+B(1+N_p))
+\end{equation}
+
+\item If we repeat the same exercise as above, but we correct for the bias in the precision matrix estimator, we are left with
+
+\begin{equation}
+\label{mockscalingcorrected}
+\langle\h{\Sigma}_\bb{p}\rangle=\Sigma_\bb{p}(1+B(1+N_p))
+\end{equation}
+
+\end{itemize} 
+%
+The complete calculations that justify (\ref{dodelsonscaling}),(\ref{mockscalinguncorrected}) and (\ref{mockscalingcorrected}) are shown in the Appendix.
+The last two examples have to be considered as academic exercises, as in a real experiment the data $\bbh{d}$ and its covariance matrix regulate the scatter of the $\bbh{p}$ estimator.
+With the $\bbh{d}$ Gaussianity assumption, the coefficient $B$ can be calculated exactly as \citep{DodelsonSchneider13,Taylor12}, and tends to $1/N_r$ in the limit of $N_r\gg N_b$.
+This leads to a degradation of order $D/N_r$ for the variance of each estimated parameter $\sigma^2_p=\Sigma_{pp}$.
+We test the scaling relation
+\begin{equation}
+\label{ourscaling}
+\langle\h{\sigma}_p^2\rangle = \sigma^2_p(N_s)\left(1+\frac{D}{N_r}\right)
+\end{equation}
+%
+on our simulations.
+We call $D$ the \textit{effective dimensionality} of the feature space which, under Gaussianity assumptions, is equal to $D=N_b-N_p$ in the case where the true covariance $\bb{C}$ is known, $D=N_p-N_b$ when the true data covariance is replaced by its estimator (computed from the same simulation set) but the biased $\bbh{\Psi}$ estimator is used, and $D=1+N_p$ when the $\bbh{\Psi}$ bias is corrected.
+
+We compute the expectation values of $\h{\sigma}^2_p$ (equations (\ref{estimatorcovariance}),(\ref{ourscaling})) averaging over 100 random resamplings of our shear ensembles.
+For the true feature covariance matrix $\langle(\bbh{d}-\bb{d}_0)(\bbh{d}-\bb{d}_0)^T\rangle=\bb{C}$ we use the estimated covariance from a grand ensemble built with the union of all the ensembles with different $N_s$.
+
+The true parameter variance $\sigma^2_p(N_s)$ in principle depends on the number of independent $N$--body simulations $N_s$, which appears in the randomization procedure we describe in \S~\ref{shearsim}.
+The reason for this can be found in that, if $N_s$ is not big enough, the different shear realizations cannot be all independent, and hence the true variance $\sigma^2_p(N_s\rightarrow\infty)$ cannot be recovered in the limit $N_r\rightarrow\infty$.
+In particular there could be some residual error in the expectation value of (\ref{estimatorcovariance}) even if $N_r$ is big.
+In the next paragraph we outline our main findings.
+
+%%%%%%%%%%%%%%%%%%% RESULTS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Results}
 
@@
 \bibliography{ref}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%% APPENDIX %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section*{Appendix: scaling of the effective dimensionality}
+\label{appendix}
+
+The goal of this appendix is giving a derivation of (\ref{dodelsonscaling}),(\ref{mockscalinguncorrected}) and (\ref{mockscalingcorrected}) following the guidelines from \citep{DodelsonSchneider13,Taylor12}.
+First consider the case in which we use the same simulation set to estimate $\bb{C},\bbh{\Psi}$: in this case equation (\ref{estimatorcovariance}) reduces to the inverse Fisher estimator $\h{\Sigma}_\bb{p}=\bbh{F}^{-1}$.
+If we write $\bbh{F}=\bb{F}+\delta\bbh{F}=\bb{F}+\bb{d}_0'^T\delta\bbh{\Psi}\bb{d}_0'$, and expand at second order in the fluctuations we get
+
+\begin{equation}
+\h{\Sigma}_\bb{p} = \bb{F}^{-1} + \bb{F}^{-1}\left(- \delta{\bbh{F}}+ \delta{\bbh{F}}\bb{F}^{-1}\delta{\bbh{F}}\right)\bb{F}^{-1}  
+\end{equation}  
+%
+If we use the precision estimator $\bbh{\Psi}=\bb{\Psi}+\delta\bbh{\Psi}$ and do not correct for the bias (\ref{psibias}), we have to use the facts that
+\begin{equation}
+\begin{matrix}
+& \langle\delta\bbh{\Psi}\rangle = \frac{1+N_b}{N_r-N_b-2}\bb{\Psi} \\ \\
+& \langle\delta\h{\Psi}_{ij}\delta\h{\Psi}_{kl}\rangle = \frac{A([N_r-1)^2+(1+N_b)^2]\Psi_{ij}\Psi_{kl} + B(N_r-1)^2(\Psi_{ik}\Psi_{kl}+\Psi_{il}\Psi_{jk})}{(N_r-N_b-2)^2}
+\end{matrix}
+\end{equation}
+%
+Keeping only the leading order $O(1/N_r)$ in the expansion we get the results
+\begin{equation}
+\label{explanationuncorrected}
+\begin{matrix}
+& \langle\delta\bbh{F}\rangle = \left(\frac{1+N_b}{N_r}\right)\bb{F} \\ \\
+& \langle\delta{\bbh{F}}\bb{F}^{-1}\delta{\bbh{F}}\rangle = B(1+N_p)\bb{F}
+\end{matrix}
+\end{equation}
+%
+which leads immediately to (\ref{mockscalinguncorrected}).
+Now suppose we correct for the bias in the precision estimator, and use the unbiased $\bbh{\Psi}$ for which $\delta\bbh{\Psi}=0$.
+This leads to equation (\ref{psifluctuations}) for the quadratic fluctuations in the precision matrix, and to the same (\ref{explanationuncorrected}), except for $\langle\delta\bbh{F}\rangle=0$.
+This leads to (\ref{mockscalingcorrected}).
+If now we keep $\bb{C}$ fixed and we estimate only $\bbh{\Psi}$ from the simulations, we get
+\begin{equation}
+\label{tempcovarianceestimate}
+\h{\Sigma}_\bb{p} = (\bbh{F}+\delta\bbh{F})^{-1}\bb{d}_0'^T(\bbh{\Psi}+\delta\bbh{\Psi})\bb{C}(\bbh{\Psi}+\delta\bbh{\Psi})\bb{d}_0'(\bbh{F}+\delta\bbh{F})^{-1}
+\end{equation}
+%
+If we isolate the second order terms in (\ref{tempcovarianceestimate}), the result is 
+\begin{equation}
+\h{\Sigma}_\bb{p}\vert_2 = \bb{F}^{-1}(\bb{d}_0'^T\delta\bbh{\Psi}\bb{C}\delta\bbh{\Psi}\bb{d}_0'-\delta{\bbh{F}}\bb{F}^{-1}\delta{\bbh{F}})\bb{F}^{-1}
+\end{equation} 
+%
+The expectation values of the quadratic fluctuations are easily computed using (\ref{psifluctuations}):
+\begin{equation}
+\begin{matrix}
+& \langle\bb{d}_0'^T\delta\bbh{\Psi}\bb{C}\delta\bbh{\Psi}\bb{d}_0'\rangle = B(1+N_b)\bb{F} \\ \\
+& \langle\delta{\bbh{F}}\bb{F}^{-1}\delta{\bbh{F}}\rangle = B(1+N_p)\bb{F}
+\end{matrix}
+\end{equation}
+%
+From which (\ref{dodelsonscaling}) immediately follows. 
 \label{lastpage}

### 2015-11-22 Paper/Figures/generate.py

@@ -188,7 +188,7 @@ def scaling_ns(cmd_args,db_filename="variance_scaling_nb_expected.sqlite",featur
 	fig.savefig("scaling_ns."+cmd_args.type)
 
 #Scaling of the effective dimensionality with Nb
-def effective_nb(cmd_args,db_filename="variance_scaling_nb_expected.sqlite",parameter="w",correct=False,evaluate="nb/(bins-3)",ylabel=r"$D/(N_b-N_p)$",fontsize=22,figname="effective_nb"):
+def effective_nb(cmd_args,db_filename="variance_scaling_nb_expected.sqlite",parameter="w",correct=False,evaluate=lambda nb:nb-3,th_label=r"$N_b-N_p$",fontsize=22,figname="effective_nb"):
 
 	#Plot panel
 	fig,ax = plt.subplots()
@@ -272,17 +272,19 @@ def effective_nb(cmd_args,db_filename="variance_scaling_nb_expected.sqlite",para
 		features = db.tables
 		nb_fit = algorithms.fit_nbins_all(db,parameter,correct=correct)
 
-	#Calculate the relative dimensionality
-	nb_fit["relative"] = nb_fit.eval(evaluate)
-
 	#Scatter each feature
 	for f in features:
 		nb_fit_feature = nb_fit.query("feature=='{0}'".format(f))
-		ax.scatter(nb_fit_feature["bins"]+offsets[f],nb_fit_feature["relative"],color=colors[f],marker=markers[f],s=10+(100-10)*(nb_fit_feature["nsim"]-1)/(200-1),label=labels[f])
+		ax.scatter(nb_fit_feature["bins"]+offsets[f],nb_fit_feature["nb"],color=colors[f],marker=markers[f],s=10+(100-10)*(nb_fit_feature["nsim"]-1)/(200-1),label=labels[f])
+
+	#Plot the theory prediction
+	bins = np.arange(1,51)
+	ax.plot(bins,evaluate(bins),color="black",linewidth=2,label=th_label)
 
 	#Axis labels
+	ax.set_xlim(0,53)
 	ax.set_xlabel(r"$N_b$",fontsize=fontsize)
-	ax.set_ylabel(ylabel,fontsize=fontsize)
+	ax.set_ylabel(r"$D$",fontsize=fontsize)
 	ax.legend(loc="upper left",prop={"size":15})
 
 	#Save the figure
[…]

### 2015-11-23 code/analysis/variance_scaling_power_gaussian.py
added numerical experiment in which the power spectrum ensembles is sampled from a gaussian

@@ -1,0 +1,121 @@
+#!/usr/bin/env python
+from __future__ import division
+import gc
+
+from lenstools.statistics.database import Database
+from lenstools.statistics.ensemble import Series,Ensemble
+from lenstools.statistics.constraints import FisherAnalysis,Emulator
+
+import numpy as np
+
+import algorithms
+
+###########################
+######Main execution#######
+###########################
+
+#Number of simulations to test
+nsim = [1,2,5,10,20,30,40,50,60,70,80,90,100,150,200]
+nreal = np.arange(100,1100,100)
+resample = 100
+
+def main():
+
+	############################################################
+	####Constraints from the power spectrum (linear binning)####
+	############################################################
+
+	#Load the emulator
+	emulator = Emulator.read("../../data/emulators/emulator_power_fine_nb39.pkl")
+	num_ell = np.load("../../Om0.260_Ol0.740_w-1.000_ns0.960_si0.800/512b240/ell_nb39.npy")
+	feature_columns = emulator[emulator.feature_names].columns
+
+	#Large and small scales
+	scales = {
+	"large" : filter(lambda s:int(s.strip("l")) in range(15),emulator[emulator.feature_names[0]].columns),
+	"small" : filter(lambda s:int(s.strip("l")) in range(15,30),emulator[emulator.feature_names[0]].columns),
+	"large+small" : filter(lambda s:int(s.strip("l")) in range(30),emulator[emulator.feature_names[0]].columns),
+	"all" : list(emulator[emulator.feature_names[0]].columns),
+	}
+
+	#Fiducial cosmology
+	fiducial_parameters = Series(np.array([0.26,-1.0,0.8]),index=["Om","w","sigma8"])
+
+	#Load in the feature Ensemble, and bootstrap the covariance using a different number of realizations
+	with Database("../../data/variance_scaling_gaussian_expected.sqlite") as db:
+
+		#This is the true covariance matrix
+		true_covariance = Ensemble(np.diag((emulator.predict(fiducial_parameters).values**2)/num_ell),index=emulator.columns,columns=emulator.columns)
+	
+		for s in scales:
+
+			#Log
+			table_name = "power_" + s
+			print("[+] Populating table {0}...".format(table_name))
+
+			#Approximate the emulator linearly around the fiducial model
[…]

### 2015-11-23 code/analysis/variance_scaling_power_gaussian.py
debug

@@ -49,17 +49,21 @@ def main():
 	
 		for s in scales:
 
+			#Cut the number of bins
+			sub_feature_names = [(emulator.feature_names[0],fb) for fb in scales[s]]
+
 			#Log
 			table_name = "power_" + s
 			print("[+] Populating table {0}...".format(table_name))
 
 			#Approximate the emulator linearly around the fiducial model
 			fisher_scale = emulator.approximate_linear(fiducial_parameters,derivative_precision=0.01).features({emulator.feature_names[0]:scales[s]})
+			true_covariance_scale = true_covariance[sub_feature_names].loc[sub_feature_names]
 
 			for n in nsim:
 		
 				#Mock the power spectrum Ensemble drawing from a multivariate Gaussian
-				ensemble_nsim = Ensemble.sample_gaussian(true_covariance,realizations=1000,mean=emulator.predict(fiducial_parameters))
+				ensemble_nsim = Ensemble.sample_gaussian(true_covariance_scale,realizations=1000,mean=emulator.predict(fiducial_parameters)[sub_feature_names])
 
 				#Bootstrap ensemble_sim and compute the parameter variance for each resample
 				for nr in nreal:
@@ -67,7 +71,7 @@ def main():
 					gc.collect()
 
 					print("[+] Bootstraping scale={0}, Nb={1}, nsim={2}, nreal={3} with {4} resamples".format(s,ensemble_nsim.shape[1],n,nr,resample))
-					variance_ensemble = ensemble_nsim.bootstrap(algorithms.bootstrap_fisher,bootstrap_size=nr,resample=resample,assemble=lambda l:Ensemble.concat(l,ignore_index=True),fisher=fisher_scale,true_covariance=true_covariance,extra_items={"nsim":n,"nreal":nr,"bins":ensemble_nsim.shape[1]})
+					variance_ensemble = ensemble_nsim.bootstrap(algorithms.bootstrap_fisher,bootstrap_size=nr,resample=resample,assemble=lambda l:Ensemble.concat(l,ignore_index=True),fisher=fisher_scale,true_covariance=true_covariance_scale,extra_items={"nsim":n,"nreal":nr,"bins":ensemble_nsim.shape[1]})
 					db.insert(Ensemble(variance_ensemble.mean()).T,table_name=table_name)
 
 
@@ -89,8 +93,14 @@ def main():
 
 	#Load in the feature Ensemble, and bootstrap the covariance using a different number of realizations
[…]

### 2015-11-23 code/analysis/variance_scaling_power_gaussian.py
debug

@@ -45,7 +45,7 @@ def main():
 	with Database("../../data/variance_scaling_gaussian_expected.sqlite") as db:
 
 		#This is the true covariance matrix
-		true_covariance = Ensemble(np.diag((emulator.predict(fiducial_parameters).values**2)/num_ell),index=emulator.columns,columns=emulator.columns)
+		true_covariance = Ensemble(np.diag((emulator.predict(fiducial_parameters).values**2)/num_ell),index=feature_columns,columns=feature_columns)
 	
 		for s in scales:
 
@@ -95,7 +95,7 @@ def main():
 	with Database("../../data/variance_scaling_gaussian_expected.sqlite") as db:
 
 		#This is the true covariance matrix
-		true_covariance = Ensemble(np.diag((emulator.predict(fiducial_parameters).values**2)/num_ell),index=emulator.columns,columns=emulator.columns)
+		true_covariance = Ensemble(np.diag((emulator.predict(fiducial_parameters).values**2)/num_ell),index=feature_columns,columns=feature_columns)
 	
 		for s in scales:
 

### 2015-11-23 code/analysis/variance_scaling_power_gaussian.py
debug

@@ -4,7 +4,7 @@ import gc
 
 from lenstools.statistics.database import Database
 from lenstools.statistics.ensemble import Series,Ensemble
-from lenstools.statistics.constraints import FisherAnalysis,Emulator
+from lenstools.statistics.constraints import Emulator
 
 import numpy as np
 
@@ -80,7 +80,7 @@ def main():
 	###########################################################
 
 	#Load the emulator
-	emulator = FisherAnalysis.read("../../data/emulators/emulator_power_fine.pkl")
+	emulator = Emulator.read("../../data/emulators/emulator_power_fine.pkl")
 	num_ell = np.load("../../Om0.260_Ol0.740_w-1.000_ns0.960_si0.800/512b240/ell.npy")
 	feature_columns = emulator[emulator.feature_names].columns
 
@@ -107,7 +107,7 @@ def main():
 			print("[+] Populating table {0}...".format(table_name))
 
 			#Approximate the emulator linearly around the fiducial model
-			fisher_scale = emulator.features({emulator.feature_names[0]:scales[s]})
+			fisher_scale = emulator.approximate_linear(fiducial_parameters,derivative_precision=0.01).features({emulator.feature_names[0]:scales[s]})
 			true_covariance_scale = true_covariance[sub_feature_names].loc[sub_feature_names]
 
 			for n in nsim:

### 2015-11-23 Paper/Figures/generate.py
compare effective dimensionality only in Gaussian case

@@ -291,11 +291,8 @@ def effective_nb(cmd_args,db_filename="variance_scaling_nb_expected.sqlite",para
 	fig.savefig(".".join([figname,cmd_args.type]))
 
 
-def effective_nb_fake_uncorrected(cmd_args):
-	effective_nb(cmd_args,db_filename="variance_scaling_nb_fake.sqlite",parameter="w",correct=False,evaluate=lambda nb:3-nb,th_label=r"$N_p-N_b$",fontsize=22,figname="effective_nb_fake_uncorrected")
-
-def effective_nb_fake_corrected(cmd_args):
-	effective_nb(cmd_args,db_filename="variance_scaling_nb_fake.sqlite",parameter="w",correct=True,evaluate=lambda nb:np.ones_like(nb)*4,th_label=r"$1+N_p$",fontsize=22,figname="effective_nb_fake_corrected")
+def effective_nb_gaussian(cmd_args):
+	effective_nb(cmd_args,db_filename="variance_scaling_gaussian_expected.sqlite",parameter="w",correct=False,evaluate=lambda nb:nb-3,th_label=r"$N_b-N_p$",fontsize=22,figname="effective_nb_gaussian")
 
 		
 ###########################################################################################################################################
@@ -307,8 +304,7 @@ method["2"] = ps_variance
 method["3"] = scaling_nr
 method["4"] = scaling_ns
 method["5a"] = effective_nb
-method["5b"] = effective_nb_fake_uncorrected
-method["5c"] = effective_nb_fake_corrected
+method["5b"] = effective_nb_gaussian
 
 #Main
 def main():

### 2015-11-23 Paper/paper.tex
updated figure 5

@@
 \includegraphics[scale=0.3]{Figures/effective_nb.eps}
-\includegraphics[scale=0.3]{Figures/effective_nb_fake_uncorrected.eps}
-\includegraphics[scale=0.3]{Figures/effective_nb_fake_corrected.eps}
-\caption{Effective dimesionality of the feature space, $D$, as a function of the number of bands $N_b$, for the features outlined in Table \ref{featuretable}.
-The solid black lines show the theory predictions from equations (\ref{dodelsonscaling}) in the left panel, equation (\ref{mockscalinguncorrected}) in the right panel and equation (\ref{mockscalingcorrected}) in the bottom panel.}
+\includegraphics[scale=0.3]{Figures/effective_nb_gaussian.eps}
+\caption{Effective dimesionality of the feature space, $D$, as a function of the number of bands $N_b$, for the features outlined in Table \ref{featuretable}.}
 \label{effectivenb}
@@
 & \langle\delta\bbh{\Psi}\rangle = \frac{1+N_b}{N_r-N_b-2}\bb{\Psi} \\ \\
-& \langle\delta\h{\Psi}_{ij}\delta\h{\Psi}_{kl}\rangle = \frac{A([N_r-1)^2+(1+N_b)^2]\Psi_{ij}\Psi_{kl} + B(N_r-1)^2(\Psi_{ik}\Psi_{kl}+\Psi_{il}\Psi_{jk})}{(N_r-N_b-2)^2}
+& \langle\delta\h{\Psi}_{ij}\delta\h{\Psi}_{kl}\rangle = \frac{A([(N_r-1)^2+(1+N_b)^2]\Psi_{ij}\Psi_{kl} + B(N_r-1)^2(\Psi_{ik}\Psi_{kl}+\Psi_{il}\Psi_{jk})}{(N_r-N_b-2)^2}
 \end{matrix}

### 2015-11-24 Paper/paper.tex
incorporated first batch of comments

@@
 The surface density on each lens is computed by projecting the three dimensional density measured from \texttt{Gadget2} snapshots.
-We then apply the multi--lens--plane algorithm (see \citep{RayTracingHartlap,RayTracingJain} for example) to trace the deflections of $2048^2$ light rays arranged on a square grid of total size $\theta_{box}$, from $z=0$ to $z_s$.
+We then apply the multi--lens--plane algorithm (see \citep{RayTracingHartlap,RayTracingJain} for example) to trace the deflections of $n_{ray}^2=2048^2$ light rays arranged on a square grid of total size $\theta_{box}$, from $z=0$ to $z_s$.
 The light deflection calculations have been performed with our implementation of multi--lens--plane algorithm, which is part of the \texttt{LensTools} computing package \citep{LensTools} (released under the \texttt{MIT} license).
@@
 \item Pick a lens redshift $z_l$, and select the snapshot at $z_l$ from the $i$--th $N$--body simulation at disposal, where $i$ is a random number in $[1,N_s]$
-\item Choose randomly a direction in $(\bb{n}_x,\bb{n}_y,\bb{n}_z)$: the lens plane will be pependicular to this direction
-\item Choose the cutting point of the plane in the snapshot: because the lenses are $80\mathrm{Mpc}/h=240/3\mathrm{Mpc}/h$ thick, we have 3 different possibilities for choosing the random cut point
+\item Choose randomly a direction between the three choices ${\bb{n}_x,\bb{n}_y,\bb{n}_z}$: the lens plane will be pependicular to this direction
+\item Choose the cutting point of the plane in the snapshot: because the lens thickness is 1/3 the size of the box, we can cut three different slices of the simulation box for each orientation ${\bb{n}_x,\bb{n}_y,\bb{n}_z}$
 \item Perform a periodical random shift of the lens plane along its two directions
@@
 \end{center}
-\caption{Catalog of feature types used in this work, along with the chosen number of bands and the plot legends for Figure \ref{effectivenb}.}
+\caption{Catalog of feature types used in this work, along with the chosen number of bands $N_b$ and the plot legends for Figure \ref{effectivenb}.}
 \label{featuretable}
@@
 \includegraphics[scale=0.3]{Figures/effective_nb_gaussian.eps}
-\caption{Effective dimesionality of the feature space, $D$, as a function of the number of bands $N_b$, for the features outlined in Table \ref{featuretable}.}
+\caption{Effective dimesionality of the feature space, $D$, as a function of the number of bands $N_b$, for the features outlined in Table \ref{featuretable}.
+The left panel shows the case in which the feature ensembles are measured from our shear simulations, while in the right panel these ensembles have been replaced by independent draws from a Gaussian multivariate distribution with mean computed from \texttt{NICAEA} and diagonal covariance from equation (\ref{gaussianvar}).
+The solid black lines show theory predictions.}
 \label{effectivenb}
@@
 %
-Let $\bbh{d}$ be the measured feature of dimension $N_b$, $\bb{d}(\bb{p})$ be the simulated feature at a point $\bb{p}$ in parameter space (which has a dimension $N_p$) and $\bb{C}$ be the $N_b\times N_b$ feature covariance matrix.
-For the purpose of this work $\bb{p}$ is the triplet $(\Omega_m,w,\sigma_8)$ and $\bb{d}$ is the convergence power spectrum $P^{\kappa\kappa}$, which is measured at $N_b=15$ log--spaced bands between $l\in[100,6000]$.
-While $d_M(\bb{p})$ can usually be predicted reasonably accurately by already existing emulators (see \citep{coyote2,Nicaea} for example), the matter is more complicated for covariance matrices.
-Measuring $\bb{C}$ from simulations involves generating a series of mock realizations $\bbh{d}_r$ with $r=1...N_r$ and estimating the sample covariance $\bbh{C}$
+Let $\bbh{d}$ a feature of dimension $N_b$, $\bb{d}(\bb{p})$ be the smooth expectation of this feature at a point $\bb{p}$ in parameter space (which has a dimension $N_p$) and $\bb{C}$ be the $N_b\times N_b$ feature covariance matrix.
+For the purpose of this work $\bb{p}$ is the triplet $(\Omega_m,w,\sigma_8)$ and $\bb{d}$ is one of the features listed in Table \ref{featuretable}.
+While, in some cases, $d(\bb{p})$ can usually be predicted reasonably accurately by already existing emulators (see \citep{coyote2,Nicaea} for example), the matter is more complicated for covariance matrices.
+Estimating $\bb{C}$ from simulations involves generating a series of mock realizations $\bbh{d}_r$ with $r=1...N_r$ and estimating the sample covariance $\bbh{C}$
 
@@
 %
-Assuming a normal feature likelihood, together with a flat prior on the parameter space, the parameter posterior distribution $\mathcal{L}(\bb{p}\vert\bbh{d})$ can be obtained using Bayes theorem
+Assuming a normal feature likelihood, together with a flat prior on the parameter space, the parameter posterior distribution $\mathcal{L}(\bb{p}\vert\bbh{d}_{obs})$ given an observed instance of $\bbh{d}$, which we call $\bbh{d}_{obs}$, can be obtained using Bayes theorem
 \begin{equation}
 \label{posteriorbayes}
-\mathcal{L}(\bb{p}\vert\bbh{d}) = \mathcal{N}_\mathcal{L}\exp{\left[-\frac{1}{2}(\bbh{d}-\bb{d}(\bb{p}))^T\bb{C}^{-1}(\bbh{d}-\bb{d}(\bb{p}))\right]}
+-2\log\mathcal{L}(\bb{p}\vert\bbh{d}_{obs}) = (\bbh{d}_{obs}-\bb{d}(\bb{p}))^T\bbh{C}^{-1}(\bbh{d}_{obs}-\bb{d}(\bb{p}))
 \end{equation}
@@
 %
-To measure the feature derivatives $\bb{d}'_0$ with respect to cosmology, we make use of the public code code NICAEA \citep{Nicaea} for the power spectrum, and we use an independent simulation set (that contains mocks at different combinations of $(\Omega_m,w,\sigma_8)$) for the peak counts.
-We can build the estimator for the posterior location parameter $\bbh{p}$, given the observation $\bbh{d}$, as follows:
+To measure the feature derivatives $\bb{d}'_0$ with respect to cosmology, we make use of the public code \texttt{NICAEA} \citep{Nicaea} for the power spectrum, and we use an independent simulation set (that contains mocks at different combinations of $(\Omega_m,w,\sigma_8)$) for the peak counts.
+We can build the estimator for the posterior maximum $\bbh{p}$, given the observation $\bbh{d}_{obs}$, as follows:
 %
@@
 \label{estimatormean}
-\bbh{p} = \bb{p}_0 + \bbh{T}(\bbh{d}-\bb{d}_0)
+\bbh{p} = \bb{p}_0 + \bbh{T}(\bbh{d}_{obs}-\bb{d}_0)
 \end{equation}
@@
 %
-Defining the \textit{precision matrix} $\bbh{\Psi}=\bbh{C}^{-1}$, we can express the estimator of the parameter covariance as
+Because $\bbh{p}$ is estimated using a noisy data instance $\bbh{d}_{obs}$, its estimate will be scattered around the true value $\langle\bbh{p}\rangle_O$.
+In the following we use the $\langle\rangle_O$ notation for expectation values taken with respect to observations, while we keep the notation $\langle\rangle$ for expectation values taken with respect to the simulations.
+Defining the \textit{precision matrix} $\bbh{\Psi}=\bbh{C}^{-1}$, we can express the estimator of the observational scatter in $\bbh{p}$
 
@@
 \label{estimatorcovariance}
-\h{\Sigma}_\bb{p} = \bbh{F}^{-1}\bb{d}_0'^T\bbh{\Psi}\bb{C}\bbh{\Psi}\bb{d}_0'\bbh{F}^{-1}
+\h{\Sigma}_\bb{p} = \bbh{F}^{-1}\bb{d}_0'^T\bbh{\Psi}\langle(\bbh{d}_{obs}-\bb{d}_0)(\bbh{d}_{obs}-\bb{d}_0)^T\rangle_O\bbh{\Psi}\bb{d}_0'\bbh{F}^{-1}
 \end{equation}
@@
 %
-Where we introduced the Fisher matrix estimator $\bbh{F} = \bb{d}_0'^T\bbh{\Psi}\bb{d}_0'$ and, for simplicity, we assumed $\langle\bbh{d}\rangle=\bb{d}_0$, so that $\langle(\bbh{d}-\bb{d}_0)(\bbh{d}-\bb{d}_0)^T\rangle=\bb{C}$.
+Where we introduced the Fisher matrix estimator $\bbh{F} = \bb{d}_0'^T\bbh{\Psi}\bb{d}_0'$ and, for simplicity, we assumed $\langle\bbh{d}_{obs}\rangle_O=\bb{d}_0$, so that $\langle(\bbh{d}_{obs}-\bb{d}_0)(\bbh{d}_{obs}-\bb{d}_0)^T\rangle_O=\bb{C}$.
+When we perform an observation $\bbh{d}_{obs}$, the parameter estimate $\bbh{p}$ is a random draw from a probability distribution with variance $\h{\Sigma}_\bb{p}$, which inherits noise from the simulations.
+In the following we review the method to compute $\langle\h{\Sigma}_\bb{p}\rangle$ \citep{DodelsonSchneider13,Taylor12}.
 The noise in the covariance estimator (\ref{covest}) and its inverse $\bbh{\Psi}$ propagates all the way to the posterior (\ref{posteriorbayes}), the parameter estimate (\ref{estimatormean}) and its variance (\ref{estimatorcovariance}).
-Following \citep{Taylor12} we can say that, if the feature vector $\bbh{d}$ from which $\bbh{C}$ is estimated is drawn from a multivariate Gaussian distribution, the precision matrix estimator $\bbh{\Psi}$ is biased
+Following \citep{Taylor12} we can say that, if the feature vector $\bbh{d}_r$ from which $\bbh{C}$ is estimated is drawn from a multivariate Gaussian distribution, the precision matrix estimator $\bbh{\Psi}$ is biased
 \begin{equation}
@@
 We consider three cases:
-\begin{itemize}
+\begin{enumerate}
 \item If the true data covariance $\bb{C}$ is known, the estimator (\ref{estimatorcovariance}) is biased, and the dominant contribution of the bias comes from the second order fluctuations in $\bbh{\Psi}$.
@@
 
-\item If we are not interested in measuring the location parameter $\bbh{p}$, but just the width of the parameter posterior, we are tempted to estimate errorbars purely from simulations, replacing the true covariance $\bb{C}$ with its estimator $\bbh{C}$, measured from the same simulation set we use to compute $\bbh{\Psi}$.
+\item Usually the true covariance is not known, and it is tempting to plug in its estimator $\bbh{C}$, measured from the same simulation set we use to compute $\bbh{\Psi}$.
+This approach has been used before in the literature (see \citep{MinkPetri,MinkShirasaki} for example).
 If we do that, and we do not correct for the bias (\ref{psibias}), the parameter variance will have a contribution from both the second and first order fluctuations in $\bbh{\Psi}$, which now have a non zero expectation value.
@@
 
-\end{itemize} 
+\end{enumerate} 
 %
 The complete calculations that justify (\ref{dodelsonscaling}),(\ref{mockscalinguncorrected}) and (\ref{mockscalingcorrected}) are shown in the Appendix.
-The last two examples have to be considered as academic exercises, as in a real experiment the data $\bbh{d}$ and its covariance matrix regulate the scatter of the $\bbh{p}$ estimator.
-With the $\bbh{d}$ Gaussianity assumption, the coefficient $B$ can be calculated exactly as \citep{DodelsonSchneider13,Taylor12}, and tends to $1/N_r$ in the limit of $N_r\gg N_b$.
-This leads to a degradation of order $D/N_r$ for the variance of each estimated parameter $\sigma^2_p=\Sigma_{pp}$.
+With the $\bbh{d}_r$ Gaussianity assumption, the coefficient $B$ can be calculated exactly as \citep{DodelsonSchneider13,Taylor12}, and tends to $1/N_r$ in the limit of $N_r\gg N_b$.
+This leads to a degradation of order $D/N_r$ for the variance of each estimated parameter $\sigma^2_p=\Sigma_{pp}$, where $D=N_b-N_p,N_p-N_b,1+N_p$ for cases 1,2,3 respectively.
+This means that, when parameter errors are estimated purely from simulations, and the same simulation set is used to estimate both $\bbh{C},\bbh{\Psi}$, these errors tend to decrease with $N_b$ (case 2), or at best remain constant (case 3), while the distribution of $\bbh{p}$ has still a variance that increases with $N_b$.
+This typically leads to underestimates in parameter errors.
 We test the scaling relation
@@
 on our simulations.
-We call $D$ the \textit{effective dimensionality} of the feature space which, under Gaussianity assumptions, is equal to $D=N_b-N_p$ in the case where the true covariance $\bb{C}$ is known, $D=N_p-N_b$ when the true data covariance is replaced by its estimator (computed from the same simulation set) but the biased $\bbh{\Psi}$ estimator is used, and $D=1+N_p$ when the $\bbh{\Psi}$ bias is corrected.
-
+We call $D$ the \textit{effective dimensionality} of the feature space.
 We compute the expectation values of $\h{\sigma}^2_p$ (equations (\ref{estimatorcovariance}),(\ref{ourscaling})) averaging over 100 random resamplings of our shear ensembles.
@@
 \label{gaussianvar}
-\mathrm{Var}(P^{\kappa\kappa}(l)) = \frac{P^{\kappa\kappa,2}(l)}{N(l)}
+\mathrm{Var}(P^{\kappa\kappa}(l)) = \frac{P^{\kappa\kappa,2}(l)}{N_{eff}(l)}
 \end{equation}
 %
-where $N(l)$ is the number of modes used to estimate the power spectrum at $l$.
-$N_l$ is measured from the Fourier trasformed image grid.
+where $N_{eff}(l)$ is the number of independent modes used to estimate the power spectrum at $l$.
+To measure $P^{\kappa\kappa}(l),N_{eff}(l)$, we compute the real Fourier transform of the pixelized map $\kappa_r(\pmb{\theta})$ with the FFT algorithm.
+Each Fourier pixel $(i_x,j_y)$ corresponds to a mode $(l_x,l_y)=2\pi(i_x,i_y)/\theta_{box}$, with $i_x=-n_{ray}/2,...,n_{ray}/2$ and $i_y=0,...,n_{ray}/2$.
+We count the number of pixels $N(l)$ that fall inside a multipole bin $(l_1,l_2)$.
+Because the $\kappa$ field is real, the modes $(\pm l_x,0)$ are not independent.
+If we let $N(l,l_y=0)$ be the number of non--independent modes, the mode counting for the variance should be corrected as
+
+\begin{equation}
+N_{eff}(l) = \frac{N^2(l)}{N(l)+N(l,l_y=0)}
+\end{equation}
+%
+We not that this correction is important at low $l$ only, where pixelization effects are more important. In other words $N_{eff}(l\gg2\pi/\theta_{box})\approx N(l)$.
+
 Figure \ref{wvar_nr} show the scaling of the expectation value of $\h{\sigma}_w^2$ with the number of mocks $N_r$ using the power spectrum and compare it with the known result obtained in \citep{DodelsonSchneider13} and expressed in equation (\ref{ourscaling}).
@@
 Finally Figure \ref{effectivenb} shows how the effective feature dimensionality $D$ depends on the number of bands $N_b$, for a variety of features and binning choices outlined in Table \ref{featuretable}.
+This behavior is compared with the one that we obtain when the power spectrum ensembles $P_r^{\kappa\kappa}$ are replaced with 1000 independent random samples from a multivariate Gaussian distribution with mean $P^{\kappa\kappa}(l)$ (computed with \texttt{NICAEA}) and diagonal covariance given by equation (\ref{gaussianvar}).
 
@@
 We determine the effective dimensionality of the feature space, $D$, with a linear regression using equation (\ref{ourscaling}), for the set of features outlined in Table \ref{featuretable}.
-The results shown in Figure \ref{effectivenb}, however, show that the feature dimensionality $D$ grows faster than the linear $O(N_b)$ optimistic case predicted by \citep{DodelsonSchneider13}.
-When we estimate the real data covariance $\bb{C}$ from the same simulation set used to measure $\bbh{C}$, the effective dimensionality $D$ shows the expected behavior.
-More in detail, the toy models (\ref{mockscalinguncorrected}) and (\ref{mockscalingcorrected}) tell us that when we do not correct for the bias in the $\bbh{\Psi}$ estimator the effective dimensionality is negative (assuming $N_b>N_p$) and the parameter variance is underestimated when $N_r$ is not large enough.
-This explains what \citep{MinkPetri} observe in their Figures 7,8.
+The results shown in Figure \ref{effectivenb}, however, show that the feature dimensionality $D$ grows faster than the linear $O(N_b)$ optimistic prediction by \citep{DodelsonSchneider13}.
+
+When we estimate the data covariance $\bb{C}$ from the same simulation set used to measure $\bbh{\Psi}$, the effective dimensionality $D$ decreases with increasing $N_b$ in the case where the $\bbh{\Psi}$ bias is corrected, and stays constant when this bias is corrected.
+This fact that should be taken into considerations when estimating parameter errors purely from simulations, as underestimations might occur.
 
@@
 The mean feature measured from a shear ensemble, though, could be inaccurate if only one $N$--body simulation is used.
-\item The $1/N_r$ scaling for the dark energy constraint has been verified in our simulations, but the effective dimensionality $D$, that regulates the degradation of the error bars, grows faster than the $O(N_b)$ that \citep{DodelsonSchneider13} predicted.
+\item The $1/N_r$ scaling for the dark energy constraint has been verified in our simulations, but the effective dimensionality $D$, that controls the degradation of the parameter error bars, grows faster than the $O(N_b)$ that \citep{DodelsonSchneider13} predicted.
 \item The fluctuations in the $w$ forecasted variance do not exibit an appreciable trend with $N_s$ 
@@
 %
-Future prospects of this work involve extending this analysis to more general feature spaces, such as the ones that characterize non--Gaussian statistics such as shear peaks and higher moments of $\kappa$ fields.
-In order to scale these considerations to future surveys such as LSST, it is necessary to see if our findinds hold when challenged by larger and higher resolutions $N$--body simulations.
+Future prospects of this work involve extending this analysis to more general feature spaces, such as the ones that characterize non--Gaussian statistics such as higher moments of $\kappa$ fields, Minkowski Functionals and higher order $\kappa$ correlators.
+In order to scale these considerations to future surveys such as LSST, it is necessary to see if our findinds hold when challenged by larger and higher resolution $N$--body simulations \citep{Qcontinuum}.
 

### 2015-11-24 Paper/Figures/generate.py

@@ -180,6 +180,7 @@ def scaling_ns(cmd_args,db_filename="variance_scaling_nb_expected.sqlite",featur
 		nb_fit_feature.plot(x="nsim",y="relative",ax=ax,color=colors[nc],label=labels[f],legend=False)
 
 	#Labels
+	ax.set_xlim(-10,210)
 	ax.set_xlabel(r"$N_s$",fontsize=fontsize)
 	ax.set_ylabel(r"$\sigma_0^2(N_s)/\sigma_{0,mean}^2$",fontsize=fontsize)
 	ax.legend()

### 2015-11-30 Paper/paper.tex
updated figure 5

@@
 Using the shear--shear power spectrum as a summary statistic, we find that a single $N$--body simulation can be recycled a large number of times to produce an ensemble of $N_r=10^5$ shear realizations that are mutually independent.
-We also find that, for a range of summary statistics that include shear--shear power spectra measured at different scales and convergence peak counts, parameter constraints degrade faster than the $O(N_b)$ prediction by \citep{DodelsonSchneider13}, where $N_b$ is the length of the feature vector.
 \end{abstract}
@@
 The fact that the ensemble of $N_r$ mocks is not completely independent if $N_s$ is not large enough can have an effect on the covariance estimators of $P^{\kappa\kappa},n(\kappa_0)$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure*}
-\includegraphics[scale=0.4]{Figures/ps_pdf.eps}
-\caption{PDF of the $\kappa$ power spectrum,$\mathcal{L}(P_l^{\kappa\kappa})$, at four selected multipoles $l=115,344,1349,5283$, for different shear ensembles constructed with $N_s=$1 (black), 2 (blue), 5 (green), 50 (red), 100 (purple).
-The thick black lines correspond to an ensemble generated with $N_s=1$ and $10^5$ mock realizations.}
-\label{ps_pdf}
-\end{figure*}
-
-\begin{figure}
-\includegraphics[scale=0.3]{Figures/ps_variance.eps}
-\caption{Variance of the $\kappa$ power spectrum as a function of the multipole $l$, in units of the expected gaussian variance from equation (\ref{gaussianvar}).
-The variance is measured from different shear ensembles with $N_s=$1 (black), 2 (blue), 5 (green), 10 (red), 50 (purple), 100 (orange).
-}
-\label{ps_var}
-\end{figure}
-
-\begin{figure}
-\includegraphics[scale=0.3]{Figures/scaling_nr.eps}
-\caption{Bias in the $w$ variance, $\langle\h{\sigma}^2_w\rangle$, as a function of the number of mock realizations $N_r$ used in the feature covariance estimator (\ref{covest}).
-Results for different mock ensembles generated with $N_s=$1 (black), 2 (blue), 5 (green), 50 (red), 100 (purple) are shown.
-The figure shows both the measured trends (solid lines) and their best fits according to equation (\ref{ourscaling}).
-The thick black line correspond to an ensemble generated with $N_s=1$ and $10^5$ mock realizations.
-}
-\label{wvar_nr}
-\end{figure}
-
-\begin{figure}
-\includegraphics[scale=0.3]{Figures/scaling_ns.eps}
-\caption{Variance on $w$ in the limit $N_r\rightarrow\infty$, varying the mock ensemble used to compute the covariance estimator (\ref{covest}).
-We show the dependence of $\sigma_0^2(N_s)$ in units of the mean over $N_s$, for the power spectrum logarithmically binned (black), the power spectrum linearly binned (red) and the peak counts (green).}
-\label{wvar_ns}
-\end{figure}
-
-\begin{table*}
-\begin{center}
-\begin{tabular}{ccccc}
-\toprule
-\textbf{Feature} &  \textbf{Specifications} & $N_b$ &  \textbf{Symbol} & \textbf{Color} \\ \hline \hline
-\midrule
-Power Spectrum, log binning  & $l \in [100,800] $ & 8 & $\times$ & black  \\ 
-Power Spectrum, log binning  & $l \in [1000,6000] $ & 7 & $\times$ & black  \\ 
-Power Spectrum, log binning  & $l \in [100,6000] $ & 15 & $\times$ & black  \\
-Power Spectrum, linear binning  & $l \in [100,2000] $ & 15 & \textcolor{red}{$+$} & \textcolor{red}{red}  \\ 
-Power Spectrum, linear binning  & $l \in [2500,4500] $ & 15 & \textcolor{red}{$\times$} & \textcolor{red}{red}  \\
-Power Spectrum, linear binning  & $l \in [100,4500] $ & 30 & \textcolor{red}{$\bullet$} & \textcolor{red}{red}  \\ 
-Power Spectrum, linear binning  & $l \in [100,6000] $ & 39 & \textcolor{red}{$\bullet$} & \textcolor{red}{red}  \\ \hline
-Low peaks  & $\kappa_0 \in [-0.06,0.09] $ & 15 & \textcolor{OliveGreen}{$+$} & \textcolor{OliveGreen}{green}  \\ 
-Intermediate peaks  & $\kappa_0 \in [0.1,0.27] $ & 15 & \textcolor{OliveGreen}{$\bigstar$} & \textcolor{OliveGreen}{green}  \\ 
-High peaks  & $\kappa_0 \in [0.28,0.45] $ & 15 & \textcolor{OliveGreen}{$\diamond$} & \textcolor{OliveGreen}{green}  \\
-Low+Intermediate peaks  & $\kappa_0 \in [-0.06,0.27] $ & 30 & \textcolor{OliveGreen}{$\times$} & \textcolor{OliveGreen}{green}  \\
-Intermediate+High peaks  & $\kappa_0 \in [0.1,0.45] $ & 30 & \textcolor{OliveGreen}{$\bullet$} & \textcolor{OliveGreen}{green}  \\
-All peaks  & $\kappa_0 \in [-0.06,0.45] $ & 45 & \textcolor{OliveGreen}{$\blacksquare$} & \textcolor{OliveGreen}{green}  \\ \hline
-\bottomrule
-\end{tabular}
-\end{center}
-\caption{Catalog of feature types used in this work, along with the chosen number of bands $N_b$ and the plot legends for Figure \ref{effectivenb}.}
-\label{featuretable}
-\end{table*}
-
-\begin{figure*}
-\includegraphics[scale=0.3]{Figures/effective_nb.eps}
-\includegraphics[scale=0.3]{Figures/effective_nb_gaussian.eps}
-\caption{Effective dimesionality of the feature space, $D$, as a function of the number of bands $N_b$, for the features outlined in Table \ref{featuretable}.
-The left panel shows the case in which the feature ensembles are measured from our shear simulations, while in the right panel these ensembles have been replaced by independent draws from a Gaussian multivariate distribution with mean computed from \texttt{NICAEA} and diagonal covariance from equation (\ref{gaussianvar}).
-The solid black lines show theory predictions.}
-\label{effectivenb}
-\end{figure*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure*}
+\includegraphics[scale=0.4]{Figures/ps_pdf.eps}
+\caption{PDF of the $\kappa$ power spectrum,$\mathcal{L}(P_l^{\kappa\kappa})$, at four selected multipoles $l=115,344,1349,5283$, for different shear ensembles constructed with $N_s=$1 (black), 2 (blue), 5 (green), 50 (red), 100 (purple).
+The thick black lines correspond to an ensemble generated with $N_s=1$ and $10^5$ mock realizations.}
+\label{ps_pdf}
+\end{figure*}
+
+\begin{figure}
+\includegraphics[scale=0.3]{Figures/ps_variance.eps}
+\caption{Variance of the $\kappa$ power spectrum as a function of the multipole $l$, in units of the expected gaussian variance from equation (\ref{gaussianvar}).
+The variance is measured from different shear ensembles with $N_s=$1 (black), 2 (blue), 5 (green), 10 (red), 50 (purple), 100 (orange).
+}
+\label{ps_var}
+\end{figure}
+
+\begin{figure}
+\includegraphics[scale=0.3]{Figures/scaling_nr.eps}
+\caption{Bias in the $w$ variance, $\langle\h{\sigma}^2_w\rangle$, as a function of the number of mock realizations $N_r$ used in the feature covariance estimator (\ref{covest}).
+Results for different mock ensembles generated with $N_s=$1 (black), 2 (blue), 5 (green), 50 (red), 100 (purple) are shown.
+The figure shows both the measured trends (solid lines) and their best fits according to equation (\ref{ourscaling}).
+The thick black line correspond to an ensemble generated with $N_s=1$ and $10^5$ mock realizations.
+}
+\label{wvar_nr}
+\end{figure}
+
+\begin{figure}
+\includegraphics[scale=0.3]{Figures/scaling_ns.eps}
+\caption{Variance on $w$ in the limit $N_r\rightarrow\infty$, varying the mock ensemble used to compute the covariance estimator (\ref{covest}).
+We show the dependence of $\sigma_0^2(N_s)$ in units of the mean over $N_s$, for the power spectrum logarithmically binned (black), the power spectrum linearly binned (red) and the peak counts (green).}
+\label{wvar_ns}
+\end{figure}
+
+\begin{table*}
+\begin{center}
+\begin{tabular}{ccccc}
+\toprule
+\textbf{Feature} &  \textbf{Specifications} & $N_b$ &  \textbf{Symbol} & \textbf{Color} \\ \hline \hline
+\midrule
+Power Spectrum, log binning  & $l \in [100,800] $ & 8 & $\times$ & black  \\ 
+Power Spectrum, log binning  & $l \in [1000,6000] $ & 7 & $\times$ & black  \\ 
+Power Spectrum, log binning  & $l \in [100,6000] $ & 15 & $\times$ & black  \\
+Power Spectrum, linear binning  & $l \in [100,2000] $ & 15 & \textcolor{red}{$+$} & \textcolor{red}{red}  \\ 
+Power Spectrum, linear binning  & $l \in [2500,4500] $ & 15 & \textcolor{red}{$\times$} & \textcolor{red}{red}  \\
+Power Spectrum, linear binning  & $l \in [100,4500] $ & 30 & \textcolor{red}{$\bullet$} & \textcolor{red}{red}  \\ 
+Power Spectrum, linear binning  & $l \in [100,6000] $ & 39 & \textcolor{red}{$\bullet$} & \textcolor{red}{red}  \\ \hline
+Low peaks  & $\kappa_0 \in [-0.06,0.09] $ & 15 & \textcolor{OliveGreen}{$+$} & \textcolor{OliveGreen}{green}  \\ 
+Intermediate peaks  & $\kappa_0 \in [0.1,0.27] $ & 15 & \textcolor{OliveGreen}{$\bigstar$} & \textcolor{OliveGreen}{green}  \\ 
+High peaks  & $\kappa_0 \in [0.28,0.45] $ & 15 & \textcolor{OliveGreen}{$\diamond$} & \textcolor{OliveGreen}{green}  \\
+Low+Intermediate peaks  & $\kappa_0 \in [-0.06,0.27] $ & 30 & \textcolor{OliveGreen}{$\times$} & \textcolor{OliveGreen}{green}  \\
+Intermediate+High peaks  & $\kappa_0 \in [0.1,0.45] $ & 30 & \textcolor{OliveGreen}{$\bullet$} & \textcolor{OliveGreen}{green}  \\
+All peaks  & $\kappa_0 \in [-0.06,0.45] $ & 45 & \textcolor{OliveGreen}{$\blacksquare$} & \textcolor{OliveGreen}{green}  \\ \hline
+\bottomrule
+\end{tabular}
+\end{center}
+\caption{Catalog of feature types used in this work, along with the chosen number of bands $N_b$ and the plot legends for Figure \ref{curvingnb}.}
+\label{featuretable}
+\end{table*}
+
+\begin{figure}
+\includegraphics[scale=0.3]{Figures/curving_nb.eps}
+\caption{Expectation value of the $w$ variance computed with equation (\ref{estimatorcovariance}) as a function of $1/N_r$, for the features outlined in Table \ref{featuretable}.
+The line width increases with the number of bands $N_b$ used for each feature.}
+\label{curvingnb}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 In this section we outline the main results of this work.
@@
 Figure \ref{wvar_ns} shows the effect of varying $N_s$ on the $w$ constraint.
-Finally Figure \ref{effectivenb} shows how the effective feature dimensionality $D$ depends on the number of bands $N_b$, for a variety of features and binning choices outlined in Table \ref{featuretable}.
-This behavior is compared with the one that we obtain when the power spectrum ensembles $P_r^{\kappa\kappa}$ are replaced with 1000 independent random samples from a multivariate Gaussian distribution with mean $P^{\kappa\kappa}(l)$ (computed with \texttt{NICAEA}) and diagonal covariance given by equation (\ref{gaussianvar}).
+Finally Figure \ref{curvingnb} shows....
 
@@
 We find that, in the range $N_s\in[1,200]$ the $w$ inferred variance $\sigma_0^2$ fluctuates stochastically and does not show an appreciable trend with $N_s$.
-
-We determine the effective dimensionality of the feature space, $D$, with a linear regression using equation (\ref{ourscaling}), for the set of features outlined in Table \ref{featuretable}.
-The results shown in Figure \ref{effectivenb}, however, show that the feature dimensionality $D$ grows faster than the linear $O(N_b)$ optimistic prediction by \citep{DodelsonSchneider13}.
 

### 2015-11-30 Paper/Figures/generate.py

@@ -16,6 +16,83 @@ parser = argparse.ArgumentParser()
 parser.add_argument("-t","--type",dest="type",default="png",help="format of the figure to save")
 parser.add_argument("fig",nargs="*")
 
+###################################################################################################
+
+##############################
+#Plot styles for each feature#
+##############################
+
+#Markers
+markers = {
+"power_logb_large" : "x",
+"power_logb_small" : "x",
+"power_logb_all" : "x",
+"power_large" : "+",
+"power_small" : "x",
+"power_large+small" : "o",
+"power_all" : "o",
+"peaks_low" : "+",
+"peaks_intermediate" : "*",
+"peaks_high" : "d",
+"peaks_low+intermediate" : "x",
+"peaks_intermediate+high" : "o",
+"peaks_all" : "s",
+} 
+
+#Colors
+colors = {
+"power_logb_large" : "black",
+"power_logb_small" : "black",
+"power_logb_all" : "black",
+"power_large" : "red",
+"power_small" : "red",
+"power_large+small" : "red",
+"power_all" : "red",
+"peaks_low" : "green",
+"peaks_intermediate" : "green",
+"peaks_high" : "green",
+"peaks_low+intermediate" : "green",
+"peaks_intermediate+high" : "green",
+"peaks_all" : "green",
+} 
+
+#Labels
+labels = {
+"power_logb_large" : "Power spectrum log binning",
+"power_logb_small" : None,
+"power_logb_all" : None,
+"power_large" : None,
+"power_small" : None,
+"power_large+small" : None,
+"power_all" : "Power spectrum linear binning",
+"peaks_low" : "Peak counts",
+"peaks_intermediate" : None,
+"peaks_high" : None,
+"peaks_low+intermediate" : None,
+"peaks_intermediate+high" : None,
+"peaks_all" : None,
+} 
+
+#Offsets
+offsets = {
+"power_logb_large" : 0,
+"power_logb_small" : 0,
+"power_logb_all" : 0,
+"power_large" : -0.5,
+"power_small" : -1,
+"power_large+small" : 0,
+"power_all" : 0,
+"peaks_low" : 0.5,
+"peaks_intermediate" : 1,
+"peaks_high" : 1.5,
+"peaks_low+intermediate" : 0.5,
+"peaks_intermediate+high" : 1,
+"peaks_all" : 0,
+}
+
+
+###################################################################################################
+
[…]

### 2015-11-30 Paper/paper.tex

@@
 The mean feature measured from a shear ensemble, though, could be inaccurate if only one $N$--body simulation is used.
-\item The $1/N_r$ scaling for the dark energy constraint has been verified in our simulations, but the effective dimensionality $D$, that controls the degradation of the parameter error bars, grows faster than the $O(N_b)$ that \citep{DodelsonSchneider13} predicted.
+\item The $1/N_r$ scaling for the dark energy constraint has been verified in our simulations for $N_r\gg 100$ 
 \item The fluctuations in the $w$ forecasted variance do not exibit an appreciable trend with $N_s$ 

### 2015-11-30 code/analysis/variance_scaling_nb.py
examine more choices of nr

@@ -16,7 +16,7 @@ import algorithms
 
 #Number of simulations to test
 nsim = [1,2,5,10,20,30,40,50,60,70,80,90,100,150,200]
-nreal = np.arange(100,1100,100)
+nreal = range(70,910,10)
 resample = 100
 
 def main():

### 2015-12-01 code/analysis/variance_scaling_power.py
measure more Nr choices

@@ -14,12 +14,12 @@ import algorithms
 ######Main execution#######
 ###########################
 
-def main():
+#Number of simulations to test
+nsim = [1,2,5,10,20,30,40,50,60,70,80,90,100,150,200]
+nreal = range(70,910,10)
+resample = 100
 
-	#Number of simulations to test
-	nsim = [1]
-	nreal = [100,500,1000] + range(2000,101000,1000)
-	resample = 100
+def main():
 
 	#Load the emulator
 	emulator = Emulator.read("../../data/emulators/emulator_power_fine.pkl")
@@ -36,7 +36,7 @@ def main():
 	fiducial_parameters = Series(np.array([0.26,-1.0,0.8]),index=["Om","w","sigma8"])
 
 	#Load in the feature Ensemble, and bootstrap the covariance using a different number of realizations
-	with Database("../../data/variance_scaling_power_largeNr.sqlite") as db:
+	with Database("../../data/variance_scaling_nb_expected.sqlite") as db:
 	
 		for s in scales:
 
@@ -55,7 +55,7 @@ def main():
 			for n in nsim:
 		
 				#Load the power spectrum Ensemble from the relevant map set
-				ensemble_nsim = Ensemble(np.load("../../Om0.260_Ol0.740_w-1.000_ns0.960_si0.800/512b240/MillionMapsPower/power_spectrum_s0.npy".format(n)),columns=emulator[emulator.feature_names[0]].columns)[scales[s]]
+				ensemble_nsim = Ensemble(np.load("../../Om0.260_Ol0.740_w-1.000_ns0.960_si0.800/512b240/Maps{0}/power_spectrum_s0.npy".format(n)),columns=emulator[emulator.feature_names[0]].columns)[scales[s]]
 				ensemble_nsim.add_name("power_spectrum")
 
 				#Bootstrap ensemble_sim and compute the parameter variance for each resample

### 2015-12-03 Paper/paper.tex
finished implementing modifications with O(1/N^2) predictions

@@
 \begin{abstract}
-Constraining cosmology using Weak Gravitational Lensing consists in comparing measured features with simulated ones.
-An accurate estimate of the feature covariance matrix is essential to obtain accurate parameter confidence intervals.
+
+Constraining cosmology using Weak Gravitational Lensing consists in comparing measured feature vectors, of various dimensions $N_b$, with simulated ones.
+An accurate estimate of the $N_b\times N_b$ feature covariance matrix is essential to obtain accurate parameter confidence intervals.
 When this covariance matrix $\bb{C}$ is measured from simulations, an important question to ask is how big the simulation set should be for an accurate estimation of $\bb{C}$.
-We construct different mock ensembles with $N_r$ realizations of the same shear field, based on $N_s<N_r$ independent $N$--body simulations.
-Using the shear--shear power spectrum as a summary statistic, we find that a single $N$--body simulation can be recycled a large number of times to produce an ensemble of $N_r=10^5$ shear realizations that are mutually independent.
+We construct different mock ensembles with $N_r$ realizations of the same shear field, using a common randomization procedure based on $N_s<N_r$ independent $N$--body simulations.
+Previous work \citep{DodelsonSchneider13} showed that noise fluctuations in the feature covariance lead, at quadratic order, to a $O(1/N_r)$ degradation of parameter constraints.
+Using a variety of features that include shear-shear power spectra and peak counts, we show that cubic and quartic covariance fluctuations lead to additional $O(1/N_r^2)$ error degradation that is not negligible when $N_r$ is only a factor of a few bigger than $N_b$.
+When we study the large $N_r$ limit we find that a single $N$--body simulation can be recycled a large number of times to produce an ensemble of $N_r=10^5$ shear realizations that are mutually independent.
+We also find that a small number of independent $N$--body simulations (1 or 2) are necessary to forecast parameter error bars at percent accuracy, while a larger number might be needed to measure accurate feature ensemble means.
+
 \end{abstract}
@@
 We fill the box with $512^3$ particles, which correspond to a mass resolution of $10^{10}M_\odot$.
-We assume a uniform galaxy distribution at a constant redshift $z_s=2$ (at which the simulation box has an angular size of $\theta_{box}=3.5\mathrm{deg}$) and we disctretize the mass distribution between $z_s$ and the observer at $z=0$ with a sequence of 46 two dimensional lenses of thickness $80\mathrm{Mpc}/h$.
+We assume a uniform galaxy distribution at a constant redshift $z_s=2$ (at which the simulation box has an angular size of $\theta_{box}=3.5\mathrm{deg}$) and we discretize the mass distribution between $z_s$ and the observer at $z=0$ with a sequence of 46 two dimensional lenses of thickness $80\mathrm{Mpc}/h$.
 The surface density on each lens is computed by projecting the three dimensional density measured from \texttt{Gadget2} snapshots.
@@
 \item Choose randomly a direction between the three choices ${\bb{n}_x,\bb{n}_y,\bb{n}_z}$: the lens plane will be pependicular to this direction
-\item Choose the cutting point of the plane in the snapshot: because the lens thickness is 1/3 the size of the box, we can cut three different slices of the simulation box for each orientation ${\bb{n}_x,\bb{n}_y,\bb{n}_z}$
+\item Choose the cutting point of the plane in the snapshot: because the lens thickness is 1/3 the size of the box, we can cut three different slices of the simulation box for each orientation ${\bb{n}_x,\bb{n}_y,\bb{n}_z}$, which gives a total of 9 choices for generating a lens plane out of a $N$--body snapshot
 \item Perform a periodical random shift of the lens plane along its two directions
@@
 %
-To measure the feature derivatives $\bb{d}'_0$ with respect to cosmology, we make use of the public code \texttt{NICAEA} \citep{Nicaea} for the power spectrum, and we use an independent simulation set (that contains mocks at different combinations of $(\Omega_m,w,\sigma_8)$) for the peak counts.
+To measure the feature derivatives $\bb{d}'_0$ with respect to cosmology, we make use of the public code \texttt{NICAEA} \citep{Nicaea} for the power spectrum, and we use an independent simulation set (that contains mocks at different combinations of $(\Omega_m,w,\sigma_8)$, see Table \ref{simtable}) for the peak counts.
+
+\begin{table}
+\begin{center}
+\begin{tabular}{c|c|c||c|c}
+\toprule
+$\Omega_m$ &  $w$ & $\sigma_8$ & $N_s$ & Number of $\kappa$ ensembles \\ \hline \hline
+\midrule
+
+0.26 & -1 & 0.8 & $1\div 200$ & 16 \\
+0.29 & -1 & 0.8 & 1 & 1 \\
+0.26 & -0.8 & 0.8 & 1 & 1 \\
+0.26 & -1 & 0.6 & 1 & 1 \\
+
+\bottomrule
+\end{tabular}
+\end{center}
+\caption{Summary table of the shear ensembles used in this work.}
+\label{simtable}
+\end{table}
+
 We can build the estimator for the posterior maximum $\bbh{p}$, given the observation $\bbh{d}_{obs}$, as follows:
@@
 When we perform an observation $\bbh{d}_{obs}$, the parameter estimate $\bbh{p}$ is a random draw from a probability distribution with variance $\h{\Sigma}_\bb{p}$, which inherits noise from the simulations.
-In the following we review the method to compute $\langle\h{\Sigma}_\bb{p}\rangle$ \citep{DodelsonSchneider13,Taylor12}.
 The noise in the covariance estimator (\ref{covest}) and its inverse $\bbh{\Psi}$ propagates all the way to the posterior (\ref{posteriorbayes}), the parameter estimate (\ref{estimatormean}) and its variance (\ref{estimatorcovariance}).
-Following \citep{Taylor12} we can say that, if the feature vector $\bbh{d}_r$ from which $\bbh{C}$ is estimated is drawn from a multivariate Gaussian distribution, the precision matrix estimator $\bbh{\Psi}$ is biased
+Following \citep{DodelsonSchneider13,Taylor12,MasumotoWishart} we compute the expectation value of (\ref{estimatorcovariance}) over simulations, $\langle\h{\Sigma}_\bb{p}\rangle$, up to $O(1/N_r^2)$ by expanding (\ref{estimatorcovariance}) to quartic order in the $\bbh{\Psi}$ statistical fluctuations.
+Indicating the noiseless parameter covariance as $\Sigma_\bb{p}=\bb{F}^{-1}$, the result we get is \footnote{The details of the calculation are given in Appendix A}
+
+\begin{widetext}
 \begin{equation}
-\label{psibias}
-\langle\bbh{\Psi}\rangle = \frac{N_r-1}{N_r-N_b-2}\bb{\Psi}
+\label{quarticdegradation}
+\langle\h{\Sigma}_\bb{p}\rangle = \Sigma_\bb{p}\left[1+\frac{N_b-N_p}{N_r}+\frac{(N_b-N_p)(N_b-N_p+2)}{N_r^2}\right] + O\left(\frac{1}{N_r^3}\right)
 \end{equation}
+\end{widetext}
 %
-and, once the bias is corrected, the residual fluctuations in $\bbh{\Psi}$ are correlated as follows
-\begin{equation}
-\label{psifluctuations}
-\langle\delta\h{\Psi}_{ij}\delta\h{\Psi}_{kl}\rangle = A\Psi_{ij}\Psi_{kl} + B(\Psi_{ik}\Psi_{jl} + \Psi_{il}\Psi_{jk})
-\end{equation}
-%
-where $A,B$ are constants that depend on $N_r,N_b$ and have the asymptotic behavior $A\propto1/N_r^2,B\propto1/N_r$.
-We want to estimate the effect of these fluctuations on the parameter constraints $\Sigma_\bb{p}$, following the guidelines of \citep{DodelsonSchneider13}.
-We consider three cases:
+Next, we restrict ourselves to the large $N_r$ limit, and we further investigate the behavior of the $O(1/N_r)$ term.
+We consider three cases \footnote{The details of these calculations are given in Appendix B}:
 \begin{enumerate}
 \item If the true data covariance $\bb{C}$ is known, the estimator (\ref{estimatorcovariance}) is biased, and the dominant contribution of the bias comes from the second order fluctuations in $\bbh{\Psi}$.
-Once the expectation values are taken as in (\ref{psifluctuations}), the bias sums up to
+Once the expectation values over simulations are taken, the bias sums up to
 
@@
 \label{dodelsonscaling}
-\langle\h{\Sigma}_\bb{p}\rangle=\Sigma_\bb{p}(1+B(N_b-N_p))
+\langle\h{\Sigma}_\bb{p}\rangle=\Sigma_\bb{p}\left(1+\frac{N_b-N_p}{N_r}\right)
 \end{equation}
@@
 This approach has been used before in the literature (see \citep{MinkPetri,MinkShirasaki} for example).
-If we do that, and we do not correct for the bias (\ref{psibias}), the parameter variance will have a contribution from both the second and first order fluctuations in $\bbh{\Psi}$, which now have a non zero expectation value.
+If we do that, and we do not correct for the $\bbh{\Psi}$ bias, the parameter variance will have a contribution from both the second and first order fluctuations in $\bbh{\Psi}$, which now have a non zero expectation value.
 In this case the bias sums up to
@@
 \label{mockscalinguncorrected}
-\langle\h{\Sigma}_\bb{p}\rangle=\Sigma_\bb{p}(1-(1+N_b)/N_r+B(1+N_p))
+\langle\h{\Sigma}_\bb{p}\rangle=\Sigma_\bb{p}\left(1-\frac{N_b-N_p}{N_r}\right)
 \end{equation}
@@
 \label{mockscalingcorrected}
-\langle\h{\Sigma}_\bb{p}\rangle=\Sigma_\bb{p}(1+B(1+N_p))
+\langle\h{\Sigma}_\bb{p}\rangle=\Sigma_\bb{p}\left(1+\frac{1+N_p}{N_r}\right)
 \end{equation}
@@
 %
-The complete calculations that justify (\ref{dodelsonscaling}),(\ref{mockscalinguncorrected}) and (\ref{mockscalingcorrected}) are shown in the Appendix.
-With the $\bbh{d}_r$ Gaussianity assumption, the coefficient $B$ can be calculated exactly as \citep{DodelsonSchneider13,Taylor12}, and tends to $1/N_r$ in the limit of $N_r\gg N_b$.
-This leads to a degradation of order $D/N_r$ for the variance of each estimated parameter $\sigma^2_p=\Sigma_{pp}$, where $D=N_b-N_p,N_p-N_b,1+N_p$ for cases 1,2,3 respectively.
+The error degradation  in each parameter $p$, at dominant order, scales as $D/N_r$, where $D=N_b-N_p,N_p-N_b,1+N_p$ for cases 1,2,3 respectively.
 This means that, when parameter errors are estimated purely from simulations, and the same simulation set is used to estimate both $\bbh{C},\bbh{\Psi}$, these errors tend to decrease with $N_b$ (case 2), or at best remain constant (case 3), while the distribution of $\bbh{p}$ has still a variance that increases with $N_b$.
@@
 \label{ourscaling}
-\langle\h{\sigma}_p^2\rangle = \sigma^2_p(N_s)\left(1+\frac{D}{N_r}\right)
+\langle\h{\sigma}_p^2\rangle = \sigma^2_{p,\infty}(N_s)\left(1+\frac{D}{N_r}\right)
 \end{equation}
 %
-on our simulations.
-We call $D$ the \textit{effective dimensionality} of the feature space.
+on our simulations for high and small $N_r$.
+We use notation $\h{\sigma}^2_p=\h{\Sigma}_{pp}$ and we indicate as $\sigma^2_{p,\infty}$ the expectation value of the variance in the limit of infinite mocks $N_r\rightarrow\infty$.
+We call $D$ the \textit{effective dimensionality} of the feature space (which, as seen before, can be negative in some cases).
 We compute the expectation values of $\h{\sigma}^2_p$ (equations (\ref{estimatorcovariance}),(\ref{ourscaling})) averaging over 100 random resamplings of our shear ensembles.
@@
 
-The true parameter variance $\sigma^2_p(N_s)$ in principle depends on the number of independent $N$--body simulations $N_s$, which appears in the randomization procedure we describe in \S~\ref{shearsim}.
-The reason for this can be found in that, if $N_s$ is not big enough, the different shear realizations cannot be all independent, and hence the true variance $\sigma^2_p(N_s\rightarrow\infty)$ cannot be recovered in the limit $N_r\rightarrow\infty$.
-In particular there could be some residual error in the expectation value of (\ref{estimatorcovariance}) even if $N_r$ is big.
+The true parameter variance $\sigma^2_{p,\infty}(N_s)$ in principle depends on the number of independent $N$--body simulations $N_s$, which appears in the randomization procedure we describe in \S~\ref{shearsim}.
+The reason for this can be found in that, if $N_s$ is not big enough, the different shear realizations cannot be all independent, and hence the true variance $\sigma^2_{p,\infty}(N_s\rightarrow\infty)$ cannot be recovered for low $N_s$ even if $N_r$ is large.
 In the next paragraph we outline our main findings.
@@
 \begin{figure}
+\includegraphics[scale=0.3]{Figures/means_ns.eps}
+\caption{Means of shear features $d$ measured from different shear ensembles.
+The quantities shown are the differences between mean features measured from ensemble with varying $N_s$, with respect to the means measured from the $N_s=200$ ensemble, in units of the statistical error measured from the $N_s=100$ ensemble.
+The colored lines refer to shear-shear power spectra measured at $l=115$ (black), 1027 (cyan), 5283 (green) and peak counts of height $\kappa_0=0.05$ (red), 0.17 (purple), 0.28 (orange).}
+\label{means_ns}
+\end{figure}
+
+\begin{figure}
 \includegraphics[scale=0.3]{Figures/ps_variance.eps}
@@
 \label{ps_var}
+\end{figure}
+
+\begin{figure}
+\includegraphics[scale=0.3]{Figures/curving_nb.eps}
+\caption{Expectation value of the $w$ variance computed with equation (\ref{estimatorcovariance}) as a function of $1/N_r$, for the features outlined in Table \ref{featuretable}.
+The dashed and solid lines show the the theory predictions from equation (\ref{quarticdegradation}) at orders $O(1/N_r),O(1/N_r^2)$.
+The asymptotic variance $\sigma^2_{w,\infty}$ has been computed from a linear regression of $\langle\h{\sigma}^2_w\rangle$ vs $1/N_r$ for $N_r>500$.}
+\label{curvingnb}
 \end{figure}
@@
 \caption{Variance on $w$ in the limit $N_r\rightarrow\infty$, varying the mock ensemble used to compute the covariance estimator (\ref{covest}).
-We show the dependence of $\sigma_0^2(N_s)$ in units of the mean over $N_s$, for the power spectrum logarithmically binned (black), the power spectrum linearly binned (red) and the peak counts (green).}
+We show the dependence of $\sigma_{w,\infty}^2(N_s)$ in units of the mean over $N_s$, for the power spectrum logarithmically binned (black), the power spectrum linearly binned (red) and the peak counts (green).}
 \label{wvar_ns}
@@
 Power Spectrum, log binning  & $l \in [1000,6000] $ & 7 & $\times$ & black  \\ 
-Power Spectrum, log binning  & $l \in [100,6000] $ & 15 & $\times$ & black  \\
+Power Spectrum, log binning  & $l \in [100,6000] $ & 15 & \textcolor{red}{$\times$} & \textcolor{red}{red}  \\
 Power Spectrum, linear binning  & $l \in [100,2000] $ & 15 & \textcolor{red}{$+$} & \textcolor{red}{red}  \\ 
 Power Spectrum, linear binning  & $l \in [2500,4500] $ & 15 & \textcolor{red}{$\times$} & \textcolor{red}{red}  \\
-Power Spectrum, linear binning  & $l \in [100,4500] $ & 30 & \textcolor{red}{$\bullet$} & \textcolor{red}{red}  \\ 
-Power Spectrum, linear binning  & $l \in [100,6000] $ & 39 & \textcolor{red}{$\bullet$} & \textcolor{red}{red}  \\ \hline
-Low peaks  & $\kappa_0 \in [-0.06,0.09] $ & 15 & \textcolor{OliveGreen}{$+$} & \textcolor{OliveGreen}{green}  \\ 
-Intermediate peaks  & $\kappa_0 \in [0.1,0.27] $ & 15 & \textcolor{OliveGreen}{$\bigstar$} & \textcolor{OliveGreen}{green}  \\ 
-High peaks  & $\kappa_0 \in [0.28,0.45] $ & 15 & \textcolor{OliveGreen}{$\diamond$} & \textcolor{OliveGreen}{green}  \\
+Power Spectrum, linear binning  & $l \in [100,4500] $ & 30 & \textcolor{OliveGreen}{$\bullet$} & \textcolor{OliveGreen}{green}  \\ 
+Power Spectrum, linear binning  & $l \in [100,6000] $ & 39 & \textcolor{blue}{$\bullet$} & \textcolor{blue}{blue}  \\ \hline
+Low peaks  & $\kappa_0 \in [-0.06,0.09] $ & 15 & \textcolor{red}{$+$} & \textcolor{red}{red}  \\ 
+Intermediate peaks  & $\kappa_0 \in [0.1,0.27] $ & 15 & \textcolor{red}{$\bigstar$} & \textcolor{red}{red}  \\ 
+High peaks  & $\kappa_0 \in [0.28,0.45] $ & 15 & \textcolor{red}{$\diamond$} & \textcolor{red}{red}  \\
 Low+Intermediate peaks  & $\kappa_0 \in [-0.06,0.27] $ & 30 & \textcolor{OliveGreen}{$\times$} & \textcolor{OliveGreen}{green}  \\
 Intermediate+High peaks  & $\kappa_0 \in [0.1,0.45] $ & 30 & \textcolor{OliveGreen}{$\bullet$} & \textcolor{OliveGreen}{green}  \\
-All peaks  & $\kappa_0 \in [-0.06,0.45] $ & 45 & \textcolor{OliveGreen}{$\blacksquare$} & \textcolor{OliveGreen}{green}  \\ \hline
+All peaks  & $\kappa_0 \in [-0.06,0.45] $ & 45 & \textcolor{magenta}{$\blacksquare$} & \textcolor{magenta}{magenta}  \\ \hline
 \bottomrule
@@
 
-\begin{figure}
-\includegraphics[scale=0.3]{Figures/curving_nb.eps}
-\caption{Expectation value of the $w$ variance computed with equation (\ref{estimatorcovariance}) as a function of $1/N_r$, for the features outlined in Table \ref{featuretable}.
-The line width increases with the number of bands $N_b$ used for each feature.}
-\label{curvingnb}
-\end{figure}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 In this section we outline the main results of this work.
-We show the qualitative behavior of the $P^{\kappa\kappa}$ probability distribution function (PDF) in ensembles built with different $N_s$.
-We also show how the forecasts on the Dark Energy equation of state, $w$, depend on $N_s$ and $N_r$.
-Figure \ref{ps_pdf} shows the power spectrum PDF at four selected multipoles, while Figure \ref{ps_var} shows the variance in each multipole.
-This result is compared to the one that we would obtain assuming that the convergence is a Gaussian random field
+We show the qualitative behavior of a variety of features $\bbh{d}_r$ probability distribution function (PDF) in ensembles built with different $N_s$.
+Figure \ref{ps_pdf} shows the power spectrum PDF at four selected multipoles, Figure \ref{means_ns} shows the dependence of feature ensemble means on $N_s$, while Figure \ref{ps_var} shows the variance in each measure power spectrum multipole.
+This last result is compared to the one that would be obtained assuming that the convergence $\kappa$ is a Gaussian random field
 \begin{equation}
@@
 
-Figure \ref{wvar_nr} show the scaling of the expectation value of $\h{\sigma}_w^2$ with the number of mocks $N_r$ using the power spectrum and compare it with the known result obtained in \citep{DodelsonSchneider13} and expressed in equation (\ref{ourscaling}).
-Figure \ref{wvar_ns} shows the effect of varying $N_s$ on the $w$ constraint.
-Finally Figure \ref{curvingnb} shows....
+Figure \ref{curvingnb} shows a comparison between the dependence of $\langle\h{\sigma^2_w}\rangle$ measured from simulations and the theory prediction from equation (\ref{quarticdegradation}).
+
+Figure \ref{wvar_nr} shows the scaling of the expectation value of $\h{\sigma}_w^2$ when the number of mocks is large, $N_r\gg500$, using the power spectrum and compare it with the known result obtained in \citep{DodelsonSchneider13} and expressed in equation (\ref{ourscaling}).
+Finally, Figure \ref{wvar_ns} shows the effect of varying $N_s$ on the $w$ constraint.
 
@@
 We need as small as $N_s=2$ to recover the right location parameter for the power spectrum on small scales.
+Figure \ref{means_ns} shows that mutiple independent $N$--body simulations $N_s>1$ are necessary for measuring the means of feature ensembles to an accuracy corresponding to 10\% of the statistical error.
+The number of required simulations $N_s$ depends on the feature type and ranges from a few (1 or 2) for the power spectrum at small multipoles $l\lesssim 500$ to an order of $30\div50$ for the power spectrum at large multipoles $l\gtrsim1000$ peak counts at a high threshold $\kappa_0\approx0.3$.
 
@@
 
-In Figure \ref{wvar_nr} we examine how the $w$ constraint depends on the number of mocks used to estimate the covariance, and we find good agreement with (\ref{ourscaling}).
-In particular we can see that one $N$--body simulation is enough to construct an ensemble of $O(10^5)$ mutually independent mock power spectra, for which the $w$ constraint scales like $1/N_r$ all the way to $N_r=10^5$.
+Figure \ref{curvingnb} shows that error degradation estimates truncated at order $O(1/N_r)$ are too optimistic when the number of mocks $N_r$ used to measure the covariance is only a factor of few larger than the dimension of the feature space $N_b$.
+In these cases effects coming the next--to--leading orders $O(1/N_r^2)$ become non--negligible on constraints degradation.
+In particular we find that already for $N_b=30$ and $N_r\sim100$, error degradation estimates at $O(1/N_r^2)$ are too optimistic, and more accurate estimates require at least the terms of order $O(1/N_r^3)$, which come from higher than quartic $\bbh{\Psi}$ fluctations.
+
+In Figure \ref{wvar_nr} we examine how the $w$ constraint depends on the number of mocks used to estimate the covariance in the limit of large $N_r$, and we find good agreement with (\ref{ourscaling}) up to values comparable to $\sim 10^5$.
+Bacause of this, we can argue that one $N$--body simulation is enough to construct an ensemble of $O(10^5)$ mutually independent mock power spectra.
 
 Figure \ref{wvar_ns} shows the dependence of the dark energy constraint with $N_s$.
-We find that, in the range $N_s\in[1,200]$ the $w$ inferred variance $\sigma_0^2$ fluctuates stochastically and does not show an appreciable trend with $N_s$.
+We find that, in the range $N_s\in[1,200]$ the $w$ inferred variance $\sigma_{w,\infty}^2$ fluctuates stochastically and does not show an appreciable trend with $N_s$.
 
@@
 \begin{itemize}
+\item When the feature covariance matrix is measured from simulations, parameter constraints are degraded.
+This degradation is appreciably larger than the $O(1/N_r)$ computed by \citep{DodelsonSchneider13} when the number of mocks $N_r$ is only a factor of few larger than the feature vector size $N_b$.
 \item We can recycle a single $N$--body simulation to produce an ensemble of $O(10^5)$ independent maps.
 The mean feature measured from a shear ensemble, though, could be inaccurate if only one $N$--body simulation is used.
-\item The $1/N_r$ scaling for the dark energy constraint has been verified in our simulations for $N_r\gg 100$ 
-\item The fluctuations in the $w$ forecasted variance do not exibit an appreciable trend with $N_s$ 
+\item One or two indpendent $N$--body simulations are sufficient to forecast $w$ errorbars to an accuracy of percent level, given that enough mock shear realizations $N_r$ are used to measure feature covariances.
+Depending on the feature type used to constrain cosmology, more $N$--body simulations might be needed to measure accurate ensemble means and hence avoid introducing biases in parameter estimators.
 \end{itemize}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%% APPENDIX %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Appendix A: cubic and quartic covariance fluctuations}
+\label{appendixA}
 
-\section*{Appendix: scaling of the effective dimensionality}
-\label{appendix}
+The goal of this appendix is to give a derivation of equation (\ref{quarticdegradation}).
+When the simulated feature vector $\bbh{d}_r$ is drawn from a Gaussian distribution, the covariance estimator $\bbh{C}$ follows the Wishart distribution, and its inverse $\bbh{\Psi}$ follows the inverse Wishart distribution.
+For the analytical expressions of these probability distributions we remand the reader to \citep{Taylor12}.
+Computing expectation values of (\ref{estimatorcovariance}) over the inverse Wishart distribution is not possible analytically, and a perturbative expansion is necessary.
+Writing $\bbh{\Psi}=\bb{\Psi}+\delta\bbh{\Psi}$, we can expand equation (\ref{quarticdegradation}) in powers of $\delta\bbh{\Psi}$.
+The expectation values of each term in this perturbative expansion can be calculated in term of the moments of the inverse Wishart distribution.
+\citep{MasumotoWishart} provide a general framework to compute these moments, and give exact expressions for moments up to quartic order.
+First, let us expand the inverse of the Fisher matrix estimator (\ref{estimatorfisher}) in powers of $\delta\bbh{\Psi}$.
+The $n$--th order of this expansion will be
 
-The goal of this appendix is giving a derivation of (\ref{dodelsonscaling}),(\ref{mockscalinguncorrected}) and (\ref{mockscalingcorrected}) following the guidelines from \citep{DodelsonSchneider13,Taylor12}.
-First consider the case in which we use the same simulation set to estimate $\bb{C},\bbh{\Psi}$: in this case equation (\ref{estimatorcovariance}) reduces to the inverse Fisher estimator $\h{\Sigma}_\bb{p}=\bbh{F}^{-1}$.
-If we write $\bbh{F}=\bb{F}+\delta\bbh{F}=\bb{F}+\bb{d}_0'^T\delta\bbh{\Psi}\bb{d}_0'$, and expand at second order in the fluctuations we get
+\begin{equation}
+\label{nthterm}
+\delta\bbh{F}^{-1}_{(n)} = (-1)^{n}(\bb{F}^{-1}\delta\bbh{F})^n\bb{F}^{-1}
+\end{equation}
+%
+with
+\begin{equation}
+\delta\bbh{F} = \bb{d}_0'^T\delta\bbh{\Psi}\bb{d}_0'
+\end{equation}
+%
+Using (\ref{nthterm}), we can expand (\ref{estimatorcovariance}) to an arbitrary order in $\delta\bbh{\Psi}$, take the expectation values of the fluctuations over the inverse Wishart distribution, and finally get to (\ref{quarticdegradation}).
+We use the notation $\nu=N_r-1$ and $\gamma=(\nu-N_b-1)/2$.
+We indicate with capital letters pairs of matrix indices, for example $I=(i_1,i_2)$, where $i_a=1..N_b$.
+The main results we take out from \citep{MasumotoWishart} regarding the first four moments are (up to order $O(1/\nu^2)$)
+
+\begin{widetext}
+
+\begin{equation}
+\label{firstmoment}
+\langle\h{\Psi}_I\rangle = \frac{\nu}{2\gamma}\Psi_I
+\end{equation}
+
+\begin{equation}
+\label{secondmoment}
+\langle\delta\h{\Psi}_I\delta\h{\Psi}_J\rangle = \frac{\nu^2\Psi_I\Psi_J + \nu^2\gamma\Psi_{[I}\Psi_{J]}}{4\gamma^2(\gamma-1)(2\gamma+1)}
+\end{equation}
+
+\begin{equation}
+\label{thirdmoment}
+\langle\delta\h{\Psi}_I\delta\h{\Psi}_J\delta\h{\Psi}_K\rangle = \frac{\nu^3\Psi_{[I}\Psi_J\Psi_{K]}}{8\gamma(\gamma-1)(\gamma-2)(\gamma+1)(2\gamma+1)}
+\end{equation}
+
+\begin{equation}
+\label{fourthmoment}
+\langle\delta\h{\Psi}_I\delta\h{\Psi}_J\delta\h{\Psi}_K\delta\h{\Psi}_L\rangle = \frac{\nu^4(2\gamma^2-5\gamma+9)\Psi_{[I}\Psi_{J]}\Psi_{[K}\Psi_{L]}}{16\gamma(\gamma-1)(\gamma-2)(\gamma-3)(2\gamma-1)(\gamma+1)(2\gamma+1)(2\gamma+3)}
+\end{equation}
+
+\end{widetext}
+%
+Where the square bracket notation is a shorthand for a symmetrization over pair of indices: for example
+\begin{equation}
+\Psi_{[I}\Psi_{J]} = \Psi_{i_1j_1}\Psi_{i_2j_2} + \Psi_{i_1j_2}\Psi_{i_2j_1}
+\end{equation}
+%
+Equation (\ref{firstmoment}) expresses the bias in the $\bbh{\Psi}$ estimator that already appears in the literature \citep{Hartlap07}.
+If we want to use the bias corrected $\bbh{\Psi}$ estimator (that is required in a perturbative expansion of (\ref{estimatorcovariance})), we need to apply an additional factor of $(2\gamma/\nu)^n$ to equations (\ref{firstmoment}--\ref{fourthmoment}), where $n$ is the order of the moment we are applying the correction to.
+If we limit ourselves to computing the expectation value of (\ref{estimatorcovariance}) up to order $O(1/\nu^2)$, we do not need to worry about this correction for equations (\ref{thirdmoment}--\ref{fourthmoment}), as the dominant term here is already $O(1/\nu^2)$.
+The next step is expanding (\ref{estimatorcovariance}) in powers of $\delta\bbh{\Psi}$ up to fourth order: this is easily done
+
+\begin{widetext}
+\begin{equation}
+\label{fullpertexpansion}
+\h{\Sigma}_\bb{p} = \left(\bb{F}^{-1}+\sum_{n=1}^4\delta\bbh{F}^{-1}_{(n)}\right)\bb{d}'^T_0(\bb{\Psi}+\delta\bbh{\Psi})\bb{C}(\bb{\Psi}+\delta\bbh{\Psi})\bb{d}'_0\left(\bb{F}^{-1}+\sum_{n=1}^4\delta\bbh{F}^{-1}_{(n)}\right)
+\end{equation}
+\end{widetext}
+%
+Carrying out the calculations is simpler than it looks: because of the structure of (\ref{fullpertexpansion}), each term in the expansion is going to be proportional to $\Sigma_\bb{p}f_a(N_b,N_p)/N_r^a$, where $f_a(N_b,N_p)$ is polynomial in $N_b,N_p$.
+Terms proportional to $N_b$ arise from index contractions of type $\mathrm{tr}(\bb{\Psi C})=N_b$, which come from symmetrization terms of type $\Psi_{[I}\Psi_{J]}$.
+Symmetrization factors of type $\Psi_{[I}\Psi_J\Psi_{K]}$ or $\Psi_{[I}\Psi_{J]}\Psi_{[K}\Psi_{L]}$, on the other hand, give rise to contractions of type $\mathrm{tr}(\bb{\Psi C})\mathrm{tr}(\bb{\bb{F}\bb{F}^{-1}})=N_bN_p$.
+Moreover, we know that, at every order $O(1/N_r^a)$, $f_a(N_b,N_p)$ has to be proportional to $N_b-N_p$ because it must vanish when $N_b=N_p$.
+The reason for this is that, when the feature derivative matrix $\bb{d}'_0$ is square and invertible (which it should be in absence of degeneracies), then (\ref{estimatorcovariance}) reduces to
+
+\begin{equation}
+\h{\Sigma}_\bb{p} = (\bb{d}'_0)^{-1}\bb{C}(\bb{d}'^T_0)^{-1}
+\end{equation} 
+%
+And every trace of the noise is gone, hence powers of $1/N_r^a$ must not appear at any order if $N_b=N_p$.
+Armed with the knowledge of the above considerations, we can compute the expectation value of (\ref{fullpertexpansion}) at second, third and fourth order in $\delta\bbh{\Psi}$, keeping the terms that are at most $O(1/\nu^2)=O(1/N_r^2)$.
+When the combinatorial factors that arise from the expansion of (\ref{fullpertexpansion}) are properly computed and the expectation values over the inverse Wishart distribution are taken according to (\ref{firstmoment}--\ref{fourthmoment}), the results should look like
+
+\begin{widetext}
+\begin{equation}
+\label{expansionbreakdown}
+\begin{cases}
+\begin{displaystyle}
+(\delta\bbh{\Psi})^2 \rightarrow \Sigma_\bb{p}\frac{\gamma(N_b-N_p)}{(\gamma-1)(2\gamma+1)} = \Sigma_\bb{p}\left[\frac{N_b-N_p}{N_r}+\frac{(N_b-N_p)(N_b+3)}{N_r^2}\right]
+\end{displaystyle} \\ \\
+
+\begin{displaystyle}
+(\delta\bbh{\Psi})^3 \rightarrow -4\Sigma_\bb{p}\frac{(N_b-N_p)(1+N_p)}{N_r^2}
+\end{displaystyle} \\ \\
+
+\begin{displaystyle}
+(\delta\bbh{\Psi})^4 \rightarrow 3\Sigma_\bb{p}\frac{(N_b-N_p)(1+N_p)}{N_r^2}
+\end{displaystyle}
+
+\end{cases}
+\end{equation}
+\end{widetext}
+%
+When the results from (\ref{expansionbreakdown}) are summed, (\ref{quarticdegradation}) immediately follows.
+
+\section*{Appendix B: negative effective dimensionality}
+\label{appendixB}
+
+The goal of this appendix is giving a justification on why the effective dimensionality $D$ that appears in equation (\ref{ourscaling}) can be negative in some cases.
+When we use the same simulation set to estimate $\bb{C},\bbh{\Psi}$, equation (\ref{estimatorcovariance}) reduces to the inverse Fisher estimator $\h{\Sigma}_\bb{p}=\bbh{F}^{-1}$.
+At second order in the $\Psi$ fluctuations this becomes
 
@@
 %
-If we use the precision estimator $\bbh{\Psi}=\bb{\Psi}+\delta\bbh{\Psi}$ and do not correct for the bias (\ref{psibias}), we have to use the facts that
+If the biased estimator for $\bbh{\Psi}$ is used, we can use equations (\ref{firstmoment}--\ref{secondmoment}) at order $O(1/\nu)$ to compute 
+\begin{widetext}
 \begin{equation}
-\begin{matrix}
-& \langle\delta\bbh{\Psi}\rangle = \frac{1+N_b}{N_r-N_b-2}\bb{\Psi} \\ \\
-& \langle\delta\h{\Psi}_{ij}\delta\h{\Psi}_{kl}\rangle = \frac{A([(N_r-1)^2+(1+N_b)^2]\Psi_{ij}\Psi_{kl} + B(N_r-1)^2(\Psi_{ik}\Psi_{kl}+\Psi_{il}\Psi_{jk})}{(N_r-N_b-2)^2}
-\end{matrix}
+\label{negativeD}
+\langle\h{\Sigma}_\bb{p}\rangle = \Sigma_\bb{p}\left(1-\frac{N_b+1}{N_r}+\frac{1+N_p}{N_r}\right) = \Sigma_\bb{p}\left(1+\frac{N_p-N_b}{N_r}\right)
 \end{equation}
+\end{widetext}
 %
-Keeping only the leading order $O(1/N_r)$ in the expansion we get the results
-\begin{equation}
-\label{explanationuncorrected}
-\begin{matrix}
-& \langle\delta\bbh{F}\rangle = \left(\frac{1+N_b}{N_r}\right)\bb{F} \\ \\
-& \langle\delta{\bbh{F}}\bb{F}^{-1}\delta{\bbh{F}}\rangle = B(1+N_p)\bb{F}
-\end{matrix}
-\end{equation}
-%
-which leads immediately to (\ref{mockscalinguncorrected}).
-Now suppose we correct for the bias in the precision estimator, and use the unbiased $\bbh{\Psi}$ for which $\delta\bbh{\Psi}=0$.
-This leads to equation (\ref{psifluctuations}) for the quadratic fluctuations in the precision matrix, and to the same (\ref{explanationuncorrected}), except for $\langle\delta\bbh{F}\rangle=0$.
-This leads to (\ref{mockscalingcorrected}).
-If now we keep $\bb{C}$ fixed and we estimate only $\bbh{\Psi}$ from the simulations, we get
-\begin{equation}
-\label{tempcovarianceestimate}
-\h{\Sigma}_\bb{p} = (\bbh{F}+\delta\bbh{F})^{-1}\bb{d}_0'^T(\bbh{\Psi}+\delta\bbh{\Psi})\bb{C}(\bbh{\Psi}+\delta\bbh{\Psi})\bb{d}_0'(\bbh{F}+\delta\bbh{F})^{-1}
-\end{equation}
-%
-If we isolate the second order terms in (\ref{tempcovarianceestimate}), the result is 
-\begin{equation}
-\h{\Sigma}_\bb{p}\vert_2 = \bb{F}^{-1}(\bb{d}_0'^T\delta\bbh{\Psi}\bb{C}\delta\bbh{\Psi}\bb{d}_0'-\delta{\bbh{F}}\bb{F}^{-1}\delta{\bbh{F}})\bb{F}^{-1}
-\end{equation} 
-%
-The expectation values of the quadratic fluctuations are easily computed using (\ref{psifluctuations}):
-\begin{equation}
-\begin{matrix}
-& \langle\bb{d}_0'^T\delta\bbh{\Psi}\bb{C}\delta\bbh{\Psi}\bb{d}_0'\rangle = B(1+N_b)\bb{F} \\ \\
-& \langle\delta{\bbh{F}}\bb{F}^{-1}\delta{\bbh{F}}\rangle = B(1+N_p)\bb{F}
-\end{matrix}
-\end{equation}
-%
-From which (\ref{dodelsonscaling}) immediately follows. 
+And we immediately see that the coefficient of $1/N_r$ is negative, because $N_b>N_p$.
+This is the result shown in (\ref{mockscalinguncorrected}).
+If the bias correction for $\bbh{\Psi}$ is applied, the first order terms $\delta{\bbh{F}}$ average to 0, and we are left with only the last term in the sum (\ref{negativeD}), which immediately yields (\ref{mockscalingcorrected}).
+
 \label{lastpage}

### 2015-12-03 Paper/Figures/generate.py

@@ -43,34 +43,51 @@ markers = {
 colors = {
 "power_logb_large" : "black",
 "power_logb_small" : "black",
-"power_logb_all" : "black",
+"power_logb_all" : "red",
 "power_large" : "red",
 "power_small" : "red",
-"power_large+small" : "red",
-"power_all" : "red",
-"peaks_low" : "green",
-"peaks_intermediate" : "green",
-"peaks_high" : "green",
+"power_large+small" : "green",
+"power_all" : "blue",
+"peaks_low" : "red",
+"peaks_intermediate" : "red",
+"peaks_high" : "red",
 "peaks_low+intermediate" : "green",
 "peaks_intermediate+high" : "green",
-"peaks_all" : "green",
+"peaks_all" : "magenta",
 } 
 
 #Labels
 labels = {
-"power_logb_large" : "Power spectrum log binning",
+"power_logb_large" : r"$N_b=7\div 8$",
 "power_logb_small" : None,
 "power_logb_all" : None,
 "power_large" : None,
-"power_small" : None,
-"power_large+small" : None,
-"power_all" : "Power spectrum linear binning",
-"peaks_low" : "Peak counts",
+"power_small" : r"$N_b=15$",
+"power_large+small" : r"$N_b=30$",
+"power_all" : r"$N_b=39$",
+"peaks_low" : None,
 "peaks_intermediate" : None,
 "peaks_high" : None,
 "peaks_low+intermediate" : None,
 "peaks_intermediate+high" : None,
-"peaks_all" : None,
+"peaks_all" : r"$N_b=45$",
+} 
+
+#Plot order
+order = {
+"power_logb_large" : 1,
+"power_logb_small" : -1,
+"power_logb_all" : -1,
+"power_large" : -1,
+"power_small" : 2,
+"power_large+small" : 3,
+"power_all" : 4,
+"peaks_low" : -1,
+"peaks_intermediate" : -1,
+"peaks_high" : -1,
+"peaks_low+intermediate" : -1,
+"peaks_intermediate+high" : -1,
+"peaks_all" : 5,
 } 
 
 #Offsets
@@ -259,7 +276,7 @@ def scaling_ns(cmd_args,db_filename="variance_scaling_nb_expected.sqlite",featur
 	#Labels
 	ax.set_xlim(-10,210)
 	ax.set_xlabel(r"$N_s$",fontsize=fontsize)
-	ax.set_ylabel(r"$\sigma_0^2(N_s)/\sigma_{0,mean}^2$",fontsize=fontsize)
[…]

### 2015-12-04 Paper/paper.tex
modified label of Fig3 and legend of Fig4

@@
 \includegraphics[scale=0.3]{Figures/scaling_nr.eps}
-\caption{Bias in the $w$ variance, $\langle\h{\sigma}^2_w\rangle$, as a function of the number of mock realizations $N_r$ used in the feature covariance estimator (\ref{covest}).
+\caption{Bias in the $w$ variance, $\langle\h{\sigma}^2_w\rangle-\sigma^2_{w,\infty}$, as a function of the number of mock realizations $N_r$ used in the feature covariance estimator (\ref{covest}).
 Results for different mock ensembles generated with $N_s=$1 (black), 2 (blue), 5 (green), 50 (red), 100 (purple) are shown.
@@
 Power Spectrum, log binning  & $l \in [100,800] $ & 8 & $\times$ & black  \\ 
-Power Spectrum, log binning  & $l \in [1000,6000] $ & 7 & $\times$ & black  \\ 
-Power Spectrum, log binning  & $l \in [100,6000] $ & 15 & \textcolor{red}{$\times$} & \textcolor{red}{red}  \\
+Power Spectrum, log binning  & $l \in [1000,6000] $ & 7 & $\blacksquare$ & black  \\ 
+Power Spectrum, log binning  & $l \in [100,6000] $ & 15 & \textcolor{red}{$\bullet$} & \textcolor{red}{red}  \\
 Power Spectrum, linear binning  & $l \in [100,2000] $ & 15 & \textcolor{red}{$+$} & \textcolor{red}{red}  \\ 
@@
 Low+Intermediate peaks  & $\kappa_0 \in [-0.06,0.27] $ & 30 & \textcolor{OliveGreen}{$\times$} & \textcolor{OliveGreen}{green}  \\
-Intermediate+High peaks  & $\kappa_0 \in [0.1,0.45] $ & 30 & \textcolor{OliveGreen}{$\bullet$} & \textcolor{OliveGreen}{green}  \\
+Intermediate+High peaks  & $\kappa_0 \in [0.1,0.45] $ & 30 & \textcolor{OliveGreen}{$\blacksquare$} & \textcolor{OliveGreen}{green}  \\
 All peaks  & $\kappa_0 \in [-0.06,0.45] $ & 45 & \textcolor{magenta}{$\blacksquare$} & \textcolor{magenta}{magenta}  \\ \hline

### 2015-12-04 Paper/Figures/generate.py

@@ -25,8 +25,8 @@ parser.add_argument("fig",nargs="*")
 #Markers
 markers = {
 "power_logb_large" : "x",
-"power_logb_small" : "x",
-"power_logb_all" : "x",
+"power_logb_small" : "s",
+"power_logb_all" : "o",
 "power_large" : "+",
 "power_small" : "x",
 "power_large+small" : "o",
@@ -35,7 +35,7 @@ markers = {
 "peaks_intermediate" : "*",
 "peaks_high" : "d",
 "peaks_low+intermediate" : "x",
-"peaks_intermediate+high" : "o",
+"peaks_intermediate+high" : "s",
 "peaks_all" : "s",
 } 
 
@@ -197,7 +197,7 @@ def scaling_nr(cmd_args,db_filename="variance_scaling_nb_expected.sqlite",parame
 	#Fit with the Dodelson scaling and overlay the fit
 	vfit = algorithms.fit_nbins(v,parameter=parameter)
 	v = Ensemble.merge(v,vfit,on="nsim")
-	v[parameter+"_fit"] = v.eval("s0*nb/nreal")
+	v[parameter+"_fit"] = v.eval("s0*D/nreal")
 	v[parameter+"_subtracted"] = v.eval("{0}-s0".format(parameter))
 	nsim_group = v.groupby("nsim")
 
@@ -216,7 +216,7 @@ def scaling_nr(cmd_args,db_filename="variance_scaling_nb_expected.sqlite",parame
 	#Fit with the Dodelson scaling and overlay the fit
 	vfit = algorithms.fit_nbins(v,parameter=parameter)
 	v = Ensemble.merge(v,vfit,on="nsim")
-	v[parameter+"_fit"] = v.eval("s0*nb/nreal")
+	v[parameter+"_fit"] = v.eval("s0*D/nreal")
 	v[parameter+"_subtracted"] = v.eval("{0}-s0".format(parameter))
 	nsim_group = v.groupby("nsim")
 
@@ -232,7 +232,7 @@ def scaling_nr(cmd_args,db_filename="variance_scaling_nb_expected.sqlite",parame
 
 	#Labels
 	ax.set_xlabel(r"$N_r$",fontsize=fontsize)
-	ax.set_ylabel(r"$\langle\hat{\sigma}^2_w\rangle$",fontsize=fontsize)
[…]

### 2015-12-04 Paper/paper.tex
fixed 100-->200 mislabel

@@
 \caption{Means of shear features $d$ measured from different shear ensembles.
-The quantities shown are the differences between mean features measured from ensemble with varying $N_s$, with respect to the means measured from the $N_s=200$ ensemble, in units of the statistical error measured from the $N_s=100$ ensemble.
+The quantities shown are the differences between mean features measured from ensemble with varying $N_s$, with respect to the means measured from the $N_s=200$ ensemble, in units of the statistical error measured from the $N_s=200$ ensemble.
 The colored lines refer to shear-shear power spectra measured at $l=115$ (black), 1027 (cyan), 5283 (green) and peak counts of height $\kappa_0=0.05$ (red), 0.17 (purple), 0.28 (orange).}

### 2015-12-04 Paper/paper.tex
mention psi bias before

@@
 This approach has been used before in the literature (see \citep{MinkPetri,MinkShirasaki} for example).
-If we do that, and we do not correct for the $\bbh{\Psi}$ bias, the parameter variance will have a contribution from both the second and first order fluctuations in $\bbh{\Psi}$, which now have a non zero expectation value.
+If we do that, and we do not correct for the $\bbh{\Psi}$ bias (see equation (\ref{firstmoment})), the parameter variance will have a contribution from both the second and first order fluctuations in $\bbh{\Psi}$, which now have a non zero expectation value.
 In this case the bias sums up to

### 2016-01-08 Paper/paper.tex
very minor change
Zoltan edits

--- 2015-12-04 Paper/paper.tex
@@
 \newcommand{\h}[1]{\hat{#1}}
+\newcommand\lsim{\mathrel{\rlap{\lower4pt\hbox{\hskip1pt$\sim$}}
+        \raise1pt\hbox{$<$}}}
+\newcommand\gsim{\mathrel{\rlap{\lower4pt\hbox{\hskip1pt$\sim$}}
+        \raise1pt\hbox{$>$}}}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\title{Simulating cosmic variance in Weak Lensing: effects on parameter inferences}
+%ZH: I changed to more catchy title:
+%\title{Simulating sample variance in weak lensing: effects on parameter inferences}
+\title{Sample variance in weak lensing: how many simulations are required?}
 
@@
 
-Constraining cosmology using Weak Gravitational Lensing consists in comparing measured feature vectors, of various dimensions $N_b$, with simulated ones.
-An accurate estimate of the $N_b\times N_b$ feature covariance matrix is essential to obtain accurate parameter confidence intervals.
-When this covariance matrix $\bb{C}$ is measured from simulations, an important question to ask is how big the simulation set should be for an accurate estimation of $\bb{C}$.
-We construct different mock ensembles with $N_r$ realizations of the same shear field, using a common randomization procedure based on $N_s<N_r$ independent $N$--body simulations.
-Previous work \citep{DodelsonSchneider13} showed that noise fluctuations in the feature covariance lead, at quadratic order, to a $O(1/N_r)$ degradation of parameter constraints.
-Using a variety of features that include shear-shear power spectra and peak counts, we show that cubic and quartic covariance fluctuations lead to additional $O(1/N_r^2)$ error degradation that is not negligible when $N_r$ is only a factor of a few bigger than $N_b$.
-When we study the large $N_r$ limit we find that a single $N$--body simulation can be recycled a large number of times to produce an ensemble of $N_r=10^5$ shear realizations that are mutually independent.
-We also find that a small number of independent $N$--body simulations (1 or 2) are necessary to forecast parameter error bars at percent accuracy, while a larger number might be needed to measure accurate feature ensemble means.
-
+Constraining cosmology using weak gravitational lensing consists of
+comparing a measured feature vector of dimension $N_b$ with its
+simulated counterpart. An accurate estimate of the $N_b\times N_b$
+feature covariance matrix $\bb{C}$ is essential to obtain accurate
+parameter confidence intervals. When $\bb{C}$ is measured from a set
+of simulations, an important question is how large this set should
+be. To answer this question, we construct different ensembles of $N_r$
+realizations of the shear field, using a common randomization
+procedure that recycles the outputs from a smaller number $N_s\leq
+N_r$ of independent ray-tracing $N$--body simulations.  We study
+parameter confidence intervals as a function of ($N_s,N_r$) in the
+range $1\leq N_s\leq 200$ and $1\leq N_r\leq 10^5$.  Previous work
+\citep{DodelsonSchneider13} has shown that Gaussian noise in the
+feature covariance lead, at quadratic order, to an $O(1/N_r)$
+degradation of the parameter confidence intervals. Using a variety of
+lensing features measured in our simulations, including shear-shear
+power spectra and peak counts, we show that cubic and quartic
+covariance fluctuations lead to additional $O(1/N_r^2)$ error
+degradation that is not negligible when $N_r$ is only a factor of few
+larger than $N_b$. We study the large $N_r$ limit, and find that a
+single $N$--body simulation ($N_s=1$) can be repeatedly recycled to
+produce as many as $N_r=10^5$ mutually independent shear maps. As a
+result, a small number of simulations ($N_b=1$ or $2$) is sufficient
+to forecast parameter confidence intervals at percent
+accuracy. However, we find that in practice, a larger number of
+simulations might be needed to measure accurate feature means and to
+avoid parameter biases.
+%ZH: I am not sure about the last sentence. I believe it is based on
+%    an overly stringent reading of Fig.2, and that in fact we could
+%    claim here, instead, that N_s=2 simulations are also sufficient
+%    to get the correct mean.
+%    See my comments at the end of the Conclusion section. 
 \end{abstract}
@@
 %
-Weak Gravitational lensing is a promising cosmological probe for constraining the Dark Energy equation of state $w$, and has been considered by a range of past (CFHTLens \citep{cfht1,cfht2}), current (DES \citep{DES}) and future (LSST \citep{LSST}) experiments.
-In an era where cosmology is becoming data driven, accurate numerical simulations of shear fields are becoming important for a number of reasons including the study of baryonic effects \citep{BaryonXiuyuan}, non--Gaussian statistics \citep{PeaksJan,MinkJan,MinkPetri} and various systematics.
-Building cosmological predictions from simulations naturally introduces fluctuations in the forecasts, mainly due to cosmic variance.
-These fluctuations have been shown to have non negligible effects on estimates of features covariance matrices and hence on parameter constraints (see \citep{DodelsonSchneider13}).
-This work studies this issue further, focusing on the number of independent $N$--body simulations that is necessary to run for obtaining accurate estimates of parameter constraints, with particular focus on $w$.
-This paper is organized as follows: in the first paragraph we briefly describe the shear simulation methods we used, as well as the formalism we adopted to compute cosmological parameter constraints.
-We then outline our main findings and discuss the results, as well as future prospects for continuing this study.
+Weak gravitational lensing (WL) is a promising cosmological probe for
+constraining the dark energy equation of state $w$, and has been
+considered by a range of past (CFHTLens \citep{cfht1,cfht2}),
+%ZH: also cite COSMOS survey here...
+ongoing (DES \citep{DES}) and future (LSST \citep{LSST})
+%ZH: also cite Euclid and WFIRST.
+experiments. In an era where cosmology is data driven, accurate
+numerical simulations of shear fields are becoming important for
+several reasons, including the study of baryonic effects
+\citep{BaryonXiuyuan}, 
+%ZH: also cite Joop Schaye's hydro-simulation papers on lensing (Semboloni et al), and earlier papers by Martin White et al...
+Lloyd Knox et al...
+and Zentner et al...
+(I think all of these are in Xiuyuan's paper).
+the computation of non--Gaussian statistics
+\citep{PeaksJan,MinkJan,MinkPetri} 
+%ZH: Add here some citations of other groups - Marian+Bernstein.... Bhuvnesh Jain et al... Refregier et al... Dietrichh+Hartmann... Shirasaki+Yoshida.. (again just copy from our previous papers).
+and the  assessment of various systematics.
+%ZH: cite papers by Jan+Morgan+Bard... and also Chihway Chan...Shirasaki+Yoshida.. and older ones by Dragan Huterer on photo-z errors..
+
+A fundamental issue with predictions from simulations is that the
+finite number of simulations naturally introduces fluctuations in the
+forecasts, due to inevitable sample variance~\footnote{Sample variance is a broad term that has been used in the literature to describe a range of phenomena.
+Throughout this paper, we use it to refer to the fluctuations in an ensemble of simulations, which represent random realizations of the same initial conditions.}.
+%ZH: I think 'cosmic variance' usually refers to observations of the actual sky (which is finite).  
+In general, quantities such as the mean or the variance of any feature
+(e.g. the shear power spectrum at a multipole $\ell$), measured from a
+finite set of simulations, will fluctuate, and can also suffer a bias.
+While biases in the estimates of both the mean and the variance have
+been studied extensively, the impact of fluctuations in the variance
+has received comparatively less attention.  These fluctuations have,
+however, been shown to have non-negligible effects on estimates of
+features covariance matrices and hence on parameter constraints. In
+particular, in the limit of Gaussian fluctuations, the parameter
+confidence limits are degraged by a factor
+$1+O(1/N_r)$~\citep{DodelsonSchneider13}.
+%also cite Taylor Joachimi and Kitching -Morgan
+
+This work studies these issues further, focusing on the number of
+independent $N$--body simulations required for an accurate estimate of
+the parameter constraints.  Ray-tracing simulations that resolve the
+cosmic structures responsible for lensing on arcminute scales are
+limited to physical sizes of hundreds of Mpc, and thus cover a solid
+angle of only $O(10$ deg$^2)$.  As a result, many simulations are
+required to tile a significant fraction of the sky, and to make
+predictions for large ``all-sky'' surveys, such as the ones by DES,
+LSST, Euclid, WFIRST.  In practice, this has led to the wide-spread
+use of ``pseudo-independent'' realizations, i.e. a procedure in which
+one randomizes and re-cycles the output of a single 3D simulation
+multiple times.
+%ZH: Add citations here of papers resorting to this technique
+In light of the forthcoming large surveys, it is imperative to assess
+the statistical validity of this approach, and to ask how many times a
+single simulation can be fairly recycled.  In this paper, we address
+these questions with ensembles of up to $N_r=10^5$ random
+realizations, extracted from up to $N_s=200$ independent ray-tracing
+N-body simulations. We focus in particular on the parameter $w$, and
+on two different statistics: the (convergence) power spectrum and
+the number counts of peaks.
+
+This paper is organized as follows.  In \S~II, we summarize the shear
+simulation methods we utilized, and describe the formalism we adopted
+to forecast cosmological parameter constraints. We then vary the
+number of simulations and the number of pseudo-independent
+realizations, and present our main findings in \S~III. These results
+are discussed further in \S~IV.  We offer our conclusions, and suggest
+follow-up future work in \S~V.
 
@@
 
-\subsection{Shear field simulations}
+\subsection{Ray-tracing simulations of the convergence field}
 \label{shearsim}
 %
-In this paragraph we describe how we constructed our shear field ensembles.
-Background galaxies at redshift $z_s$ are lensed by large scale structure between $z=0$ and $z_s$.
-The shape distortions due to the cosmic shear $\pmb{\gamma}$ can be computed in terms of the dark matter gravitational potential $\Phi(\bb{x},z)$.
-Because the evolution of $\Phi$ in redshift is non--linear, its evolution needs to be computed with numerical simulations.
-We make use of the public code \texttt{Gadget2} \citep{Gadget2}, with which we run a sequence of dark--matter--only $N$--body simulations that track the evolution of the density fluctuations in the large scale structure of the universe.
-We assume a standard $\Lambda$CDM framework with $(\Omega_m,\Omega_\Lambda,h,w,\sigma_8,n_s)=(0.26,0.74,0.72,-1,0.8,0.96)$ and we fix the comoving size of the simulation box to $240\mathrm{Mpc}/h$.
-We fill the box with $512^3$ particles, which correspond to a mass resolution of $10^{10}M_\odot$.
-We assume a uniform galaxy distribution at a constant redshift $z_s=2$ (at which the simulation box has an angular size of $\theta_{box}=3.5\mathrm{deg}$) and we discretize the mass distribution between $z_s$ and the observer at $z=0$ with a sequence of 46 two dimensional lenses of thickness $80\mathrm{Mpc}/h$.
-The surface density on each lens is computed by projecting the three dimensional density measured from \texttt{Gadget2} snapshots.
-We then apply the multi--lens--plane algorithm (see \citep{RayTracingHartlap,RayTracingJain} for example) to trace the deflections of $n_{ray}^2=2048^2$ light rays arranged on a square grid of total size $\theta_{box}$, from $z=0$ to $z_s$.
-The light deflection calculations have been performed with our implementation of multi--lens--plane algorithm, which is part of the \texttt{LensTools} computing package \citep{LensTools} (released under the \texttt{MIT} license).
-Different realizations $r$ of the same shear field $\pmb{\gamma}_r(\pmb{\theta})$ can be generated with different choices of the lenses that lay between the observer and $z_s$.
-The randomization procedure we adopt is the following:
+In this section, we describe how we constructed our shear field
+ensembles. Background galaxies at redshift $z_s$ are lensed by large
+scale structures between $z=0$ and $z_s$. The shape distortions due to
+the cosmic shear $\pmb{\gamma}$ can be computed in terms of the dark
+matter gravitational potential $\Phi(\bb{x},z)$. Because the evolution
+of $\Phi$ with redshift is non--linear, it needs to be computed with
+numerical simulations. We make use of the public code \texttt{Gadget2}
+\citep{Gadget2}, with which we run a sequence of $200$ independent
+dark--matter--only $N$--body simulations that track the evolution of
+the density fluctuations. We assume a standard $\Lambda$CDM background
+universe with the parameters
+$(\Omega_m,\Omega_\Lambda,h,w,\sigma_8,n_s)=(0.26,0.74,0.72,-1,0.8,0.96)$.
+We fix the comoving size of the simulation box to $240\mathrm{Mpc}/h$,
+and use $512^3$ particles, corresponding to a mass resolution of
+$\approx 10^{10}M_\odot$.
+%ZH: ``mass resolution'' here means DM particle mass ?
+
+We assume a uniform galaxy distribution at a constant redshift $z_s=2$
+(at which the simulation box has an angular size of $\theta_{\rm
+  box}=3.5\mathrm{deg}$) and we discretize the mass distribution
+between $z_s$ and the observer at $z=0$ with a sequence of 46 two
+dimensional lenses of thickness $80\mathrm{Mpc}/h$. The surface
+density on each lens plane is computed by projecting the
+three--dimensional density measured from \texttt{Gadget2}
+snapshots. We then apply the multi--lens--plane algorithm (see
+\citep{RayTracingHartlap,RayTracingJain} for example) to trace the
+deflections of $n_{ray}^2=2048^2$ light rays arranged on a square grid
+of total size $\theta_{\rm box}$, from $z=0$ to $z_s$. Our
+implementation of this algorithm is part of the \texttt{LensTools}
+computing package we have been developing \citep{LensTools}, and have
+released under the \texttt{MIT} license. Many different realizations
+$r$ of the same shear field $\pmb{\gamma}_r(\pmb{\theta})$ can be
+generated by picking different lens planes that lie between the
+observer and $z_s$. The randomization procedure we adopt is the
+following:
+%ZH: we should cite some paper here. We didn't invent most of this
+%procedure ourselves (except for maybe the 3-times thicker simulation
+%output, and the random mixing of the planes from different N-body sims ?).
 
 \begin{itemize}
-\item Pick a lens redshift $z_l$, and select the snapshot at $z_l$ from the $i$--th $N$--body simulation at disposal, where $i$ is a random number in $[1,N_s]$
-\item Choose randomly a direction between the three choices ${\bb{n}_x,\bb{n}_y,\bb{n}_z}$: the lens plane will be pependicular to this direction
-\item Choose the cutting point of the plane in the snapshot: because the lens thickness is 1/3 the size of the box, we can cut three different slices of the simulation box for each orientation ${\bb{n}_x,\bb{n}_y,\bb{n}_z}$, which gives a total of 9 choices for generating a lens plane out of a $N$--body snapshot
-\item Perform a periodical random shift of the lens plane along its two directions
-\item Repeat this procedure for each lens redshift $z_l$  
+\item For each lens-plane redshift $z_l$, select the snapshot at $z_l$ from the $i$--th $N$--body simulation, where $i$ is a random integer $i\in [1,N_s]$.
+\item Choose randomly between the three orthogonal directions ${\bb{n}_x,\bb{n}_y,\bb{n}_z}$: the lens plane will be perpendicular to this direction.
+\item Choose the position of the plane along the snapshot: because the lens thickness is 1/3 the size of the box, we can cut three different slices of the simulation box for each orientation ${\bb{n}_x,\bb{n}_y,\bb{n}_z}$.
+This gives a total of 9 choices for generating a lens plane out of a single $N$--body snapshot.
+\item Perform a periodic random shift of the lens plane along its two directions.
+%ZH: should we specify the range of the random shifts (0 to 1/2 the lens plane dimension?)
+\item Repeat the above procedure for each lens-plane redshift $z_l$.
 \end{itemize}  
 %
-This randomization procedure allows us to produce an arbitrary number $N_r$ of mock shear realizations $\pmb{\gamma}_r(\pmb{\theta})$, which however will not be all independent if $N_s$ is not large enough.
-Using a set of 200 independent $N$--body simulations, we construct different ensembles with different choices of $N_s\in[1,200]$, each made of 1000 mock shear realizations.
-We also build an additional ensemble with $N_s=1$ and $10^5$ mocks.
-From each of these mocks we reconstruct the convergence $\kappa_r(\pmb{\theta})$ and measure its angular power spectrum $P^{\kappa\kappa}_r(l)$ defined as
+This randomization procedure allows us to produce an (almost)
+arbitrary number $N_r$ of shear realizations
+$\pmb{\gamma}_r(\pmb{\theta})$. However, these realizations are not
+guaranteed to be independent, if $N_s$ is not large enough. Using the
+set of 200 independent $N$--body simulations, we construct different
+ensembles with different choices of $N_s\in[1,200]$. Each of these
+ensembles consists of the same number $N_r=1000$ of shear
+realizations. We also build an additional ensemble with $N_s=1$ and
+$N_r=10^5$ realizations. For each realization of each ensemble, we
+reconstruct the convergence $\kappa_r(\pmb{\theta})$ 
+%ZH: we should add 2 sentences on how you measured kappa.  Directly from the ray-tracing?
+%   (but above, when you discuss ray-tracing, you mention only gamma).  Or did you do 
+%    Kaiser-Squires on the gamma field ? 
+and measure its
+angular power spectrum $P^{\kappa\kappa}_r(l)$ defined as
 \begin{equation}
@@
 %
-As an additional summary statistic, we consider the counts of local $\kappa$ maxima of a certain height $\kappa_0$, $n_r(\kappa_0)$ (from now on \textit{peak counts}), with varying $\kappa_0$.
-The fact that the ensemble of $N_r$ mocks is not completely independent if $N_s$ is not large enough can have an effect on the covariance estimators of $P^{\kappa\kappa},n(\kappa_0)$.
+As an additional summary statistic, we consider the counts of local
+$\kappa$ maxima of a certain height $\kappa_0$, $n_r(\kappa_0)$
+(hereafter \textit{peak counts}), with varying $\kappa_0$.
+%ZH: state here the range and binning choice of $\kappa_0$
+The fact that the ensemble of $N_r$ realizations is not completely
+independent if $N_s$ is not large enough can have an effect on the
+covariance estimators of both $P^{\kappa\kappa}$ and $n(\kappa_0)$.
 
-\subsection{Parameter inference}
+%ZH: it would be logical to mention the other w,Sig,Om, sims here, and point to \ref{simtable})
+
+\subsection{Cosmological parameter inference}
 %
-Let $\bbh{d}$ a feature of dimension $N_b$, $\bb{d}(\bb{p})$ be the smooth expectation of this feature at a point $\bb{p}$ in parameter space (which has a dimension $N_p$) and $\bb{C}$ be the $N_b\times N_b$ feature covariance matrix.
-For the purpose of this work $\bb{p}$ is the triplet $(\Omega_m,w,\sigma_8)$ and $\bb{d}$ is one of the features listed in Table \ref{featuretable}.
-While, in some cases, $d(\bb{p})$ can usually be predicted reasonably accurately by already existing emulators (see \citep{coyote2,Nicaea} for example), the matter is more complicated for covariance matrices.
-Estimating $\bb{C}$ from simulations involves generating a series of mock realizations $\bbh{d}_r$ with $r=1...N_r$ and estimating the sample covariance $\bbh{C}$
+
+Let $\bbh{d}$ be a single estimate for a feature of dimension $N_b$, 
+%ZH: ``Hat'' here refers to an estimator?
+$\bb{d}(\bb{p})$ be the
+%smooth expectation
+%ZH: I believe ``smooth expectation'' means true mean value, yes?
+true mean value of this feature at a point $\bb{p}$ in parameter space
+(which has a dimension $N_p$) and $\bb{C}$ be the $N_b\times N_b$
+feature covariance matrix. For the purpose of this work $\bb{p}$ is
+the triplet $(\Omega_m,w,\sigma_8)$ and $\bb{d}$ is one of the
+features -- either a power spectrum or a peak count -- in Table
+\ref{featuretable}. While in many cases $\bb{d}(\bb{p})$ can be
+predicted reasonably accurately by already existing emulators (see
+\citep{coyote2,Nicaea} for example), the matter is more complicated
+for covariance matrices.
+%ZH: I am missing the point here.  Why is covariance matrix ``more complicated'' ?
+%    Even to estimate a mean, one has to ``generate a series of mock realizations''.
+%    Unless you are willing to equate a single realization as the mean.   But then
+%    by the same logic, you could estimate the covariance matrix from two realizations.
+%    Please clarify what you mean...  maybe I am missing something?  Or you simply mean
+%    that published emulators usually do not emulate the cov.matrix (even though they could)?
+%    Note that there is a paper by Schneider and Knox, in which they do an interpolation of the
+%    power spectrum covariance matrix.
+Estimating $\bb{C}$ from simulations involves generating a series of
+mock realizations $\bbh{d}_r$ with $r=1...N_r$ and computing the
+sample covariance $\bbh{C}$,
 
 \begin{equation}
-\bb{\bar{d}} = \frac{1}{N_r}\sum_{r=1}^{N_r} \bbh{d}_r
+\bb{\bar{d}} = \frac{1}{N_r}\sum_{r=1}^{N_r} \bbh{d}_r,
 \end{equation}
@@
 \label{covest}
-\bbh{C} = \frac{1}{N_r-1}\sum_{r=1}^{N_r} (\bbh{d}_r - \bar{\bb{d}}) (\bbh{d}_r - \bar{\bb{d}})^T
+\bbh{C} = \frac{1}{N_r-1}\sum_{r=1}^{N_r} (\bbh{d}_r - \bar{\bb{d}}) (\bbh{d}_r - \bar{\bb{d}})^T.
 \end{equation}
 %
-Assuming a normal feature likelihood, together with a flat prior on the parameter space, the parameter posterior distribution $\mathcal{L}(\bb{p}\vert\bbh{d}_{obs})$ given an observed instance of $\bbh{d}$, which we call $\bbh{d}_{obs}$, can be obtained using Bayes theorem
+Assuming a normal feature likelihood, together with a flat prior on
+the parameter space, the parameter posterior distribution
+$\mathcal{L}(\bb{p}\vert\bbh{d}_{\rm obs})$ given an observed instance of
+$\bbh{d}$, which we call $\bbh{d}_{\rm obs}$, follows from Bayes' theorem,
+%
 \begin{equation}
 \label{posteriorbayes}
--2\log\mathcal{L}(\bb{p}\vert\bbh{d}_{obs}) = (\bbh{d}_{obs}-\bb{d}(\bb{p}))^T\bbh{C}^{-1}(\bbh{d}_{obs}-\bb{d}(\bb{p}))
+-2\log\mathcal{L}(\bb{p}\vert\bbh{d}_{\rm obs}) = [\bbh{d}_{\rm obs}-\bb{d}(\bb{p})]^T\bbh{C}^{-1}[\bbh{d}_{\rm obs}-\bb{d}(\bb{p})].
 \end{equation}
 %
-For the sake of simplicity, we approximate the posterior as a Gaussian around its maximum.
-This is easily done approximating the simulated feature at first order around a point $\bb{p}_0$ (that ideally is the maximum of (\ref{posteriorbayes}))
+For the sake of simplicity, we approximate the posterior as a Gaussian
+around its maximum. This corresponds to Taylor-expanding the simulated
+feature to first order around a point $\bb{p}_0$ (ideally the maximum
+of Eq.~\ref{posteriorbayes}):
+%
 \begin{equation}
-\bb{d}(\bb{p}) \approx \bb{d}_0 + \bb{d}_0^\prime(\bb{p}-\bb{p}_0) 
+\bb{d}(\bb{p}) \approx \bb{d}_0 + \bb{d}_0^\prime(\bb{p}-\bb{p}_0).
 \end{equation}
 %
-To measure the feature derivatives $\bb{d}'_0$ with respect to cosmology, we make use of the public code \texttt{NICAEA} \citep{Nicaea} for the power spectrum, and we use an independent simulation set (that contains mocks at different combinations of $(\Omega_m,w,\sigma_8)$, see Table \ref{simtable}) for the peak counts.
+
+To measure the derivatives of the features $\bb{d}'_0$ with respect to
+the cosmological parameters, we make use of the public code
+\texttt{NICAEA} \citep{Nicaea} for the power spectrum, and we use an
+independent simulation set (containing simulations with a variety of
+different combinations of $(\Omega_m,w,\sigma_8)$, see Table
+\ref{simtable}) for the peak counts.
 
@@
 \midrule
-
-0.26 & -1 & 0.8 & $1\div 200$ & 16 \\
+%
+0.26 & -1 & 0.8 & $1$ to $200$ & 16 \\
 0.29 & -1 & 0.8 & 1 & 1 \\
@@
 0.26 & -1 & 0.6 & 1 & 1 \\
-
+%
 \bottomrule
@@
 \end{center}
-\caption{Summary table of the shear ensembles used in this work.}
+\caption{Summary of the shear ensembles used in this work.}
+%ZH: So each of these have N_r=1000, yes?  You should state this here. And also,
+%    Add the ensemble with N_s=1, N_r=10^5 to this table.
+%    Also: point the reader to this table in the text, up front, when the 
+%    ensembles are first discussed.
 \label{simtable}
@@
 
-We can build the estimator for the posterior maximum $\bbh{p}$, given the observation $\bbh{d}_{obs}$, as follows:
+We can build the estimator for the posterior maximum $\bbh{p}$, given
+the observation $\bbh{d}_{\rm obs}$, as follows:
 %
@@
 \label{estimatormean}
-\bbh{p} = \bb{p}_0 + \bbh{T}(\bbh{d}_{obs}-\bb{d}_0)
+\bbh{p} = \bb{p}_0 + \bbh{T}(\bbh{d}_{\rm obs}-\bb{d}_0),
 \end{equation}
@@
 \begin{equation}
-\bbh{T} = (\bb{d}_0'^T\bbh{C}^{-1}\bb{d}_0')^{-1}\bb{d}_0'^T\bbh{C}^{-1}
+\bbh{T} = (\bb{d}_0'^T\bbh{C}^{-1}\bb{d}_0')^{-1}\bb{d}_0'^T\bbh{C}^{-1}.
 \end{equation}
 %
-Because $\bbh{p}$ is estimated using a noisy data instance $\bbh{d}_{obs}$, its estimate will be scattered around the true value $\langle\bbh{p}\rangle_O$.
-In the following we use the $\langle\rangle_O$ notation for expectation values taken with respect to observations, while we keep the notation $\langle\rangle$ for expectation values taken with respect to the simulations.
-Defining the \textit{precision matrix} $\bbh{\Psi}=\bbh{C}^{-1}$, we can express the estimator of the observational scatter in $\bbh{p}$
+Because $\bbh{p}$ is estimated using a single noisy data instance
+$\bbh{d}_{\rm obs}$, its estimate will be scattered around the true
+value $\langle\bbh{p}\rangle_O$. In the following we use the
+$\langle\rangle_O$ notation for expectation values taken with respect
+to observations, while we keep the notation $\langle\rangle$ for
+expectation values taken with respect to the simulations. Defining the
+\textit{precision matrix} $\bbh{\Psi}=\bbh{C}^{-1}$, we can express
+the estimator of the observational scatter in $\bbh{p}$:
 
@@
 \label{estimatorcovariance}
-\h{\Sigma}_\bb{p} = \bbh{F}^{-1}\bb{d}_0'^T\bbh{\Psi}\langle(\bbh{d}_{obs}-\bb{d}_0)(\bbh{d}_{obs}-\bb{d}_0)^T\rangle_O\bbh{\Psi}\bb{d}_0'\bbh{F}^{-1}
+\h{\Sigma}_\bb{p} = \bbh{F}^{-1}\bb{d}_0'^T\bbh{\Psi}\langle(\bbh{d}_{\rm obs}-\bb{d}_0)(\bbh{d}_{\rm obs}-\bb{d}_0)^T\rangle_O\bbh{\Psi}\bb{d}_0'\bbh{F}^{-1},
 \end{equation}
@@
 \label{estimatorfisher}
-\bbh{F} = \bb{d}_0'^T\bbh{\Psi}\bb{d}_0'
+\bbh{F} = \bb{d}_0'^T\bbh{\Psi}\bb{d}_0'.
 \end{equation}
 %
-Where we introduced the Fisher matrix estimator $\bbh{F} = \bb{d}_0'^T\bbh{\Psi}\bb{d}_0'$ and, for simplicity, we assumed $\langle\bbh{d}_{obs}\rangle_O=\bb{d}_0$, so that $\langle(\bbh{d}_{obs}-\bb{d}_0)(\bbh{d}_{obs}-\bb{d}_0)^T\rangle_O=\bb{C}$.
-When we perform an observation $\bbh{d}_{obs}$, the parameter estimate $\bbh{p}$ is a random draw from a probability distribution with variance $\h{\Sigma}_\bb{p}$, which inherits noise from the simulations.
-The noise in the covariance estimator (\ref{covest}) and its inverse $\bbh{\Psi}$ propagates all the way to the posterior (\ref{posteriorbayes}), the parameter estimate (\ref{estimatormean}) and its variance (\ref{estimatorcovariance}).
-Following \citep{DodelsonSchneider13,Taylor12,MasumotoWishart} we compute the expectation value of (\ref{estimatorcovariance}) over simulations, $\langle\h{\Sigma}_\bb{p}\rangle$, up to $O(1/N_r^2)$ by expanding (\ref{estimatorcovariance}) to quartic order in the $\bbh{\Psi}$ statistical fluctuations.
-Indicating the noiseless parameter covariance as $\Sigma_\bb{p}=\bb{F}^{-1}$, the result we get is \footnote{The details of the calculation are given in Appendix A}
+Here we introduced the familiar Fisher matrix estimator $\bbh{F} =
+\bb{d}_0'^T\bbh{\Psi}\bb{d}_0'$ and, for simplicity, we assumed
+$\langle\bbh{d}_{\rm obs}\rangle_O=\bb{d}_0$, so that
+$\langle(\bbh{d}_{\rm obs}-\bb{d}_0)(\bbh{d}_{\rm
+  obs}-\bb{d}_0)^T\rangle_O=\bb{C}$.  When we perform an observation
+$\bbh{d}_{\rm obs}$, the parameter estimate $\bbh{p}$ is a random draw
+from a probability distribution with variance $\h{\Sigma}_\bb{p}$,
+which inherits noise from the simulations. The noise in the covariance
+estimator (Eq.~\ref{covest}) and in its inverse $\bbh{\Psi}$ propagate
+all the way to the posterior (Eq.~\ref{posteriorbayes}), the parameter
+estimate (Eq.~\ref{estimatormean}) and its variance
+(Eq.~\ref{estimatorcovariance}). Following
+refs.~\citep{DodelsonSchneider13,Taylor12,MasumotoWishart} we compute
+the expectation value of Eq.~(\ref{estimatorcovariance}) over
+simulations, $\langle\h{\Sigma}_\bb{p}\rangle$, up to $O(1/N_r^2)$ by
+expanding Eq.~(\ref{estimatorcovariance}) to quartic order in the
+statistical fluctuations of $\bbh{\Psi}$. Denoting the noiseless
+parameter covariance, i.e. the usual Fisher matrix, as
+$\Sigma_\bb{p}=\bb{F}^{-1}$, we find the result~\footnote{The
+  details of the calculation are given in Appendix A.}:
 
@@
 \label{quarticdegradation}
-\langle\h{\Sigma}_\bb{p}\rangle = \Sigma_\bb{p}\left[1+\frac{N_b-N_p}{N_r}+\frac{(N_b-N_p)(N_b-N_p+2)}{N_r^2}\right] + O\left(\frac{1}{N_r^3}\right)
+\langle\h{\Sigma}_\bb{p}\rangle = \Sigma_\bb{p}\left[1+\frac{N_b-N_p}{N_r}+\frac{(N_b-N_p)(N_b-N_p+2)}{N_r^2}\right] + O\left(\frac{1}{N_r^3}\right).
 \end{equation}
@@
 %
-Next, we restrict ourselves to the large $N_r$ limit, and we further investigate the behavior of the $O(1/N_r)$ term.
-We consider three cases \footnote{The details of these calculations are given in Appendix B}:
+Next, we restrict ourselves to the large $N_r$ limit, and we further
+investigate the behavior of the $O(1/N_r)$ term. We consider three
+cases \footnote{The details of these calculations are given in
+  Appendix B}:
+
 \begin{enumerate}
-\item If the true data covariance $\bb{C}$ is known, the estimator (\ref{estimatorcovariance}) is biased, and the dominant contribution of the bias comes from the second order fluctuations in $\bbh{\Psi}$.
-Once the expectation values over simulations are taken, the bias sums up to
+\item If the true data covariance $\bb{C}$ is known, the estimator in
+  Eq.~(\ref{estimatorcovariance}) is biased, and the dominant
+  contribution of the bias comes from the second order fluctuations in
+  $\bbh{\Psi}$. Once the expectation values over simulations are
+  taken, the bias sums up to
 
@@
 \label{dodelsonscaling}
-\langle\h{\Sigma}_\bb{p}\rangle=\Sigma_\bb{p}\left(1+\frac{N_b-N_p}{N_r}\right)
+\langle\h{\Sigma}_\bb{p}\rangle=\Sigma_\bb{p}\left(1+\frac{N_b-N_p}{N_r}\right).
 \end{equation}
 %
-This is the result obtained by \citep{DodelsonSchneider13}.
+This is the result obtained by ref.~\citep{DodelsonSchneider13}.
 
-\item Usually the true covariance is not known, and it is tempting to plug in its estimator $\bbh{C}$, measured from the same simulation set we use to compute $\bbh{\Psi}$.
-This approach has been used before in the literature (see \citep{MinkPetri,MinkShirasaki} for example).
-If we do that, and we do not correct for the $\bbh{\Psi}$ bias, the parameter variance will have a contribution from both the second and first order fluctuations in $\bbh{\Psi}$, which now have a non zero expectation value.
-In this case the bias sums up to
+\item Usually the true data covariance is unknown, and it is tempting
+  to plug in its estimator $\bbh{C}$, measured from the same
+  simulation set we use to compute $\bbh{\Psi}$. This approach has
+  been used before in the literature
+  (e.g.~\citep{MinkPetri,MinkShirasaki}). If this is done without
+  correcting for the bias in $\bbh{\Psi}$ (see Eq.~\ref{firstmoment}
+  below), 
+%ZH: we should probably cite Hartlap et al. and Taylor et al. here for this Psi bias.  (I assume this is what you mean in eq. 19)
+  the parameter variance will have a contribution from both the second
+  and first-order fluctuations in $\bbh{\Psi}$, which now have a
+  nonzero expectation value. In this case the bias sums up to
+%
 \begin{equation}
 \label{mockscalinguncorrected}
-\langle\h{\Sigma}_\bb{p}\rangle=\Sigma_\bb{p}\left(1-\frac{N_b-N_p}{N_r}\right)
+\langle\h{\Sigma}_\bb{p}\rangle=\Sigma_\bb{p}\left(1-\frac{N_b-N_p}{N_r}\right).
 \end{equation}
 
-\item If we repeat the same exercise as above, but we correct for the bias in the precision matrix estimator, we are left with
+\item If we repeat the same exercise as above, but we correct for the
+  bias in the precision matrix estimator, we are left with
 
@@
 \label{mockscalingcorrected}
-\langle\h{\Sigma}_\bb{p}\rangle=\Sigma_\bb{p}\left(1+\frac{1+N_p}{N_r}\right)
+\langle\h{\Sigma}_\bb{p}\rangle=\Sigma_\bb{p}\left(1+\frac{1+N_p}{N_r}\right).
 \end{equation}
@@
 %
-The error degradation  in each parameter $p$, at dominant order, scales as $D/N_r$, where $D=N_b-N_p,N_p-N_b,1+N_p$ for cases 1,2,3 respectively.
-This means that, when parameter errors are estimated purely from simulations, and the same simulation set is used to estimate both $\bbh{C},\bbh{\Psi}$, these errors tend to decrease with $N_b$ (case 2), or at best remain constant (case 3), while the distribution of $\bbh{p}$ has still a variance that increases with $N_b$.
-This typically leads to underestimates in parameter errors.
-We test the scaling relation
+The error degradation in each parameter $p$, at leading order, scales
+as $D/N_r$, where $D=N_b-N_p$, $N_p-N_b$, and $1+N_p$ for cases 1, 2,
+and 3, respectively.
+%ZH: It was not clear to me what the main point of the text below was. I paraphrased it slightly. OK?
+%This means that, when parameter errors are
+%estimated purely from simulations, and the same simulation set is used
+%to estimate both $\bbh{C},\bbh{\Psi}$, these errors tend to decrease
+%with $N_b$ (case 2), or at best remain constant (case 3), while the
+%distribution of $\bbh{p}$ has still a variance that increases with
+%$N_b$. This typically leads to underestimates in parameter errors. 
+Note that in the last case, which is most relevant when fitting actual
+data, the noise in both $\bbh{C}$ and $\bbh{\Psi}$ together degrade
+the confidence limits.  However, this degradation turns out to be less
+severe than in the idealized case 1 of a noiseless $\bbh{C}$ (assuming
+$N_b\gg N_p$).  We also note that the distribution of $\bbh{p}$ has a
+variance ($\Sigma_\bb{p}$) that increases with $N_b$, but the bias in
+$\h{\Sigma}_\bb{p}$ is independent of $N_b$ in the realistic case 3.
+
+We derived the scaling relations of the form
+%
 \begin{equation}
@@
 %
-on our simulations for high and small $N_r$.
-We use notation $\h{\sigma}^2_p=\h{\Sigma}_{pp}$ and we indicate as $\sigma^2_{p,\infty}$ the expectation value of the variance in the limit of infinite mocks $N_r\rightarrow\infty$.
-We call $D$ the \textit{effective dimensionality} of the feature space (which, as seen before, can be negative in some cases).
-We compute the expectation values of $\h{\sigma}^2_p$ (equations (\ref{estimatorcovariance}),(\ref{ourscaling})) averaging over 100 random resamplings of our shear ensembles.
-For the true feature covariance matrix $\langle(\bbh{d}-\bb{d}_0)(\bbh{d}-\bb{d}_0)^T\rangle=\bb{C}$ we use the estimated covariance from a grand ensemble built with the union of all the ensembles with different $N_s$.
+above by assuming that the noise in both $\bbh{C}$ and $\bbh{\Psi}$ is
+Gaussian.  We next directly test these scaling relations using our
+simulations, in the limits of both high and low $N_r$.
+%ZH: It is still a little unclear here what is being tested.  Is it the Gaussianity assumption? I added that.
+%    But perhaps you had some other issue in mind.
+We use the notation $\h{\sigma}^2_p=\h{\Sigma}_{pp}$ 
+%ZH: I am confused.  Why is a new symbol \sigma necessary here, on top of \Sigma ?
+%    (And also: here you write \Sigma_pp, but above it was denoted \Sigma_p  )
+and we indicate by $\sigma^2_{p,\infty}$ the expectation value of the
+variance in the limit of an infinite number of realizations
+$N_r\rightarrow\infty$.  We call $D$ the \textit{effective
+  dimensionality} of the feature space (which, as seen before, can be
+negative in some pathological cases).
+%ZH: I added pathological here.  Do you agree?  It's only negative in case 1, when
+%    N_p > N_b (which is impossible -- cannot measure N_p parameters with N_b observables)
+%    or in case 2 (when N_b > N_p, so that's OK, but this case ust means we ``forgot'' to correct for the psi-bias).
+We compute the expectation values of $\h{\sigma}^2_p$
+(equations~\ref{estimatorcovariance} and \ref{ourscaling}) by
+averaging over 100 random resamplings of our shear ensembles. For the
+true feature covariance matrix
+$\langle(\bbh{d}-\bb{d}_0)(\bbh{d}-\bb{d}_0)^T\rangle=\bb{C}$ we use
+the estimated covariance from a grand ensemble built with the union of
+all the ensembles with different $N_s$.
 
-The true parameter variance $\sigma^2_{p,\infty}(N_s)$ in principle depends on the number of independent $N$--body simulations $N_s$, which appears in the randomization procedure we describe in \S~\ref{shearsim}.
-The reason for this can be found in that, if $N_s$ is not big enough, the different shear realizations cannot be all independent, and hence the true variance $\sigma^2_{p,\infty}(N_s\rightarrow\infty)$ cannot be recovered for low $N_s$ even if $N_r$ is large.
-In the next paragraph we outline our main findings.
+The true parameter variance $\sigma^2_{p,\infty}(N_s)$ in principle
+can depend on the number of independent $N$--body simulations $N_s$,
+which appears in the randomization procedure described in
+\S~\ref{shearsim} above. This is because if $N_s$ is not large enough,
+the different shear realizations cannot be all independent, and hence
+the true variance $\sigma^2_{p,\infty}(N_s\rightarrow\infty)$ cannot
+be recovered for low $N_s$ even if $N_r$ is arbitrarily large. In the
+next section, we present our main findings.
 
@@
 \includegraphics[scale=0.4]{Figures/ps_pdf.eps}
-\caption{PDF of the $\kappa$ power spectrum,$\mathcal{L}(P_l^{\kappa\kappa})$, at four selected multipoles $l=115,344,1349,5283$, for different shear ensembles constructed with $N_s=$1 (black), 2 (blue), 5 (green), 50 (red), 100 (purple).
-The thick black lines correspond to an ensemble generated with $N_s=1$ and $10^5$ mock realizations.}
+\caption{PDF of the $\kappa$ power spectrum
+  $\mathcal{L}(P_l^{\kappa\kappa})$ at four selected multipoles
+  $\ell=115,344,1349,5283$, for different shear ensembles constructed
+  from on $N_s=$1 (black), 2 (blue), 5 (green), 50 (red), and 100
+  (purple) independent N-body simulations. Each curve is based on
+  $N_r=1000$ realizations.
+%ZH: I added the Nr=1000 above. Yes?
+  The thick
+  black curves correspond to ensembles generated with $N_s=1$ and
+  $N_r=10^5$. For $N_s\geq2$, the distributions appear
+  similar to the eye; this similarity is confirmed by the comparisons
+  in Figures \ref{means_ns} and \ref{ps_var} below. }
+%added last two sentences. -Morgan
+%Also: Thick black line draws the eye and looks like the most significant thing on the plot. replace with dotted black line or something else that stands out less.-Morgan
+%ZH: Also, include a label ``N_r=10^5'' with the other N_s=... labels in the figure panels 
+%   (it is just confusing why there are labels for all the other curves, but not for the thick black)
 \label{ps_pdf}
@@
 \includegraphics[scale=0.3]{Figures/means_ns.eps}
-\caption{Means of shear features $d$ measured from different shear ensembles.
-The quantities shown are the differences between mean features measured from ensemble with varying $N_s$, with respect to the means measured from the $N_s=200$ ensemble, in units of the statistical error measured from the $N_s=200$ ensemble.
-The colored lines refer to shear-shear power spectra measured at $l=115$ (black), 1027 (cyan), 5283 (green) and peak counts of height $\kappa_0=0.05$ (red), 0.17 (purple), 0.28 (orange).}
+\caption{The mean value 
+ $\bb{\bar{d}}$
+% $d$  
+%ZH: I think you mean  \bb{\bar{d}} here?  You introduced a lot of different
+%    subtle notations in the previous section, so we should  follow those ....
+  of various features, measured from ensembles created from different
+  numbers $N_s$ of simulations.  For each case, the difference compared
+  to the mean in the $N_s=200$ ensemble is shown, in units of the
+  statistical error measured in the $N_s=200$ ensemble.  The colored
+  curves refer to shear-shear power spectra measured at $\ell=115$
+  (black), 1027 (cyan), and 5283 (green), and peak counts 
+%of
+%ZH: I replace ``of'' with ``above''.  These are cumulative peak counts N(>kappa_0) ?
+%    Or do you mean differential counts in some delta-kappa_0 bins?   Then you should
+%    correct the text (and state the bin width).  Table II contains some kappa-bins
+%    but no obvious relation to the 0.05, 0.17  and 0.28 mentioned here...
+  with height above $\kappa_0=0.05$ (red), 0.17 (purple), and 0.28
+  (orange).  For $N_s\geq 2$, the means are statistically
+  indistinguishable from the means measured in the ensemble with $N_s=200$.}
+% added last sentence stating conclusion to be drawn from the figure-Morgan
+%ZH:  Good idea.  All figures captions should similarly state a conclusion!
+%ZH:  What is the horizontal dashed line?  It is never mentioned in the caption or
+%     the text.   I guess you decided to mark the ``0.1 sigma'' deviation?
+%     We should state that.    I suppose this is what Morgan refers to by 
+%    ``statistically indistinguishable'' ....  0.1 sigma.
 \label{means_ns}
@@
 \includegraphics[scale=0.3]{Figures/ps_variance.eps}
-\caption{Variance of the $\kappa$ power spectrum as a function of the multipole $l$, in units of the expected gaussian variance from equation (\ref{gaussianvar}).
-The variance is measured from different shear ensembles with $N_s=$1 (black), 2 (blue), 5 (green), 10 (red), 50 (purple), 100 (orange).
-}
+\caption{Variance of the $\kappa$ power spectrum as a function of the
+  multipole $\ell$, in units of the expected Gaussian variance from
+  equation (\ref{gaussianvar}). The variance is measured from
+  different shear ensembles based on $N_s=$1 (black), 2 (blue), 5
+  (green), 10 (red), 50 (purple), or 100 (orange) N-body simulations. 
+%ZH: Added ``conclusion'':
+  Non-Gaussianities of the underlying structures increase the variance on
+  small scales, but no clear trend with $N_s$ can be identied on any scale.}
 \label{ps_var}
@@
 \includegraphics[scale=0.3]{Figures/curving_nb.eps}
-\caption{Expectation value of the $w$ variance computed with equation (\ref{estimatorcovariance}) as a function of $1/N_r$, for the features outlined in Table \ref{featuretable}.
-The dashed and solid lines show the the theory predictions from equation (\ref{quarticdegradation}) at orders $O(1/N_r),O(1/N_r^2)$.
-The asymptotic variance $\sigma^2_{w,\infty}$ has been computed from a linear regression of $\langle\h{\sigma}^2_w\rangle$ vs $1/N_r$ for $N_r>500$.}
+\caption{Expectation value of the variance of $w$ computed from
+  equation (\ref{estimatorcovariance}), shown as a function of
+  $1/N_r$. The different symbols and colors correspond to the features
+  listed in Table~\ref{featuretable}.
+%ZH: It would be better to write the features on the legend embedded in the figure.
+%    Why make the reader flip back-and-forth between the figure and the Table ?
+  The dashed and solid curves show the analytic predictions from
+  equation (\ref{quarticdegradation}) at orders $O(1/N_r)$ and
+  $O(1/N_r^2)$, respectively. The asymptotic variance
+  $\sigma^2_{w,\infty}$ has been computed from a linear regression of
+  $\langle\h{\sigma}^2_w\rangle$ vs $1/N_r$ for $N_r>500$. The figure
+  clearly shows that terms beyond $O(1/N_r)$ need to be considered,
+  unless $N_r\gg N_b$.}
+%added last sentence stating conclusion to be drawn from the figure-Morgan
+%in legend box change line that reads Nb=7 divided by 8
 \label{curvingnb}
@@
 \includegraphics[scale=0.3]{Figures/scaling_nr.eps}
-\caption{Bias in the $w$ variance, $\langle\h{\sigma}^2_w\rangle-\sigma^2_{w,\infty}$, as a function of the number of mock realizations $N_r$ used in the feature covariance estimator (\ref{covest}).
-Results for different mock ensembles generated with $N_s=$1 (black), 2 (blue), 5 (green), 50 (red), 100 (purple) are shown.
-The figure shows both the measured trends (solid lines) and their best fits according to equation (\ref{ourscaling}).
-The thick black line correspond to an ensemble generated with $N_s=1$ and $10^5$ mock realizations.
-}
+\caption{Bias in the variance of $w$,
+  $\langle\h{\sigma}^2_w\rangle-\sigma^2_{w,\infty}$, as a function of
+  the number of realizations $N_r$ used to estimate the covariance
+  (eq.~\ref{covest}). Results for different ensembles, generated from
+  $N_s=$1 (black), 2 (blue), 5 (green), 50 (red), and 100 (purple)
+  simulations are shown. The figure shows both the measured trends
+  (solid lines) and their best fits based on eq.~(\ref{ourscaling}),
+  with $D$ treated as a free parameter.
+%ZH: We need to explain what you mean by best-fit (presumably you treat ``D'' as a free parameter).
+%   I added that. But if you meant something else, please correct.
+  The thick black curve corresponds to an ensemble of $N_r=10^5$
+  realizations from a single simulation ($N_s=1$).
+%ZH: I added 'conclusion':
+  No systematic deviation from the expected scaling is seen, even in
+  the extreme last case.  }
 \label{wvar_nr}
@@
 \includegraphics[scale=0.3]{Figures/scaling_ns.eps}
-\caption{Variance on $w$ in the limit $N_r\rightarrow\infty$, varying the mock ensemble used to compute the covariance estimator (\ref{covest}).
-We show the dependence of $\sigma_{w,\infty}^2(N_s)$ in units of the mean over $N_s$, for the power spectrum logarithmically binned (black), the power spectrum linearly binned (red) and the peak counts (green).}
+\caption{The variance of $w$ in the limit of $N_r\rightarrow\infty$,
+%ZH: state here what N_r was actually used to approximate the infinity limit
+  varying the number of simulations $N_s$ used in the ensemble to
+  estimate the covariance (eq.~\ref{covest}). We show the dependence
+  of $\sigma_{w,\infty}^2(N_s)$ in units of the mean over $N_s$, 
+%ZH: Just to make sure: what you mean here is an averaging of sigma_infty over the 16 different
+%    cases of N_s ?   
+  for
+  the power spectrum logarithmically binned (black), the power
+  spectrum linearly binned (red) and the peak counts (green).
+%ZH: What ell and kappa ranges were used?
+%XH: Added conclusion:
+  No trend with $N_s$ is seen for $N_s\geq 2$, and the
+  differences are only 1\%.  }
 \label{wvar_ns}
@@
 \midrule
-Power Spectrum, log binning  & $l \in [100,800] $ & 8 & $\times$ & black  \\ 
-Power Spectrum, log binning  & $l \in [1000,6000] $ & 7 & $\blacksquare$ & black  \\ 
-Power Spectrum, log binning  & $l \in [100,6000] $ & 15 & \textcolor{red}{$\bullet$} & \textcolor{red}{red}  \\
-Power Spectrum, linear binning  & $l \in [100,2000] $ & 15 & \textcolor{red}{$+$} & \textcolor{red}{red}  \\ 
-Power Spectrum, linear binning  & $l \in [2500,4500] $ & 15 & \textcolor{red}{$\times$} & \textcolor{red}{red}  \\
-Power Spectrum, linear binning  & $l \in [100,4500] $ & 30 & \textcolor{OliveGreen}{$\bullet$} & \textcolor{OliveGreen}{green}  \\ 
-Power Spectrum, linear binning  & $l \in [100,6000] $ & 39 & \textcolor{blue}{$\bullet$} & \textcolor{blue}{blue}  \\ \hline
+Power Spectrum, log binning  & $\ell \in [100,800] $ & 8 & $\times$ & black  \\ 
+Power Spectrum, log binning  & $\ell \in [1000,6000] $ & 7 & $\blacksquare$ & black  \\ 
+Power Spectrum, log binning  & $\ell \in [100,6000] $ & 15 & \textcolor{red}{$\bullet$} & \textcolor{red}{red}  \\
+Power Spectrum, linear binning  & $\ell \in [100,2000] $ & 15 & \textcolor{red}{$+$} & \textcolor{red}{red}  \\ 
+Power Spectrum, linear binning  & $\ell \in [2500,4500] $ & 15 & \textcolor{red}{$\times$} & \textcolor{red}{red}  \\
+Power Spectrum, linear binning  & $\ell \in [100,4500] $ & 30 & \textcolor{OliveGreen}{$\bullet$} & \textcolor{OliveGreen}{green}  \\ 
+Power Spectrum, linear binning  & $\ell \in [100,6000] $ & 39 & \textcolor{blue}{$\bullet$} & \textcolor{blue}{blue}  \\ \hline
 Low peaks  & $\kappa_0 \in [-0.06,0.09] $ & 15 & \textcolor{red}{$+$} & \textcolor{red}{red}  \\ 
@@
 
-In this section we outline the main results of this work.
-We show the qualitative behavior of a variety of features $\bbh{d}_r$ probability distribution function (PDF) in ensembles built with different $N_s$.
-Figure \ref{ps_pdf} shows the power spectrum PDF at four selected multipoles, Figure \ref{means_ns} shows the dependence of feature ensemble means on $N_s$, while Figure \ref{ps_var} shows the variance in each measure power spectrum multipole.
-This last result is compared to the one that would be obtained assuming that the convergence $\kappa$ is a Gaussian random field
+In this section we present the main results of this work. We show the
+qualitative behavior of a variety of feature $\bbh{d}_r$ probability
+distribution functions (PDFs) in ensembles built with different $N_s$
+and $N_r$. In Figure~\ref{ps_pdf}, we show the PDF of the power
+spectrum at four selected multipoles, spanning the linear ($\ell=115$)
+to the nonlinear ($\ell=5283$) regime. In Figure~\ref{means_ns}, we
+shows the ensemble mean for these power spectra, as well as for peak
+counts above three different $\kappa$ thresholds (corresponding to
+$\approx 2-12\sigma$ peaks), as a function of $N_s$.
+%ZH: added above 2-12.  OK ?
+In Figure~\ref{ps_var}, we show the variance of the power spectrum at
+each multipole, as a function of $N_s$, in units of the variance
+expected if the convergence $\kappa$ was a Gaussian random field
+%
+%ZH:  I changed ``l''  to ``\ell'' in many places, for the multipole
 \begin{equation}
 \label{gaussianvar}
-\mathrm{Var}(P^{\kappa\kappa}(l)) = \frac{P^{\kappa\kappa,2}(l)}{N_{eff}(l)}
+\mathrm{Var}(P^{\kappa\kappa}_\ell) = \frac{(P^{\kappa\kappa}_\ell)^2}{N_{\rm eff}(\ell).}
 \end{equation}
 %
-where $N_{eff}(l)$ is the number of independent modes used to estimate the power spectrum at $l$.
-To measure $P^{\kappa\kappa}(l),N_{eff}(l)$, we compute the real Fourier transform of the pixelized map $\kappa_r(\pmb{\theta})$ with the FFT algorithm.
-Each Fourier pixel $(i_x,j_y)$ corresponds to a mode $(l_x,l_y)=2\pi(i_x,i_y)/\theta_{box}$, with $i_x=-n_{ray}/2,...,n_{ray}/2$ and $i_y=0,...,n_{ray}/2$.
-We count the number of pixels $N(l)$ that fall inside a multipole bin $(l_1,l_2)$.
-Because the $\kappa$ field is real, the modes $(\pm l_x,0)$ are not independent.
-If we let $N(l,l_y=0)$ be the number of non--independent modes, the mode counting for the variance should be corrected as
+Here $N_{\rm eff}(l)$ is the number of independent modes used to
+estimate the power spectrum at $\ell$.
+
+In practice, we measure $P^{\kappa\kappa}_\ell$ on the Fourier
+transform of the pixelized simulated map $\kappa_r(\pmb{\theta})$,
+using the FFT algorithm, and some care must be taken to count the
+number of modes $N_{\rm eff}(\ell)$ correctly. Each pixel $(i_x,j_y)$
+in Fourier space corresponds to a mode
+$(\ell_x,\ell_y)=2\pi(i_x,i_y)/\theta_{\rm box}$, with $i_x=-n_{\rm
+  ray}/2,...,n_{\rm ray}/2$ and $i_y=0,...,n_{\rm ray}/2$.
+%ZH: added this:
+Here $n_{\rm ray}=2048$ is the linear number of pixels on the
+ray-traced convergence maps.  We count the number of pixels $N(\ell)$
+that fall inside a multipole bin $(\ell_1,\ell_2)$. Because the
+$\kappa$ field is real, the modes $(\pm \ell_x,0)$ are not
+independent. If we let $N(\ell,\ell_y=0)$ be the number of
+non--independent modes, the effective number of independent modes
+for the variance is given by
 
 \begin{equation}
-N_{eff}(l) = \frac{N^2(l)}{N(l)+N(l,l_y=0)}
+N_{\rm eff}(\ell) = \frac{N^2(\ell)}{N(\ell)+N(\ell,\ell_y=0)}.
 \end{equation}
 %
-We not that this correction is important at low $l$ only, where pixelization effects are more important. In other words $N_{eff}(l\gg2\pi/\theta_{box})\approx N(l)$.
+This correction is important at low $\ell$, where pixelization effects
+are non-negligible; $N_{\rm eff}(\ell\gg2\pi/\theta_{\rm box})\approx
+N(\ell)$.
 
-Figure \ref{curvingnb} shows a comparison between the dependence of $\langle\h{\sigma^2_w}\rangle$ measured from simulations and the theory prediction from equation (\ref{quarticdegradation}).
-
-Figure \ref{wvar_nr} shows the scaling of the expectation value of $\h{\sigma}_w^2$ when the number of mocks is large, $N_r\gg500$, using the power spectrum and compare it with the known result obtained in \citep{DodelsonSchneider13} and expressed in equation (\ref{ourscaling}).
-Finally, Figure \ref{wvar_ns} shows the effect of varying $N_s$ on the $w$ constraint.
+In Figures~\ref{curvingnb} and \ref{wvar_nr}, we show the dependence
+of the confidence range $\langle\h{\sigma}^2_w\rangle$ on $N_r$,
+derived from the power spectrum.
+%ZH: previously you only stated ``power spectrum'' for Figure 5.  But I assume Fig.4 is
+%    also based on the power spectrum?  If not, please correct.
+Figure~\ref{curvingnb} illustrates the behavior at relatively low
+$N_r$, and compares $\langle\h{\sigma}^2_w\rangle$ measured directly
+from the simulations with the analytic expectations from
+equation~(\ref{quarticdegradation}).  Figure~\ref{curvingnb} shows the
+behavior in the limit of a large number $N_r\gg500$ of realizations,
+and compares it with the scaling of the form in
+equation~(\ref{ourscaling}). Finally, in Figure~\ref{wvar_ns}, we show
+how the $w$ confidence limit changes with $N_s$.
 
@@
 
-In this section we discuss our main findings.
-Figure \ref{ps_pdf} shows that, although different choices of $N_s$ do not seem to affect the power spectrum PDF at large scales (top two panels), there are some qualitative differences on small scales (bottom two panels), on which a shear ensemble built with a small $N_s$ does not have the same statistical behavior of ensembles built with large $N_s$.
-Looking at the black curves, we see that the $N_s=1$ ensembles exibit some stochastic fluctuations in where the PDF peaks.
-We need as small as $N_s=2$ to recover the right location parameter for the power spectrum on small scales.
-Figure \ref{means_ns} shows that mutiple independent $N$--body simulations $N_s>1$ are necessary for measuring the means of feature ensembles to an accuracy corresponding to 10\% of the statistical error.
-The number of required simulations $N_s$ depends on the feature type and ranges from a few (1 or 2) for the power spectrum at small multipoles $l\lesssim 500$ to an order of $30\div50$ for the power spectrum at large multipoles $l\gtrsim1000$ peak counts at a high threshold $\kappa_0\approx0.3$.
+In this section we discuss our main findings and their
+implications. Figure \ref{ps_pdf} shows that, although different
+choices of $N_s$ do not affect the power spectrum PDF on large scales
+(top two panels), there are some qualitative differences on smaller
+scales (bottom two panels). On these smaller scales, shear ensembles
+built from $N_s=1$ do not produce the same statistical behavior as
+ensembles built with larger $N_s$. In particular, looking at the
+black curves, we see that the $N_s=1$ ensembles exibit large shifts
+with respect to the other PDFs to lower power, including the locations
+of the peaks of the PDFs.  We attribute these offsets to large
+(random) statistical errors.
+%ZH: I changed the wording above.  We didn't really prove that these are statistical errors,
+%    and not some systematic shift to low power when N_s is low.
 
-Figure \ref{ps_var} shows the variance of convergence power spectrum computed from different ensembles, in units of the Gaussian expectation.
-We find that, even with $N_s=1$, our results are in good agreement with the ones obtained by \citep{Sato12}, which used $N_s=400$.
-This fact by itself is not sufficient to conclude that $N_s$ does not have an effect on parameter inferences, since these depend on the cross band covariances.
+Interestingly, we need as few as $N_s=2$ simulations to recover the
+right PDF
+%ZH: what is ``location parameter'' ?
+%location parameter 
+for the small-scale power spectrum.  Figure~\ref{means_ns} shows that
+multiple independent $N$--body simulations $N_s\geq2$ are indeed
+necessary for measuring the means of feature ensembles to an accuracy
+corresponding to 10\% of the statistical error. The number of required
+simulations $N_s$ depends on the feature type and ranges from a few ($N_s=1$
+or 2) for the power spectrum at low multipoles ($\ell\lesssim 500$) to
+$N_s\approx 30-50$ for the power spectrum at larger
+multipoles ($\ell\gtrsim1000$) or peak counts above a high threshold
+($\kappa_0\approx0.3$).
+%ZH: I think this text above is a bit misleading.  Wny would we actually impose the ``0.1 sigma''
+%    requirement?    It sounds too stringent.  If we instead imposed, say, 0.5 sigma, would
+%    N_s=2 always be sufficient?    We should probably at least add this (delete if untrue):
+On the other hand, relaxing the required accuracy to 50\% of the statistical
+error, we find $N_s=2$ to be always sufficient.
 
-Figure \ref{curvingnb} shows that error degradation estimates truncated at order $O(1/N_r)$ are too optimistic when the number of mocks $N_r$ used to measure the covariance is only a factor of few larger than the dimension of the feature space $N_b$.
-In these cases effects coming the next--to--leading orders $O(1/N_r^2)$ become non--negligible on constraints degradation.
-In particular we find that already for $N_b=30$ and $N_r\sim100$, error degradation estimates at $O(1/N_r^2)$ are too optimistic, and more accurate estimates require at least the terms of order $O(1/N_r^3)$, which come from higher than quartic $\bbh{\Psi}$ fluctations.
+Figure \ref{ps_var} shows the variance of convergence power spectrum
+computed from different ensembles, in units of the Gaussian
+expectation. We find that, even with $N_s=1$, we are able to recover
+the known result that non-Gaussian structures increase the variance
+significantly on small scales. 
+%ZH: We could add more references here, e.g. the earlier Sato et al. 2009 paper, and the Takada and Spergel
+%    papers looking at the non-Gaussian variance of the pow.spectrum.. 
+Our results are in fact in excellent agreement with
+ref.~\citep{Sato12}, which used $N_s=400$ independent N-body
+simulations.  This result is highly encouraging, suggesting that
+individual N-body runs can be recycled repeatedly.  However, it is not
+sufficient by itself to conclude that $N_s$ does not impact the
+parameter inferences, since these depend on the cross band
+covariances.
 
-In Figure \ref{wvar_nr} we examine how the $w$ constraint depends on the number of mocks used to estimate the covariance in the limit of large $N_r$, and we find good agreement with (\ref{ourscaling}) up to values comparable to $\sim 10^5$.
-Bacause of this, we can argue that one $N$--body simulation is enough to construct an ensemble of $O(10^5)$ mutually independent mock power spectra.
+Figure \ref{curvingnb} investigates the parameter errors. This figure
+shows that error degradation estimates truncated at order $O(1/N_r)$
+are too optimistic when the number of simulations $N_r$ used to
+measure the covariance is only a factor of few larger than the
+dimension of the feature space $N_b$. In these cases effects coming
+the next--to--leading orders $O(1/N_r^2)$ become non--negligible on
+constraint degradation. In particular, we find that already for
+$N_b=30$ and $N_r\sim100$, the error degradation estimates to the next
+leading order, $O(1/N_r^2)$, remain too optimistic. Accurate analytic
+estimates in this regime would require at least terms of order
+$O(1/N_r^3)$, which come from higher--than--quartic $\bbh{\Psi}$
+fluctations.
 
-Figure \ref{wvar_ns} shows the dependence of the dark energy constraint with $N_s$.
-We find that, in the range $N_s\in[1,200]$ the $w$ inferred variance $\sigma_{w,\infty}^2$ fluctuates stochastically and does not show an appreciable trend with $N_s$.
+In Figure \ref{wvar_nr}, we examine how the degradation in the $w$
+constraint depends on the number of simulations used to estimate the
+covariance, in the limit of large $N_r$. We find excellent agreement
+with the expected scaling (eq.~\ref{ourscaling}) up to values
+comparable to $N_r\sim 10^5$. We therefore conclude that a single
+$N$--body simulation is sufficient to construct an ensemble of
+$O(10^5)$ mutually independent convergence power spectra.
 
-When we estimate the data covariance $\bb{C}$ from the same simulation set used to measure $\bbh{\Psi}$, the effective dimensionality $D$ decreases with increasing $N_b$ in the case where the $\bbh{\Psi}$ bias is corrected, and stays constant when this bias is corrected.
-This fact that should be taken into considerations when estimating parameter errors purely from simulations, as underestimations might occur.
+Figure \ref{wvar_ns} shows how the ``true'' $w$ constraint (in the
+limit $N_r\rightarrow \infty$; or equivalently the $w$ constraint with
+the known $N_r$ dependence factored out),
+%ZH: see my paraphrasing above.  I wanted to clearly distinguish the point
+%    of this paragraph from the previous paragraph.
+depends on $N_s$. We find that, in the range $N_s\in[1,200]$ the
+inferred $w$-variance $\sigma_{w,\infty}^2$ fluctuates stochastically
+only by 1\%, and does not show any trend with $N_s$.
+
+Finally, we found that when we estimate the data covariance $\bb{C}$
+from the same simulation set used to measure $\bbh{\Psi}$, the
+effective dimensionality $D$ decreases with increasing $N_b$ in the
+case where the $\bbh{\Psi}$ bias is not corrected
+(eq.~\ref{mockscalinguncorrected}).  This $N_b$-dependence disappears
+when the bias is corrected (eq.~\ref{mockscalingcorrected}).  This
+fact that should be taken into consideration when forecasting
+parameter errors purely from simulations, as the errors will otherwise
+be underestimated.
+%ZH: reworded above.  OK?  Also, I am not sure if this point is new.
+%    Didn't Hartlap (and others) make this point? If so, we should cite them.
+%    Also, it would make the point more relevant if we could cite some 
+%    papers (including our own) which neglected this correction in the past
+%    and therefore under-forecasted the errors.
 
@@
 
-\section{Conclusion}
+\section{Conclusions}
 
-In this work we examine the effect of $N$--body simulations based shear ensembles on forecasted cosmological constraints. Our main results can be summarized as follows:
+In this work, we have examined the effect of forecasting cosmological
+constraints based on shear ensembles generated from a finite number of
+$N$--body simulations.  Our main results can be summarized as follows:
+\vspace{0.4\baselineskip}
+\begin{itemize}
 
-\begin{itemize}
-\item When the feature covariance matrix is measured from simulations, parameter constraints are degraded.
-This degradation is appreciably larger than the $O(1/N_r)$ computed by \citep{DodelsonSchneider13} when the number of mocks $N_r$ is only a factor of few larger than the feature vector size $N_b$.
-\item We can recycle a single $N$--body simulation to produce an ensemble of $O(10^5)$ independent maps.
-The mean feature measured from a shear ensemble, though, could be inaccurate if only one $N$--body simulation is used.
-\item One or two indpendent $N$--body simulations are sufficient to forecast $w$ errorbars to an accuracy of percent level, given that enough mock shear realizations $N_r$ are used to measure feature covariances.
-Depending on the feature type used to constrain cosmology, more $N$--body simulations might be needed to measure accurate ensemble means and hence avoid introducing biases in parameter estimators.
+\item When the feature covariance matrix is measured from simulations,
+  parameter constraints are degraded. This degradation is appreciably
+  larger than the $O(1/N_r)$ computed by \citep{DodelsonSchneider13}
+  when the number of realizations $N_r$ is only a factor of few larger
+  than the feature vector size $N_b$.
+\item We can recycle a single $N$--body simulation to produce an
+  ensemble of $O(10^5)$ independent maps. The mean feature measured
+  from a shear ensemble, though, could be inaccurate if only one
+  $N$--body simulation is used.
+\item As few as one or two independent $N$--body simulations are
+  sufficient to forecast $w$ errorbars to 1\% accuracy, provided that
+  a sufficiently large number $N_r$ of realizations are used to
+  measure feature covariances.  In particular, provided that biases
+  in the inverse covariance are corrected, percent-level forecasts
+  require $N_r\gsim 100 N_p$ realizations (where $N_p$ is the number
+  of parameters to be constrained).
+%ZH: what is sufficiently large here?  I presume a ``few hundred'' 
+%    (or $>100N_p$, based on eq. 13).  I added that.  Please correct if 
+%    this is not OK.
+\item Depending on the feature type used to constrain cosmology, a
+  larger number of $N$--body simulations might be needed to measure
+  accurate ensemble means and hence to avoid introducing biases in
+  parameter estimators.
+%ZH:  So I am not sure about this last conclusion.   
+%     What exactly do you have in mind?   Is it Figure 2, which shows
+%     some deviations above the horizontal dashed line, for N_s up to ~50 ?
+%     But this is based on the super-stringent requirement that the bias
+%     is <0.1*sigma.
+%     The same figure seems to show that N_s=2 simulation is in fact
+%     sufficient to measure the means to within 0.5*sigma, as well.
+%     If you agree, we should revise this bullet to state this more
+%     positive conclusions!
 \end{itemize}
 %
-Future prospects of this work involve extending this analysis to more general feature spaces, such as the ones that characterize non--Gaussian statistics such as higher moments of $\kappa$ fields, Minkowski Functionals and higher order $\kappa$ correlators.
-In order to scale these considerations to future surveys such as LSST, it is necessary to see if our findinds hold when challenged by larger and higher resolution $N$--body simulations \citep{Qcontinuum}.
+Future extensions of this work should involve extending our analysis
+to a larger set of cosmological parameters, and to more general
+feature spaces, such as the ones that characterize non--Gaussian
+statistics (e.g. including higher moments of the $\kappa$ field,
+Minkowski Functionals, and higher-order $\kappa$ correlators). While
+our results are highly encouraging, and suggest that a single N-body
+simulation can be recycled repeatedly, to produce as many as $10^5$
+independent shear power spectra or peak count histograms. In order to
+scale our results to large future surveys, such as LSST, it will be
+necessary to determine if our findinds hold when challenged by larger
+and higher-resolution $N$--body simulations \citep{Qcontinuum}.
 
@@
 \section*{Acknowledgements}
+We thank Lam Hui for useful discussions.  The simulations in this work
+were performed at the NSF XSEDE facility, supported by grant number
+ACI-1053575, and at the New York Center for Computational Sciences, a
+cooperative effort between Brookhaven National Laboratory and Stony
+Brook University, supported in part by the State of New York. This
+work was supported in part by the U.S. Department of Energy under
+Contract Nos. DE-AC02-98CH10886 and DE-SC0012704, and by the NSF Grant
+No. AST-1210877 (to Z.H.) and by the Research Opportunities and
+Approaches to Data Science (ROADS) program at the Institute for Data
+Sciences and Engineering at Columbia University (to Z.H.).
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%% APPENDIX %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%ZH: I did not carefully re-read the appendices.  I guess that is OK.
+%    One cosmetic comment:  when you refer to equations, you need to say
+%    ``as in eq. (xx)''  rather than  ``as in (xx)''.
+%    
 \section*{Appendix A: cubic and quartic covariance fluctuations}
@@
 
+\clearpage
+\newpage
 \section*{Appendix B: negative effective dimensionality}

### 2016-01-08 Paper/paper.tex
added references

@@
 %\title{Simulating sample variance in weak lensing: effects on parameter inferences}
+%AP: Ok
+
 \title{Sample variance in weak lensing: how many simulations are required?}
@@
 produce as many as $N_r=10^5$ mutually independent shear maps. As a
-result, a small number of simulations ($N_b=1$ or $2$) is sufficient
+result, a small number of simulations ($N_s=1$ or $2$) is sufficient
 to forecast parameter confidence intervals at percent
-accuracy. However, we find that in practice, a larger number of
-simulations might be needed to measure accurate feature means and to
-avoid parameter biases.
+accuracy.
+
+%However, we find that in practice, a larger number of
+%simulations might be needed to measure accurate feature means and to
+%avoid parameter biases.
 %ZH: I am not sure about the last sentence. I believe it is based on
@@
 %    See my comments at the end of the Conclusion section.
+
+%AP: Ok, sentence removed
+
 \end{abstract}
@@
 constraining the dark energy equation of state $w$, and has been
-considered by a range of past (CFHTLens \citep{cfht1,cfht2}),
+considered by a range of past (CFHTLens \citep{cfht1,cfht2}, COSMOS \citep{cosmos}),
 %ZH: also cite COSMOS survey here...
-ongoing (DES \citep{DES}) and future (LSST \citep{LSST})
+%AP: done
+ongoing (DES \citep{DES}) and future (LSST \citep{LSST}, Euclid \citep{Euclid}, WFIRST \citep{WFIRST})
 %ZH: also cite Euclid and WFIRST.
+%AP: done
 experiments. In an era where cosmology is data driven, accurate
@@
 several reasons, including the study of baryonic effects
-\citep{BaryonXiuyuan}, 
+\citep{BaryonXiuyuan,BaryonSemboloni,BaryonsWhite,BaryonsKnox,BaryonsZentner1,BaryonsZentner2}, 
 %ZH: also cite Joop Schaye's hydro-simulation papers on lensing (Semboloni et al), and earlier papers by Martin White et al...
@@
 (I think all of these are in Xiuyuan's paper).
+%AP: done
 the computation of non--Gaussian statistics
-\citep{PeaksJan,MinkJan,MinkPetri} 
+\citep{PeaksJan,MinkJan,MinkPetri,NG-Marian,NG-Jain1,NG-Jain2,NG-Jain3,NG-Refregier,NG-Dietrich} 
 %ZH: Add here some citations of other groups - Marian+Bernstein.... Bhuvnesh Jain et al... Refregier et al... Dietrichh+Hartmann... Shirasaki+Yoshida.. (again just copy from our previous papers).
-and the  assessment of various systematics.
+%AP: done
+and the  assessment of various systematics
+\citep{MinkShirasaki,Sys-Bard,Sys-Chang,Sys-Huterer}.
 %ZH: cite papers by Jan+Morgan+Bard... and also Chihway Chan...Shirasaki+Yoshida.. and older ones by Dragan Huterer on photo-z errors..
+%AP: done
 
@@
 %ZH: I think 'cosmic variance' usually refers to observations of the actual sky (which is finite). 
+%AP: OK 
 In general, quantities such as the mean or the variance of any feature
@@
 confidence limits are degraged by a factor
-$1+O(1/N_r)$~\citep{DodelsonSchneider13}.
-%also cite Taylor Joachimi and Kitching -Morgan
+$1+O(1/N_r)$~\citep{DodelsonSchneider13,Taylor12}.
+%MM: also cite Taylor Joachimi and Kitching
+%AP: done
 
@@
 We fix the comoving size of the simulation box to $240\mathrm{Mpc}/h$,
-and use $512^3$ particles, corresponding to a mass resolution of
+and use $512^3$ particles, corresponding to a Dark Matter particle mass of
 $\approx 10^{10}M_\odot$.
 %ZH: ``mass resolution'' here means DM particle mass ?
+%AP: fixed
 
@@
 \citep{RayTracingHartlap,RayTracingJain} for example) to trace the
-deflections of $n_{ray}^2=2048^2$ light rays arranged on a square grid
+deflections of $n_{\rm ray}^2=2048^2$ light rays arranged on a square grid
 of total size $\theta_{\rm box}$, from $z=0$ to $z_s$. Our
@@
 observer and $z_s$. The randomization procedure we adopt is the
-following:
+following (see \citep{Sato12} for reference):
 %ZH: we should cite some paper here. We didn't invent most of this
@@
 %output, and the random mixing of the planes from different N-body sims ?).
+%AP: I added the citation to Sato et. al, which refer to this procedure without citing anyone
 
@@
 %ZH: should we specify the range of the random shifts (0 to 1/2 the lens plane dimension?)
+%AP: This is not necessary, since the shifts are periodic, in principle one could choose a random number of pixels.
+In particular this number should be between 0 and 4095, because each lens plane has 4096 pixels
 \item Repeat the above procedure for each lens-plane redshift $z_l$.
@@
 $N_r=10^5$ realizations. For each realization of each ensemble, we
-reconstruct the convergence $\kappa_r(\pmb{\theta})$ 
+reconstruct the convergence $\kappa_r(\pmb{\theta})$ from the trace of the light ray deflection Jacobian matrix, measured looking at the difference in angle deflection between nearby light rays \citep{RayTracingHartlap,RayTracingJain,Sato12}.
 %ZH: we should add 2 sentences on how you measured kappa.  Directly from the ray-tracing?
@@
 %    Kaiser-Squires on the gamma field ? 
-and measure its
-angular power spectrum $P^{\kappa\kappa}_r(l)$ defined as
-\begin{equation}
-\langle\tilde{\kappa}_r(\bb{l})\tilde{\kappa}_r(\bb{l}')\rangle = (2\pi)^2\delta_D(\bb{l}+\bb{l}')P^{\kappa\kappa}_r(l)
+%AP: done, we measure kappa directly from the ray tracing
+
+We measure the $\kappa$ angular power spectrum $P^{\kappa\kappa}_r(\ell)$ defined as
+\begin{equation}
+\langle\tilde{\kappa}_r(\pmb{\ell})\tilde{\kappa}_r(\pmb{\ell}')\rangle = (2\pi)^2\delta_D(\pmb{\ell}+\pmb{\ell}')P^{\kappa\kappa}_r(\ell)
 \end{equation}
@@
 %ZH: it would be logical to mention the other w,Sig,Om, sims here, and point to \ref{simtable})
+%AP: done, added the below
+
+To measure the cosmological dependence of the $\kappa$ peak counts, we also performed additional ray--tracing simulations with different combinations of the cosmological parameter triplet $(\Omega_m,w,\sigma_8)$ as outlined in Table \ref{simtable}.
 
@@
 the cosmological parameters, we make use of the public code
-\texttt{NICAEA} \citep{Nicaea} for the power spectrum, and we use an
+\texttt{Nicaea} \citep{Nicaea} for the power spectrum, and we use an
 independent simulation set (containing simulations with a variety of
@@
 \begin{center}
-\begin{tabular}{c|c|c||c|c}
+\begin{tabular}{c|c|c||c|c|c}
 \toprule
-$\Omega_m$ &  $w$ & $\sigma_8$ & $N_s$ & Number of $\kappa$ ensembles \\ \hline \hline
+$\Omega_m$ &  $w$ & $\sigma_8$ & $N_s$ & $N_r$ & Number of $\kappa$ ensembles \\ \hline \hline
 \midrule
 %
-0.26 & -1 & 0.8 & $1$ to $200$ & 16 \\
-0.29 & -1 & 0.8 & 1 & 1 \\
-0.26 & -0.8 & 0.8 & 1 & 1 \\
-0.26 & -1 & 0.6 & 1 & 1 \\
+0.26 & $-$1 & 0.8 & $1\div200$ & $1024\div128000$ & 16 \\
+0.29 & $-$1 & 0.8 & 1 & 1024 & 1 \\
+0.26 & $-$0.8 & 0.8 & 1 & 1024 & 1 \\
+0.26 & $-$1 & 0.6 & 1 & 1024 & 1 \\
 %
@@
   indistinguishable from the means measured in the ensemble with $N_s=200$.}
-% added last sentence stating conclusion to be drawn from the figure-Morgan
+%MM: added last sentence stating conclusion to be drawn from the figure
 %ZH:  Good idea.  All figures captions should similarly state a conclusion!
@@
   unless $N_r\gg N_b$.}
-%added last sentence stating conclusion to be drawn from the figure-Morgan
+%MM: added last sentence stating conclusion to be drawn from the figure
 %in legend box change line that reads Nb=7 divided by 8
@@
 %ZH: What ell and kappa ranges were used?
-%XH: Added conclusion:
+%ZH: Added conclusion:
   No trend with $N_s$ is seen for $N_s\geq 2$, and the
@@
 %    ``as in eq. (xx)''  rather than  ``as in (xx)''.
-%    
+%AP: done   
 \section*{Appendix A: cubic and quartic covariance fluctuations}
@@
 
-The goal of this appendix is to give a derivation of equation (\ref{quarticdegradation}).
+The goal of this appendix is to give a derivation of eq.
+(\ref{quarticdegradation}).
 When the simulated feature vector $\bbh{d}_r$ is drawn from a Gaussian distribution, the covariance estimator $\bbh{C}$ follows the Wishart distribution, and its inverse $\bbh{\Psi}$ follows the inverse Wishart distribution.
 For the analytical expressions of these probability distributions we remand the reader to \citep{Taylor12}.
-Computing expectation values of (\ref{estimatorcovariance}) over the inverse Wishart distribution is not possible analytically, and a perturbative expansion is necessary.
-Writing $\bbh{\Psi}=\bb{\Psi}+\delta\bbh{\Psi}$, we can expand equation (\ref{quarticdegradation}) in powers of $\delta\bbh{\Psi}$.
+Computing expectation values of eq.
+(\ref{estimatorcovariance}) over the inverse Wishart distribution is not possible analytically, and a perturbative expansion is necessary.
+Writing $\bbh{\Psi}=\bb{\Psi}+\delta\bbh{\Psi}$, we can expand eq.
+(\ref{quarticdegradation}) in powers of $\delta\bbh{\Psi}$.
 The expectation values of each term in this perturbative expansion can be calculated in term of the moments of the inverse Wishart distribution.
@@
 %
-Using (\ref{nthterm}), we can expand (\ref{estimatorcovariance}) to an arbitrary order in $\delta\bbh{\Psi}$, take the expectation values of the fluctuations over the inverse Wishart distribution, and finally get to (\ref{quarticdegradation}).
+Using eq.
+(\ref{nthterm}), we can expand eq.
+(\ref{estimatorcovariance}) to an arbitrary order in $\delta\bbh{\Psi}$, take the expectation values of the fluctuations over the inverse Wishart distribution, and finally get to eq.
+(\ref{quarticdegradation}).
 We use the notation $\nu=N_r-1$ and $\gamma=(\nu-N_b-1)/2$.
@@
 %
-Equation (\ref{firstmoment}) expresses the bias in the $\bbh{\Psi}$ estimator that already appears in the literature \citep{Hartlap07}.
-If we want to use the bias corrected $\bbh{\Psi}$ estimator (that is required in a perturbative expansion of (\ref{estimatorcovariance})), we need to apply an additional factor of $(2\gamma/\nu)^n$ to equations (\ref{firstmoment}--\ref{fourthmoment}), where $n$ is the order of the moment we are applying the correction to.
-If we limit ourselves to computing the expectation value of (\ref{estimatorcovariance}) up to order $O(1/\nu^2)$, we do not need to worry about this correction for equations (\ref{thirdmoment}--\ref{fourthmoment}), as the dominant term here is already $O(1/\nu^2)$.
-The next step is expanding (\ref{estimatorcovariance}) in powers of $\delta\bbh{\Psi}$ up to fourth order: this is easily done
+Eq.
+(\ref{firstmoment}) expresses the bias in the $\bbh{\Psi}$ estimator that already appears in the literature \citep{Hartlap07}.
+If we want to use the bias corrected $\bbh{\Psi}$ estimator (that is required in a perturbative expansion of eq.
+(\ref{estimatorcovariance})), we need to apply an additional factor of $(2\gamma/\nu)^n$ to eqs.
+(\ref{firstmoment}--\ref{fourthmoment}), where $n$ is the order of the moment we are applying the correction to.
+If we limit ourselves to computing the expectation value of eq.
+(\ref{estimatorcovariance}) up to order $O(1/\nu^2)$, we do not need to worry about this correction for eqs.
+(\ref{thirdmoment}--\ref{fourthmoment}), as the dominant term here is already $O(1/\nu^2)$.
+The next step is expanding eq.
+(\ref{estimatorcovariance}) in powers of $\delta\bbh{\Psi}$ up to fourth order: this is easily done
 
@@
 %
-Carrying out the calculations is simpler than it looks: because of the structure of (\ref{fullpertexpansion}), each term in the expansion is going to be proportional to $\Sigma_\bb{p}f_a(N_b,N_p)/N_r^a$, where $f_a(N_b,N_p)$ is polynomial in $N_b,N_p$.
+Carrying out the calculations is simpler than it looks: because of the structure of eq.
+(\ref{fullpertexpansion}), each term in the expansion is going to be proportional to $\Sigma_\bb{p}f_a(N_b,N_p)/N_r^a$, where $f_a(N_b,N_p)$ is polynomial in $N_b,N_p$.
 Terms proportional to $N_b$ arise from index contractions of type $\mathrm{tr}(\bb{\Psi C})=N_b$, which come from symmetrization terms of type $\Psi_{[I}\Psi_{J]}$.
@@
 Moreover, we know that, at every order $O(1/N_r^a)$, $f_a(N_b,N_p)$ has to be proportional to $N_b-N_p$ because it must vanish when $N_b=N_p$.
-The reason for this is that, when the feature derivative matrix $\bb{d}'_0$ is square and invertible (which it should be in absence of degeneracies), then (\ref{estimatorcovariance}) reduces to
+The reason for this is that, when the feature derivative matrix $\bb{d}'_0$ is square and invertible (which it should be in absence of degeneracies), then eq.
+(\ref{estimatorcovariance}) reduces to
 
@@
 And every trace of the noise is gone, hence powers of $1/N_r^a$ must not appear at any order if $N_b=N_p$.
-Armed with the knowledge of the above considerations, we can compute the expectation value of (\ref{fullpertexpansion}) at second, third and fourth order in $\delta\bbh{\Psi}$, keeping the terms that are at most $O(1/\nu^2)=O(1/N_r^2)$.
-When the combinatorial factors that arise from the expansion of (\ref{fullpertexpansion}) are properly computed and the expectation values over the inverse Wishart distribution are taken according to (\ref{firstmoment}--\ref{fourthmoment}), the results should look like
+Armed with the knowledge of the above considerations, we can compute the expectation value of eq.
+(\ref{fullpertexpansion}) at second, third and fourth order in $\delta\bbh{\Psi}$, keeping the terms that are at most $O(1/\nu^2)=O(1/N_r^2)$.
+When the combinatorial factors that arise from the expansion of eq.
+(\ref{fullpertexpansion}) are properly computed and the expectation values over the inverse Wishart distribution are taken according to eqs.
+(\ref{firstmoment}--\ref{fourthmoment}), the results should look like
 
@@
 %
-When the results from (\ref{expansionbreakdown}) are summed, (\ref{quarticdegradation}) immediately follows.
+When the results from eq. (\ref{expansionbreakdown}) are summed, eq. (\ref{quarticdegradation}) immediately follows.
 
@@
 
-The goal of this appendix is giving a justification on why the effective dimensionality $D$ that appears in equation (\ref{ourscaling}) can be negative in some cases.
-When we use the same simulation set to estimate $\bb{C},\bbh{\Psi}$, equation (\ref{estimatorcovariance}) reduces to the inverse Fisher estimator $\h{\Sigma}_\bb{p}=\bbh{F}^{-1}$.
+The goal of this appendix is giving a justification on why the effective dimensionality $D$ that appears in eq.
+(\ref{ourscaling}) can be negative in some cases.
+When we use the same simulation set to estimate $\bb{C},\bbh{\Psi}$, eq.
+(\ref{estimatorcovariance}) reduces to the inverse Fisher estimator $\h{\Sigma}_\bb{p}=\bbh{F}^{-1}$.
 At second order in the $\Psi$ fluctuations this becomes
@@
 %
-If the biased estimator for $\bbh{\Psi}$ is used, we can use equations (\ref{firstmoment}--\ref{secondmoment}) at order $O(1/\nu)$ to compute 
+If the biased estimator for $\bbh{\Psi}$ is used, we can use eqs. (\ref{firstmoment}--\ref{secondmoment}) at order $O(1/\nu)$ to compute 
 \begin{widetext}
@@
 And we immediately see that the coefficient of $1/N_r$ is negative, because $N_b>N_p$.
-This is the result shown in (\ref{mockscalinguncorrected}).
-If the bias correction for $\bbh{\Psi}$ is applied, the first order terms $\delta{\bbh{F}}$ average to 0, and we are left with only the last term in the sum (\ref{negativeD}), which immediately yields (\ref{mockscalingcorrected}).
+This is the result shown in eq.
+(\ref{mockscalinguncorrected}).
+If the bias correction for $\bbh{\Psi}$ is applied, the first order terms $\delta{\bbh{F}}$ average to 0, and we are left with only the last term in the sum (\ref{negativeD}), which immediately yields eq.
+(\ref{mockscalingcorrected}).
 

### 2016-01-08 Paper/paper.tex
implemented suggested edits

@@
 $\kappa$ maxima of a certain height $\kappa_0$, $n_r(\kappa_0)$
-(hereafter \textit{peak counts}), with varying $\kappa_0$.
+(hereafter \textit{peak counts}), with varying $\kappa_0$ chosen between the minimum and maximum values measured from the maps $(\kappa_{\rm min},\kappa_{\rm max})=(-0.06,0.45)$.
+Different choices of $\kappa_0$ binning used in this work are outlined in Table \ref{featuretable}.
 %ZH: state here the range and binning choice of $\kappa_0$
+%AP: done
 The fact that the ensemble of $N_r$ realizations is not completely
@@
 
-To measure the cosmological dependence of the $\kappa$ peak counts, we also performed additional ray--tracing simulations with different combinations of the cosmological parameter triplet $(\Omega_m,w,\sigma_8)$ as outlined in Table \ref{simtable}.
+To measure the cosmological dependence of the $\kappa$ peak counts, we also performed additional ray--tracing simulations with different combinations of the cosmological parameter triplet $(\Omega_m,w,\sigma_8)$.
+A summary of the complete set of shear ensembles used in this work is outlined in Table \ref{simtable}.
 
@@
 %
-
 Let $\bbh{d}$ be a single estimate for a feature of dimension $N_b$, 
 %ZH: ``Hat'' here refers to an estimator?
+%AP: Yes: quantities without the hat are the expectation values 
 $\bb{d}(\bb{p})$ be the
@@
 %ZH: I believe ``smooth expectation'' means true mean value, yes?
-true mean value of this feature at a point $\bb{p}$ in parameter space
+%AP: yes
+true value of this feature at a point $\bb{p}$ in parameter space
 (which has a dimension $N_p$) and $\bb{C}$ be the $N_b\times N_b$
@@
 the triplet $(\Omega_m,w,\sigma_8)$ and $\bb{d}$ is one of the
-features -- either a power spectrum or a peak count -- in Table
-\ref{featuretable}. While in many cases $\bb{d}(\bb{p})$ can be
-predicted reasonably accurately by already existing emulators (see
-\citep{coyote2,Nicaea} for example), the matter is more complicated
-for covariance matrices.
+features -- either a power spectrum or a peak count histogram -- in Table
+\ref{featuretable}. Although existing emulators (see
+\citep{coyote2,Nicaea,SchneiderKnoxCovariance} for example) can be used to compute $\bb{d}(\bb{p}),\bb{C}$ in some cases, this is not true in the general case. 
 %ZH: I am missing the point here.  Why is covariance matrix ``more complicated'' ?
@@
 %    power spectrum covariance matrix.
-Estimating $\bb{C}$ from simulations involves generating a series of
-mock realizations $\bbh{d}_r$ with $r=1...N_r$ and computing the
+%AP: The intended meaning is the latter: published emulators only predict the means.
+It is also true that getting the covariance accurate is more difficult than getting the means accurate.
+I rephrased the sentence.
+Estimating $\bb{C}$ from simulations involves generating a series of mock realizations $\bbh{d}_r$ with $r=1...N_r$ and computing the
 sample covariance $\bbh{C}$,
@@
 
-\begin{table}
+\begin{table*}
 \begin{center}
-\begin{tabular}{c|c|c||c|c|c}
+\begin{tabular}{c|c|c||c|c}
 \toprule
-$\Omega_m$ &  $w$ & $\sigma_8$ & $N_s$ & $N_r$ & Number of $\kappa$ ensembles \\ \hline \hline
+$\Omega_m$ &  $w$ & $\sigma_8$ & $(N_s,N_r)$ & Number of $\kappa$ ensembles \\ \hline \hline
 \midrule
 %
-0.26 & $-$1 & 0.8 & $1\div200$ & $1024\div128000$ & 16 \\
-0.29 & $-$1 & 0.8 & 1 & 1024 & 1 \\
-0.26 & $-$0.8 & 0.8 & 1 & 1024 & 1 \\
-0.26 & $-$1 & 0.6 & 1 & 1024 & 1 \\
+0.26 & $-$1 & 0.8 & $(1\div200,1024),(1,128000)$ & 16 \\
+0.29 & $-$1 & 0.8 & (1,1024) & 1 \\
+0.26 & $-$0.8 & 0.8 & (1,1024) & 1 \\
+0.26 & $-$1 & 0.6 & (1,1024) & 1 \\
 %
@@
 %    ensembles are first discussed.
+%AP: done
 \label{simtable}
-\end{table}
+\end{table*}
 
@@
 parameter covariance, i.e. the usual Fisher matrix, as
-$\Sigma_\bb{p}=\bb{F}^{-1}$, we find the result~\footnote{The
-  details of the calculation are given in Appendix A.}:
+$\Sigma_\bb{p}=\bb{F}^{-1}$, we find the result~\footnote{The details of the calculation are given in Appendix A.}:
 
@@
 investigate the behavior of the $O(1/N_r)$ term. We consider three
-cases \footnote{The details of these calculations are given in
-  Appendix B}:
+cases \footnote{The details of these calculations are given in Appendix B}:
 
 \begin{enumerate}
-\item If the true data covariance $\bb{C}$ is known, the estimator in
-  Eq.~(\ref{estimatorcovariance}) is biased, and the dominant
-  contribution of the bias comes from the second order fluctuations in
-  $\bbh{\Psi}$. Once the expectation values over simulations are
-  taken, the bias sums up to
+\item If the true data covariance $\bb{C}$ is known, the estimator in eq.~(\ref{estimatorcovariance}) is biased, and the dominant contribution of the bias comes from the second order fluctuations in $\bbh{\Psi}$.
+Once the expectation values over simulations are taken, the bias sums up to
 
@@
 
-\item Usually the true data covariance is unknown, and it is tempting
-  to plug in its estimator $\bbh{C}$, measured from the same
-  simulation set we use to compute $\bbh{\Psi}$. This approach has
-  been used before in the literature
-  (e.g.~\citep{MinkPetri,MinkShirasaki}). If this is done without
-  correcting for the bias in $\bbh{\Psi}$ (see Eq.~\ref{firstmoment}
-  below), 
+\item Usually the true data covariance is unknown, and it is tempting to plug in its estimator $\bbh{C}$, measured from the same simulation set we use to compute $\bbh{\Psi}$.
+This approach has been used before in the literature (e.g.~\citep{MinkPetri,MinkShirasaki}).
+If this is done without correcting for the bias in $\bbh{\Psi}$ (see eq.~(\ref{firstmoment}) below or \citep{Taylor12} for reference),
 %ZH: we should probably cite Hartlap et al. and Taylor et al. here for this Psi bias.  (I assume this is what you mean in eq. 19)
-  the parameter variance will have a contribution from both the second
-  and first-order fluctuations in $\bbh{\Psi}$, which now have a
-  nonzero expectation value. In this case the bias sums up to
+%AP: done
+the parameter variance will have a contribution from both the second and first-order fluctuations in $\bbh{\Psi}$, which now have a nonzero expectation value. In this case the bias sums up to
 %
@@
 
-\item If we repeat the same exercise as above, but we correct for the
-  bias in the precision matrix estimator, we are left with
+\item If we repeat the same exercise as above, but we correct for the bias in the precision matrix estimator, we are left with
 
@@
 %$N_b$. This typically leads to underestimates in parameter errors. 
-Note that in the last case, which is most relevant when fitting actual
-data, the noise in both $\bbh{C}$ and $\bbh{\Psi}$ together degrade
-the confidence limits.  However, this degradation turns out to be less
-severe than in the idealized case 1 of a noiseless $\bbh{C}$ (assuming
-$N_b\gg N_p$).  We also note that the distribution of $\bbh{p}$ has a
-variance ($\Sigma_\bb{p}$) that increases with $N_b$, but the bias in
-$\h{\Sigma}_\bb{p}$ is independent of $N_b$ in the realistic case 3.
-
+%AP: Not exactly: my point was that the distribution of \bbh{p} has a true variance that increases with Nb, but the estimate of this variance (which we quote as the errorbar) does not increase with Nb.
+Hence we get the wrong parameter fit (i.e.
+which excludes the true value at high significance level)
+Note that in the last case, which is most relevant when fitting actual data, the estimated degradation turns out to be too optimistic: the parameter estimate $\bbh{p}$ has a variance that grows linearly with $N_b$, but the estimated degradation in eq.
+(\ref{mockscalingcorrected}) is constant with $N_b$.
+This can lead to underestimation of error bars, which can be mistakenly interpreted as a parameter bias.
 We derived the scaling relations of the form
@@
 %
-above by assuming that the noise in both $\bbh{C}$ and $\bbh{\Psi}$ is
-Gaussian.  We next directly test these scaling relations using our
-simulations, in the limits of both high and low $N_r$.
+above by assuming that the noise in $\bbh{d}$ is Gaussian. We then directly test these scaling relations using our simulations, in the limits of both high and low $N_r$.
 %ZH: It is still a little unclear here what is being tested.  Is it the Gaussianity assumption? I added that.
 %    But perhaps you had some other issue in mind.
-We use the notation $\h{\sigma}^2_p=\h{\Sigma}_{pp}$ 
+%AP: The noise in $\bbh{C}$ and $\bbh{\Psi}$ is not Gaussian: if the data vector from which $\bbh{C}$ and $\bbh{\Psi}$ are estimated in Gaussian, then these matrices are distibuted according to, respectively, the Wishart and inverse Wishart distributions.
+We are testing that the degradation effectively decreases as 1/Nr at leading order.
+We indicate the diagonal elements of $\h{\Sigma}_{\bb{p}}$ as $\h{\sigma}^2_p=\mathrm{diag}(\h{\Sigma}_{\bb{p}})$ 
 %ZH: I am confused.  Why is a new symbol \sigma necessary here, on top of \Sigma ?
 %    (And also: here you write \Sigma_pp, but above it was denoted \Sigma_p  )
-and we indicate by $\sigma^2_{p,\infty}$ the expectation value of the
-variance in the limit of an infinite number of realizations
-$N_r\rightarrow\infty$.  We call $D$ the \textit{effective
-  dimensionality} of the feature space (which, as seen before, can be
+%AP: fixed. I introduced the \sigma symbol for the single parameter variances (as opposed to the full parameter covariance), because these are the quantities we plot
+and we indicate by $\sigma^2_{p,\infty}$ the expectation value of the variance of each parameter in the limit of an infinite number of realizations
+$N_r\rightarrow\infty$.  We call $D$ the \textit{effective dimensionality} of the feature space (which, as seen before, can be
 negative in some pathological cases).
@@
 %    or in case 2 (when N_b > N_p, so that's OK, but this case ust means we ``forgot'' to correct for the psi-bias).
+%AP: agreed
 We compute the expectation values of $\h{\sigma}^2_p$
-(equations~\ref{estimatorcovariance} and \ref{ourscaling}) by
+(eqs.~\ref{estimatorcovariance} and \ref{ourscaling}) by
 averaging over 100 random resamplings of our shear ensembles. For the
-true feature covariance matrix
-$\langle(\bbh{d}-\bb{d}_0)(\bbh{d}-\bb{d}_0)^T\rangle=\bb{C}$ we use
+true feature covariance matrix $\langle(\bbh{d}-\bb{d}_0)(\bbh{d}-\bb{d}_0)^T\rangle=\bb{C}$ we use
 the estimated covariance from a grand ensemble built with the union of
@@
   (purple) independent N-body simulations. Each curve is based on
-  $N_r=1000$ realizations.
+  $N_r=1024$ realizations.
 %ZH: I added the Nr=1000 above. Yes?
-  The thick
-  black curves correspond to ensembles generated with $N_s=1$ and
-  $N_r=10^5$. For $N_s\geq2$, the distributions appear
+%AP: Yes, 1024 in reality, but it doesn't change much
+  The dashed black curves correspond to ensembles generated with $N_s=1$ and
+  $N_r=128000$. For $N_s\geq2$, the distributions appear
   similar to the eye; this similarity is confirmed by the comparisons
-  in Figures \ref{means_ns} and \ref{ps_var} below. }
-%added last two sentences. -Morgan
-%Also: Thick black line draws the eye and looks like the most significant thing on the plot. replace with dotted black line or something else that stands out less.-Morgan
+  in Figures \ref{means_ns} and \ref{ps_var} below.}
+%MM: added last two sentences
+%MM: Thick black line draws the eye and looks like the most significant thing on the plot. replace with dotted black line or something else that stands out less.
 %ZH: Also, include a label ``N_r=10^5'' with the other N_s=... labels in the figure panels 
 %   (it is just confusing why there are labels for all the other curves, but not for the thick black)
+%AP: done
 \label{ps_pdf}
@@
 \includegraphics[scale=0.3]{Figures/means_ns.eps}
-\caption{The mean value 
- $\bb{\bar{d}}$
+\caption{The mean value $\bb{\bar{d}}$
 % $d$  
@@
 %    subtle notations in the previous section, so we should  follow those ....
+%AP: OK
   of various features, measured from ensembles created from different
@@
   statistical error measured in the $N_s=200$ ensemble.  The colored
-  curves refer to shear-shear power spectra measured at $\ell=115$
+  curves refer to shear--shear power spectra measured at $\ell=115$
   (black), 1027 (cyan), and 5283 (green), and peak counts 
-%of
 %ZH: I replace ``of'' with ``above''.  These are cumulative peak counts N(>kappa_0) ?
@@
 %    but no obvious relation to the 0.05, 0.17  and 0.28 mentioned here...
-  with height above $\kappa_0=0.05$ (red), 0.17 (purple), and 0.28
-  (orange).  For $N_s\geq 2$, the means are statistically
-  indistinguishable from the means measured in the ensemble with $N_s=200$.}
+%AP: The peak counts are differential, I added the clarifications; I chose three values of kappa0 for the sake of presentation simplicity (one value in the low height peaks, one in the middle and one in the large)
+  with height of $\kappa_0=0.05$ (red), 0.17 (purple), and 0.28
+  (orange).
+The $\kappa$ bin width for the peak counts has been fixed to $\Delta\kappa=0.011$.
+The dashed black line shows a level of $0.1\sigma$ accuracy for reference.
+For $N_s\geq 2$, the means are statistically indistinguishable (at $\sim0.1\sigma$) from the means measured in the ensemble with $N_s=200$.}
 %MM: added last sentence stating conclusion to be drawn from the figure
@@
 %    ``statistically indistinguishable'' ....  0.1 sigma.
+%AP: Ok, added the clarifications to the caption
 \label{means_ns}
@@
   different shear ensembles based on $N_s=$1 (black), 2 (blue), 5
-  (green), 10 (red), 50 (purple), or 100 (orange) N-body simulations. 
+  (green), 10 (red), 50 (purple), or 100 (orange) N--body simulations. 
 %ZH: Added ``conclusion'':
-  Non-Gaussianities of the underlying structures increase the variance on
+%AP: OK
+  Non--Gaussianities of the underlying structures increase the variance on
   small scales, but no clear trend with $N_s$ can be identied on any scale.}
@@
 %    Why make the reader flip back-and-forth between the figure and the Table ?
+%AP: done
   The dashed and solid curves show the analytic predictions from
@@
 %in legend box change line that reads Nb=7 divided by 8
+%AP: done, the legend is comprehensive now
 \label{curvingnb}
@@
 %   I added that. But if you meant something else, please correct.
-  The thick black curve corresponds to an ensemble of $N_r=10^5$
+%AP: OK
+  The thick black curve corresponds to an ensemble of $N_r=128000$
   realizations from a single simulation ($N_s=1$).
 %ZH: I added 'conclusion':
+%AP: OK
   No systematic deviation from the expected scaling is seen, even in
@@
 \includegraphics[scale=0.3]{Figures/scaling_ns.eps}
-\caption{The variance of $w$ in the limit of $N_r\rightarrow\infty$,
+\caption{The variance of $w$ in the limit of $N_r\rightarrow\infty$ (measured from the intercept of the fit $\sigma^2_w$ vs $1/N_r$),
 %ZH: state here what N_r was actually used to approximate the infinity limit
+%AP: the value plotted is actually $N_r\rightarrow\infty$, because it is estimated from the intercept of the fit.
+Even if all the points have Nr finite, the intercept of the line corresponds to Nr infinite.
   varying the number of simulations $N_s$ used in the ensemble to
   estimate the covariance (eq.~\ref{covest}). We show the dependence
-  of $\sigma_{w,\infty}^2(N_s)$ in units of the mean over $N_s$, 
+  of $\sigma_{w,\infty}^2(N_s)$ in units of the mean over the 16 ensembles with different $N_s$, 
 %ZH: Just to make sure: what you mean here is an averaging of sigma_infty over the 16 different
 %    cases of N_s ?   
-  for
-  the power spectrum logarithmically binned (black), the power
-  spectrum linearly binned (red) and the peak counts (green).
+%AP: Yes
+  for the power spectrum logarithmically binned (black, $N_b=15,\ell\in[100,6000]$), the power spectrum linearly binned (red,$N_b=39,\ell\in[100,6000]$) and the peak counts (green,$N_b=45,\kappa_0\in[-0.06,0.45]$).
 %ZH: What ell and kappa ranges were used?
 %ZH: Added conclusion:
-  No trend with $N_s$ is seen for $N_s\geq 2$, and the
-  differences are only 1\%.  }
+%AP: OK, added binning information
+  No trend with $N_s$ is seen for $N_s\geq 2$, and the differences are only of order 1\%.}
 \label{wvar_ns}
@@
 shows the ensemble mean for these power spectra, as well as for peak
-counts above three different $\kappa$ thresholds (corresponding to
-$\approx 2-12\sigma$ peaks), as a function of $N_s$.
+counts of three different $\kappa_0$ heights (corresponding to
+$\approx 2\div13\sigma$ peaks), as a function of $N_s$.
 %ZH: added above 2-12.  OK ?
+%AP: the actual numbers are 2-13, but again, only minor change
 In Figure~\ref{ps_var}, we show the variance of the power spectrum at
@@
 %ZH:  I changed ``l''  to ``\ell'' in many places, for the multipole
+%AP: OK, I fixed this throughout the rest of the paper
 \begin{equation}
@@
 %ZH: added this:
+%AP: OK
 Here $n_{\rm ray}=2048$ is the linear number of pixels on the
-ray-traced convergence maps.  We count the number of pixels $N(\ell)$
+ray--traced convergence maps.  We count the number of pixels $N(\ell)$
 that fall inside a multipole bin $(\ell_1,\ell_2)$. Because the
@@
 of the confidence range $\langle\h{\sigma}^2_w\rangle$ on $N_r$,
-derived from the power spectrum.
+derived from the features used in this work (see Table \ref{featuretable} for a comprehensive list).
+Figure \ref{wvar_nr} shows the $N_r$ trends of the $w$ constraint obtained with the power spectrum logarithmically binned with $\ell\in[100,6000],N_b=15$.
 %ZH: previously you only stated ``power spectrum'' for Figure 5.  But I assume Fig.4 is
 %    also based on the power spectrum?  If not, please correct.
+%AP: OK, fixed
 Figure~\ref{curvingnb} illustrates the behavior at relatively low
@@
 %    and not some systematic shift to low power when N_s is low.
+%AP: OK
 
@@
 %location parameter 
-for the small-scale power spectrum.  Figure~\ref{means_ns} shows that
+%AP: location parameter usually indicated where the PDF peaks. This might be the mean, but not always. 
+for the small--scale power spectrum.  Figure~\ref{means_ns} shows that
 multiple independent $N$--body simulations $N_s\geq2$ are indeed
@@
 %    N_s=2 always be sufficient?    We should probably at least add this (delete if untrue):
+%AP: OK, agreed
 On the other hand, relaxing the required accuracy to 50\% of the statistical
@@
 expectation. We find that, even with $N_s=1$, we are able to recover
-the known result that non-Gaussian structures increase the variance
-significantly on small scales. 
+the known result that non--Gaussian structures increase the variance
+significantly on small scales (see \citep{Sato12,TakadaSpergel14} for reference). 
 %ZH: We could add more references here, e.g. the earlier Sato et al. 2009 paper, and the Takada and Spergel
 %    papers looking at the non-Gaussian variance of the pow.spectrum.. 
-Our results are in fact in excellent agreement with
-ref.~\citep{Sato12}, which used $N_s=400$ independent N-body
+%AP: Done: that is, in fact, the Sato 2009 paper, I mis-labelled it with Sato12 in the bibtex
+Our results are in fact in excellent agreement with \citep{Sato12}, which used $N_s=400$ independent N-body
 simulations.  This result is highly encouraging, suggesting that
-individual N-body runs can be recycled repeatedly.  However, it is not
+individual $N$--body runs can be recycled repeatedly.  However, it is not
 sufficient by itself to conclude that $N_s$ does not impact the
@@
 %    of this paragraph from the previous paragraph.
+%AP: OK
 depends on $N_s$. We find that, in the range $N_s\in[1,200]$ the
-inferred $w$-variance $\sigma_{w,\infty}^2$ fluctuates stochastically
+inferred $w$--variance $\sigma_{w,\infty}^2$ fluctuates stochastically
 only by 1\%, and does not show any trend with $N_s$.
@@
 parameter errors purely from simulations, as the errors will otherwise
-be underestimated.
+be underestimated. A similar conclusion was reached by \citep{Hartlap07}.
 %ZH: reworded above.  OK?  Also, I am not sure if this point is new.
@@
 %    and therefore under-forecasted the errors.
+%AP: yes, Hartlap et al.
+reached a similar conclusion.
+I think we are saying something more though: even if the bias in the Psi estimator is corrected, if the same simulation set for Psi and C is used, parameter errors are still underestimated because of the explanation we give in section II-B.
+I don't think this point appears in Hartlap et al.
 
@@
   measure feature covariances.  In particular, provided that biases
-  in the inverse covariance are corrected, percent-level forecasts
-  require $N_r\gsim 100 N_p$ realizations (where $N_p$ is the number
-  of parameters to be constrained).
+  in the inverse covariance are corrected, percent--level forecasts
+  require $N_r\gsim 100 (N_b-N_p)$ realizations.
 %ZH: what is sufficiently large here?  I presume a ``few hundred'' 
@@
 %    this is not OK.
+%AP: OK, the quantity to compare to is Nb-Np though. If Nb=Np there is no degradation at every order
 \item Depending on the feature type used to constrain cosmology, a
   larger number of $N$--body simulations might be needed to measure
-  accurate ensemble means and hence to avoid introducing biases in
-  parameter estimators.
+  accurate ensemble means to an accuracy corresponding 10\% of the statistical error.
+If this accuracy requirement is relaxed to 50\% of the statistical error, we find that as low as $N_s=2$ simulations are needed, for the feature types we consider in this work.
 %ZH:  So I am not sure about this last conclusion.   
@@
 %     positive conclusions!
+%AP: Agreed, I rephrased the bullet point
 \end{itemize}

### 2016-01-08 Paper/Figures/generate.py

@@ -58,36 +58,36 @@ colors = {
 
 #Labels
 labels = {
-"power_logb_large" : r"$N_b=7\div 8$",
-"power_logb_small" : None,
-"power_logb_all" : None,
-"power_large" : None,
-"power_small" : r"$N_b=15$",
-"power_large+small" : r"$N_b=30$",
-"power_all" : r"$N_b=39$",
-"peaks_low" : None,
-"peaks_intermediate" : None,
-"peaks_high" : None,
-"peaks_low+intermediate" : None,
-"peaks_intermediate+high" : None,
-"peaks_all" : r"$N_b=45$",
+"power_logb_large" : r"$\ell\in[100,800],N_b=8(\mathrm{log})$",
+"power_logb_small" : r"$\ell\in[1000,6000],N_b=7(\mathrm{log})$",
+"power_logb_all" : r"$\ell\in[100,6000],N_b=15(\mathrm{log})$",
+"power_large" : r"$\ell\in[100,2000],N_b=15(\mathrm{lin})$",
+"power_small" : r"$\ell\in[2500,4500],N_b=15(\mathrm{lin})$",
+"power_large+small" : r"$\ell\in[100,4500],N_b=30(\mathrm{lin})$",
+"power_all" : r"$\ell\in[2500,6000],N_b=39(\mathrm{lin})$",
+"peaks_low" : r"$\kappa_0\in[-0.06,0.09],N_b=15$",
+"peaks_intermediate" : r"$\kappa_0\in[0.1,0.27],N_b=15$",
+"peaks_high" : r"$\kappa_0\in[0.28,0.45],N_b=15$",
+"peaks_low+intermediate" : r"$\kappa_0\in[-0.06,0.27],N_b=30$",
+"peaks_intermediate+high" : r"$\kappa_0\in[0.1,0.45],N_b=30$",
+"peaks_all" : r"$\kappa_0\in[-0.06,0.45],N_b=45$",
 } 
 
 #Plot order
 order = {
-"power_logb_large" : 1,
-"power_logb_small" : -1,
-"power_logb_all" : -1,
-"power_large" : -1,
-"power_small" : 2,
-"power_large+small" : 3,
-"power_all" : 4,
-"peaks_low" : -1,
-"peaks_intermediate" : -1,
-"peaks_high" : -1,
-"peaks_low+intermediate" : -1,
-"peaks_intermediate+high" : -1,
-"peaks_all" : 5,
+"power_logb_large" : 8,
[…]

### 2016-01-09 code/measure/peaks_direct.py
fixed type bug

@@ -44,7 +44,7 @@ def singleRedshift(pool,batch,settings,id,**kwargs):
 
 	if len(parts)==2:
 
-		assert isinstance(settings,PowerSpectrumSettings)
+		assert isinstance(settings,PeaksSettings)
 	
 		#Separate the id into cosmo_id and geometry_id
 		cosmo_id,geometry_id = parts
@@ -59,7 +59,7 @@ def singleRedshift(pool,batch,settings,id,**kwargs):
 
 	elif len(parts)==1:
 
-		assert isinstance(settings,PowerSpectrumSettings)
+		assert isinstance(settings,PeaksSettings)
 
 		#Get a handle on the model
 		model = batch.getModel(parts[0])
@@ -310,9 +310,9 @@ def singleRedshift(pool,batch,settings,id,**kwargs):
 
 ############################################################################################################################################################################
 
-########################################################
-###########PowerSpectrumSettings class##################
-########################################################
+################################################
+###########PeaksSettings class##################
+################################################
 
 class PeaksSettings(MapSettings):
 

### 2016-01-09 Paper/paper.tex
Paper/paper.tex

@@
 \begin{document}
-
-%ZH: I changed to more catchy title:
-%\title{Simulating sample variance in weak lensing: effects on parameter inferences}
-%AP: Ok
 
@@
 
-%However, we find that in practice, a larger number of
-%simulations might be needed to measure accurate feature means and to
-%avoid parameter biases.
-%ZH: I am not sure about the last sentence. I believe it is based on
-%    an overly stringent reading of Fig.2, and that in fact we could
-%    claim here, instead, that N_s=2 simulations are also sufficient
-%    to get the correct mean.
-%    See my comments at the end of the Conclusion section.
-
-%AP: Ok, sentence removed
-
 \end{abstract}
@@
 constraining the dark energy equation of state $w$, and has been
-considered by a range of past (CFHTLens \citep{cfht1,cfht2}, COSMOS \citep{cosmos}),
-%ZH: also cite COSMOS survey here...
-%AP: done
-ongoing (DES \citep{DES}) and future (LSST \citep{LSST}, Euclid \citep{Euclid}, WFIRST \citep{WFIRST})
-%ZH: also cite Euclid and WFIRST.
-%AP: done
+considered by a range of past (CFHTLens \citep{cfht1,cfht2}, COSMOS
+\citep{cosmos}), ongoing (DES \citep{DES}) and future (LSST
+\citep{LSST}, Euclid \citep{Euclid}, WFIRST \citep{WFIRST})
 experiments. In an era where cosmology is data driven, accurate
@@
 \citep{BaryonXiuyuan,BaryonSemboloni,BaryonsWhite,BaryonsKnox,BaryonsZentner1,BaryonsZentner2},
-%ZH: also cite Joop Schaye's hydro-simulation papers on lensing (Semboloni et al), and earlier papers by Martin White et al...
-Lloyd Knox et al...
-and Zentner et al...
-(I think all of these are in Xiuyuan's paper).
-%AP: done
 the computation of non--Gaussian statistics
 \citep{PeaksJan,MinkJan,MinkPetri,NG-Marian,NG-Jain1,NG-Jain2,NG-Jain3,NG-Refregier,NG-Dietrich}
-%ZH: Add here some citations of other groups - Marian+Bernstein.... Bhuvnesh Jain et al... Refregier et al... Dietrichh+Hartmann... Shirasaki+Yoshida.. (again just copy from our previous papers).
-%AP: done
 and the assessment of various systematics
 \citep{MinkShirasaki,Sys-Bard,Sys-Chang,Sys-Huterer}.
-%ZH: cite papers by Jan+Morgan+Bard... and also Chihway Chan...Shirasaki+Yoshida.. and older ones by Dragan Huterer on photo-z errors..
-%AP: done
 
@@
 finite number of simulations naturally introduces fluctuations in the
-forecasts, due to inevitable sample variance~\footnote{Sample variance is a broad term that has been used in the literature to describe a range of phenomena.
-Throughout this paper, we use it to refer to the fluctuations in an ensemble of simulations, which represent random realizations of the same initial conditions.}.
-%ZH: I think 'cosmic variance' usually refers to observations of the actual sky (which is finite). 
-%AP: OK 
-In general, quantities such as the mean or the variance of any feature
-(e.g. the shear power spectrum at a multipole $\ell$), measured from a
-finite set of simulations, will fluctuate, and can also suffer a bias.
-While biases in the estimates of both the mean and the variance have
-been studied extensively, the impact of fluctuations in the variance
-has received comparatively less attention.  These fluctuations have,
+forecasts, due to inevitable sample variance~\footnote{Sample variance
+  is a broad term that has been used in the literature to describe a
+  range of phenomena.  Throughout this paper, we use it to refer to
+  the fluctuations in an ensemble of simulations, which represent
+  random realizations of the same initial conditions.}.  In general,
+quantities such as the mean or the variance of any feature (e.g. the
+shear power spectrum at a multipole $\ell$), measured from a finite
+set of simulations, will fluctuate, and can also suffer a bias.  While
+biases in the estimates of both the mean and the variance have been
+studied extensively, the impact of fluctuations in the variance has
+received comparatively less attention.  These fluctuations have,
 however, been shown to have non-negligible effects on estimates of
@@
 $1+O(1/N_r)$~\citep{DodelsonSchneider13,Taylor12}.
-%MM: also cite Taylor Joachimi and Kitching
-%AP: done
 
@@
 one randomizes and re-cycles the output of a single 3D simulation
-multiple times.
-%ZH: Add citations here of papers resorting to this technique
-In light of the forthcoming large surveys, it is imperative to assess
-the statistical validity of this approach, and to ask how many times a
-single simulation can be fairly recycled.  In this paper, we address
-these questions with ensembles of up to $N_r=10^5$ random
-realizations, extracted from up to $N_s=200$ independent ray-tracing
-N-body simulations. We focus in particular on the parameter $w$, and
-on two different statistics: the (convergence) power spectrum and
-the number counts of peaks.
+multiple times.  In light of the forthcoming large surveys, it is
+imperative to assess the statistical validity of this approach, and to
+ask how many times a single simulation can be fairly recycled.  In
+this paper, we address these questions with ensembles of up to
+$N_r=10^5$ random realizations, extracted from up to $N_s=200$
+independent ray-tracing N-body simulations. We focus in particular on
+the parameter $w$, and on two different statistics: the (convergence)
+power spectrum and the number counts of peaks.
 
@@
 We fix the comoving size of the simulation box to $240\mathrm{Mpc}/h$,
-and use $512^3$ particles, corresponding to a Dark Matter particle mass of
-$\approx 10^{10}M_\odot$.
-%ZH: ``mass resolution'' here means DM particle mass ?
-%AP: fixed
+and use $512^3$ particles, corresponding to a dark matter particle
+mass of $\approx 10^{10}M_\odot$.
 
@@
 following (see \citep{Sato12} for reference):
-%ZH: we should cite some paper here. We didn't invent most of this
-%procedure ourselves (except for maybe the 3-times thicker simulation
-%output, and the random mixing of the planes from different N-body sims ?).
-%AP: I added the citation to Sato et. al, which refer to this procedure without citing anyone
 
@@
 \item Perform a periodic random shift of the lens plane along its two directions.
-%ZH: should we specify the range of the random shifts (0 to 1/2 the lens plane dimension?)
-%AP: This is not necessary, since the shifts are periodic, in principle one could choose a random number of pixels.
-In particular this number should be between 0 and 4095, because each lens plane has 4096 pixels
 \item Repeat the above procedure for each lens-plane redshift $z_l$.
@@
 $N_r=10^5$ realizations. For each realization of each ensemble, we
-reconstruct the convergence $\kappa_r(\pmb{\theta})$ from the trace of the light ray deflection Jacobian matrix, measured looking at the difference in angle deflection between nearby light rays \citep{RayTracingHartlap,RayTracingJain,Sato12}.
-%ZH: we should add 2 sentences on how you measured kappa.  Directly from the ray-tracing?
-%   (but above, when you discuss ray-tracing, you mention only gamma).  Or did you do 
-%    Kaiser-Squires on the gamma field ? 
-%AP: done, we measure kappa directly from the ray tracing
+reconstruct the convergence $\kappa_r(\pmb{\theta})$ from the trace of
+the light-ray deflection Jacobian matrix, measured from the difference
+in deflection angles between nearby light-rays
+\citep{RayTracingHartlap,RayTracingJain,Sato12}.
 
@@
 $\kappa$ maxima of a certain height $\kappa_0$, $n_r(\kappa_0)$
-(hereafter \textit{peak counts}), with varying $\kappa_0$ chosen between the minimum and maximum values measured from the maps $(\kappa_{\rm min},\kappa_{\rm max})=(-0.06,0.45)$.
-Different choices of $\kappa_0$ binning used in this work are outlined in Table \ref{featuretable}.
-%ZH: state here the range and binning choice of $\kappa_0$
-%AP: done
-The fact that the ensemble of $N_r$ realizations is not completely
-independent if $N_s$ is not large enough can have an effect on the
-covariance estimators of both $P^{\kappa\kappa}$ and $n(\kappa_0)$.
-
-%ZH: it would be logical to mention the other w,Sig,Om, sims here, and point to \ref{simtable})
-%AP: done, added the below
-
-To measure the cosmological dependence of the $\kappa$ peak counts, we also performed additional ray--tracing simulations with different combinations of the cosmological parameter triplet $(\Omega_m,w,\sigma_8)$.
-A summary of the complete set of shear ensembles used in this work is outlined in Table \ref{simtable}.
+(hereafter \textit{peak counts}), with varying $\kappa_0$ chosen
+between the minimum and maximum values measured from the maps
+$(\kappa_{\rm min},\kappa_{\rm max})=(-0.06,0.45)$. Different choices
+of $\kappa_0$ binning used in this work are outlined in Table
+\ref{featuretable}.  The fact that the ensemble of $N_r$ realizations
+is not completely independent if $N_s$ is not large enough can have an
+effect on the covariance estimators of both $P^{\kappa\kappa}$ and
+$n(\kappa_0)$.
+
+To measure the cosmological dependence of the $\kappa$ peak counts, we
+performed a set of additional ray--tracing simulations with different
+combinations of the cosmological parameter triplet
+$(\Omega_m,w,\sigma_8)$. A summary of the complete set of shear
+ensembles used in this work is listed in Table \ref{simtable}.
 
@@
 Let $\bbh{d}$ be a single estimate for a feature of dimension $N_b$,
-%ZH: ``Hat'' here refers to an estimator?
-%AP: Yes: quantities without the hat are the expectation values 
-$\bb{d}(\bb{p})$ be the
-%smooth expectation
-%ZH: I believe ``smooth expectation'' means true mean value, yes?
-%AP: yes
-true value of this feature at a point $\bb{p}$ in parameter space
-(which has a dimension $N_p$) and $\bb{C}$ be the $N_b\times N_b$
-feature covariance matrix. For the purpose of this work $\bb{p}$ is
-the triplet $(\Omega_m,w,\sigma_8)$ and $\bb{d}$ is one of the
-features -- either a power spectrum or a peak count histogram -- in Table
-\ref{featuretable}. Although existing emulators (see
-\citep{coyote2,Nicaea,SchneiderKnoxCovariance} for example) can be used to compute $\bb{d}(\bb{p}),\bb{C}$ in some cases, this is not true in the general case. 
+$\bb{d}(\bb{p})$ be the true value of this feature at a point $\bb{p}$
+in parameter space (which has a dimension $N_p$) and $\bb{C}$ be the
+$N_b\times N_b$ feature covariance matrix. For the purpose of this
+work $\bb{p}$ is the triplet $(\Omega_m,w,\sigma_8)$ and $\bb{d}$ is
+one of the features -- either a power spectrum or a peak count
+histogram -- in Table \ref{featuretable}. Although existing emulators
+can be used, in principle, to compute both $\bb{d}(\bb{p})$ and
+$\bb{C}$, the latter is more difficult, and typically only the mean,
+$\bb{d}(\bb{p})$, has been computed to date (refs.~\citep{coyote2,Nicaea}, but see
+an exception by ref.~\citep{SchneiderKnoxCovariance}).
 %ZH: I am missing the point here.  Why is covariance matrix ``more complicated'' ?
@@
 I rephrased the sentence.
-Estimating $\bb{C}$ from simulations involves generating a series of mock realizations $\bbh{d}_r$ with $r=1...N_r$ and computing the
+%ZH2: OK, I rephrased it a bit above to be clearer.  I believe only Schneider et al. did ``C''.
+Estimating $\bb{C}$ from simulations involves generating a series of
+mock realizations $\bbh{d}_r$ with $r=1...N_r$ and computing the
 sample covariance $\bbh{C}$,
@@
 %
-0.26 & $-$1 & 0.8 & $(1\div200,1024),(1,128000)$ & 16 \\
+0.26 & $-$1 & 0.8 & (1 to 200,1024) & 16 \\
+0.26 & $-$1 & 0.8 & (1,128000) & 1 \\
 0.29 & $-$1 & 0.8 & (1,1024) & 1 \\
@@
 \end{center}
-\caption{Summary of the shear ensembles used in this work.}
+\caption{Summary of the shear ensembles used in this work. $N_s$ and
+  $N_r$ refer to the number of independent N-body simulations, and the
+  number of pseudo-independent realizations created from these
+  simulations, respectively.}
 %ZH: So each of these have N_r=1000, yes?  You should state this here. And also,
@@
 %AP: done
+%ZH2: The first raw was a bit confusing, so I separated it into two rows. Also added words to the caption
+%    (also, the N_r=10^5 one is the 17th ensemble, in addition to the 16 you listed here before, no? So 16 should have been 17?)
 \label{simtable}
@@
 parameter covariance, i.e. the usual Fisher matrix, as
-$\Sigma_\bb{p}=\bb{F}^{-1}$, we find the result~\footnote{The details of the calculation are given in Appendix A.}:
+$\Sigma_\bb{p}=\bb{F}^{-1}$, we find the result~\footnote{The details
+  of the calculation are given in Appendix A.}:
 
@@
 \begin{enumerate}
-\item If the true data covariance $\bb{C}$ is known, the estimator in eq.~(\ref{estimatorcovariance}) is biased, and the dominant contribution of the bias comes from the second order fluctuations in $\bbh{\Psi}$.
-Once the expectation values over simulations are taken, the bias sums up to
+\item If the true data covariance $\bb{C}$ is known, the estimator in
+  eq.~(\ref{estimatorcovariance}) is biased, and the dominant
+  contribution of the bias comes from the second order fluctuations in
+  $\bbh{\Psi}$. Once the expectation values over simulations are
+  taken, the bias sums up to
 
@@
 
-\item Usually the true data covariance is unknown, and it is tempting to plug in its estimator $\bbh{C}$, measured from the same simulation set we use to compute $\bbh{\Psi}$.
-This approach has been used before in the literature (e.g.~\citep{MinkPetri,MinkShirasaki}).
-If this is done without correcting for the bias in $\bbh{\Psi}$ (see eq.~(\ref{firstmoment}) below or \citep{Taylor12} for reference),
-%ZH: we should probably cite Hartlap et al. and Taylor et al. here for this Psi bias.  (I assume this is what you mean in eq. 19)
-%AP: done
-the parameter variance will have a contribution from both the second and first-order fluctuations in $\bbh{\Psi}$, which now have a nonzero expectation value. In this case the bias sums up to
+\item Usually the true data covariance is unknown, and it is tempting
+  to plug in its estimator $\bbh{C}$, measured from the same
+  simulation set we use to compute $\bbh{\Psi}$. This approach has
+  been used before in the literature
+  (e.g.~\citep{MinkPetri,MinkShirasaki}). If this is done without
+  correcting for the bias in $\bbh{\Psi}$ (see Ref.~\citep{Taylor12}
+  and eq.~\ref{firstmoment} below), the parameter variance will have a
+  contribution from both the second and first-order fluctuations in
+  $\bbh{\Psi}$, which now have a nonzero expectation value. In this
+  case the bias sums up to
 %
@@
 
-\item If we repeat the same exercise as above, but we correct for the bias in the precision matrix estimator, we are left with
+\item If we repeat the same exercise as above, but we correct for the
+  bias in the precision matrix estimator, we are left with
 
@@
 which excludes the true value at high significance level)
-Note that in the last case, which is most relevant when fitting actual data, the estimated degradation turns out to be too optimistic: the parameter estimate $\bbh{p}$ has a variance that grows linearly with $N_b$, but the estimated degradation in eq.
-(\ref{mockscalingcorrected}) is constant with $N_b$.
-This can lead to underestimation of error bars, which can be mistakenly interpreted as a parameter bias.
-We derived the scaling relations of the form
+%ZH2: OK.  I think by `` the parameter estimate $\bbh{p}$ has a variance that grows linearly with $N_b$,'' you mean equation 10
+%   (i.e.  technically it is [variance-1] grows linearly with N_b.   I rephrased below to say ``whose noise'' grows linearly and
+% cite eq.10.    OK?
+Note that in the last case, which is most relevant when fitting actual
+data, the estimated degradation turns out to be too optimistic: the
+parameter estimate $\bbh{p}$ has a variance whose noise grows linearly
+with $N_b$ (eq.~\ref{quarticdegradation}), whereas the degradation
+estimated via eq. (\ref{mockscalingcorrected}) is constant with
+$N_b$. This can lead to underestimation of error bars, which can be
+mistakenly interpreted as a parameter bias.  We derived the scaling
+relations of the form
 %
@@
 %
-above by assuming that the noise in $\bbh{d}$ is Gaussian. We then directly test these scaling relations using our simulations, in the limits of both high and low $N_r$.
+above by assuming that the noise in $\bbh{d}$ is Gaussian. We then
+directly test these scaling relations using our simulations, in the
+limits of both high and low $N_r$.
 %ZH: It is still a little unclear here what is being tested.  Is it the Gaussianity assumption? I added that.
@@
 We are testing that the degradation effectively decreases as 1/Nr at leading order.
-We indicate the diagonal elements of $\h{\Sigma}_{\bb{p}}$ as $\h{\sigma}^2_p=\mathrm{diag}(\h{\Sigma}_{\bb{p}})$ 
-%ZH: I am confused.  Why is a new symbol \sigma necessary here, on top of \Sigma ?
-%    (And also: here you write \Sigma_pp, but above it was denoted \Sigma_p  )
-%AP: fixed. I introduced the \sigma symbol for the single parameter variances (as opposed to the full parameter covariance), because these are the quantities we plot
-and we indicate by $\sigma^2_{p,\infty}$ the expectation value of the variance of each parameter in the limit of an infinite number of realizations
-$N_r\rightarrow\infty$.  We call $D$ the \textit{effective dimensionality} of the feature space (which, as seen before, can be
-negative in some pathological cases).
-%ZH: I added pathological here.  Do you agree?  It's only negative in case 1, when
-%    N_p > N_b (which is impossible -- cannot measure N_p parameters with N_b observables)
-%    or in case 2 (when N_b > N_p, so that's OK, but this case ust means we ``forgot'' to correct for the psi-bias).
-%AP: agreed
-We compute the expectation values of $\h{\sigma}^2_p$
-(eqs.~\ref{estimatorcovariance} and \ref{ourscaling}) by
-averaging over 100 random resamplings of our shear ensembles. For the
-true feature covariance matrix $\langle(\bbh{d}-\bb{d}_0)(\bbh{d}-\bb{d}_0)^T\rangle=\bb{C}$ we use
+%ZH2: I am still confused.  What is it that could go wrong?   I.e. do you have something in mind that could cause a departure from this 1/N_r
+%     scaling?    That is what we are testing, then, but I am not sure what it is.   Are we testing whether the simulations could have a bug?  
+%     Or maybe you simply are testing the validity of truncating the expansion at second order in DeltaPsi ?   
+%     Or maybe what you have in mond is the possible importance of high-order terms in the expansion (beyond the quartic terms, 
+%     and beyond 1/N_r^2) could cause a deviation from 1/N_r that is different from the 1/N_r^2 term in eq.10 ?  In other words,
+%     then we're testing for the importance of the 1/N_r^3 and higher terms numerically...  is that your point?
+%
+We indicate the diagonal elements of $\h{\Sigma}_{\bb{p}}$ as
+$\h{\sigma}^2_p=\mathrm{diag}(\h{\Sigma}_{\bb{p}})$ and we indicate by
+$\sigma^2_{p,\infty}$ the expectation value of the variance of each
+parameter in the limit of an infinite number of realizations
+$N_r\rightarrow\infty$.  We call $D$ the \textit{effective
+  dimensionality} of the feature space (which, as seen before, can be
+negative in some pathological cases).  We compute the expectation
+values of $\h{\sigma}^2_p$ (eqs.~\ref{estimatorcovariance} and
+\ref{ourscaling}) by averaging over 100 random resamplings of our
+shear ensembles. For the true feature covariance matrix
+$\langle(\bbh{d}-\bb{d}_0)(\bbh{d}-\bb{d}_0)^T\rangle=\bb{C}$ we use
 the estimated covariance from a grand ensemble built with the union of
@@
   (purple) independent N-body simulations. Each curve is based on
-  $N_r=1024$ realizations.
-%ZH: I added the Nr=1000 above. Yes?
-%AP: Yes, 1024 in reality, but it doesn't change much
-  The dashed black curves correspond to ensembles generated with $N_s=1$ and
-  $N_r=128000$. For $N_s\geq2$, the distributions appear
-  similar to the eye; this similarity is confirmed by the comparisons
-  in Figures \ref{means_ns} and \ref{ps_var} below.}
-%MM: added last two sentences
-%MM: Thick black line draws the eye and looks like the most significant thing on the plot. replace with dotted black line or something else that stands out less.
-%ZH: Also, include a label ``N_r=10^5'' with the other N_s=... labels in the figure panels 
-%   (it is just confusing why there are labels for all the other curves, but not for the thick black)
-%AP: done
+  $N_r=1024$ realizations.  The dashed black curves correspond to
+  ensembles generated with $N_s=1$ and $N_r=128000$. For $N_s\geq2$,
+  the distributions appear similar to the eye; this similarity is
+  confirmed by the comparisons in Figures \ref{means_ns} and
+  \ref{ps_var} below.}
 \label{ps_pdf}
@@
 \includegraphics[scale=0.3]{Figures/means_ns.eps}
-\caption{The mean value $\bb{\bar{d}}$
-% $d$  
-%ZH: I think you mean  \bb{\bar{d}} here?  You introduced a lot of different
-%    subtle notations in the previous section, so we should  follow those ....
-%AP: OK
-  of various features, measured from ensembles created from different
-  numbers $N_s$ of simulations.  For each case, the difference compared
-  to the mean in the $N_s=200$ ensemble is shown, in units of the
-  statistical error measured in the $N_s=200$ ensemble.  The colored
-  curves refer to shear--shear power spectra measured at $\ell=115$
-  (black), 1027 (cyan), and 5283 (green), and peak counts 
-%ZH: I replace ``of'' with ``above''.  These are cumulative peak counts N(>kappa_0) ?
-%    Or do you mean differential counts in some delta-kappa_0 bins?   Then you should
-%    correct the text (and state the bin width).  Table II contains some kappa-bins
-%    but no obvious relation to the 0.05, 0.17  and 0.28 mentioned here...
-%AP: The peak counts are differential, I added the clarifications; I chose three values of kappa0 for the sake of presentation simplicity (one value in the low height peaks, one in the middle and one in the large)
-  with height of $\kappa_0=0.05$ (red), 0.17 (purple), and 0.28
-  (orange).
-The $\kappa$ bin width for the peak counts has been fixed to $\Delta\kappa=0.011$.
-The dashed black line shows a level of $0.1\sigma$ accuracy for reference.
-For $N_s\geq 2$, the means are statistically indistinguishable (at $\sim0.1\sigma$) from the means measured in the ensemble with $N_s=200$.}
-%MM: added last sentence stating conclusion to be drawn from the figure
-%ZH:  Good idea.  All figures captions should similarly state a conclusion!
-%ZH:  What is the horizontal dashed line?  It is never mentioned in the caption or
-%     the text.   I guess you decided to mark the ``0.1 sigma'' deviation?
-%     We should state that.    I suppose this is what Morgan refers to by 
-%    ``statistically indistinguishable'' ....  0.1 sigma.
-%AP: Ok, added the clarifications to the caption
+\caption{The mean value $\bb{\bar{d}}$ of various features, measured
+  from ensembles created from different numbers $N_s$ of simulations.
+  For each case, the difference compared to the mean in the $N_s=200$
+  ensemble is shown, in units of the statistical error measured in the
+  $N_s=200$ ensemble.  The colored curves refer to shear--shear power
+  spectra measured at $\ell=115$ (black), 1027 (cyan), and 5283
+  (green), and peak counts with heights $\kappa_0=0.05$ (red), 0.17
+  (purple), and 0.28 (orange). The $\kappa$ bin width for the peak
+  counts has been fixed to $\Delta\kappa=0.011$. The dashed black line
+  shows a level of $0.1\sigma$ accuracy for reference.  For $N_s\geq
+  2$, the means are statistically indistinguishable (even at
+  $\sim0.1\sigma$) from those in the ensemble with $N_s=200$.}
 \label{means_ns}
@@
   (green), 10 (red), 50 (purple), or 100 (orange) N--body simulations.
-%ZH: Added ``conclusion'':
-%AP: OK
-  Non--Gaussianities of the underlying structures increase the variance on
-  small scales, but no clear trend with $N_s$ can be identied on any scale.}
+  Non--Gaussianities of the underlying structures increase the
+  variance on small scales, but no clear trend with $N_s$ can be
+  identied on any scale.}
 \label{ps_var}
@@
   $1/N_r$. The different symbols and colors correspond to the features
-  listed in Table~\ref{featuretable}.
-%ZH: It would be better to write the features on the legend embedded in the figure.
-%    Why make the reader flip back-and-forth between the figure and the Table ?
-%AP: done
-  The dashed and solid curves show the analytic predictions from
-  equation (\ref{quarticdegradation}) at orders $O(1/N_r)$ and
-  $O(1/N_r^2)$, respectively. The asymptotic variance
-  $\sigma^2_{w,\infty}$ has been computed from a linear regression of
-  $\langle\h{\sigma}^2_w\rangle$ vs $1/N_r$ for $N_r>500$. The figure
-  clearly shows that terms beyond $O(1/N_r)$ need to be considered,
-  unless $N_r\gg N_b$.}
-%MM: added last sentence stating conclusion to be drawn from the figure
-%in legend box change line that reads Nb=7 divided by 8
-%AP: done, the legend is comprehensive now
+  listed in Table~\ref{featuretable}.  The dashed and solid curves
+  show the analytic predictions from equation
+  (\ref{quarticdegradation}) at orders $O(1/N_r)$ and $O(1/N_r^2)$,
+  respectively. The asymptotic variance $\sigma^2_{w,\infty}$ has been
+  computed from a linear regression of $\langle\h{\sigma}^2_w\rangle$
+  vs $1/N_r$ for $N_r>500$. The figure clearly shows that terms beyond
+  $O(1/N_r)$ need to be considered, unless $N_r\gg N_b$.}
 \label{curvingnb}
@@
   (solid lines) and their best fits based on eq.~(\ref{ourscaling}),
-  with $D$ treated as a free parameter.
-%ZH: We need to explain what you mean by best-fit (presumably you treat ``D'' as a free parameter).
-%   I added that. But if you meant something else, please correct.
-%AP: OK
-  The thick black curve corresponds to an ensemble of $N_r=128000$
-  realizations from a single simulation ($N_s=1$).
-%ZH: I added 'conclusion':
-%AP: OK
-  No systematic deviation from the expected scaling is seen, even in
-  the extreme last case.  }
+  with $D$ treated as a free parameter.  The thick black curve
+  corresponds to an ensemble of $N_r=128000$ realizations from a
+  single simulation ($N_s=1$).  No systematic deviation from the
+  expected scaling is seen, even in the extreme last case.  }
 \label{wvar_nr}
@@
 \includegraphics[scale=0.3]{Figures/scaling_ns.eps}
-\caption{The variance of $w$ in the limit of $N_r\rightarrow\infty$ (measured from the intercept of the fit $\sigma^2_w$ vs $1/N_r$),
-%ZH: state here what N_r was actually used to approximate the infinity limit
-%AP: the value plotted is actually $N_r\rightarrow\infty$, because it is estimated from the intercept of the fit.
-Even if all the points have Nr finite, the intercept of the line corresponds to Nr infinite.
+\caption{The variance of $w$ in the limit of $N_r\rightarrow\infty$
+  (measured from the intercept of the fit $\sigma^2_w$ vs $1/N_r$),
   varying the number of simulations $N_s$ used in the ensemble to
   estimate the covariance (eq.~\ref{covest}). We show the dependence
-  of $\sigma_{w,\infty}^2(N_s)$ in units of the mean over the 16 ensembles with different $N_s$, 
-%ZH: Just to make sure: what you mean here is an averaging of sigma_infty over the 16 different
-%    cases of N_s ?   
-%AP: Yes
-  for the power spectrum logarithmically binned (black, $N_b=15,\ell\in[100,6000]$), the power spectrum linearly binned (red,$N_b=39,\ell\in[100,6000]$) and the peak counts (green,$N_b=45,\kappa_0\in[-0.06,0.45]$).
-%ZH: What ell and kappa ranges were used?
-%ZH: Added conclusion:
-%AP: OK, added binning information
-  No trend with $N_s$ is seen for $N_s\geq 2$, and the differences are only of order 1\%.}
+  of $\sigma_{w,\infty}^2(N_s)$ in units of the mean over the 16
+  ensembles with different $N_s$, for the power spectrum
+  logarithmically binned (black, $N_b=15,\ell\in[100,6000]$), the
+  power spectrum linearly binned (red,$N_b=39,\ell\in[100,6000]$) and
+  the peak counts (green,$N_b=45,\kappa_0\in[-0.06,0.45]$).  No trend
+  with $N_s$ is seen for $N_s\geq 2$, and the differences are only of
+  order 1\%.}
 \label{wvar_ns}
@@
 \end{center}
-\caption{Catalog of feature types used in this work, along with the chosen number of bands $N_b$ and the plot legends for Figure \ref{curvingnb}.}
+\caption{Catalog of feature types used in this work, along with the
+  chosen number of bands $N_b$ and the plot legends for Figure
+  \ref{curvingnb}.}
 \label{featuretable}
@@
 counts of three different $\kappa_0$ heights (corresponding to
-$\approx 2\div13\sigma$ peaks), as a function of $N_s$.
-%ZH: added above 2-12.  OK ?
-%AP: the actual numbers are 2-13, but again, only minor change
-In Figure~\ref{ps_var}, we show the variance of the power spectrum at
+$\approx 2-13\sigma$ peaks), as a function of $N_s$.  In
+Figure~\ref{ps_var}, we show the variance of the power spectrum at
 each multipole, as a function of $N_s$, in units of the variance
@@
 %
-%ZH:  I changed ``l''  to ``\ell'' in many places, for the multipole
-%AP: OK, I fixed this throughout the rest of the paper
 \begin{equation}
@@
 $(\ell_x,\ell_y)=2\pi(i_x,i_y)/\theta_{\rm box}$, with $i_x=-n_{\rm
-  ray}/2,...,n_{\rm ray}/2$ and $i_y=0,...,n_{\rm ray}/2$.
-%ZH: added this:
-%AP: OK
-Here $n_{\rm ray}=2048$ is the linear number of pixels on the
-ray--traced convergence maps.  We count the number of pixels $N(\ell)$
-that fall inside a multipole bin $(\ell_1,\ell_2)$. Because the
-$\kappa$ field is real, the modes $(\pm \ell_x,0)$ are not
-independent. If we let $N(\ell,\ell_y=0)$ be the number of
-non--independent modes, the effective number of independent modes
-for the variance is given by
+  ray}/2,...,n_{\rm ray}/2$ and $i_y=0,...,n_{\rm ray}/2$.  Here
+$n_{\rm ray}=2048$ is the linear number of pixels on the ray--traced
+convergence maps.  We count the number of pixels $N(\ell)$ that fall
+inside a multipole bin $(\ell_1,\ell_2)$. Because the $\kappa$ field
+is real, the modes $(\pm \ell_x,0)$ are not independent. If we let
+$N(\ell,\ell_y=0)$ be the number of non--independent modes, the
+effective number of independent modes for the variance is given by
 
@@
 of the confidence range $\langle\h{\sigma}^2_w\rangle$ on $N_r$,
-derived from the features used in this work (see Table \ref{featuretable} for a comprehensive list).
-Figure \ref{wvar_nr} shows the $N_r$ trends of the $w$ constraint obtained with the power spectrum logarithmically binned with $\ell\in[100,6000],N_b=15$.
-%ZH: previously you only stated ``power spectrum'' for Figure 5.  But I assume Fig.4 is
-%    also based on the power spectrum?  If not, please correct.
-%AP: OK, fixed
+derived from the features used in this work (see Table
+\ref{featuretable} for a comprehensive list). Figure \ref{wvar_nr}
+shows the $N_r$ trends of the $w$ constraint obtained with the power
+spectrum logarithmically binned with $\ell\in[100,6000], N_b=15$.
 Figure~\ref{curvingnb} illustrates the behavior at relatively low
@@
 built from $N_s=1$ do not produce the same statistical behavior as
-ensembles built with larger $N_s$. In particular, looking at the
-black curves, we see that the $N_s=1$ ensembles exibit large shifts
-with respect to the other PDFs to lower power, including the locations
-of the peaks of the PDFs.  We attribute these offsets to large
-(random) statistical errors.
-%ZH: I changed the wording above.  We didn't really prove that these are statistical errors,
-%    and not some systematic shift to low power when N_s is low.
-%AP: OK
+ensembles built with larger $N_s$. In particular, looking at the black
+curves, we see that the $N_s=1$ ensembles exibit large shifts with
+respect to the other PDFs to lower power, including the locations of
+the peaks of the PDFs.  We attribute these offsets to large (random)
+statistical errors.
 
 Interestingly, we need as few as $N_s=2$ simulations to recover the
-right PDF
-%ZH: what is ``location parameter'' ?
-%location parameter 
-%AP: location parameter usually indicated where the PDF peaks. This might be the mean, but not always. 
-for the small--scale power spectrum.  Figure~\ref{means_ns} shows that
-multiple independent $N$--body simulations $N_s\geq2$ are indeed
-necessary for measuring the means of feature ensembles to an accuracy
-corresponding to 10\% of the statistical error. The number of required
-simulations $N_s$ depends on the feature type and ranges from a few ($N_s=1$
-or 2) for the power spectrum at low multipoles ($\ell\lesssim 500$) to
-$N_s\approx 30-50$ for the power spectrum at larger
-multipoles ($\ell\gtrsim1000$) or peak counts above a high threshold
-($\kappa_0\approx0.3$).
-%ZH: I think this text above is a bit misleading.  Wny would we actually impose the ``0.1 sigma''
-%    requirement?    It sounds too stringent.  If we instead imposed, say, 0.5 sigma, would
-%    N_s=2 always be sufficient?    We should probably at least add this (delete if untrue):
-%AP: OK, agreed
-On the other hand, relaxing the required accuracy to 50\% of the statistical
-error, we find $N_s=2$ to be always sufficient.
+right PDF for the small--scale power spectrum.  Figure~\ref{means_ns}
+shows that multiple independent $N$--body simulations $N_s\geq2$ are
+indeed necessary for measuring the means of feature ensembles to an
+accuracy corresponding to 10\% of the statistical error. The number of
+required simulations $N_s$ depends on the feature type and ranges from
+a few ($N_s=1$ or 2) for the power spectrum at low multipoles
+($\ell\lesssim 500$) to $N_s\approx 30-50$ for the power spectrum at
+larger multipoles ($\ell\gtrsim1000$) or peak counts above a high
+threshold ($\kappa_0\approx0.3$).  On the other hand, relaxing the
+required accuracy to 50\% of the statistical error, we find $N_s=2$ to
+be always sufficient.
 
@@
 the known result that non--Gaussian structures increase the variance
-significantly on small scales (see \citep{Sato12,TakadaSpergel14} for reference). 
-%ZH: We could add more references here, e.g. the earlier Sato et al. 2009 paper, and the Takada and Spergel
-%    papers looking at the non-Gaussian variance of the pow.spectrum.. 
-%AP: Done: that is, in fact, the Sato 2009 paper, I mis-labelled it with Sato12 in the bibtex
-Our results are in fact in excellent agreement with \citep{Sato12}, which used $N_s=400$ independent N-body
+significantly on small scales (see \citep{Sato12,TakadaSpergel14} for
+reference).  Our results are in fact in excellent quantitative
+agreement with \citep{Sato12}, which used $N_s=400$ independent N-body
 simulations.  This result is highly encouraging, suggesting that
-individual $N$--body runs can be recycled repeatedly.  However, it is not
-sufficient by itself to conclude that $N_s$ does not impact the
+individual $N$--body runs can be recycled repeatedly.  However, it is
+not sufficient by itself to conclude that $N_s$ does not impact the
 parameter inferences, since these depend on the cross band
@@
 limit $N_r\rightarrow \infty$; or equivalently the $w$ constraint with
-the known $N_r$ dependence factored out),
-%ZH: see my paraphrasing above.  I wanted to clearly distinguish the point
-%    of this paragraph from the previous paragraph.
-%AP: OK
-depends on $N_s$. We find that, in the range $N_s\in[1,200]$ the
-inferred $w$--variance $\sigma_{w,\infty}^2$ fluctuates stochastically
-only by 1\%, and does not show any trend with $N_s$.
+the known $N_r$ dependence factored out), depends on $N_s$. We find
+that, in the range $N_s\in[1,200]$ the inferred $w$--variance
+$\sigma_{w,\infty}^2$ fluctuates stochastically only by 1\%, and does
+not show any trend with $N_s$.
 
@@
 parameter errors purely from simulations, as the errors will otherwise
-be underestimated. A similar conclusion was reached by \citep{Hartlap07}.
+be underestimated. A similar conclusion was reached by
+\citep{Hartlap07} (although their paper did not address the impact of
+using the same simulation set for $\bb{C}$ and $\bbh{\Psi}$).
+
 %ZH: reworded above.  OK?  Also, I am not sure if this point is new.
@@
 I don't think this point appears in Hartlap et al.
+%ZH2: OK I added this clarification above.
 
@@
   require $N_r\gsim 100 (N_b-N_p)$ realizations.
-%ZH: what is sufficiently large here?  I presume a ``few hundred'' 
-%    (or $>100N_p$, based on eq. 13).  I added that.  Please correct if 
-%    this is not OK.
-%AP: OK, the quantity to compare to is Nb-Np though. If Nb=Np there is no degradation at every order
 \item Depending on the feature type used to constrain cosmology, a
   larger number of $N$--body simulations might be needed to measure
-  accurate ensemble means to an accuracy corresponding 10\% of the statistical error.
-If this accuracy requirement is relaxed to 50\% of the statistical error, we find that as low as $N_s=2$ simulations are needed, for the feature types we consider in this work.
-%ZH:  So I am not sure about this last conclusion.   
-%     What exactly do you have in mind?   Is it Figure 2, which shows
-%     some deviations above the horizontal dashed line, for N_s up to ~50 ?
-%     But this is based on the super-stringent requirement that the bias
-%     is <0.1*sigma.
-%     The same figure seems to show that N_s=2 simulation is in fact
-%     sufficient to measure the means to within 0.5*sigma, as well.
-%     If you agree, we should revise this bullet to state this more
-%     positive conclusions!
-%AP: Agreed, I rephrased the bullet point
+  accurate ensemble means to an accuracy corresponding 10\% of the
+  statistical error. If this accuracy requirement is relaxed to 50\%
+  of the statistical error, we find that as low as $N_s=2$ simulations
+  are sufficient for the feature types we consider in this work.
 \end{itemize}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%% APPENDIX %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%ZH: I did not carefully re-read the appendices.  I guess that is OK.
-%    One cosmetic comment:  when you refer to equations, you need to say
-%    ``as in eq. (xx)''  rather than  ``as in (xx)''.
-%AP: done   
+%ZH2: I went through the appendix, too, now, and made minor cosmetic changes.
+%     
 \section*{Appendix A: cubic and quartic covariance fluctuations}
@@
 
-The goal of this appendix is to give a derivation of eq.
-(\ref{quarticdegradation}).
-When the simulated feature vector $\bbh{d}_r$ is drawn from a Gaussian distribution, the covariance estimator $\bbh{C}$ follows the Wishart distribution, and its inverse $\bbh{\Psi}$ follows the inverse Wishart distribution.
-For the analytical expressions of these probability distributions we remand the reader to \citep{Taylor12}.
-Computing expectation values of eq.
-(\ref{estimatorcovariance}) over the inverse Wishart distribution is not possible analytically, and a perturbative expansion is necessary.
-Writing $\bbh{\Psi}=\bb{\Psi}+\delta\bbh{\Psi}$, we can expand eq.
-(\ref{quarticdegradation}) in powers of $\delta\bbh{\Psi}$.
-The expectation values of each term in this perturbative expansion can be calculated in term of the moments of the inverse Wishart distribution.
-\citep{MasumotoWishart} provide a general framework to compute these moments, and give exact expressions for moments up to quartic order.
-First, let us expand the inverse of the Fisher matrix estimator (\ref{estimatorfisher}) in powers of $\delta\bbh{\Psi}$.
-The $n$--th order of this expansion will be
+The goal of this appendix is to give a derivation of
+eq. (\ref{quarticdegradation}). When the simulated feature vector
+$\bbh{d}_r$ is drawn from a Gaussian distribution, the covariance
+estimator $\bbh{C}$ follows the Wishart distribution, and its inverse
+$\bbh{\Psi}$ follows the inverse Wishart distribution (see
+Ref.~\citep{Taylor12} for analytical expressions for these probability
+distributions). Computing expectation values of
+eq. (\ref{estimatorcovariance}) over the inverse Wishart distribution
+is not possible analytically, and a perturbative expansion is
+necessary. Writing $\bbh{\Psi}=\bb{\Psi}+\delta\bbh{\Psi}$, we can
+expand eq. (\ref{quarticdegradation}) 
+%ZH2: you must mean eq.~(\ref{estimatorcovariance}) above, instead of eq.10 
+in powers of $\delta\bbh{\Psi}$. The expectation value of each term in
+this expansion can be calculated in terms of moments of the inverse
+Wishart distribution. Ref.~\citep{MasumotoWishart} provides a general
+framework to compute these moments, and give exact expressions for
+moments up to quartic order. First, let us expand the inverse of the
+Fisher matrix estimator (eq.~\ref{estimatorfisher}) in powers of
+$\delta\bbh{\Psi}$. The $n$--th order of this expansion will be
 
@@
 %
-Using eq.
-(\ref{nthterm}), we can expand eq.
-(\ref{estimatorcovariance}) to an arbitrary order in $\delta\bbh{\Psi}$, take the expectation values of the fluctuations over the inverse Wishart distribution, and finally get to eq.
-(\ref{quarticdegradation}).
-We use the notation $\nu=N_r-1$ and $\gamma=(\nu-N_b-1)/2$.
-We indicate with capital letters pairs of matrix indices, for example $I=(i_1,i_2)$, where $i_a=1..N_b$.
-The main results we take out from \citep{MasumotoWishart} regarding the first four moments are (up to order $O(1/\nu^2)$)
+Using eq. (\ref{nthterm}), we can expand
+eq. (\ref{estimatorcovariance}) to an arbitrary order in
+$\delta\bbh{\Psi}$, take the expectation values of the fluctuations
+over the inverse Wishart distribution, and finally arrive at
+eq.~(\ref{quarticdegradation}). We use the notation $\nu\equiv N_r-1$
+and $\gamma\equiv (\nu-N_b-1)/2$, and we indicate with capital letters
+pairs of matrix indices, for example $I=(i_1,i_2)$, where
+$i_a=1..N_b$. The main results we utilize from
+ref.~\citep{MasumotoWishart} regarding the first four moments are (up
+to order $O(1/\nu^2)$)
 
@@
 \label{fourthmoment}
-\langle\delta\h{\Psi}_I\delta\h{\Psi}_J\delta\h{\Psi}_K\delta\h{\Psi}_L\rangle = \frac{\nu^4(2\gamma^2-5\gamma+9)\Psi_{[I}\Psi_{J]}\Psi_{[K}\Psi_{L]}}{16\gamma(\gamma-1)(\gamma-2)(\gamma-3)(2\gamma-1)(\gamma+1)(2\gamma+1)(2\gamma+3)}
+\langle\delta\h{\Psi}_I\delta\h{\Psi}_J\delta\h{\Psi}_K\delta\h{\Psi}_L\rangle = \frac{\nu^4(2\gamma^2-5\gamma+9)\Psi_{[I}\Psi_{J]}\Psi_{[K}\Psi_{L]}}{16\gamma(\gamma-1)(\gamma-2)(\gamma-3)(2\gamma-1)(\gamma+1)(2\gamma+1)(2\gamma+3)}.
 \end{equation}
@@
 %
-Where the square bracket notation is a shorthand for a symmetrization over pair of indices: for example
+Here the square bracket notation is a shorthand for a symmetrization over pair of indices: for example
 \begin{equation}
@@
 %
-Eq.
-(\ref{firstmoment}) expresses the bias in the $\bbh{\Psi}$ estimator that already appears in the literature \citep{Hartlap07}.
-If we want to use the bias corrected $\bbh{\Psi}$ estimator (that is required in a perturbative expansion of eq.
-(\ref{estimatorcovariance})), we need to apply an additional factor of $(2\gamma/\nu)^n$ to eqs.
-(\ref{firstmoment}--\ref{fourthmoment}), where $n$ is the order of the moment we are applying the correction to.
-If we limit ourselves to computing the expectation value of eq.
-(\ref{estimatorcovariance}) up to order $O(1/\nu^2)$, we do not need to worry about this correction for eqs.
-(\ref{thirdmoment}--\ref{fourthmoment}), as the dominant term here is already $O(1/\nu^2)$.
-The next step is expanding eq.
-(\ref{estimatorcovariance}) in powers of $\delta\bbh{\Psi}$ up to fourth order: this is easily done
+Eq. (\ref{firstmoment}) expresses the bias in the $\bbh{\Psi}$
+estimator that already appears in the literature~\citep{Hartlap07}. If
+we want to use the bias-corrected $\bbh{\Psi}$ estimator (required for
+the perturbative expansion of eq.~\ref{estimatorcovariance}), we need
+to apply an additional factor of $(2\gamma/\nu)^n$ to
+eqs. (\ref{firstmoment}--\ref{fourthmoment}), where $n$ is the order
+of the moment up to which we are applying the correction. If we limit
+ourselves to computing the expectation value of
+eq. (\ref{estimatorcovariance}) up to order $O(1/\nu^2)$, we do not
+need to worry about this correction for
+eqs. (\ref{thirdmoment}--\ref{fourthmoment}), as the dominant term
+here is already $O(1/\nu^2)$. The next step is expanding
+eq. (\ref{estimatorcovariance}) in powers of $\delta\bbh{\Psi}$ up to
+fourth order: this is easily done:
 
@@
 \label{fullpertexpansion}
-\h{\Sigma}_\bb{p} = \left(\bb{F}^{-1}+\sum_{n=1}^4\delta\bbh{F}^{-1}_{(n)}\right)\bb{d}'^T_0(\bb{\Psi}+\delta\bbh{\Psi})\bb{C}(\bb{\Psi}+\delta\bbh{\Psi})\bb{d}'_0\left(\bb{F}^{-1}+\sum_{n=1}^4\delta\bbh{F}^{-1}_{(n)}\right)
+\h{\Sigma}_\bb{p} = \left(\bb{F}^{-1}+\sum_{n=1}^4\delta\bbh{F}^{-1}_{(n)}\right)\bb{d}'^T_0(\bb{\Psi}+\delta\bbh{\Psi})\bb{C}(\bb{\Psi}+\delta\bbh{\Psi})\bb{d}'_0\left(\bb{F}^{-1}+\sum_{n=1}^4\delta\bbh{F}^{-1}_{(n)}\right).
 \end{equation}
@@
 %
-Carrying out the calculations is simpler than it looks: because of the structure of eq.
-(\ref{fullpertexpansion}), each term in the expansion is going to be proportional to $\Sigma_\bb{p}f_a(N_b,N_p)/N_r^a$, where $f_a(N_b,N_p)$ is polynomial in $N_b,N_p$.
-Terms proportional to $N_b$ arise from index contractions of type $\mathrm{tr}(\bb{\Psi C})=N_b$, which come from symmetrization terms of type $\Psi_{[I}\Psi_{J]}$.
-Symmetrization factors of type $\Psi_{[I}\Psi_J\Psi_{K]}$ or $\Psi_{[I}\Psi_{J]}\Psi_{[K}\Psi_{L]}$, on the other hand, give rise to contractions of type $\mathrm{tr}(\bb{\Psi C})\mathrm{tr}(\bb{\bb{F}\bb{F}^{-1}})=N_bN_p$.
-Moreover, we know that, at every order $O(1/N_r^a)$, $f_a(N_b,N_p)$ has to be proportional to $N_b-N_p$ because it must vanish when $N_b=N_p$.
-The reason for this is that, when the feature derivative matrix $\bb{d}'_0$ is square and invertible (which it should be in absence of degeneracies), then eq.
-(\ref{estimatorcovariance}) reduces to
-
-\begin{equation}
-\h{\Sigma}_\bb{p} = (\bb{d}'_0)^{-1}\bb{C}(\bb{d}'^T_0)^{-1}
-\end{equation} 
-%
-And every trace of the noise is gone, hence powers of $1/N_r^a$ must not appear at any order if $N_b=N_p$.
-Armed with the knowledge of the above considerations, we can compute the expectation value of eq.
-(\ref{fullpertexpansion}) at second, third and fourth order in $\delta\bbh{\Psi}$, keeping the terms that are at most $O(1/\nu^2)=O(1/N_r^2)$.
-When the combinatorial factors that arise from the expansion of eq.
-(\ref{fullpertexpansion}) are properly computed and the expectation values over the inverse Wishart distribution are taken according to eqs.
-(\ref{firstmoment}--\ref{fourthmoment}), the results should look like
+Carrying out the calculations is simpler than it looks: because of the
+structure of eq. (\ref{fullpertexpansion}), each term in the expansion
+is proportional to $\Sigma_\bb{p}f_a(N_b,N_p)/N_r^a$, where
+$f_a(N_b,N_p)$ is a polynomial in $N_b$ and $N_p$. Terms proportional
+to $N_b$ arise from index contractions of type $\mathrm{tr}(\bb{\Psi
+  C})=N_b$, which come from symmetrization terms of type
+$\Psi_{[I}\Psi_{J]}$. Symmetrization factors of type
+$\Psi_{[I}\Psi_J\Psi_{K]}$ or $\Psi_{[I}\Psi_{J]}\Psi_{[K}\Psi_{L]}$,
+on the other hand, give rise to contractions of type
+$\mathrm{tr}(\bb{\Psi
+  C})\mathrm{tr}(\bb{\bb{F}\bb{F}^{-1}})=N_bN_p$. Moreover, we know
+that, at every order $O(1/N_r^a)$, $f_a(N_b,N_p)$ has to be
+proportional to $N_b-N_p$, because it must vanish when $N_b=N_p$. The
+reason for this is that if the feature derivative matrix $\bb{d}'_0$
+is square and invertible (which it should be in absence of
+degeneracies), then eq. (\ref{estimatorcovariance}) reduces to
+
+\begin{equation}
+\h{\Sigma}_\bb{p} = (\bb{d}'_0)^{-1}\bb{C}(\bb{d}'^T_0)^{-1}.
+\end{equation} 
+%
+Every trace of the noise is gone, hence powers of $1/N_r^a$ must not
+appear at any order if $N_b=N_p$. Armed with the knowledge of the
+above considerations, we can compute the expectation value of
+eq. (\ref{fullpertexpansion}) at second, third and fourth order in
+$\delta\bbh{\Psi}$, keeping the terms that are at most
+$O(1/\nu^2)=O(1/N_r^2)$. When the combinatorial factors that arise
+from the expansion of eq. (\ref{fullpertexpansion}) are properly
+computed and the expectation values over the inverse Wishart
+distribution are taken according to
+eqs. (\ref{firstmoment}--\ref{fourthmoment}), the results take the form
 
@@
 \begin{displaystyle}
-(\delta\bbh{\Psi})^4 \rightarrow 3\Sigma_\bb{p}\frac{(N_b-N_p)(1+N_p)}{N_r^2}
+(\delta\bbh{\Psi})^4 \rightarrow 3\Sigma_\bb{p}\frac{(N_b-N_p)(1+N_p)}{N_r^2}.
 \end{displaystyle}
@@
 
-The goal of this appendix is giving a justification on why the effective dimensionality $D$ that appears in eq.
+The goal of this appendix is to give a justification for why the effective dimensionality $D$ that appears in eq.
 (\ref{ourscaling}) can be negative in some cases.
@@
 \label{negativeD}
-\langle\h{\Sigma}_\bb{p}\rangle = \Sigma_\bb{p}\left(1-\frac{N_b+1}{N_r}+\frac{1+N_p}{N_r}\right) = \Sigma_\bb{p}\left(1+\frac{N_p-N_b}{N_r}\right)
+\langle\h{\Sigma}_\bb{p}\rangle = \Sigma_\bb{p}\left(1-\frac{N_b+1}{N_r}+\frac{1+N_p}{N_r}\right) = \Sigma_\bb{p}\left(1+\frac{N_p-N_b}{N_r}\right).
 \end{equation}
@@
 %
-And we immediately see that the coefficient of $1/N_r$ is negative, because $N_b>N_p$.
+We immediately see that the coefficient of $1/N_r$ is negative, because $N_b>N_p$.
 This is the result shown in eq.
 (\ref{mockscalinguncorrected}).
-If the bias correction for $\bbh{\Psi}$ is applied, the first order terms $\delta{\bbh{F}}$ average to 0, and we are left with only the last term in the sum (\ref{negativeD}), which immediately yields eq.
+If the bias correction for $\bbh{\Psi}$ is applied, the first order terms $\delta{\bbh{F}}$ average to 0, and we are left with only the last term in the sum eq.~(\ref{negativeD}), which immediately yields eq.
 (\ref{mockscalingcorrected}).

### 2016-01-09 Paper/paper.tex
addressed ZH2 comments

@@
 parameter confidence intervals as a function of ($N_s,N_r$) in the
-range $1\leq N_s\leq 200$ and $1\leq N_r\leq 10^5$.  Previous work
+range $1\leq N_s\leq 200$ and $1\leq N_r\lesssim 10^5$.  Previous work
 \citep{DodelsonSchneider13} has shown that Gaussian noise in the
@@
 finite number of simulations naturally introduces fluctuations in the
-forecasts, due to inevitable sample variance~\footnote{Sample variance
-  is a broad term that has been used in the literature to describe a
-  range of phenomena.  Throughout this paper, we use it to refer to
-  the fluctuations in an ensemble of simulations, which represent
-  random realizations of the same initial conditions.}.  In general,
+forecasts, due to inevitable sample variance~\footnote{Sample variance is a broad term that has been used in the literature to describe a range of phenomena.
+Throughout this paper, we use it to refer to the fluctuations in an ensemble of simulations, which represent random realizations of the same initial conditions.}.
+In general,
 quantities such as the mean or the variance of any feature (e.g. the
@@
 %ZH2: OK, I rephrased it a bit above to be clearer.  I believe only Schneider et al. did ``C''.
+%AP2: OK
 Estimating $\bb{C}$ from simulations involves generating a series of
@@
 %AP: done
-%ZH2: The first raw was a bit confusing, so I separated it into two rows. Also added words to the caption
+%ZH2: The first row was a bit confusing, so I separated it into two rows. Also added words to the caption
 %    (also, the N_r=10^5 one is the 17th ensemble, in addition to the 16 you listed here before, no? So 16 should have been 17?)
+%AP2: OK
 \label{simtable}
@@
 % cite eq.10.    OK?
+%AP2: OK
 Note that in the last case, which is most relevant when fitting actual
@@
 $N_b$. This can lead to underestimation of error bars, which can be
-mistakenly interpreted as a parameter bias.  We derived the scaling
+mistakenly interpreted as a parameter bias. We test scaling
 relations of the form
@@
 %
-above by assuming that the noise in $\bbh{d}$ is Gaussian. We then
-directly test these scaling relations using our simulations, in the
-limits of both high and low $N_r$.
+againts our simulations, in the limits of both high and low $N_r$.
 %ZH: It is still a little unclear here what is being tested.  Is it the Gaussianity assumption? I added that.
@@
 %
+%AP2: Technically the 1/Nr scaling has been obtained using the inverse Wishart distribution; if the data is non Gaussian, the covariance is not Wishart, but maybe one can say that for an arbitrary, not too crazy, distribution the leading term is still 1/Nr and the coefficient is not too different from Nb-Np...
+This is indeed what we find: the error degradation is basically the same should we use power spectra or peak counts which have different PDFs...
+I removed the mention to the Gaussianity, which is not what we test.
+What we test is eq.
+10 in the low Nr limit and the (possible) deviations from 1/Nr when Nr is very large (due to the maps being pseudo independent).
 We indicate the diagonal elements of $\h{\Sigma}_{\bb{p}}$ as
@@
 %ZH2: OK I added this clarification above.  
+%AP2: OK: Hartlap focuses on the Psi distribution, translating it into a parameter distribution using a naive Fisher analysis; what he does is in fact use the same simulation set for Psi and C, but this kind of discussion is absent from his paper.
 
@@
 %ZH2: I went through the appendix, too, now, and made minor cosmetic changes.
-%     
+%AP2: OK     
 \section*{Appendix A: cubic and quartic covariance fluctuations}
@@
 necessary. Writing $\bbh{\Psi}=\bb{\Psi}+\delta\bbh{\Psi}$, we can
-expand eq. (\ref{quarticdegradation}) 
+expand eq.~(\ref{estimatorcovariance}) 
 %ZH2: you must mean eq.~(\ref{estimatorcovariance}) above, instead of eq.10 
+%AP2: yes
 in powers of $\delta\bbh{\Psi}$. The expectation value of each term in

### 2016-01-10 Paper/Figures/generate.py
renamed large Nr database

@@ -211,7 +211,7 @@ def scaling_nr(cmd_args,db_filename="variance_scaling_nb_expected.sqlite",parame
 	####################################################################################################################################
 
 	#Open the database and look for different nsim
-	with Database("data/variance_scaling_power_largeNr.sqlite") as db:
+	with Database("data/variance_scaling_largeNr.sqlite") as db:
 		v = db.query("SELECT nsim,nreal,bins,{0} FROM power_logb_all".format(parameter))
 
 	#Fit with the Dodelson scaling and overlay the fit

### 2016-01-10 code/analysis/variance_scaling_peaks_largeNr.py
variance scaling for ensemble with large Nr, high peaks

@@ -1,0 +1,72 @@
+#!/usr/bin/env python
+from __future__ import division
+import gc
+
+from lenstools.statistics.database import Database
+from lenstools.statistics.ensemble import Series,Ensemble
+from lenstools.statistics.constraints import FisherAnalysis,Emulator
+
+import numpy as np
+
+import algorithms
+
+###########################
+######Main execution#######
+###########################
+
+#Number of simulations to test
+nsim = [1]
+nreal = range(100,1000,100) + range(1000,111000,1000)
+resample = 100
+
+def main():
+
+	###########################################
+	####Constraints from the peak counts#######
+	###########################################
+
+	#Load the emulator
+	emulator = FisherAnalysis.read("../../data/emulators/fisher_peaks.pkl")
+	feature_columns = emulator[emulator.feature_names].columns
+
+	#Large and small scales
+	scales = {
+	"high" : filter(lambda s:int(s) in range(30,45),emulator[emulator.feature_names[0]].columns),
+	}
+
+	#Load in the feature Ensemble, and bootstrap the covariance using a different number of realizations
+	with Database("../../data/variance_scaling_largeNr.sqlite") as db:
+	
+		for s in scales:
+
+			#Log
+			table_name = "peaks_" + s
+			print("[+] Populating table {0}...".format(table_name))
+
+			#Approximate the emulator linearly around the fiducial model
+			fisher_scale = emulator.features({emulator.feature_names[0]:scales[s]})
+
+			#This is the reference covariance matrix
+			true_covariance_ensemble = Ensemble(np.load("../../Om0.260_Ol0.740_w-1.000_ns0.960_si0.800/512b240/GrandEnsemble/peaks_s0.npy"),columns=emulator[emulator.feature_names[0]].columns)[scales[s]]
+			true_covariance_ensemble.add_name(emulator.feature_names[0])
+			true_covariance = true_covariance_ensemble.cov()
+			diagonal_covariance = Ensemble(np.diag(true_covariance.values.diagonal()),index=true_covariance.index,columns=true_covariance.columns)
+
+			for n in nsim:
+		
+				#Load the power spectrum Ensemble from the relevant map set
+				ensemble_nsim = Ensemble(np.load("../../Om0.260_Ol0.740_w-1.000_ns0.960_si0.800/512b240/MillionMapsPower/peaks_s0.npy"))[scales[s]]
[…]

### 2016-01-10 code/analysis/algorithms.py
new fit method: "subtract"

@@ -74,6 +74,9 @@ def fit_nbins(variance_ensemble,parameter="w",extra_columns=["bins"],correct=Fal
 		fit_results["D2"] = list()
 		fit_results["res_exponent"] = list()
 
+	if kind=="subtract":
+		fit_results["decay_exponent"] = list()
+
 	for c in extra_columns:
 		fit_results[c] = list()
 
@@ -88,6 +91,17 @@ def fit_nbins(variance_ensemble,parameter="w",extra_columns=["bins"],correct=Fal
 			a,b,r_value,p_value,err = linregress(vmean_group["1/nreal"],vmean_group[parameter])
 			fit_results["D"].append(a/b)
 			fit_results["s0"].append(b)
+
+		elif kind=="subtract":
+
+			#Let the variance with the highest nreal be the intercept
+			vmean_group_sorted = vmean_group.sort_values("1/nreal")
+			s0 = vmean_group_sorted[parameter].iloc[0]
+			fit_results["s0"].append(s0)
+			a,b,r_value,p_value,err = linregress(np.log(vmean_group_sorted["nreal"].values[1:]),np.log(np.abs((vmean_group_sorted[parameter]-s0).values[1:])))
+
+			fit_results["decay_exponent"].append(a)
+			fit_results["D"].append(np.exp(b)/s0)
 
 		elif kind=="quadratic":
 

### 2016-01-10 code/analysis/variance_scaling_power_largeNr.py
added variance scaling for large Nr with power spectrum

@@ -1,0 +1,77 @@
+#!/usr/bin/env python
+from __future__ import division
+import gc
+
+from lenstools.statistics.database import Database
+from lenstools.statistics.ensemble import Series,Ensemble
+from lenstools.statistics.constraints import FisherAnalysis,Emulator
+
+import numpy as np
+
+import algorithms
+
+###########################
+######Main execution#######
+###########################
+
+#Number of simulations to test
+nsim = [1]
+nreal = range(100,1000,100) + range(1000,111000,1000)
+resample = 100
+
+def main():
+
+	###########################################
+	####Constraints from the power spectrum####
+	###########################################
+
+	#Load the emulator
+	emulator = Emulator.read("../../data/emulators/emulator_power_fine.pkl")
+	feature_columns = emulator[emulator.feature_names].columns
+
+	#Large and small scales
+	scales = {
+	"all" : list(emulator[emulator.feature_names[0]].columns),
+	}
+
+	#Fiducial cosmology
+	fiducial_parameters = Series(np.array([0.26,-1.0,0.8]),index=["Om","w","sigma8"])
+
+	#Load in the feature Ensemble, and bootstrap the covariance using a different number of realizations
+	with Database("../../data/variance_scaling_largeNr.sqlite") as db:
+	
+		for s in scales:
+
+			#Log
+			table_name = "power_logb_" + s
+			print("[+] Populating table {0}...".format(table_name))
+
+			#Approximate the emulator linearly around the fiducial model
+			fisher_scale = emulator.approximate_linear(fiducial_parameters,derivative_precision=0.01).features({emulator.feature_names[0]:scales[s]})
+
+			#This is the reference covariance matrix
+			true_covariance_ensemble = Ensemble(np.load("../../Om0.260_Ol0.740_w-1.000_ns0.960_si0.800/512b240/GrandEnsemble/power_spectrum_s0.npy"),columns=emulator[emulator.feature_names[0]].columns)[scales[s]]
+			true_covariance_ensemble.add_name(emulator.feature_names[0])
+			true_covariance = true_covariance_ensemble.cov()
+			diagonal_covariance = Ensemble(np.diag(true_covariance.values.diagonal()),index=true_covariance.index,columns=true_covariance.columns)
+
+			for n in nsim:
+		
+				#Load the power spectrum Ensemble from the relevant map set
[…]

### 2016-01-11 code/analysis/algorithms.py
fit for nbins using different maximum Nr

@@ -143,3 +143,19 @@ def fit_nbins_all(db,**kwargs):
 	#Return to user
 	return Ensemble.concat(nb_all,axis=0,ignore_index=True)
 
+#Fit a single table, but vary the threshold for the maximum Nr
+def fit_nbins_nr(variance_ensemble,nrmax,**kwargs):
+
+	nb_all = list()
+
+	#Fit all Nr tables
+	for nr in nrmax:
+		nb = fit_nbins(variance_ensemble,vfilter=lambda db:db.query("nreal<={0}".format(nr)),**kwargs)
+		nb["nreal_max"] = nr
+		nb_all.append(nb)
+
+	#Return to user
+	return Ensemble.concat(nb_all,axis=0,ignore_index=True)
+
+
+

### 2016-01-11 Paper/paper.tex
modified Figure 5

@@
-%\documentclass[useAMS, usenatbib,usegraphicx,letter]{mn2e}
-%\documentclass[11pt]{article}
 \documentclass[reprint,aps,prd,superscriptaddress,showkeys,showpacs]{revtex4-1}
@@
 single $N$--body simulation ($N_s=1$) can be repeatedly recycled to
-produce as many as $N_r=10^5$ mutually independent shear maps. As a
+produce as many as $N_r={\rm few}\times10^4$ mutually independent shear maps. As a
 result, a small number of simulations ($N_s=1$ or $2$) is sufficient
@@
   the number of realizations $N_r$ used to estimate the covariance
-  (eq.~\ref{covest}). Results for different ensembles, generated from
-  $N_s=$1 (black), 2 (blue), 5 (green), 50 (red), and 100 (purple)
-  simulations are shown. The figure shows both the measured trends
-  (solid lines) and their best fits based on eq.~(\ref{ourscaling}),
-  with $D$ treated as a free parameter.  The thick black curve
-  corresponds to an ensemble of $N_r=128000$ realizations from a
-  single simulation ($N_s=1$).  No systematic deviation from the
-  expected scaling is seen, even in the extreme last case.  }
+  (eq.~\ref{covest}). The figure shows both the measured trends
+  (solid lines) and their theoretical behavior according to eq.~(\ref{ourscaling}) with $D=N_b-N_p$.
+The asymptotic variance $\sigma^2_{w,\infty}$ has been estimated with a linear regression of $\langle\h{\sigma}^2_w\rangle$ vs $1/N_r$ with $500\leq N_r\leq 10000$ (black), with $\langle\h{\sigma}^2_w\rangle(N_r=50000)$ (red) and $\langle\h{\sigma}^2_w\rangle(N_r=100000)$ (green).
+No deviations from the expected $1/N_r$ behavior are observed until $N_r={\rm few}\times 10^4$.}
 \label{wvar_nr}
@@
 with the expected scaling (eq.~\ref{ourscaling}) up to values
-comparable to $N_r\sim 10^5$. We therefore conclude that a single
-$N$--body simulation is sufficient to construct an ensemble of
-$O(10^5)$ mutually independent convergence power spectra.
+comparable to $N_r\sim {\rm few}\times10^4$.
+We can see from the plot that around these values of $N_r$ the $\langle\hat{\sigma}^2_w\rangle - \sigma^2_{w,\infty}$ curve becomes noisy and reaches negative values.
+This is a clear indication that the $1/N_r$ behavior is broken and a plateau is reached.
+The negative values in the plot are a consequence of the noise in the estimation of the $\langle\hat{\sigma}^2_w\rangle$ plateau value.
+We therefore conclude that a single $N$--body simulation is sufficient to construct an ensemble of $O(10^4)$ mutually independent convergence power spectra, before realizations start repeating themselves.
+For $N_r\gg10^4$, the shear realizations cannot be considered all independent.
 
@@
 \item We can recycle a single $N$--body simulation to produce an
-  ensemble of $O(10^5)$ independent maps. The mean feature measured
+  ensemble of $O(10^4)$ independent maps. The mean feature measured
   from a shear ensemble, though, could be inaccurate if only one
@@
 \label{secondmoment}
-\langle\delta\h{\Psi}_I\delta\h{\Psi}_J\rangle = \frac{\nu^2\Psi_I\Psi_J + \nu^2\gamma\Psi_{[I}\Psi_{J]}}{4\gamma^2(\gamma-1)(2\gamma+1)}
+\langle\delta\h{\Psi}_I\delta\h{\Psi}_J\rangle = \frac{\nu^2\Psi_I\Psi_J + \nu^2\gamma\Psi_{\{I}\Psi_{J\}}}{4\gamma^2(\gamma-1)(2\gamma+1)}
 \end{equation}
@@
 \label{thirdmoment}
-\langle\delta\h{\Psi}_I\delta\h{\Psi}_J\delta\h{\Psi}_K\rangle = \frac{\nu^3\Psi_{[I}\Psi_J\Psi_{K]}}{8\gamma(\gamma-1)(\gamma-2)(\gamma+1)(2\gamma+1)}
+\langle\delta\h{\Psi}_I\delta\h{\Psi}_J\delta\h{\Psi}_K\rangle = \frac{\nu^3\Psi_{\{I}\Psi_J\Psi_{K\}}}{8\gamma(\gamma-1)(\gamma-2)(\gamma+1)(2\gamma+1)}
 \end{equation}
@@
 \label{fourthmoment}
-\langle\delta\h{\Psi}_I\delta\h{\Psi}_J\delta\h{\Psi}_K\delta\h{\Psi}_L\rangle = \frac{\nu^4(2\gamma^2-5\gamma+9)\Psi_{[I}\Psi_{J]}\Psi_{[K}\Psi_{L]}}{16\gamma(\gamma-1)(\gamma-2)(\gamma-3)(2\gamma-1)(\gamma+1)(2\gamma+1)(2\gamma+3)}.
+\langle\delta\h{\Psi}_I\delta\h{\Psi}_J\delta\h{\Psi}_K\delta\h{\Psi}_L\rangle = \frac{\nu^4(2\gamma^2-5\gamma+9)\Psi_{\{I}\Psi_{J\}}\Psi_{\{K}\Psi_{L\}}}{16\gamma(\gamma-1)(\gamma-2)(\gamma-3)(2\gamma-1)(\gamma+1)(2\gamma+1)(2\gamma+3)}.
 \end{equation}
@@
 %
-Here the square bracket notation is a shorthand for a symmetrization over pair of indices: for example
-\begin{equation}
-\Psi_{[I}\Psi_{J]} = \Psi_{i_1j_1}\Psi_{i_2j_2} + \Psi_{i_1j_2}\Psi_{i_2j_1}
+Here the curly bracket notation is a shorthand for a symmetrization over pair of indices: for example
+\begin{equation}
+\Psi_{\{I}\Psi_{J\}} = \Psi_{i_1j_1}\Psi_{i_2j_2} + \Psi_{i_1j_2}\Psi_{i_2j_1}
 \end{equation}
@@
   C})=N_b$, which come from symmetrization terms of type
-$\Psi_{[I}\Psi_{J]}$. Symmetrization factors of type
-$\Psi_{[I}\Psi_J\Psi_{K]}$ or $\Psi_{[I}\Psi_{J]}\Psi_{[K}\Psi_{L]}$,
+$\Psi_{\{I}\Psi_{J\}}$. Symmetrization factors of type
+$\Psi_{\{I}\Psi_J\Psi_{K\}}$ or $\Psi_{\{I}\Psi_{J\}}\Psi_{\{K}\Psi_{L\}}$,
 on the other hand, give rise to contractions of type

### 2016-01-11 Paper/Figures/generate.py

@@ -182,48 +182,43 @@ def ps_pdf(cmd_args,nell=[0,4,9,14],nsim=[1,2,5,50,100],colors=["black","blue","
 	fig.savefig("ps_pdf."+cmd_args.type)
 
 #Scaling of the variance with Nr
-def scaling_nr(cmd_args,db_filename="variance_scaling_nb_expected.sqlite",parameter="w",nsim=[1,2,5,50,100],colors=["black","blue","green","red","purple"],fontsize=22):
-
-	assert len(colors)>=len(nsim)
+def scaling_nr(cmd_args,db_filename="variance_scaling_nb_expected.sqlite",parameter="w",fontsize=22):
 
 	#Plot panel
 	fig,ax = plt.subplots()
 
-	####################################################################################################################################
-
-	#Open the database and look for different nsim
-	with Database("data/"+db_filename) as db:
-		v = db.query("SELECT nsim,nreal,bins,{0} FROM power_logb_all WHERE nsim IN ({1})".format(parameter,",".join([str(n) for n in nsim])))
-
-	#Fit with the Dodelson scaling and overlay the fit
-	vfit = algorithms.fit_nbins(v,parameter=parameter)
-	v = Ensemble.merge(v,vfit,on="nsim")
-	v[parameter+"_fit"] = v.eval("s0*D/nreal")
-	v[parameter+"_subtracted"] = v.eval("{0}-s0".format(parameter))
-	nsim_group = v.groupby("nsim")
-
-	for nc,ns in enumerate(nsim):
-		nsim_group.get_group(ns).plot(x="nreal",y=parameter+"_subtracted",linestyle="-",color=colors[nc],ax=ax,label=r"$N_s={0}$".format(ns))
-		nsim_group.get_group(ns).plot(x="nreal",y=parameter+"_fit",linestyle="--",color=colors[nc],ax=ax,legend=False)
-
-	####################################################################################################################################
-	###############Same thing for the BIG simulation set################################################################################
-	####################################################################################################################################
+	##############################################################################################################################
+	###############Consider the BIG simulation set################################################################################
[…]

### 2016-01-13 Paper/paper.tex
Paper/paper.tex

@@
 $\bb{C}$, the latter is more difficult, and typically only the mean,
-$\bb{d}(\bb{p})$, has been computed to date (refs.~\citep{coyote2,Nicaea}, but see
-an exception by ref.~\citep{SchneiderKnoxCovariance}).
-%ZH: I am missing the point here.  Why is covariance matrix ``more complicated'' ?
-%    Even to estimate a mean, one has to ``generate a series of mock realizations''.
-%    Unless you are willing to equate a single realization as the mean.   But then
-%    by the same logic, you could estimate the covariance matrix from two realizations.
-%    Please clarify what you mean...  maybe I am missing something?  Or you simply mean
-%    that published emulators usually do not emulate the cov.matrix (even though they could)?
-%    Note that there is a paper by Schneider and Knox, in which they do an interpolation of the
-%    power spectrum covariance matrix.
-%AP: The intended meaning is the latter: published emulators only predict the means.
-It is also true that getting the covariance accurate is more difficult than getting the means accurate.
-I rephrased the sentence.
-%ZH2: OK, I rephrased it a bit above to be clearer.  I believe only Schneider et al. did ``C''.
-%AP2: OK
-Estimating $\bb{C}$ from simulations involves generating a series of
-mock realizations $\bbh{d}_r$ with $r=1...N_r$ and computing the
-sample covariance $\bbh{C}$,
+$\bb{d}(\bb{p})$, has been computed to date
+(refs.~\citep{coyote2,Nicaea}, but see an exception by
+ref.~\citep{SchneiderKnoxCovariance}).  Estimating $\bb{C}$ from
+simulations involves generating a series of mock realizations
+$\bbh{d}_r$ with $r=1...N_r$ and computing the sample covariance
+$\bbh{C}$,
 
@@
   simulations, respectively.}
-%ZH: So each of these have N_r=1000, yes?  You should state this here. And also,
-%    Add the ensemble with N_s=1, N_r=10^5 to this table.
-%    Also: point the reader to this table in the text, up front, when the 
-%    ensembles are first discussed.
-%AP: done
-%ZH2: The first row was a bit confusing, so I separated it into two rows. Also added words to the caption
-%    (also, the N_r=10^5 one is the 17th ensemble, in addition to the 16 you listed here before, no? So 16 should have been 17?)
-%AP2: OK
 \label{simtable}
@@
 as $D/N_r$, where $D=N_b-N_p$, $N_p-N_b$, and $1+N_p$ for cases 1, 2,
-and 3, respectively.
-%ZH: It was not clear to me what the main point of the text below was. I paraphrased it slightly. OK?
-%This means that, when parameter errors are
-%estimated purely from simulations, and the same simulation set is used
-%to estimate both $\bbh{C},\bbh{\Psi}$, these errors tend to decrease
-%with $N_b$ (case 2), or at best remain constant (case 3), while the
-%distribution of $\bbh{p}$ has still a variance that increases with
-%$N_b$. This typically leads to underestimates in parameter errors. 
-%AP: Not exactly: my point was that the distribution of \bbh{p} has a true variance that increases with Nb, but the estimate of this variance (which we quote as the errorbar) does not increase with Nb.
-Hence we get the wrong parameter fit (i.e.
-which excludes the true value at high significance level)
-%ZH2: OK.  I think by `` the parameter estimate $\bbh{p}$ has a variance that grows linearly with $N_b$,'' you mean equation 10
-%   (i.e.  technically it is [variance-1] grows linearly with N_b.   I rephrased below to say ``whose noise'' grows linearly and
-% cite eq.10.    OK?
-%AP2: OK
-Note that in the last case, which is most relevant when fitting actual
-data, the estimated degradation turns out to be too optimistic: the
-parameter estimate $\bbh{p}$ has a variance whose noise grows linearly
-with $N_b$ (eq.~\ref{quarticdegradation}), whereas the degradation
-estimated via eq. (\ref{mockscalingcorrected}) is constant with
-$N_b$. This can lead to underestimation of error bars, which can be
-mistakenly interpreted as a parameter bias. We test scaling
-relations of the form
+and 3, respectively.  Note that in the last case, which is most
+relevant when fitting actual data, the estimated degradation turns out
+to be too optimistic: the parameter estimate $\bbh{p}$ has a variance
+whose noise grows linearly with $N_b$ (eq.~\ref{quarticdegradation}),
+whereas the degradation estimated via eq. (\ref{mockscalingcorrected})
+is constant with $N_b$. This can lead to underestimation of error
+bars, which can be mistakenly interpreted as a parameter bias. We test
+scaling relations of the form
 %
@@
 %
-againts our simulations, in the limits of both high and low $N_r$.
-%ZH: It is still a little unclear here what is being tested.  Is it the Gaussianity assumption? I added that.
-%    But perhaps you had some other issue in mind.
-%AP: The noise in $\bbh{C}$ and $\bbh{\Psi}$ is not Gaussian: if the data vector from which $\bbh{C}$ and $\bbh{\Psi}$ are estimated in Gaussian, then these matrices are distibuted according to, respectively, the Wishart and inverse Wishart distributions.
-We are testing that the degradation effectively decreases as 1/Nr at leading order.
-%ZH2: I am still confused.  What is it that could go wrong?   I.e. do you have something in mind that could cause a departure from this 1/N_r
-%     scaling?    That is what we are testing, then, but I am not sure what it is.   Are we testing whether the simulations could have a bug?  
-%     Or maybe you simply are testing the validity of truncating the expansion at second order in DeltaPsi ?   
-%     Or maybe what you have in mond is the possible importance of high-order terms in the expansion (beyond the quartic terms, 
-%     and beyond 1/N_r^2) could cause a deviation from 1/N_r that is different from the 1/N_r^2 term in eq.10 ?  In other words,
-%     then we're testing for the importance of the 1/N_r^3 and higher terms numerically...  is that your point?
-%
-%AP2: Technically the 1/Nr scaling has been obtained using the inverse Wishart distribution; if the data is non Gaussian, the covariance is not Wishart, but maybe one can say that for an arbitrary, not too crazy, distribution the leading term is still 1/Nr and the coefficient is not too different from Nb-Np...
-This is indeed what we find: the error degradation is basically the same should we use power spectra or peak counts which have different PDFs...
-I removed the mention to the Gaussianity, which is not what we test.
-What we test is eq.
-10 in the low Nr limit and the (possible) deviations from 1/Nr when Nr is very large (due to the maps being pseudo independent).
-We indicate the diagonal elements of $\h{\Sigma}_{\bb{p}}$ as
+against our simulations, in the limits of both high and low $N_r$.  We
+indicate the diagonal elements of $\h{\Sigma}_{\bb{p}}$ as
 $\h{\sigma}^2_p=\mathrm{diag}(\h{\Sigma}_{\bb{p}})$ and we indicate by
@@
   the number of realizations $N_r$ used to estimate the covariance
-  (eq.~\ref{covest}). The figure shows both the measured trends
-  (solid lines) and their theoretical behavior according to eq.~(\ref{ourscaling}) with $D=N_b-N_p$.
-The asymptotic variance $\sigma^2_{w,\infty}$ has been estimated with a linear regression of $\langle\h{\sigma}^2_w\rangle$ vs $1/N_r$ with $500\leq N_r\leq 10000$ (black), with $\langle\h{\sigma}^2_w\rangle(N_r=50000)$ (red) and $\langle\h{\sigma}^2_w\rangle(N_r=100000)$ (green).
-No deviations from the expected $1/N_r$ behavior are observed until $N_r={\rm few}\times 10^4$.}
+  (eq.~\ref{covest}). The figure shows both the trend measured in the
+  simulations (solid lines) and their scaling expected from
+  Eq.~(\ref{ourscaling}) with $D=N_b-N_p$ (dashed line). The
+  asymptotic variance $\sigma^2_{w,\infty}$ has been estimated with a
+  linear regression of $\langle\h{\sigma}^2_w\rangle$ vs $1/N_r$ using
+  the range $500\leq N_r\leq 10000$ (black), or else simply assumed to
+  be equal to the value $\langle\h{\sigma}^2_w\rangle(N_r=50000)$
+  (red) or $\langle\h{\sigma}^2_w\rangle(N_r=100000)$ (green). No
+  deviations from the expected $1/N_r$ behavior are observed up to
+  $N_r={\rm few}\times 10^4$.}
 \label{wvar_nr}
@@
 covariance, in the limit of large $N_r$. We find excellent agreement
-with the expected scaling (eq.~\ref{ourscaling}) up to values
-comparable to $N_r\sim {\rm few}\times10^4$.
-We can see from the plot that around these values of $N_r$ the $\langle\hat{\sigma}^2_w\rangle - \sigma^2_{w,\infty}$ curve becomes noisy and reaches negative values.
-This is a clear indication that the $1/N_r$ behavior is broken and a plateau is reached.
-The negative values in the plot are a consequence of the noise in the estimation of the $\langle\hat{\sigma}^2_w\rangle$ plateau value.
-We therefore conclude that a single $N$--body simulation is sufficient to construct an ensemble of $O(10^4)$ mutually independent convergence power spectra, before realizations start repeating themselves.
-For $N_r\gg10^4$, the shear realizations cannot be considered all independent.
+with the expected scaling (eq.~\ref{ourscaling}) up to $N_r\sim {\rm
+  few}\times10^4$. As the figure shows, around these values of $N_r$
+the $\langle\hat{\sigma}^2_w\rangle - \sigma^2_{w,\infty}$ curve
+becomes noisy and reaches negative values. This is a clear indication
+that the $1/N_r$ behavior is broken and a plateau in
+$\langle\hat{\sigma}^2_w\rangle$ is reached. The negative values in
+the plot are a consequence of the noise in the estimation of this
+plateau value (or equivalently in the estimated value of
+$\sigma^2_{w,\infty}$).  We therefore conclude that a single $N$--body
+simulation is sufficient to construct an ensemble of up to a
+few$\times 10^4$ mutually independent convergence power spectra. For
+$N_r\gg10^4$, the shear realizations can no longer be considered
+independent.
 
@@
 using the same simulation set for $\bb{C}$ and $\bbh{\Psi}$).
-
-%ZH: reworded above.  OK?  Also, I am not sure if this point is new.
-%    Didn't Hartlap (and others) make this point? If so, we should cite them.
-%    Also, it would make the point more relevant if we could cite some 
-%    papers (including our own) which neglected this correction in the past
-%    and therefore under-forecasted the errors.
-%AP: yes, Hartlap et al.
-reached a similar conclusion.
-I think we are saying something more though: even if the bias in the Psi estimator is corrected, if the same simulation set for Psi and C is used, parameter errors are still underestimated because of the explanation we give in section II-B.
-I don't think this point appears in Hartlap et al.
-%ZH2: OK I added this clarification above.  
-%AP2: OK: Hartlap focuses on the Psi distribution, translating it into a parameter distribution using a naive Fisher analysis; what he does is in fact use the same simulation set for Psi and C, but this kind of discussion is absent from his paper.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%% APPENDIX %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%ZH2: I went through the appendix, too, now, and made minor cosmetic changes.
-%AP2: OK     
 \section*{Appendix A: cubic and quartic covariance fluctuations}
@@
 necessary. Writing $\bbh{\Psi}=\bb{\Psi}+\delta\bbh{\Psi}$, we can
-expand eq.~(\ref{estimatorcovariance}) 
-%ZH2: you must mean eq.~(\ref{estimatorcovariance}) above, instead of eq.10 
-%AP2: yes
-in powers of $\delta\bbh{\Psi}$. The expectation value of each term in
-this expansion can be calculated in terms of moments of the inverse
-Wishart distribution. Ref.~\citep{MasumotoWishart} provides a general
+expand eq.~(\ref{estimatorcovariance}) in powers of
+$\delta\bbh{\Psi}$. The expectation value of each term in this
+expansion can be calculated in terms of moments of the inverse Wishart
+distribution. Ref.~\citep{MasumotoWishart} provides a general
 framework to compute these moments, and give exact expressions for

### 2016-01-16 code/analysis/variance_scaling_peaks_largeNr.py
add two tables to the largeNr database

@@ -31,7 +31,7 @@ def main():
 
 	#Large and small scales
 	scales = {
-	"high" : filter(lambda s:int(s) in range(30,45),emulator[emulator.feature_names[0]].columns),
+	"highest_kappa" : filter(lambda s:int(s) in [45,46,47,48],emulator[emulator.feature_names[0]].columns),
 	}
 
 	#Load in the feature Ensemble, and bootstrap the covariance using a different number of realizations

### 2016-01-16 code/analysis/variance_scaling_power_largeNr.py

@@ -31,7 +31,7 @@ def main():
 
 	#Large and small scales
 	scales = {
-	"all" : list(emulator[emulator.feature_names[0]].columns),
+	"lowest_ell" : filter(lambda s:int(s.strip("l")) in range(4),emulator[emulator.feature_names[0]].columns)
 	}
 
 	#Fiducial cosmology

### 2016-01-16 Paper/paper.tex
removed comments
modified Figure 5 with new tests

@@
 }
-% \usepackage{graphicx}
-% \usepackage{epstopdf}
-% \usepackage{natbib}
 
@@
 \citep{DodelsonSchneider13} has shown that Gaussian noise in the
-feature covariance lead, at quadratic order, to an $O(1/N_r)$
+feature vectors (from which the covariance is estimated) lead, at quadratic order, to an $O(1/N_r)$
 degradation of the parameter confidence intervals. Using a variety of
@@
 larger than $N_b$. We study the large $N_r$ limit, and find that a
-single $N$--body simulation ($N_s=1$) can be repeatedly recycled to
-produce as many as $N_r={\rm few}\times10^4$ mutually independent shear maps. As a
-result, a small number of simulations ($N_s=1$ or $2$) is sufficient
-to forecast parameter confidence intervals at percent
-accuracy.
+single, 240Mpc$/h$ sized, $N$--body simulation ($N_s=1$) can be repeatedly recycled to
+produce as many as $N_r={\rm few}\times10^4$ shear maps whose power spectra can be treated as statistically independent.
+As a result, a small number of simulations ($N_s=1$ or $2$) is sufficient to forecast parameter confidence intervals at percent accuracy.
 
@@
 $N_r=10^5$ random realizations, extracted from up to $N_s=200$
-independent ray-tracing N-body simulations. We focus in particular on
+independent ray-tracing $N$--body simulations. We focus in particular on
 the parameter $w$, and on two different statistics: the (convergence)
@@
 deflections of $n_{\rm ray}^2=2048^2$ light rays arranged on a square grid
-of total size $\theta_{\rm box}$, from $z=0$ to $z_s$. Our
-implementation of this algorithm is part of the \texttt{LensTools}
+of total size $\theta_{\rm box}$, from $z=0$ to $z_s$. This corresponds to a pixel angular resolution of $0.1^\prime$. 
+Our implementation of this algorithm is part of the \texttt{LensTools}
 computing package we have been developing \citep{LensTools}, and have
@@
 \caption{Summary of the shear ensembles used in this work. $N_s$ and
-  $N_r$ refer to the number of independent N-body simulations, and the
+  $N_r$ refer to the number of independent $N$--body simulations, and the
   number of pseudo-independent realizations created from these
@@
   from on $N_s=$1 (black), 2 (blue), 5 (green), 50 (red), and 100
-  (purple) independent N-body simulations. Each curve is based on
+  (purple) independent $N$--body simulations. Each curve is based on
   $N_r=1024$ realizations.  The dashed black curves correspond to
@@
   Eq.~(\ref{ourscaling}) with $D=N_b-N_p$ (dashed line). The
-  asymptotic variance $\sigma^2_{w,\infty}$ has been estimated with a
-  linear regression of $\langle\h{\sigma}^2_w\rangle$ vs $1/N_r$ using
-  the range $500\leq N_r\leq 10000$ (black), or else simply assumed to
-  be equal to the value $\langle\h{\sigma}^2_w\rangle(N_r=50000)$
-  (red) or $\langle\h{\sigma}^2_w\rangle(N_r=100000)$ (green). No
-  deviations from the expected $1/N_r$ behavior are observed up to
-  $N_r={\rm few}\times 10^4$.}
+  asymptotic variance $\sigma^2_{w,\infty}$ has been estimated to be the value $\langle\h{\sigma}^2_w\rangle(N_r=10^5)$.
+Different features are considered: power spectra with logarithmically spaced $\ell\in[100,6000]$ (black), $\ell\in[100,250]$ (red) and peak counts of height $\kappa_0\in[0.44,0.48]$ (blue).
+No deviations from the expected $1/N_r$ behavior are observed up to $N_r\approx{\rm few}\times10^4$, except for the large scale power spectrum, in which case the deviations occur much earlier ($N_r\approx 10^3$).}
 \label{wvar_nr}
@@
 derived from the features used in this work (see Table
-\ref{featuretable} for a comprehensive list). Figure \ref{wvar_nr}
-shows the $N_r$ trends of the $w$ constraint obtained with the power
-spectrum logarithmically binned with $\ell\in[100,6000], N_b=15$.
+\ref{featuretable} for a comprehensive list). 
+Figure~\ref{curvingnb} shows the
+behavior in the limit of a large number $N_r\gg500$ of realizations,
+and compares it with the scaling of the form in
+equation~(\ref{ourscaling}).
+Figure \ref{wvar_nr} shows the large $N_r$ trends of the $w$ constraint.
 Figure~\ref{curvingnb} illustrates the behavior at relatively low
@@
 from the simulations with the analytic expectations from
-equation~(\ref{quarticdegradation}).  Figure~\ref{curvingnb} shows the
-behavior in the limit of a large number $N_r\gg500$ of realizations,
-and compares it with the scaling of the form in
-equation~(\ref{ourscaling}). Finally, in Figure~\ref{wvar_ns}, we show
+equation~(\ref{quarticdegradation}). Finally, in Figure~\ref{wvar_ns}, we show
 how the $w$ confidence limit changes with $N_s$.
@@
 reference).  Our results are in fact in excellent quantitative
-agreement with \citep{Sato12}, which used $N_s=400$ independent N-body
+agreement with \citep{Sato12}, which used $N_s=400$ independent $N$--body
 simulations.  This result is highly encouraging, suggesting that
@@
 covariance, in the limit of large $N_r$. We find excellent agreement
-with the expected scaling (eq.~\ref{ourscaling}) up to $N_r\sim {\rm
-  few}\times10^4$. As the figure shows, around these values of $N_r$
-the $\langle\hat{\sigma}^2_w\rangle - \sigma^2_{w,\infty}$ curve
-becomes noisy and reaches negative values. This is a clear indication
-that the $1/N_r$ behavior is broken and a plateau in
+with the expected scaling (eq.~\ref{ourscaling}) up to $N_r\sim {\rm few}\times10^4$ when using the $\kappa$ power spectrum in the multipole range $\ell\in[100,6000]$.
+As the figure shows, around these values of $N_r$ the $\langle\hat{\sigma}^2_w\rangle - \sigma^2_{w,\infty}$ curve
+becomes noisy and reaches negative values. This is a clear indication that the $1/N_r$ behavior is broken and a plateau in
 $\langle\hat{\sigma}^2_w\rangle$ is reached. The negative values in
@@
 independent.
+We should emphasize that the validity of this statement is conditional to the size of the simulation box (which in our case has been chosen to be 240Mpc$/h$) and the range of multipoles $\ell$ used to constrain the parameters.
+Figure \ref{wvar_nr} shows indeed that, when we try infer $w$ only from large scale modes, $\ell\lesssim250$, the plateau is reached at least an order of magnitude earlier in the number of realizations.
+In other words, the number of independent power spectra gets lower and lower as we increase the spatial scales of interest.
+This is due to the fact that, because of the finite box size, the number of independent lens plane shifts (as described in \S~\ref{shearsim}) decreases as the mode size approaches the size of the box.
 
@@
   than the feature vector size $N_b$.
-\item We can recycle a single $N$--body simulation to produce an
-  ensemble of $O(10^4)$ independent maps. The mean feature measured
-  from a shear ensemble, though, could be inaccurate if only one
-  $N$--body simulation is used.
+\item We can recycle a single 240Mpc$/h$ $N$--body simulation to produce an
+  ensemble of $O(10^4)$ shear maps whose power spectra are statistically independent in the range $\ell\in[100,6000]$. The mean feature measured
+  from a shear ensemble, though, could be inaccurate if only one $N$--body simulation is used.
 \item As few as one or two independent $N$--body simulations are
-  sufficient to forecast $w$ errorbars to 1\% accuracy, provided that
+  sufficient to forecast $w$ error bars to 1\% accuracy, provided that
   a sufficiently large number $N_r$ of realizations are used to
@@
 Minkowski Functionals, and higher-order $\kappa$ correlators). While
-our results are highly encouraging, and suggest that a single N-body
-simulation can be recycled repeatedly, to produce as many as $10^5$
+our results are highly encouraging, and suggest that a single $N$--body
+simulation can be recycled repeatedly, to produce as many as $10^4$
 independent shear power spectra or peak count histograms. In order to
 scale our results to large future surveys, such as LSST, it will be
-necessary to determine if our findinds hold when challenged by larger
+necessary to determine if our findings hold when challenged by larger
 and higher-resolution $N$--body simulations \citep{Qcontinuum}.

### 2016-01-16 Paper/Figures/generate.py

@@ -61,6 +61,7 @@ labels = {
 "power_logb_large" : r"$\ell\in[100,800],N_b=8(\mathrm{log})$",
 "power_logb_small" : r"$\ell\in[1000,6000],N_b=7(\mathrm{log})$",
 "power_logb_all" : r"$\ell\in[100,6000],N_b=15(\mathrm{log})$",
+"power_logb_lowest_ell" : r"$\ell\in[100,250],N_b=4(\mathrm{log})$",
 "power_large" : r"$\ell\in[100,2000],N_b=15(\mathrm{lin})$",
 "power_small" : r"$\ell\in[2500,4500],N_b=15(\mathrm{lin})$",
 "power_large+small" : r"$\ell\in[100,4500],N_b=30(\mathrm{lin})$",
@@ -71,6 +72,7 @@ labels = {
 "peaks_low+intermediate" : r"$\kappa_0\in[-0.06,0.27],N_b=30$",
 "peaks_intermediate+high" : r"$\kappa_0\in[0.1,0.45],N_b=30$",
 "peaks_all" : r"$\kappa_0\in[-0.06,0.45],N_b=45$",
+"peaks_highest_kappa" : r"$\kappa_0\in[0.44,0.48],N_b=4$",
 } 
 
 #Plot order
@@ -182,7 +184,7 @@ def ps_pdf(cmd_args,nell=[0,4,9,14],nsim=[1,2,5,50,100],colors=["black","blue","
 	fig.savefig("ps_pdf."+cmd_args.type)
 
 #Scaling of the variance with Nr
-def scaling_nr(cmd_args,db_filename="variance_scaling_nb_expected.sqlite",parameter="w",fontsize=22):
+def scaling_nr(cmd_args,db_filename="variance_scaling_nb_expected.sqlite",features=["power_logb_all","power_logb_lowest_ell","peaks_highest_kappa"],colors=["black","red","blue"],nrmax=100000,parameter="w",fontsize=22):
 
 	#Plot panel
 	fig,ax = plt.subplots()
@@ -193,31 +195,23 @@ def scaling_nr(cmd_args,db_filename="variance_scaling_nb_expected.sqlite",parame
 
 	#Open the database and look for different nsim
 	with Database("data/variance_scaling_largeNr.sqlite") as db:
-		v = db.query("SELECT nsim,nreal,bins,{0} FROM power_logb_all".format(parameter))
 
-	#Number of bins
-	nb = v["bins"].iloc[0]
+		for n,feature in enumerate(features):
[…]

### 2016-01-18 code/measure/measure_from_maps.py
measure peaks with broader threshold choice

@@ -35,6 +35,28 @@ def convergence_power(fname,map_set,l_edges,smoothing_scale=0.0*u.arcmin):
 	except IOError:
 		return None
 
+##############################################################################
+##############Peak counts#####################################################
+##############################################################################
+
+def convergence_peaks(fname,map_set,kappa_edges,smoothing_scale=0.0*u.arcmin):
+	
+	try:
+		conv = ConvergenceMap.load(map_set.path(fname))
+
+		if "0001r" in fname:
+			np.save(os.path.join(map_set.home_subdir,"th_peaks_nb{0}.npy".format(len(kappa_edges)-1)),0.5*(kappa_edges[1:]+kappa_edges[:-1]))
+	
+		if smoothing_scale>0:
+			conv = conv.smooth(smoothing_scale,kind="gaussianFFT")
+
+		k,peaks = conv.peakCount(kappa_edges)
+		return peaks
+
+	except IOError:
+		return None
+
+
 #################################################################################
 ##############Main execution#####################################################
 #################################################################################
@@ -61,8 +83,8 @@ if __name__=="__main__":
 	redshift = 2.0
 
 	#What to measure
-	#l_edges = np.logspace(2.0,np.log10(6.0e3),16)
 	l_edges = np.arange(100,6000,150)
+	kappa_edges = np.linspace(-.08,.8,101)
 
 	#How many realizations
 	num_realizations = 1024
@@ -91,13 +113,14 @@ if __name__=="__main__":
 
 		#Measure the descriptors spreading calculations on a MPIPool
 		for c in range(chunks):
-			ensemble_all.append(Ensemble.compute([ "WLconv_z{0:.2f}_{1:04d}r.fits".format(redshift,r+1) for r in range(realizations_per_chunk*c,realizations_per_chunk*(c+1)) ],callback_loader=convergence_power,pool=pool,map_set=map_set,l_edges=l_edges))
+			#ensemble_all.append(Ensemble.compute([ "WLconv_z{0:.2f}_{1:04d}r.fits".format(redshift,r+1) for r in range(realizations_per_chunk*c,realizations_per_chunk*(c+1)) ],callback_loader=convergence_power,pool=pool,map_set=map_set,l_edges=l_edges))
[…]

### 2016-01-18 code/measure/measure_from_maps.py
lenstools.pipeline --> lenstools.pipeline.simulation

@@ -6,7 +6,7 @@ import logging
 
 from lenstools.image.convergence import ConvergenceMap
 from lenstools.statistics.ensemble import Ensemble
-from lenstools.pipeline import SimulationBatch
+from lenstools.pipeline.simulation import SimulationBatch
 
 import numpy as np
 import astropy.units as u

### 2016-01-18 code/measure/peaks_direct.py
measure peaks with 1 arcmin smoothing

@@ -269,12 +269,16 @@ def singleRedshift(pool,batch,settings,id,**kwargs):
 			#Compute the convergence
 			convMap = ConvergenceMap(data=1.0-0.5*(jacobian[0]+jacobian[3]),angle=map_angle)
 
+			#Smooth if necessary
+			if settings.smoothing_scale>0.0:
+				convMap = convMap.smooth(settings.smoothing_scale*u.arcmin,kind="gaussianFFT")
+
 			#Count the peaks in the map
 			kappa,num_peaks = convMap.peakCount(settings.kappa_edges)
 
 			#Save the multipoles maybe
 			if r==0:
-				savename = os.path.join(map_batch.home_subdir,"kappa_peaks.npy")
+				savename = os.path.join(map_batch.home_subdir,"kappa_peaks_s{0}_nb{1}.npy".format(int(settings.smoothing_scale),len(kappa)))
 				logdriver.info("Saving peak heights to {0}".format(savename))
 				np.save(savename,kappa)
 
@@ -296,9 +300,9 @@ def singleRedshift(pool,batch,settings,id,**kwargs):
 
 	#Save the local processor Ensemble to disk
 	if pool is not None:
-		savename = os.path.join(map_batch.home_subdir,"{0}_rank{1:03d}.npy".format(settings.ensemble_root,pool.rank))
+		savename = os.path.join(map_batch.home_subdir,"{0}_s{1}_nb{2}_rank{3:03d}.npy".format(settings.ensemble_root,int(settings.smoothing_scale),peaks_ensemble.shape[1],pool.rank))
 	else:
-		savename = os.path.join(map_batch.home_subdir,"{0}.npy".format(settings.ensemble_root))
+		savename = os.path.join(map_batch.home_subdir,"{0}_s{1}_nb{2}.npy".format(settings.ensemble_root,int(settings.smoothing_scale),peaks_ensemble.shape[1]))
 
 	logdriver.info("Saving peak count Ensemble to {0}".format(savename))
 	np.save(savename,peaks_ensemble)
@@ -338,6 +342,7 @@ class PeaksSettings(MapSettings):
 
 	def _read_peak_heights(self,options,section):
 		
+		self.smoothing_scale = options.getfloat(section,"smoothing_scale")
 		self.kappa_min = options.getfloat(section,"kappa_min")
 		self.kappa_max = options.getfloat(section,"kappa_max")
 		self.num_bins = options.getint(section,"num_bins")

### 2016-01-18 code/measure/measure_from_maps.py
measure peaks with 1 arcmin smoothing

@@ -39,7 +39,7 @@ def convergence_power(fname,map_set,l_edges,smoothing_scale=0.0*u.arcmin):
 ##############Peak counts#####################################################
 ##############################################################################
 
-def convergence_peaks(fname,map_set,kappa_edges,smoothing_scale=0.0*u.arcmin):
+def convergence_peaks(fname,map_set,kappa_edges,smoothing_scale=1.0*u.arcmin):
 	
 	try:
 		conv = ConvergenceMap.load(map_set.path(fname))
@@ -84,7 +84,7 @@ if __name__=="__main__":
 
 	#What to measure
 	l_edges = np.arange(100,6000,150)
-	kappa_edges = np.linspace(-.08,.8,101)
+	kappa_edges = np.linspace(-.07,.6,101)
 
 	#How many realizations
 	num_realizations = 1024
@@ -120,7 +120,7 @@ if __name__=="__main__":
 		ensemble_all = Ensemble.concat(ensemble_all,axis=0,ignore_index=True)
 
 		#Save to disk
-		savename = os.path.join(map_set.home_subdir,"peaks_s{0}_nb{1}.npy".format(0,ensemble_all.shape[1]))
+		savename = os.path.join(map_set.home_subdir,"peaks_s{0}_nb{1}.npy".format(1,ensemble_all.shape[1]))
 		logging.info("Writing {0}".format(savename))
 		np.save(savename,ensemble_all.values)
 

### 2016-01-19 code/measure/peaks_direct.py
enable garbage collection

@@ -5,6 +5,7 @@ import logging
 import time
 import cPickle
 import resource
+import gc
 
 from distutils import config
 
@@ -35,6 +36,9 @@ def peaksExecution():
 ################################################
 
 def singleRedshift(pool,batch,settings,id,**kwargs):
+
+	#Enable garbage collection
+	gc.enable()
 
 	#Safety check
 	assert isinstance(pool,MPIWhirlPool) or (pool is None)
@@ -182,6 +186,9 @@ def singleRedshift(pool,batch,settings,id,**kwargs):
 
 	#We need one of these for cycles for each map random realization
 	for rloc,r in enumerate(range(first_map_realization,last_map_realization)):
+
+		#Collect garbage
+		gc.collect()
 
 		#Instantiate the RayTracer
 		tracer = RayTracer()

### 2016-01-19 code/measure/peaks_direct.py
log progress of raytracing to user

@@ -10,7 +10,7 @@ import gc
 from distutils import config
 
 from lenstools.utils import MPIWhirlPool
-from lenstools.simulations.logs import logdriver
+from lenstools.simulations.logs import logdriver,logstderr
 
 from lenstools import ConvergenceMap
 
@@ -300,6 +300,7 @@ def singleRedshift(pool,batch,settings,id,**kwargs):
 		now = time.time()
 		logdriver.info("Weak lensing calculations for realization {0} completed in {1:.3f}s".format(r+1,now-last_timestamp))
 		logdriver.info("Memory usage: {0:.3f} GB".format(resource.getrusage(resource.RUSAGE_SELF).ru_maxrss/(1024**3)))
+		logstderr.info("Progress: {0:.2f}%".format((rloc+1.)/realizations_per_task))
 	
 	#Safety sync barrier
 	if pool is not None:

### 2016-01-19 code/measure/peaks_direct.py
reduce error logs

@@ -300,7 +300,9 @@ def singleRedshift(pool,batch,settings,id,**kwargs):
 		now = time.time()
 		logdriver.info("Weak lensing calculations for realization {0} completed in {1:.3f}s".format(r+1,now-last_timestamp))
 		logdriver.info("Memory usage: {0:.3f} GB".format(resource.getrusage(resource.RUSAGE_SELF).ru_maxrss/(1024**3)))
-		logstderr.info("Progress: {0:.2f}%".format((rloc+1.)/realizations_per_task))
+
+		if (pool is None) or (pool.is_master()):
+			logstderr.info("Progress: {0:.2f}%".format((rloc+1.)/realizations_per_task))
 	
 	#Safety sync barrier
 	if pool is not None:

### 2016-01-19 code/measure/measure_from_maps.py
modify kappa thresholds for correct smoothing

@@ -84,7 +84,7 @@ if __name__=="__main__":
 
 	#What to measure
 	l_edges = np.arange(100,6000,150)
-	kappa_edges = np.linspace(-.07,.6,101)
+	kappa_edges = np.linspace(-.05,.2,101)
 
 	#How many realizations
 	num_realizations = 1024

### 2016-01-20 code/measure/peaks_direct.py
track total memory usage in peaks_direct

@@ -1,11 +1,10 @@
 from __future__ import division,with_statement
 
-import sys,os
+import sys,os,platform
 import logging
 import time
 import cPickle
-import resource
-import gc
+import gc,resource
 
 from distutils import config
 
@@ -23,6 +22,16 @@ from lenstools.pipeline.settings import MapSettings
 import numpy as np
 import pandas as pd
 import astropy.units as u
+
+
+#Multiplicative factor to convert resource output into GB
+ostype = platform.system()
+if ostype in ["Darwin","darwin"]:
+	to_gbyte = 1024.**3
+elif ostype in ["Linux","linux"]:
+	to_gbyte = 1024.**2
+else:
+	to_gbyte = np.nan
 
 
 #Orchestra director of the execution
@@ -316,10 +325,9 @@ def singleRedshift(pool,batch,settings,id,**kwargs):
 
 			now = time.time()
 			logdriver.info("Weak lensing calculations for realization {0} completed in {1:.3f}s".format(r+1,now-last_timestamp))
-			logdriver.info("Memory usage: {0:.3f} GB".format(resource.getrusage(resource.RUSAGE_SELF).ru_maxrss/(1024**3)))
 
 			if (pool is None) or (pool.is_master()):
-				logstderr.info("Progress: {0:.2f}%".format(100*(rloc+1.)/realizations_per_task))
+				logstderr.info("Progress: {0:.2f}%, peak memory usage (per task): {1:.3f}GB".format(100*(rloc+1.)/realizations_per_task,resource.getrusage(resource.RUSAGE_SELF).ru_maxrss/to_gbyte))
 	
 	
 	#######################################################################################################################################

### 2016-01-20 code/measure/peaks_direct.py
Log initial memory usage

@@ -208,6 +208,10 @@ def singleRedshift(pool,batch,settings,id,**kwargs):
 	#Open the connection to the database
 	with Database(dbname) as db:
 
+		#Log initial memory load
+		if (pool is None) or (pool.is_master()):
+			logstderr.info("Initial memory usage (per task): {0:.3f}GB".format(resource.getrusage(resource.RUSAGE_SELF).ru_maxrss/to_gbyte))
+
 		#We need one of these for cycles for each map random realization
 		for rloc,r in enumerate(range(first_map_realization,last_map_realization)):
 

### 2016-01-21 code/measure/peaks_direct.py
use peakMemory to log memory usage

@@ -1,15 +1,15 @@
 from __future__ import division,with_statement
 
-import sys,os,platform
+import sys,os
 import logging
 import time
 import cPickle
-import gc,resource
+import gc
 
 from distutils import config
 
 from lenstools.utils import MPIWhirlPool
-from lenstools.simulations.logs import logdriver,logstderr
+from lenstools.simulations.logs import logdriver,logstderr,peakMemory
 
 from lenstools import ConvergenceMap
 
@@ -22,17 +22,6 @@ from lenstools.pipeline.settings import MapSettings
 import numpy as np
 import pandas as pd
 import astropy.units as u
-
-
-#Multiplicative factor to convert resource output into GB
-ostype = platform.system()
-if ostype in ["Darwin","darwin"]:
-	to_gbyte = 1024.**3
-elif ostype in ["Linux","linux"]:
-	to_gbyte = 1024.**2
-else:
-	to_gbyte = np.nan
-
 
 #Orchestra director of the execution
 def peaksExecution():
@@ -210,7 +199,7 @@ def singleRedshift(pool,batch,settings,id,**kwargs):
 
 		#Log initial memory load
 		if (pool is None) or (pool.is_master()):
-			logstderr.info("Initial memory usage (per task): {0:.3f}GB".format(resource.getrusage(resource.RUSAGE_SELF).ru_maxrss/to_gbyte))
+			logstderr.info("Initial memory usage (per task): {0:.3f}".format(peakMemory()))
 
 		#We need one of these for cycles for each map random realization
 		for rloc,r in enumerate(range(first_map_realization,last_map_realization)):
@@ -331,7 +320,7 @@ def singleRedshift(pool,batch,settings,id,**kwargs):
 			logdriver.info("Weak lensing calculations for realization {0} completed in {1:.3f}s".format(r+1,now-last_timestamp))
 
 			if (pool is None) or (pool.is_master()):
-				logstderr.info("Progress: {0:.2f}%, peak memory usage (per task): {1:.3f}GB".format(100*(rloc+1.)/realizations_per_task,resource.getrusage(resource.RUSAGE_SELF).ru_maxrss/to_gbyte))
+				logstderr.info("Progress: {0:.2f}%, peak memory usage (per task): {1:.3f}GB".format(100*(rloc+1.)/realizations_per_task,peakMemory()))
 	
 	
 	#######################################################################################################################################

### 2016-01-21 code/measure/peaks_direct.py
Update peaks_direct.py

@@ -320,7 +320,7 @@ def singleRedshift(pool,batch,settings,id,**kwargs):
 			logdriver.info("Weak lensing calculations for realization {0} completed in {1:.3f}s".format(r+1,now-last_timestamp))
 
 			if (pool is None) or (pool.is_master()):
-				logstderr.info("Progress: {0:.2f}%, peak memory usage (per task): {1:.3f}GB".format(100*(rloc+1.)/realizations_per_task,peakMemory()))
+				logstderr.info("Progress: {0:.2f}%, peak memory usage (per task): {1:.3f}".format(100*(rloc+1.)/realizations_per_task,peakMemory()))
 	
 	
 	#######################################################################################################################################

### 2016-01-21 code/measure/peaks_direct.py
Log all tasks memory usage

@@ -9,7 +9,7 @@ import gc
 from distutils import config
 
 from lenstools.utils import MPIWhirlPool
-from lenstools.simulations.logs import logdriver,logstderr,peakMemory
+from lenstools.simulations.logs import logdriver,logstderr,peakMemory,peakMemoryAll
 
 from lenstools import ConvergenceMap
 
@@ -198,8 +198,9 @@ def singleRedshift(pool,batch,settings,id,**kwargs):
 	with Database(dbname) as db:
 
 		#Log initial memory load
+		peak_memory_task,peak_memory_all = peakMemory(),peakMemoryAll(pool)
 		if (pool is None) or (pool.is_master()):
-			logstderr.info("Initial memory usage (per task): {0:.3f}".format(peakMemory()))
+			logstderr.info("Initial memory usage: {0:.3f} (task), {1[0]:.3f} (all {1[1]} tasks)".format(peak_memory_task,peak_memory_all))
 
 		#We need one of these for cycles for each map random realization
 		for rloc,r in enumerate(range(first_map_realization,last_map_realization)):
@@ -319,8 +320,10 @@ def singleRedshift(pool,batch,settings,id,**kwargs):
 			now = time.time()
 			logdriver.info("Weak lensing calculations for realization {0} completed in {1:.3f}s".format(r+1,now-last_timestamp))
 
+			#Log progress and peak memory usage to stderr
+			peak_memory_task,peak_memory_all = peakMemory(),peakMemoryAll(pool)
 			if (pool is None) or (pool.is_master()):
-				logstderr.info("Progress: {0:.2f}%, peak memory usage (per task): {1:.3f}".format(100*(rloc+1.)/realizations_per_task,peakMemory()))
+				logstderr.info("Progress: {0:.2f}%, peak memory usage: {1:.3f} (task), {2[0]:.3f} (all {2[1]} tasks)".format(100*(rloc+1.)/realizations_per_task,peak_memory_task,peak_memory_all))
 	
 	
 	#######################################################################################################################################

### 2016-01-22 code/analysis/variance_scaling_peaks_largeNr.py
measure peak constraints with 1 arcmin smoothing scale

@@ -16,7 +16,7 @@ import algorithms
 
 #Number of simulations to test
 nsim = [1]
-nreal = range(100,1000,100) + range(1000,111000,1000)
+nreal = range(500,1000,100) + range(1000,111000,1000)
 resample = 100
 
 def main():
@@ -26,12 +26,12 @@ def main():
 	###########################################
 
 	#Load the emulator
-	emulator = FisherAnalysis.read("../../data/emulators/fisher_peaks.pkl")
+	emulator = FisherAnalysis.read("../../data/emulators/fisher_peaks_s1_nb100.pkl")
 	feature_columns = emulator[emulator.feature_names].columns
 
 	#Large and small scales
 	scales = {
-	"highest_kappa" : filter(lambda s:int(s) in [45,46,47,48],emulator[emulator.feature_names[0]].columns),
+	"highest_kappa_s1" : filter(lambda s:int(s)>=80,emulator[emulator.feature_names[0]].columns),
 	}
 
 	#Load in the feature Ensemble, and bootstrap the covariance using a different number of realizations
@@ -47,7 +47,7 @@ def main():
 			fisher_scale = emulator.features({emulator.feature_names[0]:scales[s]})
 
 			#This is the reference covariance matrix
-			true_covariance_ensemble = Ensemble(np.load("../../Om0.260_Ol0.740_w-1.000_ns0.960_si0.800/512b240/GrandEnsemble/peaks_s0.npy"),columns=emulator[emulator.feature_names[0]].columns)[scales[s]]
+			true_covariance_ensemble = Ensemble(np.load("../../Om0.260_Ol0.740_w-1.000_ns0.960_si0.800/512b240/GrandEnsemble/peaks_s1_nb100.npy"),columns=emulator[emulator.feature_names[0]].columns)[scales[s]]
 			true_covariance_ensemble.add_name(emulator.feature_names[0])
 			true_covariance = true_covariance_ensemble.cov()
 			diagonal_covariance = Ensemble(np.diag(true_covariance.values.diagonal()),index=true_covariance.index,columns=true_covariance.columns)
@@ -55,7 +55,7 @@ def main():
 			for n in nsim:
 		
 				#Load the power spectrum Ensemble from the relevant map set
[…]

### 2016-01-22 Paper/Figures/generate.py
modify figure 5 (again)

@@ -73,6 +73,7 @@ labels = {
 "peaks_intermediate+high" : r"$\kappa_0\in[0.1,0.45],N_b=30$",
 "peaks_all" : r"$\kappa_0\in[-0.06,0.45],N_b=45$",
 "peaks_highest_kappa" : r"$\kappa_0\in[0.44,0.48],N_b=4$",
+"peaks_highest_kappa_s1" : r"$\kappa_0(\theta_G=1^\prime)>0.15,N_b=20$",
 } 
 
 #Plot order
@@ -184,7 +185,7 @@ def ps_pdf(cmd_args,nell=[0,4,9,14],nsim=[1,2,5,50,100],colors=["black","blue","
 	fig.savefig("ps_pdf."+cmd_args.type)
 
 #Scaling of the variance with Nr
-def scaling_nr(cmd_args,db_filename="variance_scaling_nb_expected.sqlite",features=["power_logb_all","power_logb_lowest_ell","peaks_highest_kappa"],colors=["black","red","blue"],nrmax=100000,parameter="w",fontsize=22):
+def scaling_nr(cmd_args,db_filename="variance_scaling_nb_expected.sqlite",features=["power_logb_all","power_logb_lowest_ell","peaks_highest_kappa_s1"],colors=["black","red","blue"],nrmax=100000,parameter="w",fontsize=22):
 
 	#Plot panel
 	fig,ax = plt.subplots()

### 2016-01-23 Paper/paper.tex
Update paper text with new comments for Figure 5

@@
 single, 240Mpc$/h$ sized, $N$--body simulation ($N_s=1$) can be repeatedly recycled to
-produce as many as $N_r={\rm few}\times10^4$ shear maps whose power spectra can be treated as statistically independent.
+produce as many as $N_r={\rm few}\times10^4$ shear maps whose power spectra and high significance peak counts can be treated as statistically independent.
 As a result, a small number of simulations ($N_s=1$ or $2$) is sufficient to forecast parameter confidence intervals at percent accuracy.
@@
 
-\keywords{Weak Gravitational Lensing --- Simulations --- Methods: numerical,statistical}
+\keywords{Weak Gravitational Lensing --- Simulations --- Methods: analytical, numerical, statistical}
 \pacs{98.80.-k, 95.36.+x, 95.30.Sf, 98.62.Sb}
@@
 (at which the simulation box has an angular size of $\theta_{\rm
-  box}=3.5\mathrm{deg}$) and we discretize the mass distribution
+  box}=3.5^\circ$) and we discretize the mass distribution
 between $z_s$ and the observer at $z=0$ with a sequence of 46 two
@@
 $\langle\bbh{d}_{\rm obs}\rangle_O=\bb{d}_0$, so that
-$\langle(\bbh{d}_{\rm obs}-\bb{d}_0)(\bbh{d}_{\rm
-  obs}-\bb{d}_0)^T\rangle_O=\bb{C}$.  When we perform an observation
+$\langle(\bbh{d}_{\rm obs}-\bb{d}_0)(\bbh{d}_{\rm obs}-\bb{d}_0)^T\rangle_O=\bb{C}$.  When we perform an observation
 $\bbh{d}_{\rm obs}$, the parameter estimate $\bbh{p}$ is a random draw
@@
   asymptotic variance $\sigma^2_{w,\infty}$ has been estimated to be the value $\langle\h{\sigma}^2_w\rangle(N_r=10^5)$.
-Different features are considered: power spectra with logarithmically spaced $\ell\in[100,6000]$ (black), $\ell\in[100,250]$ (red) and peak counts of height $\kappa_0\in[0.44,0.48]$ (blue).
+Different features are considered: power spectra with logarithmically spaced $\ell\in[100,6000]$ (black), $\ell\in[100,250]$ (red), peak counts in the unsmoothed maps with height $\kappa_0\in[0.44,0.48]$ (green) and peak counts in the smoothed maps (with a Gaussian kernel of size $\theta_G=1^\prime$) with height $\kappa_0>0.15$ (blue).
 No deviations from the expected $1/N_r$ behavior are observed up to $N_r\approx{\rm few}\times10^4$, except for the large scale power spectrum, in which case the deviations occur much earlier ($N_r\approx 10^3$).}
@@
 with the expected scaling (eq.~\ref{ourscaling}) up to $N_r\sim {\rm few}\times10^4$ when using the $\kappa$ power spectrum in the multipole range $\ell\in[100,6000]$.
+The same behavior is observed when considering the high significance peak counts ($>10\sigma$ for unsmoothed maps and $>5\sigma$ for $1^\prime$ smoothed maps).
 As the figure shows, around these values of $N_r$ the $\langle\hat{\sigma}^2_w\rangle - \sigma^2_{w,\infty}$ curve
@@
 \item We can recycle a single 240Mpc$/h$ $N$--body simulation to produce an
-  ensemble of $O(10^4)$ shear maps whose power spectra are statistically independent in the range $\ell\in[100,6000]$. The mean feature measured
-  from a shear ensemble, though, could be inaccurate if only one $N$--body simulation is used.
+  ensemble of $O(10^4)$ shear maps whose small scale power spectra and high significance peak counts are statistically independent.
+The mean feature measured from a shear ensemble, though, could be inaccurate if only one $N$--body simulation is used.
 \item As few as one or two independent $N$--body simulations are

### 2016-01-23 Paper/Figures/generate.py

@@ -185,7 +185,7 @@ def ps_pdf(cmd_args,nell=[0,4,9,14],nsim=[1,2,5,50,100],colors=["black","blue","
 	fig.savefig("ps_pdf."+cmd_args.type)
 
 #Scaling of the variance with Nr
-def scaling_nr(cmd_args,db_filename="variance_scaling_nb_expected.sqlite",features=["power_logb_all","power_logb_lowest_ell","peaks_highest_kappa_s1"],colors=["black","red","blue"],nrmax=100000,parameter="w",fontsize=22):
+def scaling_nr(cmd_args,db_filename="variance_scaling_nb_expected.sqlite",features=["power_logb_all","power_logb_lowest_ell","peaks_highest_kappa","peaks_highest_kappa_s1"],colors=["black","red","green","blue"],nrmax=100000,parameter="w",fontsize=22):
 
 	#Plot panel
 	fig,ax = plt.subplots()
@@ -223,10 +223,10 @@ def scaling_nr(cmd_args,db_filename="variance_scaling_nb_expected.sqlite",featur
 
 	#Axes limits
 	ax.set_xlim(100,110000)
-	ax.set_ylim(1.0e-7,4.0e2)
+	ax.set_ylim(1.0e-7,1.0e3)
 
 	#Labels
-	ax.legend()
+	ax.legend(loc="lower left")
 	ax.set_xlabel(r"$N_r$",fontsize=fontsize)
 	ax.set_ylabel(r"$\langle\hat{\sigma}^2_w\rangle - \sigma^2_{w,\infty}$",fontsize=fontsize)
 

### 2016-01-23 Paper/paper.tex
incorporated Zoltan edits (2)

@@
 larger than $N_b$. We study the large $N_r$ limit, and find that a
-single, 240Mpc$/h$ sized, $N$--body simulation ($N_s=1$) can be repeatedly recycled to
-produce as many as $N_r={\rm few}\times10^4$ shear maps whose power spectra and high significance peak counts can be treated as statistically independent.
+single, 240Mpc$/h$ sized $512^3$-particle $N$--body simulation ($N_s=1$) can be repeatedly recycled to
+produce as many as $N_r={\rm few}\times10^4$ shear maps whose power spectra and high-significance peak counts can be treated as statistically independent.
 As a result, a small number of simulations ($N_s=1$ or $2$) is sufficient to forecast parameter confidence intervals at percent accuracy.
@@
 numerical simulations of shear fields are becoming important for
-several reasons, including the study of baryonic effects
+several reasons, including assessing baryonic effects
 \citep{BaryonXiuyuan,BaryonSemboloni,BaryonsWhite,BaryonsKnox,BaryonsZentner1,BaryonsZentner2},
-the computation of non--Gaussian statistics
+the utility of non--Gaussian statistics
 \citep{PeaksJan,MinkJan,MinkPetri,NG-Marian,NG-Jain1,NG-Jain2,NG-Jain3,NG-Refregier,NG-Dietrich}
-and the assessment of various systematics
+and various systematic effects
 \citep{MinkShirasaki,Sys-Bard,Sys-Chang,Sys-Huterer}.
@@
 studied extensively, the impact of fluctuations in the variance has
-received comparatively less attention.  These fluctuations have,
-however, been shown to have non-negligible effects on estimates of
-features covariance matrices and hence on parameter constraints. In
+received less attention.  These fluctuations have been shown to have non-negligible effects on estimates of
+features covariances and hence on parameter constraints. In
 particular, in the limit of Gaussian fluctuations, the parameter
@@
 Different features are considered: power spectra with logarithmically spaced $\ell\in[100,6000]$ (black), $\ell\in[100,250]$ (red), peak counts in the unsmoothed maps with height $\kappa_0\in[0.44,0.48]$ (green) and peak counts in the smoothed maps (with a Gaussian kernel of size $\theta_G=1^\prime$) with height $\kappa_0>0.15$ (blue).
-No deviations from the expected $1/N_r$ behavior are observed up to $N_r\approx{\rm few}\times10^4$, except for the large scale power spectrum, in which case the deviations occur much earlier ($N_r\approx 10^3$).}
+No deviations from the expected $1/N_r$ behavior are observed up to $N_r\approx{\rm few}\times10^4$, except for the large-scale power spectrum, in which case the deviations occur much earlier ($N_r\approx 10^3$).}
 \label{wvar_nr}
@@
 with the expected scaling (eq.~\ref{ourscaling}) up to $N_r\sim {\rm few}\times10^4$ when using the $\kappa$ power spectrum in the multipole range $\ell\in[100,6000]$.
-The same behavior is observed when considering the high significance peak counts ($>10\sigma$ for unsmoothed maps and $>5\sigma$ for $1^\prime$ smoothed maps).
+The same behavior is observed when considering the high-significance peak counts ($>10\sigma$ for unsmoothed maps and $>5\sigma$ for $1^\prime$ smoothed maps).
 As the figure shows, around these values of $N_r$ the $\langle\hat{\sigma}^2_w\rangle - \sigma^2_{w,\infty}$ curve
@@
 plateau value (or equivalently in the estimated value of
-$\sigma^2_{w,\infty}$). We therefore conclude that a single $N$--body
+$\sigma^2_{w,\infty}$).
+
+We conclude that a single $N$--body
 simulation is sufficient to construct an ensemble of up to a
@@
 independent.
-We should emphasize that the validity of this statement is conditional to the size of the simulation box (which in our case has been chosen to be 240Mpc$/h$) and the range of multipoles $\ell$ used to constrain the parameters.
-Figure \ref{wvar_nr} shows indeed that, when we try infer $w$ only from large scale modes, $\ell\lesssim250$, the plateau is reached at least an order of magnitude earlier in the number of realizations.
-In other words, the number of independent power spectra gets lower and lower as we increase the spatial scales of interest.
+We emphasize that the precise value of this $N_r$ will depend on the size of the simulation box (which, in our case, is (240Mpc$/h$)$^3$, with $512^3$ particles) and also on the range of multipoles $\ell$ used to constrain the parameters.
+Figure \ref{wvar_nr} shows that when we infer $w$ only from large--scale modes, $\ell\lesssim250$, the plateau is reached at least an order of magnitude earlier in the number of realizations.
+In other words, the number of independent power spectra we can generate decreases as we increase the spatial scales of interest.
 This is due to the fact that, because of the finite box size, the number of independent lens plane shifts (as described in \S~\ref{shearsim}) decreases as the mode size approaches the size of the box.
+Similarly, one may expect that the independence in the statistics of high-amplitude peaks, which are predominantly produced by single massive halos, may be compromised by these halos being present repeatedly, in many of the pseudo-independent realizations.
+However, Figure \ref{wvar_nr} shows that this is not the case: the peak count statistics are shown at $\kappa$ thresholds corresponding to massive ($\approx 10^{15}~{\rm M_\odot}$) halos, yet there is no evidence that the independence of the maps breaks down until $N_r=$few$\times 10^4$.
+Apparently, randomly projected structures, which vary from realization-to-realization, contribute significantly to the statistics of these high peaks.
 
@@
 \item We can recycle a single 240Mpc$/h$ $N$--body simulation to produce an
-  ensemble of $O(10^4)$ shear maps whose small scale power spectra and high significance peak counts are statistically independent.
+  ensemble of $O(10^4)$ shear maps whose small-scale power spectra and high-signficiance peak counts are statistically independent.
 The mean feature measured from a shear ensemble, though, could be inaccurate if only one $N$--body simulation is used.

### 2016-03-02 Paper/paper.tex
incorporated comments from referee

@@
 %
-
+\textbf{\textcolor{blue}{We chose $\bb{p}_0$ to be the triplet $(\Omega_m,w,\sigma_8)=(0.26,-1,0.8)$.}}
 To measure the derivatives of the features $\bb{d}'_0$ with respect to
@@
 expanding Eq.~(\ref{estimatorcovariance}) to quartic order in the
-statistical fluctuations of $\bbh{\Psi}$. Denoting the noiseless
-parameter covariance, i.e. the usual Fisher matrix, as
+statistical fluctuations of $\bbh{\Psi}$. Denoting the \textbf{\textcolor{blue}{true}}
+parameter covariance, i.e. the usual \textbf{\textcolor{blue}{inverse}} Fisher matrix, as
 $\Sigma_\bb{p}=\bb{F}^{-1}$, we find the result~\footnote{The details
@@
 %
+\textbf{\textcolor{blue}{Although we truncated the expansion to second order in $1/N_r$, an exact expression for $\langle\h{\Sigma}_\bb{p}\rangle$ has been proposed by \citep{Taylor14}}}
+\begin{equation}
+\label{empiricalexact}
+\textcolor{blue}{\langle\h{\Sigma}_\bb{p}\rangle_{\rm empirical} = \Sigma_\bb{p}\left(\frac{N_r-2}{N_r-N_b+N_p-2}\right)}
+\end{equation}
+%
+\textbf{\textcolor{blue}{This empirical expression reduces to equation (\ref{quarticdegradation}) when expanded at order $O(1/N_r^2)$ but, to our knowledge, no first principles proof of its correctness exists.}}
 Next, we restrict ourselves to the large $N_r$ limit, and we further
@@
   $1/N_r$. The different symbols and colors correspond to the features
-  listed in Table~\ref{featuretable}.  The dashed and solid curves
+  listed in Table~\ref{featuretable}.  The dashed and this solid curves
   show the analytic predictions from equation
   (\ref{quarticdegradation}) at orders $O(1/N_r)$ and $O(1/N_r^2)$,
-  respectively. The asymptotic variance $\sigma^2_{w,\infty}$ has been
+  respectively. \textbf{\textcolor{blue}{The thick solid curves show the empirical predictions from equation (\ref{empiricalexact})}}. 
+  The asymptotic variance $\sigma^2_{w,\infty}$ has been
   computed from a linear regression of $\langle\h{\sigma}^2_w\rangle$
@@
   estimate the covariance (eq.~\ref{covest}). We show the dependence
-  of $\sigma_{w,\infty}^2(N_s)$ in units of the mean over the 16
-  ensembles with different $N_s$, for the power spectrum
+  of $\sigma_{w,\infty}^2(N_s)$ in units of the mean over the \textbf{\textcolor{blue}{union of}} 16
+  ensembles with different $N_s$ \textbf{\textcolor{blue}{and $N_r=1024$}}, for the power spectrum
   logarithmically binned (black, $N_b=15,\ell\in[100,6000]$), the
@@
 be always sufficient.
+\textbf{\textcolor{blue}{As pointed out by \citep{NbodySample}, the box size used for the $N$--body simulations can also play an important role in the accuracy of the power spectrum ensemble means.}}
 

### 2016-03-02 Paper/Figures/generate.py

@@ -346,6 +346,7 @@ def curving_nb(cmd_args,db_filename="variance_scaling_nb_expected.sqlite",parame
 			x = 1./np.linspace(1000,65,100)
 			ax.plot(x,1+x*(Nb-Np),linestyle="--",color=colors[f])
 			ax.plot(x,1+(Nb-Np)*x+(Nb-Np)*(Nb-Np+2)*(x**2),linestyle="-",color=colors[f])
+			ax.plot(x,(1-2*x)/(1-(Nb-Np+2)*x),linestyle="-",linewidth=3,color=colors[f])
 
 
 	#Axis bounds

### 2016-03-08 Paper/paper.tex

--- 2016-01-23 Paper/paper.tex
@@
 %
-
+We chose $\bb{p}_0$ to be the triplet $(\Omega_m,w,\sigma_8)=(0.26,-1,0.8)$.
 To measure the derivatives of the features $\bb{d}'_0$ with respect to
@@
 expanding Eq.~(\ref{estimatorcovariance}) to quartic order in the
-statistical fluctuations of $\bbh{\Psi}$. Denoting the noiseless
-parameter covariance, i.e. the usual Fisher matrix, as
+statistical fluctuations of $\bbh{\Psi}$. Denoting the true
+parameter covariance, i.e. the usual inverse Fisher matrix, as
 $\Sigma_\bb{p}=\bb{F}^{-1}$, we find the result~\footnote{The details
@@
 %
+Although we truncated the expansion to second order in $1/N_r$, an exact expression for $\langle\h{\Sigma}_\bb{p}\rangle$ has been proposed by \citep{Taylor14}
+\begin{equation}
+\label{empiricalexact}
+\langle\h{\Sigma}_\bb{p}\rangle_{\rm empirical} = \Sigma_\bb{p}\left(\frac{N_r-2}{N_r-N_b+N_p-2}\right)
+\end{equation}
+%
+This empirical expression reduces to equation (\ref{quarticdegradation}) when expanded at order $O(1/N_r^2)$ but, to our knowledge, no first principles proof of its correctness exists. 
 Next, we restrict ourselves to the large $N_r$ limit, and we further
@@
   $1/N_r$. The different symbols and colors correspond to the features
-  listed in Table~\ref{featuretable}.  The dashed and solid curves
+  listed in Table~\ref{featuretable}.  The dashed and this solid curves
   show the analytic predictions from equation
   (\ref{quarticdegradation}) at orders $O(1/N_r)$ and $O(1/N_r^2)$,
-  respectively. The asymptotic variance $\sigma^2_{w,\infty}$ has been
+  respectively. The thick solid curves show the empirical predictions from equation (\ref{empiricalexact}). 
+  The asymptotic variance $\sigma^2_{w,\infty}$ has been
   computed from a linear regression of $\langle\h{\sigma}^2_w\rangle$
@@
   estimate the covariance (eq.~\ref{covest}). We show the dependence
-  of $\sigma_{w,\infty}^2(N_s)$ in units of the mean over the 16
-  ensembles with different $N_s$, for the power spectrum
+  of $\sigma_{w,\infty}^2(N_s)$ in units of the mean over the union of 16
+  ensembles with different $N_s$ and $N_r=1024$, for the power spectrum
   logarithmically binned (black, $N_b=15,\ell\in[100,6000]$), the
@@
 required accuracy to 50\% of the statistical error, we find $N_s=2$ to
-be always sufficient.
+be always sufficient. As pointed out by \citep{NbodySample}, the box size used for the $N$--body simulations can also play an important role in the accuracy of the power spectrum ensemble means.
 
